### 2022-05-17 docs/manuscript/manuscript.tex
Upload manuscript.tex for Overleaf integration

\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Reproducibility Survey Manuscript}
\author{peter.kedron }
\date{April 2022}

\begin{document}

\maketitle

\section{Introduction}
Since the 1600s, replication has been a defining characteristic of the scientific method and an essential tool of researchers working to remove errors from our understanding of phenomena. 
\citet{nosek2020} broadly define a replication as any study that has at least one outcome that would be considered to be diagnostic evidence of a claim from prior research.
More frequently, replication is defined along two axes that help to distinguish the type of diagnostic evidence a study will provide and the function or purpose it is intended to serve. 
First, it is common to distinguish whether a replication study used the same data as the original study, or if new data were collected and analyzed. 
Second, it is helpful to identify whether a replication is focused on the question of whether the specific results of the original study can be reobserved, or whether the conclusions drawn from the original study are robust to changes in procedure or context.

When a researcher asks whether the same data and procedures can be used to generate the same results as an original study the central purpose of their study is verification.
If the researcher uses the original data, but introduces procedural differences they think may effect the original result they pursue a reanalysis designed to determine whether the original reasoning was somehow erroneous. 
Both of these approaches to replication assess the internal validity of research and are more commonly referred to as reproductions.
If the researcher tries to follow the procedures of an original study, but collects new data, the purpose shifts to evaluating the external validity of the original result by retesting it under new conditions.
This approach is commonly referred to as replication.

While a replication or reproduction can never provide conclusive evidence for or against a finding, either type of study can be informative. 
If a well-executed, high-quality replication or reproduction recreates the result of an original study, we are apt to increase our confidence in the original findings. 
If a finding cannot be recreated, it reduces our confidence in the original result and suggests that our current understanding of the system being studied or our methods of testing that system are insufficient.

\end{document}

### 2022-06-27 docs/manuscript/manuscript.tex
Add prior survey research section
Update to Annals template

@@
-\documentclass{article}
-\usepackage[utf8]{inputenc}
+\documentclass[]{interact}
+\usepackage{epstopdf}% To incorporate .eps illustrations using PDFLaTeX, etc.
+\usepackage{subfigure}% Support for small, `sub' figures and tables
+%\usepackage[nolists,tablesfirst]{endfloat}% To `separate' figures and tables from text if required
 
-\title{Reproducibility Survey Manuscript}
-\author{peter.kedron }
-\date{April 2022}
+\usepackage{natbib}% Citation support using natbib.sty
+\bibpunct[, ]{(}{)}{;}{a}{}{,}% Citation support using natbib.sty
+\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty
+
+\theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}[theorem]{Proposition}
+
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{example}[theorem]{Example}
+
+\theoremstyle{remark}
+\newtheorem{remark}{Remark}
+\newtheorem{notation}{Notation}
 
 \begin{document}
+
+\articletype{DRAFT MANUSCRIPT}
+
+\title{Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey}
+
+\author{
+\name{Peter Kedron\textsuperscript{a,b}\thanks{CONTACT Peter Kedron. Email: Peter.Kedron@asu.edu}, Joseph Holler\textsuperscript{c}, and Sarah Bardin\textsuperscript{a,b}}
+\affil{\textsuperscript{a}School of Geographical Sciences and Urban Planning, Arizona State University, Tempe, Arizona, USA; \textsuperscript{b}Spatial Analysis Research Center (SPARC), Arizona State University, Tempe, Arizona, USA; \textsuperscript{c}Department of Geography, Middlebury College, Middlebury, Vermont, USA}
+}
+
+\maketitle
+
+\begin{abstract}
+This template is for authors who are preparing a manuscript for a Taylor \& Francis journal using the \LaTeX\ document preparation system and the \texttt{interact} class file, which is available via selected journals' home pages on the Taylor \& Francis website.
+\end{abstract}
+
+\begin{keywords}
+Reproducible Research, Epistemology, Geographic Research Methods
+\end{keywords}
 
@@
 
+\section{Prior Survey Research on Reproducible Research}
+
 \end{document}

### 2022-07-08 docs/manuscript/manuscript.tex
Drafted data and methods section

@@
 
-\usepackage{natbib}% Citation support using natbib.sty
-\bibpunct[, ]{(}{)}{;}{a}{}{,}% Citation support using natbib.sty
+\usepackage{natbib}
+\bibliographystyle{chicago}
+\setcitestyle{authoryear,open={(},close={)}}
 \renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty
+
+\usepackage{hyperref}
+\hypersetup{
+    colorlinks=true,
+    linkcolor=blue,
+    filecolor=magenta,
+    urlcolor=blue,
+    citecolor=blue,
+}
+
+\usepackage{titlesec}
+\titleformat*{\section}{\Large\bfseries}
+\titleformat*{\subsection}{\large\bfseries}
 
@@
 
-\section{Introduction}
+\section*{Introduction}
 Since the 1600s, replication has been a defining characteristic of the scientific method and an essential tool of researchers working to remove errors from our understanding of phenomena. 
@@
 
-\section{Prior Survey Research on Reproducible Research}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Prior Survey Research on Reproducible Research}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Data and Methods}
+Complete documentation of the procedures and materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
+Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
+We amended that plan at the close of data collection to reflect a change in stopping rule we used to end the survey.
+
+The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.
+All approved documentation, study protocols, and consent materials are available through the above repository.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Survey Design}
+Our target population of interest is researchers who have recently published in the field of geography. 
+We followed a 4-step procedure to create a sampling frame for our survey that captures this diverse population of researchers and the approaches they use when studying geography.
+
+First, beginning at the publication level, we identified journals indexed as either geography or physical geography by the \href{https://access.clarivate.com/}{Web of Science's Journal Citation Reports} that also had a 5-year impact factor greater than 1.5.
+From those journals, we created a database of all articles published between 2017 and 2021.
+
+Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication.
+Because our intention is to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = "Article"} and removed all other publication types (e.g., editorials, book reviews) from our article database.
+We also removed articles with missing authorship information.
+
+Third, we next moved to the author level to create a condensed list of corresponding authors. 
+We chose to focus on corresponding authors for two reasons. 
+(1) Corresponding authorship is one indicator of the level of involvement an individual had in a given work. 
+While imperfect, it was the best available indicator in the Scopus database as across journals there is no commonly adopted policy for declarations of author work (e.g., CRediT Statements).
+(2) Scopus maintains email contact information for all corresponding authors, which gave us a means of contacting researchers in our sampling frame.
+Scopus also maintains a unique identifier for each author (author-id) across time, which allowed us to identify authors across publications.
+
+Fourth, we associated each corresponding author with their contact email address and deduplicated to create a single record for each corresponding author. 
+To maximize our chance or response, we retained the latest available contact information for each author by sorting the initial list by author-id and publication year (descending) and keeping the latest available entry for each author-id.
+For authors who had two or more distinct emails in the latest year of publication, we deduplicated by giving a ranked preference to .edu, .gov, and then .org extensions.
+
+Applying these criteria yielded a sampling frame of 29,828 authors. 
+On average, these authors published 2.7 articles in top geography journals between 2017 and 2021. 
+Roughly one-third (33 percent) were most recently a corresponding author for an article published in a general geography journal. 
+A similar proportion (32 percent) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions in the social sciences and cultural geography (20 percent and 16 percent, respectively).
+
+The survey instrument used in this study is available through the Survey of Reproducibility in Geographic Research Repository.
+The survey consists of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reprodicibility.
+Survey questions were developed following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature.
+Because this survey had not been previously fielded, we pilot tested the instrument with a subset of \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background.
+After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Data Collection}
+We used a digital form of the Tailored Design Method \citep{dillman2014internet} to survey geographic researchers between May 17 and June 10, 2022.
+A simple random sample of 2,000 researchers was drawn without replacement from our sampling frame, and those researchers were invited via email to participate in the online survey. 
+Researchers received their initial invitation on May 17, 2022. 
+Two reminder emails were sent to researchers that had not yet completed the survey on May 26 and May 31, 2022.
+
+Participation in the survey was entirely voluntary. 
+Each researcher that opted to participate in the survey was provided with IRB approved consent documentation and linked to the internet survey instrument. 
+Participants were also given the option to enter a random prize draw. 
+The total possible compensation a participant was eligible to receive was 90 US dollars, awarded as a prepaid credit card.
+Three prize winners were selected at random from those electing to enter the prize draw at the end of the data collection period.
+
+The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
+Each question on the survey was presented as a unique page. 
+Adaptive questioning, conditionally displaying items based on responses to other items, was used to reduce the number of complexity of questions.
+Participating researchers had the option to exit and re-enter the survey and were also able to review and/or change their answers using a back button as they progressed through the survey.
+
+At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
+Responses were downloaded from Qualtrics, anonymized, and stored in a password-protected databases.
+We used a unique key to link this data with participant information (e.g., citation history) stored in separate database for our statistical analyses. 
+To preserve participant privacy that connection was severed at the end of our analysis and we have only shared the anonymized response file through our public repository. 
+As a result some of the result presented below cannot be directly replicated. 
+We have indicated throughout our results section which analysis can and cannot be replicated using the data files and code share through our public repository.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Statistical Analyses}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Results}
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Response Rates}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgement(s)}
+We thank Tyler Hoffman for providing technical assistance in the development and execution of a set of trial queries using the Scopus API.
+
+\section*{Funding}
+This material is based on work supported by the National Science Foundation under Grant No. \textbf{BCS-2049837}.
+
+\section*{Notes on contributor(s)}
+\textbf{Kedron:} Conceptualization, Methodology, Writing - Original Draft, Writing - Review and Editing, Supervision, Project Administration, Funding Acquisition.
+\textbf{Holler:} Conceptualization, Methodology, Data Curation, Writing - Review and Editing, Funding Acquisition.
+\textbf{Bardin:} Conceptualization, Methodology, Writing - Original Draft, Writing - Review and Editing, Data Curation, Software.
+
+\newpage
+\bibliography{references}
+
+\newpage
+\noindent PETER KEDRON is an Associate Professor in the School of Geographical Science and Urban Planning and core faculty member in the Spatial Analysis Research Center (SPARC) at Arizona State University, Tempe, AZ, 85283, US.
+Email: Peter.Kedron@asu.edu.
+His research interests include spatial analysis, geographic information science, economic geography, and the accumulation of knowledge about geographic phenomena.
+\\
+
+\noindent JOSEPH HOLLER is an Assistant Professor of Geography at Middlebury College, Middlebury, VT, 05753, US. Email: \\
+
+\noindent SARAH BARDIN is a PhD candidate ...
 

### 2022-07-08 docs/manuscript/manuscript.tex
Add outcome rate info

@@
 
+\usepackage{endnotes}
+\let\footnote=\endnote
+\usepackage{etoolbox}
+\patchcmd{\enoteformat}{1.8em}{0pt}{}{}
+
 \theoremstyle{plain}% Theorem-like structures provided by amsthm.sty
@@
 \newtheorem{notation}{Notation}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \begin{abstract}
-This template is for authors who are preparing a manuscript for a Taylor \& Francis journal using the \LaTeX\ document preparation system and the \texttt{interact} class file, which is available via selected journals' home pages on the Taylor \& Francis website.
+While the number of reproduction and replication studies undertaken in the social and behavioural sciences continues to rise, such studies have not yet become commonplace in geography. 
+Existing attempts to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 
+Despite this suggestive evidence, we have not yet systematically assessed geographers' perceptions of reproducibility, the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have kept geographers from conducting more reproduction studies.
+This study addresses each of these questions by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
+We find ...
+CONClUSION...
+
 \end{abstract}
@@
 
-\maketitle
-
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Introduction}
@@
 
+\begin{itemize}
+    \item Attempting reproductions
+    \item Attempting reproductions in geography
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Prior Survey Research on Reproducible Research}
+\begin{itemize}
+    \item Reproducibility surveys
+    \item the problems with these surveys
+    \item reproducibilty surveys in geography
+    \item how they fall prey to the same problems
+\end{itemize}
 
@@
 Responses were downloaded from Qualtrics, anonymized, and stored in a password-protected databases.
-We used a unique key to link this data with participant information (e.g., citation history) stored in separate database for our statistical analyses. 
-To preserve participant privacy that connection was severed at the end of our analysis and we have only shared the anonymized response file through our public repository. 
+We used a unique key to link this data with participant information (e.g., citation history) stored in a separate database during our statistical analyses. 
+To preserve participant privacy that connection was severed at the end of our analysis.
+We have only shared the anonymized response file through our public repository. 
 As a result some of the result presented below cannot be directly replicated. 
@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Response Rates}
+A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis.
+The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent.
+The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards.
+The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Discussion}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Conclusion}
+
+\theendnotes
 

### 2022-08-11 docs/manuscript/manuscript.tex

@@
 
-\begin{itemize}
-    \item Attempting reproductions
-    \item Attempting reproductions in geography
-\end{itemize}
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Prior Survey Research on Reproducible Research}
-\begin{itemize}
-    \item Reproducibility surveys
-    \item the problems with these surveys
-    \item reproducibilty surveys in geography
-    \item how they fall prey to the same problems
-\end{itemize}
+There are several ways to assess the reproducibility of research.
+The most direct approach is to simply conduct a study that follows the methods of an existing study and then compare the results of the new study to the results of the old study. 
+The direct approach can be implemented in two ways: as a one-to-one comparison, in which as single reproduction is used to assess the results and inferences of one prior study; or as a many-to-one comparison, in which teams of researchers attempt multiple reproductions and make a set of comparisons and collective assessment of one prior study \citep{NASEM2019}.
+Published reproductions of both forms are becoming increasingly common in many disciplines with researchers generally only able to partially reproduce study results, often observing small effect sizes \citep[e.g.,][]{begley2012raise, camerer2016evaluating, camerer2018evaluating, wagenmakers2016registered}.
+
+Such published reproductions have not yet become common in geography. 
+The small number of studies that have attempted assess the reproducibility of geographic research by reproducing existing work suggest that many studies cannot be fully reproduced \citep{Kedron2021ssrn, nust2018, ostermann2021}, or are simply missing components needed to attempt a reproduction \citep{Kedron_VijayanRP, konkol2019, ostermann2021}.
+For example, as part of an ongoing research initiative of the Association of Geographic Information Laboratories in Europe, a group of researchers annually attempts to reproduce the computational results of submissions to that association's annual meeting \citep{Nust_AGILE_2020, Nust2021AGILE, Nust_AGILE_2022}.
+In published reports the researchers document whether the study could be reproduced and record factors that hindered reproduction such as the accessibility of data, code, and computational environment.
+\citet{konkol2019} similarly attempted computational reproduction of 41 open-access research papers that used spatial methods.
+Focusing their analysis on the execution of code and the similarity of figures, the authors found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures they reproduce deviated from the original result in a significant way.
+
+To date, the researchers attempting these reproductions have also emphasized the computational reproducibility of geographic research ahead of other dimensions.
+
+While these and similar efforts have produced useful guidelines \citep{hofer2019reproducible, wilson2021} and moved forward the development of the computational and institutional infrastructure \citep{nust2019, nust2021} needed to foster reproducibility in the field, they have not assessed the use of reproducible research practices across the disciplines diverse research traditions, or identified what has barred geographers from conducting more reproduction studies.
+
+The root of the problem is that the direct approach to assessing reproducibility presents a trade off. 
+The careful reproduction of a study can provide rich evidence about that particular study, but offers at best limited evidence about the validity of other studies or the prevalence of the research practices observed.
+For example, if a reproduction identified a flaw in the design of a study that impacted the results of that study it would be reasonable to be concerned that observing the same flaw in other studies could impact the results of those studies.
+However, until other studies are gathered and checked we would know how common the flaw is, or whether or not it impacts other studies in a similar way.
+
+\subsection{Indirect}
+Another approach to understanding the reproducibility of research is to survey active researchers about their perceptions of reproducibility and their own research practices.
+Researcher surveys provide indirect measurements of reproducibility that offer
+
+\subsubsection{Geog Indirect}
+For example, \citet{ostermann2017} use a literature review of volunteered geographic information research publications to assess computational reproducibility based on availability of original data, metadata, source code, or pseudocode.
+
+\subsubsection{common problems of surveys}
+While these surveys are suggestive of reproducibility concerns across the sciences, they share a set of common methodological problems. 
+First, many prior surveys have used non-systematic sampling methods to draw data from non-representative, self-selected populations (e.g., professional association memberships), and/or use non-probability sampling schemes, which collectively limits our ability to draw generalizable conclusion or make inferences about specific sub-fields \citep{NASEM2019}.
+Prior surveys also commonly failed to systematically report survey details (e.g., response rate) needed to assess and address potential bias.
 
@@
 Applying these criteria yielded a sampling frame of 29,828 authors. 
-On average, these authors published 2.7 articles in top geography journals between 2017 and 2021. 
+On average, these authors published 2.7 articles in geography journals meeting our criteria between 2017 and 2021. 
 Roughly one-third (33 percent) were most recently a corresponding author for an article published in a general geography journal. 
@@
 \section*{Conclusion}
+A standing question is how should geographic research approaches be designed to efficiently generate reliable knowledge.
 

### 2022-09-21 procedure/code/202_analysis.R
code data factors
created ordered factors for relevant questions and saved RDS file with new data structure

@@ -1,6 +1,7 @@
 library(here)
 library(tidyverse)
 
+
 #--------------------------------#
 #-                              -#
 #- PERFORM DESCRIPTIVE ANALYSIS -#
@@ -94,14 +95,68 @@ survey_resp %>% select(Q3, Q4, Q5, Q6) %>%
   arrange(Q5, Q4) %>%
   write.csv(here("results", "tables", "definitions.csv"))
 
-# convert extent questions into factors
-extent <- c("To a great extent", "Somewhat", "Very little", "Not at all", "")
-extentQs <- c("Q5", "Q7a","Q7b", "Q7c", "Q7d", "Q7e")
-survey_resp[extentQs] <- lapply(survey_resp[extentQs], factor, levels=extent, ordered = TRUE)
+##### FACTOR MANAGEMENT #####
+# if anyone can compress all of this into a function that uses a table of 
+# questions & ordered responses, by all means...
 
-# convert agree questions into factors
-agree <- c("Strongly disagree", "Disagree", "Agree", "Strongly agree", "")
-agreeQs <- c()
+# Simplify sub-field labels
+values <- c("Human geography",
+            "Physical geography, earth and environmental sciences",
+            "Nature and society",
+            "Geographic methods, GIS, spatial statistics")
+survey_resp$Q3 <- factor(survey_resp$Q3, levels=values)
+values <- c("Human", "Physical", "Nature/Society", "Methods")
+levels(survey_resp$Q3) <- values
 
+# convert extent questions into ordered factors
+values <- c("To a great extent", "Somewhat", "Very little", "Not at all", "")
+questions <- c("Q5", "Q7a","Q7b", "Q7c", "Q7d", "Q7e")
+survey_resp[questions] <- lapply(survey_resp[questions], factor, levels=values, ordered = TRUE)
+
+# convert frequency questions into ordered factors
+values <- c("Always", "Most of the time", "Some of the time", "Rarely", "Never", "")
+questions <- c("Q7a_1", "Q7a_3", "Q7b_1", "Q7c_1", "Q7c_2", "Q7c_3", "Q7d_1", "Q7d_2", "Q7e_1")
+survey_resp[questions] <- lapply(survey_resp[questions], factor, levels=values, ordered = TRUE)
+
+# convert agree questions into ordered factors
[…]

### 2022-09-21 procedure/code/202_analysis.R
updated analysis code
analyzed responses about familiarity with practices and about beliefs

@@ -85,9 +85,7 @@ for (i in numeric_vars){
   write.csv(xtab, here("results","tables","Age",paste0("Age_Xtab_",i, ".csv", sep = "")))
 }
 
-ftable(data = survey_resp, Q3 ~ Q5)
 
-ftable(data = survey_resp, Q4 ~ Q5)
 
 # how did folks define "reproducibility" ?
 survey_resp %>% select(Q3, Q4, Q5, Q6) %>%
@@ -109,54 +107,217 @@ values <- c("Human", "Physical", "Nature/Society", "Methods")
 levels(survey_resp$Q3) <- values
 
 # convert extent questions into ordered factors
-values <- c("To a great extent", "Somewhat", "Very little", "Not at all", "")
+values <- c("Not at all", "Very little", "Somewhat", "To a great extent")
 questions <- c("Q5", "Q7a","Q7b", "Q7c", "Q7d", "Q7e")
-survey_resp[questions] <- lapply(survey_resp[questions], factor, levels=values, ordered = TRUE)
+survey_resp[questions] <- lapply(survey_resp[questions], 
+                                 factor, 
+                                 levels=values,
+                                 ordered = TRUE,
+                                 exclude="")
 
 # convert frequency questions into ordered factors
-values <- c("Always", "Most of the time", "Some of the time", "Rarely", "Never", "")
+values <- c("Never", "Rarely", "Some of the time", "Most of the time", "Always")
 questions <- c("Q7a_1", "Q7a_3", "Q7b_1", "Q7c_1", "Q7c_2", "Q7c_3", "Q7d_1", "Q7d_2", "Q7e_1")
-survey_resp[questions] <- lapply(survey_resp[questions], factor, levels=values, ordered = TRUE)
+survey_resp[questions] <- lapply(survey_resp[questions], 
+                                 factor, 
+                                 levels=values,
+                                 ordered = TRUE,
+                                 exclude="")
 
 # convert agree questions into ordered factors
-values <- c("Strongly disagree", "Disagree", "Agree", "Strongly agree", "Don't know", "")
+values <- c("Strongly disagree", "Disagree", "Agree", "Strongly agree")
 questions <- c("Q8_1", "Q8_2", "Q8_3", "Q8_4","Q8_5", "Q8_6")
-survey_resp[questions] <- lapply(survey_resp[questions], factor, levels=values, ordered = TRUE)
+survey_resp[questions] <- lapply(survey_resp[questions], 
+                                 factor, 
[…]

### 2022-09-23 docs/manuscript/manuscript.tex
Updates from Overleaf

--- 2022-07-08 docs/manuscript/manuscript.tex
@@
 
-\begin{itemize}
-    \item Attempting reproductions
-    \item Attempting reproductions in geography
-\end{itemize}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Assessing the Reproducibility of Research}
+The reproducibility of research can be assessed directly or indirectly \citep{NASEM2019}.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Prior Survey Research on Reproducible Research}
-\begin{itemize}
-    \item Reproducibility surveys
-    \item the problems with these surveys
-    \item reproducibilty surveys in geography
-    \item how they fall prey to the same problems
-\end{itemize}
+In a direct assessment of reproducibility 
+Indirect reproducibility assessments
+
+There are several ways to assess the reproducibility of research.
+The most direct approach is to simply conduct a study that follows the methods of an existing study and then compare the results of the new study to the results of the old study.
+
+\subsection*{Direct Reproducibility Assessments}
+Direct reproducibility assessments can be implemented in two ways: as a one-to-one comparison, in which a single reproduction is used to assess the results and inferences of one prior study; or as a many-to-one comparison, in which teams of researchers attempt multiple parallel reproductions and make a set of comparisons and a collective assessment of one prior study.
+Published reproductions of both forms are becoming increasingly common in many disciplines \citep[e.g.,][]{begley2012raise, camerer2016evaluating, camerer2018evaluating, wagenmakers2016registered}. 
+However, the researchers conducting those studies have generally only able to partially reproduce study results, often observing small effect sizes.
+
+Such published reproductions have not yet become common in geography. 
+The small number of studies that have attempted to assess the reproducibility of geographic research by recreating existing work suggest that many studies cannot be fully reproduced \citep{Kedron2021ssrn, nust2018, ostermann2021}, or are simply missing components needed to attempt a reproduction \citep{Kedron_VijayanRP, konkol2019, ostermann2021}.
+For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort.
+A related effort to reproduce 31 papers published in the conference series of the Association of Geographic Information Laboratories in Europe \citep{Nust_AGILE_2020, Nust2021AGILE, Nust_AGILE_2022} similarly identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results.
+\citet{konkol2019}'s attempt to reproduce of 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves).
+
+Moving past the question of whether the computational results of a study can be recreated using the same data and code, a handful of geographic researchers are using the reproduction process as a way of examining not only the execution of a prior study, but its conceptualization and inferences \citep{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP}.
+While this form of the direct approach to reproduction opens a new door to the critical evaluation of geographic research, it primarily provides evidence about a particular research study and the phenomenon that study investigates.
+Similarly, while computationally focused reproductions have produced useful guidelines \citep{hofer2019reproducible, wilson2021} and moved forward the development of the computational and institutional infrastructure \citep{Kedron_Holler_Bardin_Hilgendorf_2022, nust2019, nust2021,}\textbf{ADD SHAOWEN} needed to foster reproducibility in the field, they have not yet assessed the use of reproducible research practices across the disciplines diverse research traditions, or identified the factors that have barred geographers from adopting practices that foster reproducibility or from conducting more reproduction studies.
+
+The root of the problem is that the direct approach to assessing reproducibility presents a trade off. 
+The careful reproduction of a study can provide rich evidence about that particular study, but offers at best suggestive evidence about the validity of other studies or the prevalence of the research practices observed.
+For example, if a reproduction identified a flaw in the design of a study that impacted the results of that study it would be reasonable to be concerned that observing the same flaw in other studies could impact the results of those studies.
+However, until other studies are gathered and checked we would not know how common the flaw is, or if it impacts other studies in a similar way.
+
+\subsection*{Indirect Reproducibility Assessments}
+Indirect reproducibility assessments are one way to address this breadth problem. 
+During  the indirect approach to reproducibility assessment a researcher gathers information about the transparency and availability of information needed to attempt reproduction and the
+
+An alternative approach to understanding the reproducibility of research is to survey active researchers about their perceptions of reproducibility and their own research practices.
+Researcher surveys measure reproducibility indirectly by gathering information about research transparency and researcher practices and motivationsthat
+
+can be used to understand how common certain practices are and what motivates those practices.
+
+Surveys of researchers working across the sciences suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}.
+Perceptions on the cause of irreproducibility range from natural variation to fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}, with an estimated 33 percent of researchers admitting to some form of questionable research practices \citep{fanelli2009many}.
+Researchers also appear to support a broad range of solutions to the challenge of irreproducibility including improved training in research design and statistics and better research mentoring and supervision \citep{baker20161}.
+
+\subsubsection{Geog Indirect}
+To date only a handful studies have tried to indirectly measure the reproducibility of geographic research.
+In a survey of participants from the 2016 European Geosciences Union General Assembly, \citet{konkol2019} assessed the frequency with which researchers published their work in ways that enabled computational reproducibility.
+Those authors found that only 33 percent of respondents included links to the data used in their analyses and only 12 percent provided their analytical code. 
+The authors also found that only seven percent of respondents ever attempted to reproduce the work of other researchers.
+For example, \citet{ostermann2017} use a literature review of volunteered geographic information research publications to assess computational reproducibility based on availability of original data, metadata, source code, or pseudocode.
+
+\subsubsection{common problems of surveys}
+While these surveys are suggestive of reproducibility concerns across the sciences, they share a set of common methodological problems. 
+First, many prior surveys have used non-systematic sampling methods to draw data from non-representative, self-selected populations (e.g., professional association memberships), and/or use non-probability sampling schemes, which collectively limits our ability to draw generalizable conclusion or make inferences about specific sub-fields \citep{NASEM2019}.
+Prior surveys also commonly failed to systematically report survey details (e.g., response rate) needed to assess and address potential bias. 
+To make sound conclusions about the extent of irreproducibility in geography, we need to not only gather additional evidence, we need to do so in a manner consistent with the best practices for survey research \citep[see][]{dillman2014internet, aapor}.
 

### 2022-09-24 procedure/code/00-qualtRics.R
Create 00-qualtRics.R
code for using Qualtrics API

@@ -1,0 +1,25 @@
+# Code for downloading survey data from Qualtrics API
+
+library(qualtRics)
+library(svDialogs)
+
+qualtrics_url <- dlgInput("Qualtrics URL:","middlebury.az1.qualtrics.com")$res
+qualtrics_key <- dlgInput("Qualtrics API Key:")$res 
+rpr_survey_id <- dlgInput("Survey ID:","SV_...")$res
+# find API key and survey ID in Qualtrics "my account" info --> Qualtrics IDs menu
+# find URL in the address bar while you're logged into your Qualtrics projects
+
+qualtrics_api_credentials(api_key = qualtrics_key, 
+                          base_url = qualtrics_url, # e.g. "middlebury.az1.qualtrics.com"
+                          install = TRUE)
+
+readRenviron("~/.Renviron")
+
+# get survey metadata as nested lists, incl questions and possible responses
+rpr_survey_metadata <- metadata(rpr_survey_id)
+
+# get data frame with four columns with question ID, name, text and required 
+rpr_survey_questions <- survey_questions(rpr_survey_id)
+
+# get survey responses as data frame - ordinal responses are ordered factors
+rpr_responses <- fetch_survey(rpr_survey_id)

### 2022-09-28 procedure/code/203_results.Rmd
Create 203_results.Rmd
add markdown for visualizing results

---
title: "Reproduction Survey Analysis"
author: "Joseph Holler, Sarah Bardin, Peter Kedron"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(here)
library(tidyverse)
```

## R Markdown

Abstract...

```{r load}
survey_resp <- readRDS(here("data", "derived", "public", "survey_resp.RDS"))
summary(survey_resp)
```

```{r sub-fields-by-methods}
# crosstab sub-fields and methods
ftable(data = survey_resp, Q4 ~ Q3)
```

```{r familiarity-by-subfield-and-method}
# crosstab familiarity with sub-fields and methods
ftable(data = survey_resp, Q5 ~ Q3 + Q4)
```

```{r familiarity-by-subfield}

# calculate familiarity with reproducible practices
survey_resp <- survey_resp %>% mutate(familiar = as.numeric(Q7a) + 
                                        as.numeric(Q7b) + as.numeric(Q7c) +
                                        as.numeric(Q7d) + as.numeric(Q7e))

# summarize and ANOVA familiarity with practices by subfield
group_by(survey_resp, Q3) %>%
  summarise(
    count = n(),
    mean = mean(familiar, na.rm = TRUE),
    sd = sd(familiar, na.rm = TRUE)
  )
```

```{r familiarity-by-subfield-anova}
aov(familiar ~ Q3, data=survey_resp) %>% summary()
```

#### Summarize reproducible research practices ####
# there must be a prettier option for a crosstabulation with marginal sums!

summary(survey_resp$Q7a)
summary(survey_resp$Q7a_1)
ftable(data = survey_resp, Q7a_1 ~ Q7a)
summary(survey_resp$Q7a_3)
ftable(data = survey_resp, Q7a_3 ~ Q7a)
# FAMILIARITY with open source software outstrips USE of open source software
# and of documenting the computational environment
# low percentage of researchers "always" share information about computational environment

summary(survey_resp$Q7b)
summary(survey_resp$Q7b_1)
ftable(data = survey_resp, Q7b_1 ~ Q7b)
# FAMILIARITY with notebooks also outstrips their USE 
# less than 17% of researchers always use notebooks (lab, field, or computational)
# less than 40% use them most of the time

summary(survey_resp$Q7c)
summary(survey_resp$Q7c_1)
ftable(data = survey_resp, Q7c_1 ~ Q7c)
summary(survey_resp$Q7c_2)
ftable(data = survey_resp, Q7c_2 ~ Q7c)
summary(survey_resp$Q7c_3)
ftable(data = survey_resp, Q7c_3 ~ Q7c)
# most researchers are familiar with sharing/archiving data, but still only 16%
# report always doing so
# use of DOIs is inconsistent and use of metadata is rare

summary(survey_resp$Q7d)
summary(survey_resp$Q7d_1)
ftable(data = survey_resp, Q7d_1 ~ Q7d)
summary(survey_resp$Q7d_2)
ftable(data = survey_resp, Q7d_2 ~ Q7d)
# most researchers are at least somewhat familiar with sharing code or scripts
# but less than 40% actually do so all or most of the time
# and only 14% use version control software some or most of the time

summary(survey_resp$Q7e)
summary(survey_resp$Q7e_1)
ftable(data = survey_resp, Q7e_1 ~ Q7e)
# familiarity with pre-analysis plan registration is rare:
# 48% of respondents have no familiarity
# only 6 respondents reported using pre-analysis registrations all or most of the time

# In Sum, most geographers are at least somewhat familiar with open source software,
# data sharing, and code sharing.
# there are large gaps in implementation across all practices
# some practices are practically unknown in geography, including metadata, 
# version control software, and pre-analysis plan registration.

##### Summarize Beliefs #####

survey_resp %>% select(starts_with("Q8")) %>% summary()

# calculate familiarity with reproducible practices
survey_resp <- survey_resp %>% mutate(belief = as.numeric(Q8_1) + 
                                        (4 - as.numeric(Q8_2)) + 
                                        as.numeric(Q8_3) +
                                        as.numeric(Q8_4) + 
                                        as.numeric(Q8_5) +
                                        (4 - as.numeric(Q8_6))
                                      )
# a majority of geographers believe a failed reproduction does not disprove
# the original study, and geographers are split on whether it detracts from
# the original study's validity
# the most agreement is for students attempting reproductions as part of training

survey_resp %>% select(starts_with("Q8")) %>% lapply(as.numeric) %>% lapply(summary, na.rm=TRUE)
# we can see that in aggregate, geographers do not tend to strongly agree or disagree
# with beliefs about reproducibility
# most in favor of students conducting replications, and reproducibility contributing
# to credibility, and even some degree of compatibility with epistemology in the field
# however geographers are, on average, neutral about loss of validity for failed reproductions
# or loss of trust for studies without available data. 
# we disagree with a failed reproduction falsifying the original study.

# summarize and ANOVA beliefs with practices by subfield
group_by(survey_resp, Q3) %>%
  summarise(
    count = n(),
    mean = mean(belief, na.rm = TRUE),
    sd = sd(belief, na.rm = TRUE)
  )

aov(belief ~ Q3, data=survey_resp) %>% summary()
# again, significant differences in aggregate beliefs about the role of 
# reproducibility in subfields, with physical holding strongest affirmative
# beliefs, then methods, nature/society, and human geography

### 2022-09-28 procedure/code/203_results.Rmd
markdown of analysis
I split the analysis into an Rmarkdown document (203_results.Rmd), keeping pre-processing in 202_analysis.R  (which could be renamed now)

@@
 
-## R Markdown
+## Reproducibility Survey Results
 
-Abstract...
+First, load the pre-processed data.
 
@@
 
+### What research methods does each sub-field use?
+
+The methods and statistics subfield primarily uses quantitative methods, and secondarily uses mixed methods.
+The physical geography subfield uses quantitative and mixed methods, likely including qualitative researcher
+interpretations as "mixed methods".
+The human geography and nature/society subfields use qualitative, quantitative and mixed methods, with the majority preferring qualitative or mixed methods.
+
 ```{r sub-fields-by-methods}
 # crosstab sub-fields and methods
-ftable(data = survey_resp, Q4 ~ Q3)
+addmargins(table(survey_resp$Q4, survey_resp$Q3))
 ```
 
-```{r familiarity-by-subfield-and-method}
-# crosstab familiarity with sub-fields and methods
-ftable(data = survey_resp, Q5 ~ Q3 + Q4)
+### How familiar is each subfield with the term "reproducibility"?
+
+Physical and Methods subfields are more familiar with the
+term "reproducibility" than the Nature/Society or Human subfields.
+
+```{r familiarity-by-subfield}
+addmargins(table(survey_resp$Q5, survey_resp$Q3))
 ```
 
+### How familiar is each method with the term "reproducibility"?
+
+Quantitative and Mixed Methods researchers are more familiar with the
+term "reproducibility" than qualitative researchers.
+
+```{r familiarity-by-methods}
+addmargins(table(survey_resp$Q5, survey_resp$Q4))
+```
+
+### How do geographers define reproducibility?
+
+The following code creates a results table, `definitions.csv`, organizing
+definitions by researcher's self-reported familiarity with the term reproducibility
+and their preferred methodology (quant, qual, or mixed).
+
+We can see a trend where the more familiar a researcher is with the term "reproducibility", 
+the more likely they are to report a definition consistent with the NASEM.
+The less familiar a researcher is, the more likely they are to report a definition
+consistent with "replication", whereby different data may be used and results are 
+expected to be similar, but not identical, to the original results.
+
+```{r define-reproducibility}
+# how did folks define "reproducibility" ?
+survey_resp %>% select(Q3, Q4, Q5, Q6) %>%
+  filter(Q5 != "Not at all") %>%
+  arrange(Q5, Q4) %>%
+  write.csv(here("results", "tables", "definitions.csv"))
+```
+
+### How familiar is each subfield with reproducible research practices?
+
+The following analysis aggregates familiarity with several different research 
+practices into a single indicator, including:
+1. use of open source software,
+2. research notebooks (lab, field, or computational),
+3. data sharing,
+4. code sharing, and 
+5. pre-analysis research protocol registration.
+
+Familiarity is measured from 1 (not at all) to 4 (to a great extent) for each
+research practice, resulting in possible scores from 5 (not familiar with any practice)
+to 20 (greatly familiar with every practice).
+
+The methods and physical geography subfields report the most familiarity with
+reproducible research practices, followed by nature/society and lastly human geography.
+
 ```{r familiarity-by-subfield}
-
-# calculate familiarity with reproducible practices
-survey_resp <- survey_resp %>% mutate(familiar = as.numeric(Q7a) + 
-                                        as.numeric(Q7b) + as.numeric(Q7c) +
-                                        as.numeric(Q7d) + as.numeric(Q7e))
-
-# summarize and ANOVA familiarity with practices by subfield
 group_by(survey_resp, Q3) %>%
@@
     count = n(),
-    mean = mean(familiar, na.rm = TRUE),
-    sd = sd(familiar, na.rm = TRUE)
+    mean = round(mean(familiar, na.rm = TRUE),2),
+    sd = round(sd(familiar, na.rm = TRUE),2)
   )
 ```
+
+There are significant differences between subfields with regards to familiarity with reproducible research practices.
 
@@
 
-#### Summarize reproducible research practices ####
-# there must be a prettier option for a crosstabulation with marginal sums!
+## Does familiarity with practices translate into applying them to research?
 
-summary(survey_resp$Q7a)
-summary(survey_resp$Q7a_1)
-ftable(data = survey_resp, Q7a_1 ~ Q7a)
-summary(survey_resp$Q7a_3)
-ftable(data = survey_resp, Q7a_3 ~ Q7a)
-# FAMILIARITY with open source software outstrips USE of open source software
-# and of documenting the computational environment
-# low percentage of researchers "always" share information about computational environment
+### Do researchers familiar with open source software use it in research?
 
-summary(survey_resp$Q7b)
-summary(survey_resp$Q7b_1)
-ftable(data = survey_resp, Q7b_1 ~ Q7b)
-# FAMILIARITY with notebooks also outstrips their USE 
-# less than 17% of researchers always use notebooks (lab, field, or computational)
-# less than 40% use them most of the time
+Although a majority of researchers are familiar with open source software, they
+less frequently use the software for research.
 
-summary(survey_resp$Q7c)
-summary(survey_resp$Q7c_1)
-ftable(data = survey_resp, Q7c_1 ~ Q7c)
-summary(survey_resp$Q7c_2)
-ftable(data = survey_resp, Q7c_2 ~ Q7c)
-summary(survey_resp$Q7c_3)
-ftable(data = survey_resp, Q7c_3 ~ Q7c)
-# most researchers are familiar with sharing/archiving data, but still only 16%
-# report always doing so
-# use of DOIs is inconsistent and use of metadata is rare
+```{r open-source-use}
+addmargins(table(survey_resp$Q7a, survey_resp$Q7a_1))
+```
 
-summary(survey_resp$Q7d)
-summary(survey_resp$Q7d_1)
-ftable(data = survey_resp, Q7d_1 ~ Q7d)
-summary(survey_resp$Q7d_2)
-ftable(data = survey_resp, Q7d_2 ~ Q7d)
-# most researchers are at least somewhat familiar with sharing code or scripts
-# but less than 40% actually do so all or most of the time
-# and only 14% use version control software some or most of the time
+### What do researchers use open source software for?
 
-summary(survey_resp$Q7e)
-summary(survey_resp$Q7e_1)
-ftable(data = survey_resp, Q7e_1 ~ Q7e)
-# familiarity with pre-analysis plan registration is rare:
-# 48% of respondents have no familiarity
-# only 6 respondents reported using pre-analysis registrations all or most of the time
+```{r open-source-use}
 
-# In Sum, most geographers are at least somewhat familiar with open source software,
-# data sharing, and code sharing.
-# there are large gaps in implementation across all practices
-# some practices are practically unknown in geography, including metadata, 
-# version control software, and pre-analysis plan registration.
+## variables not ready for analysis
 
-##### Summarize Beliefs #####
+```
 
+### Do researchers familiar with open source software share the computational environment?
+
+Although a majority of researchers are familiar with open source software, they
+less frequently share the details of the computational environment used in their
+research.
+
+```{r environment-share}
+addmargins(table(survey_resp$Q7a, survey_resp$Q7a_3))
+```
+
+### Do researchers familiar with research notbooks use them in their research?
+
+FAMILIARITY with notebooks exceeds their use in research. 
+Less than 17% of researchers always use notebooks (lab, field, or computational)
+Less than 40% use them most of the time.
+If researchers are at best somewhat familiar with notebooks, then they only
+use them some of the time.
+
+```{r notebook-use}
+addmargins(table(survey_resp$Q7b, survey_resp$Q7b_1))
+```
+
+### Do researchers familiar with sharing data do so in their research?
+
+Very few researchers always share their data, and familiarity with sharing
+data exceeds the frequency with which researchers do so.
+
+```{r data-share}
+addmargins(table(survey_resp$Q7c, survey_resp$Q7c_1))
+```
+
+Even for those sharing data most of the time, they do not necessarily use
+digital object identifiers (DOIs) to persistently link to the data.
+
+```{r doi}
+addmargins(table(survey_resp$Q7c, survey_resp$Q7c_2))
+```
+
+And an even larger number of researchers rarely if ever document spatial metadata
+for the data that they are sharing, nullifying its usefulness for others.
+Just 16% of researchers report always documenting spatial metadata.
+
+```{r metadata}
+addmargins(table(survey_resp$Q7c, survey_resp$Q7c_3))
+```
+
+### Do researchers familiar with sharing code do so in their research?
+
+Most researchers are at least somewhat familiar with sharing code or scripts,
+but less than 40% actually do so all or most of the time
+
+```{r share-code}
+addmargins(table(survey_resp$Q7d, survey_resp$Q7d_1))
+```
+
+Only 14% use version control software some or most of the time
+
+```{r version-control}
+addmargins(table(survey_resp$Q7d, survey_resp$Q7d_2))
+```
+
+### Do researchers familiar with pre-analysis planning register pre-analysis plans for their research?
+
+Only 52% of respondents have any familiarity with pre-analysis plans, and of those
+just 6 researchers register plans all or or most of the time.
+
+```{r pre-analysis}
+addmargins(table(survey_resp$Q7e, survey_resp$Q7e_1))
+```
+
+In Sum, most geographers are at least somewhat familiar with open source software,
+data sharing, and code sharing.
+there are large gaps in implementation across all practices
+some practices are practically unknown in geography, including metadata, 
+version control software, and pre-analysis plan registration.
+
+# Beliefs about Reproducibility
+
+```{r beliefs-summary}
 survey_resp %>% select(starts_with("Q8")) %>% summary()
+```
 
-# calculate familiarity with reproducible practices
-survey_resp <- survey_resp %>% mutate(belief = as.numeric(Q8_1) + 
-                                        (4 - as.numeric(Q8_2)) + 
-                                        as.numeric(Q8_3) +
-                                        as.numeric(Q8_4) + 
-                                        as.numeric(Q8_5) +
-                                        (4 - as.numeric(Q8_6))
-                                      )
-# a majority of geographers believe a failed reproduction does not disprove
-# the original study, and geographers are split on whether it detracts from
-# the original study's validity
-# the most agreement is for students attempting reproductions as part of training
+A majority of geographers believe a failed reproduction does not disprove the original study,
+and geographers are split on whether it detracts from the original study's validity.
+The most agreement is for students attempting reproductions as part of training
 
+```{r beliefs-stats}
 survey_resp %>% select(starts_with("Q8")) %>% lapply(as.numeric) %>% lapply(summary, na.rm=TRUE)
-# we can see that in aggregate, geographers do not tend to strongly agree or disagree
-# with beliefs about reproducibility
-# most in favor of students conducting replications, and reproducibility contributing
-# to credibility, and even some degree of compatibility with epistemology in the field
-# however geographers are, on average, neutral about loss of validity for failed reproductions
-# or loss of trust for studies without available data. 
-# we disagree with a failed reproduction falsifying the original study.
+```
 
-# summarize and ANOVA beliefs with practices by subfield
+we can see that in aggregate, geographers do not tend to strongly agree or disagree
+with beliefs about reproducibility
+most in favor of students conducting replications, and reproducibility contributing
+to credibility, and even some degree of compatibility with epistemology in the field
+however geographers are, on average, neutral about loss of validity for failed reproductions
+or loss of trust for studies without available data. 
+we disagree with a failed reproduction falsifying the original study.
+
+# Do subfields vary in their aggregate beliefs about reproducibility?
+
+There are differences in aggregate beliefs about the role of 
+reproducibility between the four subfields, with physical holding strongest affirmative
+beliefs, then methods, nature/society, and human geography
+
+```{r beliefs-stats-by-subfield}
 group_by(survey_resp, Q3) %>%
@@
   )
+```
 
+The differences are statistically significant.
+
+```{r beliefs-anova}
 aov(belief ~ Q3, data=survey_resp) %>% summary()
-# again, significant differences in aggregate beliefs about the role of 
-# reproducibility in subfields, with physical holding strongest affirmative
-# beliefs, then methods, nature/society, and human geography
+```

### 2022-09-28 procedure/code/202_analysis.R

@@ -86,13 +86,6 @@ for (i in numeric_vars){
 }
 
 
-
-# how did folks define "reproducibility" ?
-survey_resp %>% select(Q3, Q4, Q5, Q6) %>%
-  filter(Q5 != "Not at all") %>%
-  arrange(Q5, Q4) %>%
-  write.csv(here("results", "tables", "definitions.csv"))
-
 ##### FACTOR MANAGEMENT #####
 # if anyone can compress all of this into a function that uses a table of 
 # questions & ordered responses, by all means...
@@ -181,143 +174,29 @@ survey_resp[questions] <- lapply(survey_resp[questions],
 # check data types for the full survey
 sapply(survey_resp, class)
 
-# save revised survey data
-saveRDS(survey_resp, here("data", "derived", "public", "survey_resp.RDS"))
+##### Calculate Aggregate Indicators #####
 
-# optionally, load revised survey data
-survey_resp <- readRDS(here("data", "derived", "public", "survey_resp.RDS"))
-
-
-##### SUMMARIZING RESULTS #####
-
-# Summarize the survey data
-summary(survey_resp)
-
-
-
-# need to convert:
-# Q7a_2 into four binary variables
-# Q13_1_! and Q13_2_1 into numeric
-# consider coding Q7 frequency questions as "never" if they skipped the question because
-# of no familiarity
-
-# crosstab sub-fields and methods
-ftable(data = survey_resp, Q4 ~ Q3)
-
-# crosstab familiarity with sub-fields and methods
-ftable(data = survey_resp, Q5 ~ Q3 + Q4)
-
-# calculate familiarity with reproducible practices
+# familiarity with reproducible practices
 survey_resp <- survey_resp %>% mutate(familiar = as.numeric(Q7a) + 
                                         as.numeric(Q7b) + as.numeric(Q7c) +
                                         as.numeric(Q7d) + as.numeric(Q7e))
 
-# summarize and ANOVA familiarity with practices by subfield
-group_by(survey_resp, Q3) %>%
-  summarise(
-    count = n(),
-    mean = mean(familiar, na.rm = TRUE),
-    sd = sd(familiar, na.rm = TRUE)
-  )
-
-aov(familiar ~ Q3, data=survey_resp) %>% summary()
-# there are significant differences between sub-fields, with Methods / Spatial
-# analysis and Phsycial geography both more familiar than nature/society or
-# human geography
-
-# calculate use of reproducible practices
[…]

### 2022-10-12 docs/manuscript/manuscript.tex
Minor additions to direct/indirect section

@@
 
-There are several ways to assess the reproducibility of research.
 The most direct approach is to simply conduct a study that follows the methods of an existing study and then compare the results of the new study to the results of the old study.
@@
 Direct reproducibility assessments can be implemented in two ways: as a one-to-one comparison, in which a single reproduction is used to assess the results and inferences of one prior study; or as a many-to-one comparison, in which teams of researchers attempt multiple parallel reproductions and make a set of comparisons and a collective assessment of one prior study.
-Published reproductions of both forms are becoming increasingly common in many disciplines \citep[e.g.,][]{begley2012raise, camerer2016evaluating, camerer2018evaluating, wagenmakers2016registered}. 
+Published reproductions of both forms are increasingly common in many disciplines \citep[e.g.,][]{begley2012raise, camerer2016evaluating, camerer2018evaluating, wagenmakers2016registered}. 
 However, the researchers conducting those studies have generally only able to partially reproduce study results, often observing small effect sizes.
@@
 For example, \citet{ostermann2017} use a literature review of volunteered geographic information research publications to assess computational reproducibility based on availability of original data, metadata, source code, or pseudocode.
+Remote Sensing survey.
 

### 2022-11-05 procedure/code/00-qualtRics.R
Updated read-in program to pull data from Qualtrics API and save .RDS files. Updated de-identification program to reference .RDS file and output new raw file.

@@ -2,16 +2,18 @@
 
 library(qualtRics)
 library(svDialogs)
+library(here)
 
-qualtrics_url <- dlgInput("Qualtrics URL:","middlebury.az1.qualtrics.com")$res
-qualtrics_key <- dlgInput("Qualtrics API Key:")$res 
-rpr_survey_id <- dlgInput("Survey ID:","SV_...")$res
+qualtrics_url <- dlgInput("Qualtrics URL:","asu.co1.qualtrics.com")$res
+qualtrics_key <- dlgInput("Qualtrics API Key:", )$res 
+rpr_survey_id <- dlgInput("Survey ID:","SV_e2Id3c5vvtqtazI")$res
 # find API key and survey ID in Qualtrics "my account" info --> Qualtrics IDs menu
 # find URL in the address bar while you're logged into your Qualtrics projects
 
 qualtrics_api_credentials(api_key = qualtrics_key, 
                           base_url = qualtrics_url, # e.g. "middlebury.az1.qualtrics.com"
-                          install = TRUE)
+                          install = TRUE,
+                          overwrite = TRUE)
 
 readRenviron("~/.Renviron")
 
@@ -23,3 +25,8 @@ rpr_survey_questions <- survey_questions(rpr_survey_id)
 
 # get survey responses as data frame - ordinal responses are ordered factors
 rpr_responses <- fetch_survey(rpr_survey_id)
+
+saveRDS(rpr_responses, here("data","raw","private","raw_rpr_responses.rds"))
+saveRDS(rpr_survey_questions, here("data","raw","private","raw_rpr_survey_questions.rds"))
+saveRDS(rpr_survey_metadata, here("data","raw","private","raw_rpr_survey_metadata.rds"))
+

### 2022-11-05 procedure/code/200_deidentify.R

@@ -2,18 +2,22 @@ library(here)
 library(tidyverse)
 
 
-hegs_repro <- read.csv(here("data","raw","private","HEGS-Reproducibility_2022_22_06.csv"))
-head(hegs_repro$StartDate)
+raw_rpr_responses <- readRDS(here("data","raw","private","raw_rpr_responses.rds"))
+  head(raw_rpr_responses)
+  str(raw_rpr_responses)
 
-hegs_repro = hegs_repro[-1,]
-hegs_repro = hegs_repro[-1,] # drop first two rows from data as these contain variable labels
-head(hegs_repro$StartDate)
-
-hegs_deidentified <- hegs_repro %>% 
+hegs_rpr_deidentified <- raw_rpr_responses %>% 
                       select(-c(RecipientLastName, 
                                 RecipientFirstName, 
                                 RecipientEmail,
-                                IPAddress))
+                                IPAddress,
+                                Status,
+                                ExternalReference,
+                                LocationLatitude,
+                                LocationLongitude,
+                                DistributionChannel,
+                                UserLanguage))
 
-write.csv(hegs_deidentified, here("data","raw","deidentified","hegsrr_raw_reprod.csv"))
+saveRDS(hegs_rpr_deidentified, here("data","raw","public","raw_hegs_rpr.rds"))
+
                         

### 2022-11-08 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 \section*{Introduction}
-Since the 1600s, replication has been a defining characteristic of the scientific method and an essential tool of researchers working to remove errors from our understanding of phenomena. 
-\citet{nosek2020} broadly define a replication as any study that has at least one outcome that would be considered to be diagnostic evidence of a claim from prior research.
-More frequently, replication is defined along two axes that help to distinguish the type of diagnostic evidence a study will provide and the function or purpose it is intended to serve. 
-First, it is common to distinguish whether a replication study used the same data as the original study, or if new data were collected and analyzed. 
-Second, it is helpful to identify whether a replication is focused on the question of whether the specific results of the original study can be reobserved, or whether the conclusions drawn from the original study are robust to changes in procedure or context.
 
-When a researcher asks whether the same data and procedures can be used to generate the same results as an original study the central purpose of their study is verification.
-If the researcher uses the original data, but introduces procedural differences they think may effect the original result they pursue a reanalysis designed to determine whether the original reasoning was somehow erroneous.
-Both of these approaches to replication assess the internal validity of research and are more commonly referred to as reproductions.
-If the researcher tries to follow the procedures of an original study, but collects new data, the purpose shifts to evaluating the external validity of the original result by retesting it under new conditions.
-This approach is commonly referred to as replication.
-
-While a replication or reproduction can never provide conclusive evidence for or against a finding, either type of study can be informative. 
-If a well-executed, high-quality replication or reproduction recreates the result of an original study, we are apt to increase our confidence in the original findings. 
-If a finding cannot be recreated, it reduces our confidence in the original result and suggests that our current understanding of the system being studied or our methods of testing that system are insufficient.
+\newpage
 
@@
 \section*{Assessing the Reproducibility of Research}
-The reproducibility of research can be assessed directly or indirectly \citep{NASEM2019}.
+The reproducibility of research can be assessed directly or indirectly. 
+In a direct assessment of reproducibility, an independent team(s) of researchers repeats the analytical steps of a previous study using the same data and then evaluates the consistency of the two sets of results\footnote{Insert paragraph on the difficulty of developing in using consistency criteria}.
+By contrast, during an indirect assessment of reproducibility, a research team gathers information about the transparency of a study and the availability of the research components (e.g., data and code) needed to recreate that study, but does not directly attempt to recreate the results.
+Indirect assessments also often take the form of surveys in which researchers are asked about their research practices, incentives, and motivations.
 
-In a direct assessment of reproducibility 
-Indirect reproducibility assessments
+Direct and indirect reproducibility assessments present a trade off between the depth and breadth of evaluation.  
+A direct assessment that carefully reproduces a study can provide insight into how a particular study was conducted and why a consistent result could, or could not, be obtained.  
+However, such assessments are resource and time intensive, which makes them difficult to scale to a large number of studies. 
+Constrained to a limited number of studies, direct assessments offer only suggestive evidence about the reproducibility of unevaluated studies and the prevalence of reproducible research practices. 
+In contrast, comparatively less resource intensive indirect assessments that catalog reproducible research practices can be more easily scaled.
+By evaluating many studies, indirect assessments provide evidence of how common reproducible research practices are and, by extension, how reproducible work in a field of study is likely to be.
+The trade off being that indirect assessments do not offer as detailed a look into why a particular result in a specific instance could, or could not, be obtained.
 
-The most direct approach is to simply conduct a study that follows the methods of an existing study and then compare the results of the new study to the results of the old study.
+The available body of direct and indirect reproducibility assessments currently provides
 
-\subsection*{Direct Reproducibility Assessments}
-Direct reproducibility assessments can be implemented in two ways: as a one-to-one comparison, in which a single reproduction is used to assess the results and inferences of one prior study; or as a many-to-one comparison, in which teams of researchers attempt multiple parallel reproductions and make a set of comparisons and a collective assessment of one prior study.
-Published reproductions of both forms are increasingly common in many disciplines \citep[e.g.,][]{begley2012raise, camerer2016evaluating, camerer2018evaluating, wagenmakers2016registered}. 
-However, the researchers conducting those studies have generally only able to partially reproduce study results, often observing small effect sizes.
+insufficient evidence to conclusively evaluate the reproducibility of scientific research generally, or disciplinary research specifically \citep{NASEM2019}.
+This knowledge gap exists in part because while available evidence consistently suggests that inadequate record keeping, opaque reporting, and unavailable research components are drivers of research irreproducibility, how common these practices are remains unclear.
+We have been unable to estimate the prevalence and impact of these practices because indirect assessments have used non-probability based sampling methods to draw data from non-representative, self-selected populations (e.g., professional association memberships).
 
-Such published reproductions have not yet become common in geography. 
+Prior surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias.
+
+Surveys of researchers working across the sciences suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}.
+Perceptions on the cause of irreproducibility range from natural variation to fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}, with an estimated 33 percent of researchers admitting to some form of questionable research practices \citep{fanelli2009many}.
+Researchers also appear to support a broad range of solutions to the challenge of irreproducibility including improved training in research design and statistics and better research mentoring and supervision \citep{baker20161}.
+
+\subsection*{Assessing the Reproducibility of Geographic Research}
+Direct and indirect assessments of research reproducibility
+
+Geographic researchers are beginning to address these questions by conducting direct and indirect assessments of the reproducibility of geographic research. 
+However, only a small number of such studies currently exist resulting in a similarly limited set of evidence about reprodubibility within the discipline.
+
+There is reason to believe that each of these factors is present in geography, but limited evidence because published reproductions have not yet become common in geography. 
 The small number of studies that have attempted to assess the reproducibility of geographic research by recreating existing work suggest that many studies cannot be fully reproduced \citep{Kedron2021ssrn, nust2018, ostermann2021}, or are simply missing components needed to attempt a reproduction \citep{Kedron_VijayanRP, konkol2019, ostermann2021}.
@@
 
-The root of the problem is that the direct approach to assessing reproducibility presents a trade off. 
-The careful reproduction of a study can provide rich evidence about that particular study, but offers at best suggestive evidence about the validity of other studies or the prevalence of the research practices observed.
-For example, if a reproduction identified a flaw in the design of a study that impacted the results of that study it would be reasonable to be concerned that observing the same flaw in other studies could impact the results of those studies.
-However, until other studies are gathered and checked we would not know how common the flaw is, or if it impacts other studies in a similar way.
-
-\subsection*{Indirect Reproducibility Assessments}
-Indirect reproducibility assessments are one way to address this breadth problem. 
-During  the indirect approach to reproducibility assessment a researcher gathers information about the transparency and availability of information needed to attempt reproduction and the
-
-An alternative approach to understanding the reproducibility of research is to survey active researchers about their perceptions of reproducibility and their own research practices.
-Researcher surveys measure reproducibility indirectly by gathering information about research transparency and researcher practices and motivationsthat
-
-can be used to understand how common certain practices are and what motivates those practices.
-
-Surveys of researchers working across the sciences suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}.
-Perceptions on the cause of irreproducibility range from natural variation to fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}, with an estimated 33 percent of researchers admitting to some form of questionable research practices \citep{fanelli2009many}.
-Researchers also appear to support a broad range of solutions to the challenge of irreproducibility including improved training in research design and statistics and better research mentoring and supervision \citep{baker20161}.
-
-\subsubsection{Geog Indirect}
 To date only a handful studies have tried to indirectly measure the reproducibility of geographic research.
@@
 
-\subsubsection{common problems of surveys}
-While these surveys are suggestive of reproducibility concerns across the sciences, they share a set of common methodological problems. 
-First, many prior surveys have used non-systematic sampling methods to draw data from non-representative, self-selected populations (e.g., professional association memberships), and/or use non-probability sampling schemes, which collectively limits our ability to draw generalizable conclusion or make inferences about specific sub-fields \citep{NASEM2019}.
-Prior surveys also commonly failed to systematically report survey details (e.g., response rate) needed to assess and address potential bias. 
-To make sound conclusions about the extent of irreproducibility in geography, we need to not only gather additional evidence, we need to do so in a manner consistent with the best practices for survey research \citep[see][]{dillman2014internet, aapor}.
+\subsubsection*{Research Summary to Transition}
+The evidence available from direct and indirect assessments of reproducibility suggests that studies are often not reproducible because researchers do provide the information or materials others need to recreate their work.
+
+However, may of our indirect assessment are on shaky methodological grounds and we have not studied this in geography.
 

### 2022-11-09 procedure/code/203_results.Rmd
Latest coding updates to produce analysis file.

@@
 ```{r load}
-survey_resp <- readRDS(here("data", "derived", "public", "survey_resp.RDS"))
+survey_resp <- readRDS(here("data","derived","public","analysis_hegs_rpr.rds"))
 summary(survey_resp)
@@
 # crosstab sub-fields and methods
-addmargins(table(survey_resp$Q4, survey_resp$Q3))
+addmargins(table(survey_resp$Q3_recoded, survey_resp$Q4))
 ```
@@
 ```{r familiarity-by-subfield}
-addmargins(table(survey_resp$Q5, survey_resp$Q3))
+addmargins(table(survey_resp$Q5, survey_resp$Q3_recoded))
 ```
@@
 # how did folks define "reproducibility" ?
-survey_resp %>% select(Q3, Q4, Q5, Q6) %>%
+survey_resp %>% select(Q3_recoded, Q4, Q5, Q6) %>%
   filter(Q5 != "Not at all") %>%
@@
 ```{r familiarity-by-subfield}
-group_by(survey_resp, Q3) %>%
+group_by(survey_resp, Q3_recoded) %>%
   summarise(
@@
 ```{r familiarity-by-subfield-anova}
-aov(familiar ~ Q3, data=survey_resp) %>% summary()
+aov(familiar ~ Q3_recoded, data=survey_resp) %>% summary()
 ```

### 2022-11-09 procedure/code/201_clean.R

@@ -2,39 +2,100 @@ library(here)
 library(tidyverse)
 library(janitor)
 
-#-----------------------------------#
+#--------------------------------------------#
 
-#- Merge survey data back to frame -#
+#- Read in and limit data file to completes -#
 
-#-----------------------------------#
-#- Read in data files -#
-survey_resp <- read.csv(here("data","raw","public","hegsrr_raw_reprod.csv"))
-survey_samp <- read.csv(here("data","raw","private","analysis","Survey-Response-Tracking_qualtrics_update_v4.csv"))
+#--------------------------------------------#
+raw_hegs_rpr <- readRDS(here("data","raw","public","raw_hegs_rpr.rds"))
+int_hegs_rpr <- raw_hegs_rpr %>% filter(Progress > 70 & Q1 != "Under 18")
+  summary(int_hegs_rpr$Progress)
 
-#- Merge files -#
-raw <- right_join(survey_resp, survey_samp,by = c("ResponseId" = "Response.ID"))
-table(raw$disposition_final)
+#------------------------------------#
 
-# Filter out partial completes and underage respondent
-raw_filtered <- raw %>% filter(disposition_final %in% c("1.1","1.2") & Q1 != "Under 18")
+#- Backcode other specify responses -#
+
+#------------------------------------#
+table(toupper(int_hegs_rpr$Q3_5_TEXT))
+
+#-Open response areas of specialization to recode-#
+hum_list  <- c("ECONOMIC GEOGRAPHY","POLITICAL GEOGRAPHY", "POLITICAL SCIENCE", "SOCIO-ANTHROPOLOGY",
+              "SOCIOLOGY","TRANSPORT GEOGRAPHY","TRANSPORTATION","TRANSPORTATION ENGINEERING", "URBAN GEOGRAPHY")
+
+phys_list <- c("PALEOBOTANY","PALEOCLIMATOLOGY")
+
+nat_list  <- c("BIOGEOGRAPHY","CITY PLANNING, SUSTAINABILITY TRANSFORMATIONS","ENVIRONMENTAL ARCHAEOLOGY","ARCHAEOLOGY",
+              "MOBILITIES")
+
+gis_list  <- c("GEOSPATIAL INFORMATION SCIENCE", "SPATIAL ECONOMETRICS", "CARTOGRAPHY","REMOTE SENSING",
+              "REMOTE SENSING OF ENVIRONMENT")
+
+int_hegs_rpr <- int_hegs_rpr %>% 
[…]

### 2022-11-09 procedure/code/200_deidentify.R
Updated cleaning code

@@ -1,11 +1,39 @@
 library(here)
 library(tidyverse)
+library(qualtRics)
+library(svDialogs)
 
 
-raw_rpr_responses <- readRDS(here("data","raw","private","raw_rpr_responses.rds"))
-  head(raw_rpr_responses)
-  str(raw_rpr_responses)
+# Code for downloading survey data from Qualtrics API
+qualtrics_url <- dlgInput("Qualtrics URL:","asu.co1.qualtrics.com")$res
+qualtrics_key <- dlgInput("Qualtrics API Key:", )$res 
+rpr_survey_id <- dlgInput("Survey ID:","SV_e2Id3c5vvtqtazI")$res
+# find API key and survey ID in Qualtrics "my account" info --> Qualtrics IDs menu
+# find URL in the address bar while you're logged into your Qualtrics projects
 
+qualtrics_api_credentials(api_key = qualtrics_key, 
+                          base_url = qualtrics_url, # e.g. "middlebury.az1.qualtrics.com"
+                          install = TRUE,
+                          overwrite = TRUE)
+
+readRenviron("~/.Renviron")
+
+# get survey metadata as nested lists, incl questions and possible responses
+rpr_survey_metadata <- metadata(rpr_survey_id)
+
+# get data frame with four columns with question ID, name, text and required 
+rpr_survey_questions <- survey_questions(rpr_survey_id)
+
+# get survey responses as data frame - ordinal responses are ordered factors
+rpr_responses <- fetch_survey(rpr_survey_id)
+
+# Save permenant raw files and associated documentation for archvial purposes
+saveRDS(rpr_responses, here("data","raw","private","raw_rpr_responses.rds"))
+saveRDS(rpr_survey_questions, here("data","raw","private","raw_rpr_survey_questions.rds"))
+saveRDS(rpr_survey_metadata, here("data","raw","private","raw_rpr_survey_metadata.rds"))
+
+
+# De-identify file to create public raw version
 hegs_rpr_deidentified <- raw_rpr_responses %>% 
                       select(-c(RecipientLastName, 
                                 RecipientFirstName, 

### 2022-11-09 procedure/code/201_clean.R

@@ -1,6 +1,19 @@
-library(here)
-library(tidyverse)
-library(janitor)
+# list of required packages
+packages = c("here","tidyverse")
+
+# load and install required packages
+package.check <- lapply(
+  packages,
+  FUN = function(x) {
+    if (!require(x, character.only = TRUE)) {
+      install.packages(x, dependencies = TRUE)
+      library(x, character.only = TRUE)
+    }
+  }
+)
+
+# save the R processing environment to r_environment.txt
+writeLines(capture.output(sessionInfo()),here("procedure","environment","r_environment.txt"))
 
 #--------------------------------------------#
 
@@ -16,6 +29,7 @@ int_hegs_rpr <- raw_hegs_rpr %>% filter(Progress > 70 & Q1 != "Under 18")
 #- Backcode other specify responses -#
 
 #------------------------------------#
+  
 table(toupper(int_hegs_rpr$Q3_5_TEXT))
 
 #-Open response areas of specialization to recode-#
@@ -45,9 +59,69 @@ levels(int_hegs_rpr$Q3_recoded) <- c("Human geography",
 table(int_hegs_rpr$Q3_recoded,int_hegs_rpr$Q3)
 ## Note: 2 respondents skipped Q3 and 1 respondent who indicated "other" did not specify what their subfield is
 
-##Unsure how to backcode these variables yet
+
+#---------------------------------------------------------------------------------------------------------------------------
+
+res_scientist <- c("Government scientist (applied)","Project Scientist","Researcher (policy)",
+                   "Senior Research Fellow", "Senior Consultant and external lecturer")
+
+int_hegs_rpr <- int_hegs_rpr %>% 
+  mutate(Q19_recoded = as.factor(ifelse(Q19 %in% res_scientist, 5, 
+                                       ifelse(Q19 == "Lecturer/teacher at a university of applied sciences.", 2, Q19))))
+
+levels(int_hegs_rpr$Q19_recoded) <- c("Full professor/lecturer",
+                                      "Associate professor/lecturer",
+                                      "Assistant professor/lecturer",
+                                      "Laboratory director/head",
+                                      "Research scientist",
+                                      "Post-doctoral fellow",
+                                      "Graduate student (PhD, masters)",
+                                      "Technician/research assistant",
+                                      "Other (specify)",
+                                      "NA")
+
[…]

### 2022-11-10 docs/manuscript/manuscript.tex

@@
 
-The available body of direct and indirect reproducibility assessments currently provides
+Despite their growing number, the available body of direct and indirect reproducibility assessments currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically \citep{NASEM2019}.
+This knowledge gap exists because neither direct nor indirect reproducibility assessments have been designed so the results of the sample of studies evaluated can be extended to the population of research as a whole.
+Reproduction attempts remain relatively rare, and those that do exist \citep[see][]{chang2015economics, moraila2014measuring} have selectively targeted publications in high-impact journals and conference papers series in a limited number of disciplines that are not representative of many forms of research.
+Indirect reproducibility assessments that catalog the availability of research components similarly focus on conveniently accessible archives, such as conference paper series \citep{gundersen2018state, ostermann2017}, or target specific journals and disciplinary repositories \citep{stodden2018empirical, stodden2018enabling, byrne_2017}.
+These assessments have also tended to focus on evaluating the computational components of research such as data and code availability, as this information is easier to identify and assess at scale when compared to components like field procedures or qualitative analysis that may be included only in text.
+Surveys of researcher practices and attitudes on reproducibility face similar challenges to their generalizability. 
+Rather than carefully defining researcher populations of interest, prior surveys have drawn data non-randomly from self-selecting populations that are convenient to survey (e.g., members of professional association, conference attendees), but are not necessarily representative of researchers active in a particular field.
+These surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response.
 
-insufficient evidence to conclusively evaluate the reproducibility of scientific research generally, or disciplinary research specifically \citep{NASEM2019}.
-This knowledge gap exists in part because while available evidence consistently suggests that inadequate record keeping, opaque reporting, and unavailable research components are drivers of research irreproducibility, how common these practices are remains unclear.
-We have been unable to estimate the prevalence and impact of these practices because indirect assessments have used non-probability based sampling methods to draw data from non-representative, self-selected populations (e.g., professional association memberships).
+While it may not be possible to determine the extent of irreproducibility across or within disciplines, it is possible to draw lessons about potential sources of irreproducibility from available studies.
+The evidence available from direct and indirect reproducibility assessments suggests inadequate record keeping, opaque reporting, unavailable research components, and a lack of incentives are important factors contributing to the irreproducibility of research \citep{NASEM2019}.
+Prominent attempts to reproduce research in economics \citep{chang2015economics}, computer science \citep{moraila2014measuring}, and psychology \citep{open2015estimating} have all been able to reproduce only a small portion of studies because original authors did not share data or adequate information about their procedures.
+Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread, as the majority of articles reviewed did not share data adequate for reproducibility.
 
-Prior surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias.
-
-Surveys of researchers working across the sciences suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}.
-Perceptions on the cause of irreproducibility range from natural variation to fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}, with an estimated 33 percent of researchers admitting to some form of questionable research practices \citep{fanelli2009many}.
-Researchers also appear to support a broad range of solutions to the challenge of irreproducibility including improved training in research design and statistics and better research mentoring and supervision \citep{baker20161}.
+Surveys of researchers about reproducibility issues and related research practices paint a similar picture. 
+Recent surveys suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
+Moreover, a sizable portion of the researchers responding to these surveys admit to engaging in questionable research practices linked to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
+For example, in a survey of 807 ecologists and evolutionary biologists, 64 percent admitted to failing to report non-significant results and 51 percent admitted to presenting unexpected findings as if they been hypothesized from the start of the research \citep{fraser2018questionable}.
+These findings also match researcher perceptions, which link irreproducibility to causes ranging from natural variation to outright fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}.
 
 \subsection*{Assessing the Reproducibility of Geographic Research}
+Reproducibility has only recently moved forward on Geography's disciplinary research agenda.
+
 Direct and indirect assessments of research reproducibility

### 2022-11-12 procedure/code/00-qualtRics.R
Clean up code base to remove redundant scripts.

@@ -1,32 +1,0 @@
-# Code for downloading survey data from Qualtrics API
-
-library(qualtRics)
-library(svDialogs)
-library(here)
-
-qualtrics_url <- dlgInput("Qualtrics URL:","asu.co1.qualtrics.com")$res
-qualtrics_key <- dlgInput("Qualtrics API Key:", )$res 
-rpr_survey_id <- dlgInput("Survey ID:","SV_e2Id3c5vvtqtazI")$res
-# find API key and survey ID in Qualtrics "my account" info --> Qualtrics IDs menu
-# find URL in the address bar while you're logged into your Qualtrics projects
-
-qualtrics_api_credentials(api_key = qualtrics_key, 
-                          base_url = qualtrics_url, # e.g. "middlebury.az1.qualtrics.com"
-                          install = TRUE,
-                          overwrite = TRUE)
-
-readRenviron("~/.Renviron")
-
-# get survey metadata as nested lists, incl questions and possible responses
-rpr_survey_metadata <- metadata(rpr_survey_id)
-
-# get data frame with four columns with question ID, name, text and required 
-rpr_survey_questions <- survey_questions(rpr_survey_id)
-
-# get survey responses as data frame - ordinal responses are ordered factors
-rpr_responses <- fetch_survey(rpr_survey_id)
-
-saveRDS(rpr_responses, here("data","raw","private","raw_rpr_responses.rds"))
-saveRDS(rpr_survey_questions, here("data","raw","private","raw_rpr_survey_questions.rds"))
-saveRDS(rpr_survey_metadata, here("data","raw","private","raw_rpr_survey_metadata.rds"))
-

### 2022-11-30 procedure/code/201_clean.R
Updated cleaning code to implement Q16 backcoding and constructions and saved changes to analysis file.

@@ -85,37 +85,31 @@ table(int_hegs_rpr$Q19_recoded,toupper(int_hegs_rpr$Q19))
 
 #---------------------------------------------------------------------------------------------------------------------------
 
-##Unsure how to backcode the Q16 series of variables
 int_hegs_rpr %>% filter(!is.na(Q16_5)) %>% select(c(Q16_1,Q16_2,Q16_3,Q16_4,Q16_5_TEXT)) 
+int_hegs_rpr %>% filter(!is.na(Q16_5_TEXT)) %>% select(c(Q16_5_TEXT)) 
 
-int_hegs_rpr %>% filter(!is.na(Q16_5)) %>% select(c(Q16_5_TEXT)) 
-table(toupper(int_hegs_rpr$Q16_5_TEXT))
+int_hegs_rpr %>% filter(!is.na(Q16_5_TEXT)) %>% select(c(Q16_1,Q16_2,Q16_3,Q16_4,Q16_5, Q16_5_TEXT)) 
+Q16_all_coauths <- c("all co-authors on a publication","All researchers on the team",
+                 "Students and first authors", "co-investigators",
+                 "Researchers (scientist, students, post doc, Principle investigator, etc)  who are producing the data should be ethical enough to produce  reproducible data")
+Q16_none <- c("Nobody?","Noone","Question assumes that reproducibility should be enforced - dont agree")
+Q16_dk   <- c("don't know","see earlier comment.")
+Q16_all  <- "All of the above, especially the PI, but also researchers who attempt to reproduce. They must adapt models, methods and other elements for research to be reproducible in diverse contexts. This is paradoxical but mostly true."
 
-# Should we create an "all co-authors option"; many of these "other" responses also checked Principal investigator of the study
-#      - all co-authors on a publication
-#      - All researchers on the team 
-#      - Students and first authors  
-#      - Researchers (scientist, students, post doc, Principle investigator, etc)  who are producing the data should be ethical enough to produce  reproducible data
-#      - co-investigators 
+int_hegs_rpr <- int_hegs_rpr %>% 
+                    mutate(Q16_6 = as.numeric(Q16_5_TEXT %in% Q16_all_coauths),
+                           Q16_7 = as.numeric(Q16_5_TEXT %in% Q16_none),
[…]

### 2022-11-30 docs/manuscript/manuscript.tex

@@
 \section*{Introduction}
+Reproducibility as a characteristic of a study that lends it credibility v. Reproducibility as a error correcting function of science.
 
@@
 \subsection*{Assessing the Reproducibility of Geographic Research}
-Reproducibility has only recently moved forward on Geography's disciplinary research agenda.
+To date, only a small number of studies have attempted to reproduce geographic research.
+The reproductions that are available within the discipline suggest that many studies cannot be fully reproduced \citep{Kedron2021ssrn, nust2018, ostermann2021}, or are simply missing the components needed to attempt a reproduction \citep{Kedron_VijayanRP, konkol2019, ostermann2021}.
 
-Direct and indirect assessments of research reproducibility
-
-Geographic researchers are beginning to address these questions by conducting direct and indirect assessments of the reproducibility of geographic research. 
-However, only a small number of such studies currently exist resulting in a similarly limited set of evidence about reprodubibility within the discipline.
-
-There is reason to believe that each of these factors is present in geography, but limited evidence because published reproductions have not yet become common in geography. 
-The small number of studies that have attempted to assess the reproducibility of geographic research by recreating existing work suggest that many studies cannot be fully reproduced \citep{Kedron2021ssrn, nust2018, ostermann2021}, or are simply missing components needed to attempt a reproduction \citep{Kedron_VijayanRP, konkol2019, ostermann2021}.
 For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort.
@@
 
+\subsection{Survey Demographics}
+
+\subsection{Definition of Reproducibility}
+Definition Questions and Q8 about beliefs about the interpretation for reproductions.
+Dig into those respondents that had variations in beliefs on Q8 sequence.
+Q17 about importance of reproduction.
+Close with Q13.
+
+\subsection{Familiarity and Frequency of Practices}
+Summary of Table showing Familiarity 1) all survey, 2) Methods, 3) Subfield Split
+Summary of Table showing Implementation 1) all survey, 2) Methods, 3) Subfield Split
+
+\subsection{Actual Reproductions}
+Summary of Q10-Q12
+
+\subsection{Barriers to Reproduction}
+Q14
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2022-12-06 procedure/code/200_deidentify.R
small rev to raw data saving
switch code to save into public folder (where the .rds files are now stored), and remove HTML tags from question text

@@ -24,13 +24,17 @@ rpr_survey_metadata <- metadata(rpr_survey_id)
 # get data frame with four columns with question ID, name, text and required 
 rpr_survey_questions <- survey_questions(rpr_survey_id)
 
+# remove html formatting from questions
+rpr_survey_questions <- rpr_survey_questions %>% 
+  mutate(question = gsub("<(.*?)>","",question))
+
 # get survey responses as data frame - ordinal responses are ordered factors
 rpr_responses <- fetch_survey(rpr_survey_id)
 
-# Save permenant raw files and associated documentation for archvial purposes
+# Save permanent raw files and associated documentation for archival purposes
 saveRDS(rpr_responses, here("data","raw","private","raw_rpr_responses.rds"))
-saveRDS(rpr_survey_questions, here("data","raw","private","raw_rpr_survey_questions.rds"))
-saveRDS(rpr_survey_metadata, here("data","raw","private","raw_rpr_survey_metadata.rds"))
+saveRDS(rpr_survey_questions, here("data","raw","public","raw_rpr_survey_questions.rds"))
+saveRDS(rpr_survey_metadata, here("data","raw","public","raw_rpr_survey_metadata.rds"))
 
 
 # De-identify file to create public raw version

### 2022-12-07 procedure/code/203_results.Rmd
Update raw results, including frequencies and cross tabs by methods (quant, qual, mixed) and field.

@@
 ```{r beliefs-stats-by-subfield}
-group_by(survey_resp, Q3) %>%
+group_by(survey_resp, Q3_recoded) %>%
   summarise(
@@
 ```{r beliefs-anova}
-aov(belief ~ Q3, data=survey_resp) %>% summary()
+aov(belief ~ Q3_recoded, data=survey_resp) %>% summary()
 ```

### 2022-12-07 procedure/code/202_preprocess.R

@@ -7,23 +7,18 @@ library(tidyverse)
 #- PERFORM DESCRIPTIVE ANALYSIS -#
 #-                              -#
 #--------------------------------#
-survey_resp <- read.csv(here("data","derived","public","hegsrr_analysis_reprod.csv"))
+survey_resp <- readRDS(here("data","derived","public","analysis_hegs_rpr.rds"))
 
 #- Define variable lists -#
-demo <- c("Q1", "Q2", "Q3","Q4","Q5", "Q18", "Q19", "Q20", "Q21", "Q22")
+demo <- c("Q1", "Q2", "Q3_recoded","Q4","Q5", "Q18", "Q19", "Q20")
 
-practice <- c("Q7a","Q7a_1","Q7a_3", 
+practice <- c("Q7a","Q7a_1", "Q7a_3", 
               "Q7b","Q7b_1",
               "Q7c","Q7c_1","Q7c_2","Q7c_3",
               "Q7d","Q7d_1","Q7d_2",
-              "Q7e","Q7e_1",
-              "Q9_1", "Q9_2", "Q9_3", "Q9_4",
-              "Q9_5", "Q9_6", "Q9_7",
-              "Q11_1", "Q11_2", "Q11_3",
-              "Q12_1", "Q12_2", "Q12_3", "Q12_4")
+              "Q7e","Q7e_1")
 
-importance <- c("Q8_1", "Q8_2", "Q8_3", 
-                "Q8_4", "Q8_5", "Q8_6",
+importance <- c("Q13_1", "Q13_2",
                 "Q17_1", "Q17_2", "Q17_3", "Q17_4",
                 "Q17_5", "Q17_6", "Q17_7", "Q17_8",
                 "Q17_9", "Q17_10")
@@ -33,10 +28,10 @@ barriers <- c("Q14_1", "Q14_2", "Q14_3", "Q14_4",
               "Q14_9", "Q14_10", "Q14_11", "Q14_12",
               "Q16", "Q19_9_TEXT", "Q20_5_TEXT", "Q21_7_TEXT")
 
-numeric_vars <- c(demo, practice, importance, barriers)
+numeric_vars <- c(demo, practice, importance)
 
 
-char_vars <- c("Q3_5_TEXT", "Q6", "Q7a_2", "Q12a", 
+char_vars <- c("Q6", "Q7a_2", "Q12a", 
                "Q13_1_1", "Q13_2_1", "Q15", "Q16_5_TEXT",
                "Q17a")
 
[…]

### 2022-12-13 procedure/code/201_clean.R
Updated cleaning program to revise Q3 recoding and convert character variables to ordered factors.

@@ -1,5 +1,5 @@
 # list of required packages
-packages = c("here","tidyverse")
+packages = c("here","tidyverse","table1")
 
 # load and install required packages
 package.check <- lapply(
@@ -33,13 +33,12 @@ int_hegs_rpr <- raw_hegs_rpr %>% filter(Progress > 70 & Q1 != "Under 18")
 table(toupper(int_hegs_rpr$Q3_5_TEXT))
 
 #-Open response areas of specialization to recode-#
-hum_list  <- c("ECONOMIC GEOGRAPHY","POLITICAL GEOGRAPHY", "POLITICAL SCIENCE", "SOCIO-ANTHROPOLOGY",
+hum_list  <- c("ECONOMIC GEOGRAPHY","POLITICAL GEOGRAPHY", "POLITICAL SCIENCE", "SOCIO-ANTHROPOLOGY", "MOBILITIES",
               "SOCIOLOGY","TRANSPORT GEOGRAPHY","TRANSPORTATION","TRANSPORTATION ENGINEERING", "URBAN GEOGRAPHY")
 
-phys_list <- c("PALEOBOTANY","PALEOCLIMATOLOGY")
+phys_list <- c("BIOGEOGRAPHY","PALEOBOTANY","PALEOCLIMATOLOGY")
 
-nat_list  <- c("BIOGEOGRAPHY","CITY PLANNING, SUSTAINABILITY TRANSFORMATIONS","ENVIRONMENTAL ARCHAEOLOGY","ARCHAEOLOGY",
-              "MOBILITIES")
+nat_list  <- c("CITY PLANNING, SUSTAINABILITY TRANSFORMATIONS","ENVIRONMENTAL ARCHAEOLOGY","ARCHAEOLOGY")
 
 gis_list  <- c("GEOSPATIAL INFORMATION SCIENCE", "SPATIAL ECONOMETRICS", "CARTOGRAPHY","REMOTE SENSING",
               "REMOTE SENSING OF ENVIRONMENT")
@@ -49,10 +48,10 @@ int_hegs_rpr <- int_hegs_rpr %>%
                                         ifelse(toupper(Q3_5_TEXT) %in% phys_list, 2, 
                                             ifelse(toupper(Q3_5_TEXT) %in% nat_list, 3, 
                                                    ifelse(toupper(Q3_5_TEXT) %in% gis_list, 4, Q3))))))
-levels(int_hegs_rpr$Q3_recoded) <- c("Human geography", 
[…]

### 2022-12-13 procedure/code/202_preprocess.R
Updated analysis code to generate draft report tables.

@@ -1,6 +1,7 @@
 library(here)
 library(tidyverse)
-
+library(table1)
+library(flextable)
 
 #--------------------------------#
 #-                              -#
@@ -8,6 +9,251 @@ library(tidyverse)
 #-                              -#
 #--------------------------------#
 survey_resp <- readRDS(here("data","derived","public","analysis_hegs_rpr.rds"))
+
+#-----------------------#
+#-- Cross tabulations --#
+#-----------------------#
+
+#- Table 1) Summary Characteristics of Respondents -#
+
+table1::label(survey_resp$Q3_recoded) <- "Subdiscipline"
+table1::label(survey_resp$Q4)         <- "Methods"
+table1::label(survey_resp$Q18)        <- "Size of lab"
+table1::label(survey_resp$Q19)        <- "Title"
+table1::label(survey_resp$Q20)        <- "Gender"
+table1::label(survey_resp$Q1)         <- "Age"
+
+Q3_table1 <- table1::table1(~Q4 + Q18 + Q19 + Q20 + Q1  | Q3_recoded, data = survey_resp)
+Q4_table1 <- table1::table1(~Q3_recoded + Q18 + Q19 + Q20 + Q1  | Q4, data = survey_resp)
+
+# Output tables using write table and flextable
+write.table(Q3_table1 , here("results","tables","Table1_Summary_discipline.csv"), col.names = T, row.names=F, append= T, sep=',')
+write.table(Q4_table1 , here("results","tables","Table1_Summary_method.csv"), col.names = T, row.names=F, append= T, sep=',')
+
+t1flex(Q3_table1) %>% 
+  save_as_docx(path = here("results","tables","MSWord","Table1_Summary_discipline.docx"))
+
+t1flex(Q4_table1) %>% 
+  save_as_docx(path = here("results","tables","MSWord","Table1_Summary_method.docx"))
+
+#---------------------------------------------------------------------------------------
+#- Table 2) Definitions of Reproducibility -#
+table(survey_resp$Q17_1)
+table1::label(survey_resp$Q5) <- "Familiarity with reproducibility"
+
+Q3_table2 <- table1::table1(~Q5  | Q3_recoded, data = survey_resp)
+Q4_table2 <- table1::table1(~Q5  | Q4, data = survey_resp)
+
+# Output tables using write table and flextable
[…]

### 2022-12-13 procedure/code/202_preprocess.R
Creating binary versions of familiarity, practices, and barriers variables and constructing aggregate measures for each and outputting to .csv and MSWord tables.

@@ -245,9 +245,112 @@ t1flex(Q4_table8) %>%
 #- Summary Table for Results Section -#
 
 #- Summary measure on familiarity, practices, and barriers
-#------- Familiarity : threshold is "somewhat"
-#------- Practices :   threshold is "most of the time"
-#------- Barriers :    threshold is "occasionally"
+#------- Familiarity : threshold is "somewhat"  (Q7a + Q7b + Q7c + Q7d + Q7e)
+#------- Practices :   threshold is "most of the time" (Q7a_1 + Q7b_1 + Q7c_1 + Q7d_1 + Q7e_1)
+#------- Barriers :    threshold is "occasionally"  (Q14_1 + Q14_2 + Q14_3 + Q14_4 + Q14_5)
+
+table(survey_resp$Q14_1)
+levels(survey_resp$Q7a_1)
+survey_resp <- survey_resp %>% mutate(#RECODE FAMILIARITY VARIABLES
+                                      Q7a_bin = as.numeric(as.character(recode(Q7a, "To a great extent" = "1",
+                                                                               "Somewhat" = "1",
+                                                                               .default = "0"))),
+                                      Q7b_bin = as.numeric(as.character(recode(Q7b, "To a great extent" = "1",
+                                                                               "Somewhat" = "1",
+                                                                               .default = "0"))),
+                                      Q7c_bin = as.numeric(as.character(recode(Q7c, "To a great extent" = "1",
+                                                                               "Somewhat" = "1",
+                                                                               .default = "0"))),
+                                      Q7d_bin = as.numeric(as.character(recode(Q7d, "To a great extent" = "1",
+                                                                                "Somewhat" = "1",
+                                                                                .default = "0"))),
+                                      Q7e_bin = as.numeric(as.character(recode(Q7e, "To a great extent" = "1",
+                                                                               "Somewhat" = "1",
+                                                                               .default = "0"))),
+                                      #RECODE PRACTICES VARIABLES
+                                      Q7a_1_bin = as.numeric(as.character(recode(Q7a_1, "Always" = "1",
+                                                                               "Most of the time" = "1",
+                                                                               .default = "0"))),
+                                      Q7b_1_bin = as.numeric(as.character(recode(Q7b_1, "Always" = "1",
+                                                                               "Most of the time" = "1",
+                                                                               .default = "0"))),
[…]

### 2022-12-14 docs/manuscript/manuscript.tex

@@
 
+\subsection*{Survey Demographics}
 A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis.
@@
 The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
+ADD COMPARISON TO SAMPLE FRAME.
 
-\subsection{Survey Demographics}
+\subsection*{PCAish Summary Across Dimensions}
+This subsection will pivot on Table 9 that has rows representing PCA-like aggregate measures of 1) definition, 2) Familiarity 3)practice, 4) Barriers and two groups of rows (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).
 
-\subsection{Definition of Reproducibility}
+\subsubsection*{Definition of Reproducibility}
 Definition Questions and Q8 about beliefs about the interpretation for reproductions.
@@
 
-\subsection{Familiarity and Frequency of Practices}
-Summary of Table showing Familiarity 1) all survey, 2) Methods, 3) Subfield Split
-Summary of Table showing Implementation 1) all survey, 2) Methods, 3) Subfield Split
+\subsubsection*{Familiarity with Reproduciblity Practices}
+
+\subsubsection*{Frequency of Reproduciblity Practices}
+
+Q9 will feather in to contextualize the measure
+
+\subsubsection*{Barriers to Reproduction}
+Discussion of details from Q14
 
 \subsection{Actual Reproductions}
-Summary of Q10-Q12
-
-\subsection{Barriers to Reproduction}
-Q14
+Start with the outline of what the population is here because not all respondents answered these questions.
+Start with descriptives that show this sub-sample of respondents.
+Summary discussion of Q10-Q12.
 

### 2022-12-14 docs/manuscript/manuscript.tex
Results - Tables Update 1

@@
 The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
-ADD COMPARISON TO SAMPLE FRAME.
 
-\subsection*{PCAish Summary Across Dimensions}
-This subsection will pivot on Table 9 that has rows representing PCA-like aggregate measures of 1) definition, 2) Familiarity 3)practice, 4) Barriers and two groups of rows (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).
+\begin{itemize}
+    \item Include a comparison of sample to the sample frame along the dimensions available from the frame. (Table 0)
+    \item Include a summary of the key in sample characteristics (Table 1?).
+Rows - Title, Citations (pulled from frame), Gender; cols - methods and subfields.
+\textcolor{red}{Does this need to be a table?
+I am not sure any of these demographics really matter to our analysis.
+That is unless we plan to look at some measure across seniority or 'impact', which we could do.}
+\end{itemize}
+
+\subsection*{Aggregate Measures Along 4-Dimensions}
+This subsection will pivot on Table 9 that has rows representing aggregate measures of 1) definition, 2) Familiarity 3) Experience, 4) Barriers and two groups of columns representing (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).
+
+\begin{itemize}
+    \item Overall story is that collectively geographers are aware of reproducible research practices, but don't have a matching amount of direct experience using those practices.
+There are also many perceived barriers to conducting reproducible research.
+    \item High - Low gradient across all aggregate measures from Quant-MM-Qual.
+    \item High - Low familiarity gradient Method-Physs-NS-H
+    \item Likely need to comment on survey including many reproducible research practices that center on, or are easier to accomplish with, when using quantitative data and methods.
+This reality may automatically deflate the aggregate measures of certain sub-group.
+We can use the response to Q8f as a filter to explore this issue.
+\textcolor{red}{For conclusions - Points to the emphasis on quantitative, particularly computational, focus in the reproducibility literature.
+Suggests a meed to examine what reproducibility means in the context of geography's qual, NS, and human traditions.}
+\end{itemize}
 
 \subsubsection*{Definition of Reproducibility}
-Definition Questions and Q8 about beliefs about the interpretation for reproductions.
-Dig into those respondents that had variations in beliefs on Q8 sequence.
-Q17 about importance of reproduction.
-Close with Q13.
+\begin{itemize}
+    \item Self-reported definition (Q6) analysis.
+    \item Interpretations of reproductions (Q8) - focus on Q8a, Q8b, Q8e as these provide the most direct information about how a respondent processes the evidence provided by a reproduction.
+Match Q8e with 17c, 17e, 17f which are importance questions about credibility.
+Match Q8b with 17a which are both about validity.
+    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
+    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
+\end{itemize}
 

### 2022-12-14 docs/manuscript/manuscript.tex
Adjusted Results Plan

@@
 \begin{itemize}
-    \item Include a comparison of sample to the sample frame along the dimensions available from the frame. (Table 0)
-    \item Include a summary of the key in sample characteristics (Table 1?).
-Rows - Title, Citations (pulled from frame), Gender; cols - methods and subfields.
-\textcolor{red}{Does this need to be a table?
-I am not sure any of these demographics really matter to our analysis.
-That is unless we plan to look at some measure across seniority or 'impact', which we could do.}
+    \item Include a text summary of the key in sample characteristics summarized in Table 1a and 1b.
 \end{itemize}
@@
 
-\subsubsection*{Definition of Reproducibility}
-\begin{itemize}
-    \item Self-reported definition (Q6) analysis.
-    \item Interpretations of reproductions (Q8) - focus on Q8a, Q8b, Q8e as these provide the most direct information about how a respondent processes the evidence provided by a reproduction.
-Match Q8e with 17c, 17e, 17f which are importance questions about credibility.
-Match Q8b with 17a which are both about validity.
-    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
-    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
-\end{itemize}
-
 \subsubsection*{Familiarity with Reproduciblity Practices}
@@
 Summary discussion of Q10-Q12.
+
+\subsection*{Definition of Reproducibility}
+\begin{itemize}
+    \item Self-reported definition (Q6) analysis: Qualitative analysis that will present a typology of definitions by combination of the Q,Q,M and M,P,NS,H splits that match on the 8 category coding of the provided definitions.
+    \item Interpretations (Q8) and Importance (Q17) of reproductions: Develop a split that distinguishes between Qs that focus on epistemology Q8a+Q8b+Q8f+17a, as these provide the most direct information about how a respondent processes the evidence provided by a reproduction; and Qs that focus on reproducibility as a quality of a study Q8e+Q8c+17c+17e+17f.
+We will explore how these question groups crosstab with the typologies we draw from Q6.
+Initial assumption is that many will support reproduction as a study characteristic or label, and less will link it with epistomological function.
+Examine by subfields and methods, which we expect to align with typologies from Q6.
+    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other open science goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
+    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
+\end{itemize}
 

### 2022-12-15 docs/manuscript/manuscript.tex
Update survey response demographics

@@
 Complete documentation of the procedures and materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
+That repository connects to a Github repository which hosts the anonymized dataset and code used to create all results and supplemental materials and along with a complete history of their development.
 Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
-We amended that plan at the close of data collection to reflect a change in stopping rule we used to end the survey.
+We later amended that plan to reflect a change in stopping rule we used to end the survey and to include additional statistical analyses we conducted after viewing the survey response.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Survey Response Demographics}
+A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis. 
+The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. 
+The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards.
+The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
+Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
+The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
+Respondents were similarly well balanced across the disciplinary subfields - Human Geography (30.7\%), Physical Geography (29.8\%), Nature and Society (10.1\%), Geographic Methods and GISci (28.0\%); and methodological approaches - quantitative (42.2\%), qualitative (18.3\%), and mixed-methods (39.0\%) research.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Statistical Analyses}
@@
 
-\subsection*{Survey Demographics}
-A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis.
-The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent.
-The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards.
-The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
-
-\begin{itemize}
-    \item Include a text summary of the key in sample characteristics summarized in Table 1a and 1b.
-\end{itemize}
-
+%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Aggregate Measures Along 4-Dimensions}
@@
 
-\subsubsection*{Familiarity with Reproduciblity Practices}
-
-\subsubsection*{Frequency of Reproduciblity Practices}
-
-Q9 will feather in to contextualize the measure
-
-\subsubsection*{Barriers to Reproduction}
-Discussion of details from Q14
-
-\subsection{Actual Reproductions}
-Start with the outline of what the population is here because not all respondents answered these questions.
-Start with descriptives that show this sub-sample of respondents.
-Summary discussion of Q10-Q12.
-
-\subsection*{Definition of Reproducibility}
+%%%%%%%%%%%
+\subsubsection*{Definition of Reproducibility}
 \begin{itemize}
@@
 
+%%%%%%%%%%%
+\subsubsection*{Familiarity with Reproduciblity Practices}
+
+%%%%%%%%%%%
+\subsubsection*{Frequency of Reproduciblity Practices}
+Q9 will feather in to contextualize the measure
+
+%%%%%%%%%%%
+\subsubsection*{Barriers to Reproduction}
+Discussion of details from Q14
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Actual Reproductions}
+Start with the outline of what the population is here because not all respondents answered these questions.
+Start with descriptives that show this sub-sample of respondents.
+Summary discussion of Q10-Q12.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\begin{itemize}
+    \item The reproducibility literature emphasizes quantitative, particularly computational, forms of research.
+This emphasis necessarily carried over into our survey instrument, which may automatically lower response scores for researchers not working in these areas (e.g., qualitative, human geography).
+These scores do reflect their present level of understanding, but the practices may not be relevant to their methods or epistomologies.
+This fact suggests a meed to examine what reproducibility means in the context of geography's qual, NS, and human traditions.
+    \item A standing question is how should geographic research approaches be designed to efficiently generate reliable knowledge.
+\end{itemize}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Conclusion}
-A standing question is how should geographic research approaches be designed to efficiently generate reliable knowledge.
 

### 2022-12-15 procedure/code/201_clean.R
Updated analysis code to apply ordering to factor variables and updated flextable options to format MSWord output.

@@ -1,5 +1,5 @@
 # list of required packages
-packages = c("here","tidyverse","table1")
+packages = c("here","tidyverse","table1","officer")
 
 # load and install required packages
 package.check <- lapply(
@@ -196,69 +196,6 @@ table(int_hegs_rpr$Q13_2_1, int_hegs_rpr$Q13_2, useNA = "always")
 summary(int_hegs_rpr$Q13_1)
 summary(int_hegs_rpr$Q13_2)
 
-
-#----------------------------------------------------------#
-
-#- Convert character to ordered factors-#
-
-#----------------------------------------------------------#
-# convert agree questions into ordered factors
-values <- c("Strongly disagree", "Disagree", "Agree", "Strongly agree")
-questions <- c("Q8_1", "Q8_2", "Q8_3", "Q8_4","Q8_5", "Q8_6")
-survey_resp[questions] <- lapply(survey_resp[questions], 
-                                 factor, 
-                                 levels=values,
-                                 ordered = TRUE,
-                                 exclude=c("", "Don't Know"))
-
-# convert yes/no questions into ordered factors
-values <- c("Yes", "No", "Don't Know")
-questions <- c("Q9_1", "Q9_2", "Q9_3", "Q9_4", "Q9_5", "Q9_6", "Q9_7")
-survey_resp[questions] <- lapply(survey_resp[questions], 
-                                 factor, 
-                                 levels=values,
-                                 ordered = TRUE,
-                                 exclude="")
-
-# convert proportion questions into ordered factors
-values <- c("All", "Some", "None", "Don't Know")
-questions <- c("Q11_1", "Q11_2", "Q11_3")
-survey_resp[questions] <- lapply(survey_resp[questions], 
-                                 factor, 
-                                 levels=values,
-                                 ordered = TRUE,
-                                 exclude="")
-
-# convert yes/no proportion questions into ordered factors
-values <- c("Yes, all", "Yes, some", "No", "Did not attempt")
-questions <- c("Q12_1", "Q12_2", "Q12_3", "Q12_4")
-survey_resp[questions] <- lapply(survey_resp[questions], 
-                                 factor, 
-                                 levels=values,
-                                 ordered = TRUE,
-                                 exclude="")
-
-# convert frequency questions into ordered factors
-values <- c("Frequently", "Occasionally", "Rarely", "Never")
[…]

### 2022-12-15 procedure/code/202_preprocess.R

@@ -2,6 +2,7 @@ library(here)
 library(tidyverse)
 library(table1)
 library(flextable)
+library(officer)
 
 #--------------------------------#
 #-                              -#
@@ -9,6 +10,79 @@ library(flextable)
 #-                              -#
 #--------------------------------#
 survey_resp <- readRDS(here("data","derived","public","analysis_hegs_rpr.rds"))
+
+#----------------------------------------------------------#
+
+#- Convert character to ordered factors-#
+
+#----------------------------------------------------------#
+# convert agree questions into ordered factors
+values <- c("Strongly agree", "Agree", "Disagree","Strongly disagree")
+questions <- c("Q8_1", "Q8_2", "Q8_3", "Q8_4","Q8_5", "Q8_6")
+survey_resp[questions] <- lapply(survey_resp[questions], 
+                                 factor, 
+                                 levels=values,
+                                 ordered = TRUE,
+                                 exclude=c("", "Don't Know"))
+
+# convert yes/no questions into ordered factors
+values <- c("Yes", "No", "Don't Know")
+questions <- c("Q9_1", "Q9_2", "Q9_3", "Q9_4", "Q9_5", "Q9_6", "Q9_7")
+survey_resp[questions] <- lapply(survey_resp[questions], 
+                                 factor, 
+                                 levels=values,
+                                 ordered = TRUE,
+                                 exclude="")
+
+# convert proportion questions into ordered factors
+values <- c("All", "Some", "None", "Don't Know")
+questions <- c("Q11_1", "Q11_2", "Q11_3")
+survey_resp[questions] <- lapply(survey_resp[questions], 
+                                 factor, 
+                                 levels=values,
+                                 ordered = TRUE,
+                                 exclude="")
+
+# convert yes/no proportion questions into ordered factors
+values <- c("Yes, all", "Yes, some", "No", "Did not attempt")
+questions <- c("Q12_1", "Q12_2", "Q12_3", "Q12_4")
+survey_resp[questions] <- lapply(survey_resp[questions], 
+                                 factor, 
+                                 levels=values,
+                                 ordered = TRUE,
+                                 exclude="")
+
+# convert frequency questions into ordered factors
[…]

### 2022-12-15 procedure/code/201_clean.R
Added ordered factor code back to clean program to apply storage type changes to permanent analysis file and re-ran tables.

@@ -196,6 +196,68 @@ table(int_hegs_rpr$Q13_2_1, int_hegs_rpr$Q13_2, useNA = "always")
 summary(int_hegs_rpr$Q13_1)
 summary(int_hegs_rpr$Q13_2)
 
+#----------------------------------------------------------#
+
+#- Convert character to ordered factors-#
+
+#----------------------------------------------------------#
+# convert agree questions into ordered factors
+values <- c("Strongly agree", "Agree", "Disagree","Strongly disagree")
+questions <- c("Q8_1", "Q8_2", "Q8_3", "Q8_4","Q8_5", "Q8_6")
+int_hegs_rpr[questions] <- lapply(int_hegs_rpr[questions], 
+                                 factor, 
+                                 levels=values,
+                                 ordered = TRUE,
+                                 exclude=c("", "Don't Know"))
+
+# convert yes/no questions into ordered factors
+values <- c("Yes", "No", "Don't Know")
+questions <- c("Q9_1", "Q9_2", "Q9_3", "Q9_4", "Q9_5", "Q9_6", "Q9_7")
+int_hegs_rpr[questions] <- lapply(int_hegs_rpr[questions], 
+                                 factor, 
+                                 levels=values,
+                                 ordered = TRUE,
+                                 exclude="")
+
+# convert proportion questions into ordered factors
+values <- c("All", "Some", "None", "Don't Know")
+questions <- c("Q11_1", "Q11_2", "Q11_3")
+int_hegs_rpr[questions] <- lapply(int_hegs_rpr[questions], 
+                                 factor, 
+                                 levels=values,
+                                 ordered = TRUE,
+                                 exclude="")
+
+# convert yes/no proportion questions into ordered factors
+values <- c("Yes, all", "Yes, some", "No", "Did not attempt")
+questions <- c("Q12_1", "Q12_2", "Q12_3", "Q12_4")
+int_hegs_rpr[questions] <- lapply(int_hegs_rpr[questions], 
+                                 factor, 
+                                 levels=values,
+                                 ordered = TRUE,
+                                 exclude="")
+
+# convert frequency questions into ordered factors
+values <- c("Frequently", "Occasionally", "Rarely", "Never")
+questions <- c("Q14_1", "Q14_2", "Q14_3", "Q14_4", "Q14_5", "Q14_6", "Q14_7", "Q14_8", "Q14_9", "Q14_10", "Q14_11", "Q14_12")
+int_hegs_rpr[questions] <- lapply(int_hegs_rpr[questions], 
[…]

### 2022-12-15 procedure/code/202_preprocess.R
Removed ordered factoring code from analysis program.

@@ -11,69 +11,6 @@ library(officer)
 #--------------------------------#
 survey_resp <- readRDS(here("data","derived","public","analysis_hegs_rpr.rds"))
 
-#----------------------------------------------------------#
-
-#- Convert character to ordered factors-#
-
-#----------------------------------------------------------#
-# convert agree questions into ordered factors
-values <- c("Strongly agree", "Agree", "Disagree","Strongly disagree")
-questions <- c("Q8_1", "Q8_2", "Q8_3", "Q8_4","Q8_5", "Q8_6")
-survey_resp[questions] <- lapply(survey_resp[questions], 
-                                 factor, 
-                                 levels=values,
-                                 ordered = TRUE,
-                                 exclude=c("", "Don't Know"))
-
-# convert yes/no questions into ordered factors
-values <- c("Yes", "No", "Don't Know")
-questions <- c("Q9_1", "Q9_2", "Q9_3", "Q9_4", "Q9_5", "Q9_6", "Q9_7")
-survey_resp[questions] <- lapply(survey_resp[questions], 
-                                 factor, 
-                                 levels=values,
-                                 ordered = TRUE,
-                                 exclude="")
-
-# convert proportion questions into ordered factors
-values <- c("All", "Some", "None", "Don't Know")
-questions <- c("Q11_1", "Q11_2", "Q11_3")
-survey_resp[questions] <- lapply(survey_resp[questions], 
-                                 factor, 
-                                 levels=values,
-                                 ordered = TRUE,
-                                 exclude="")
-
-# convert yes/no proportion questions into ordered factors
-values <- c("Yes, all", "Yes, some", "No", "Did not attempt")
-questions <- c("Q12_1", "Q12_2", "Q12_3", "Q12_4")
-survey_resp[questions] <- lapply(survey_resp[questions], 
-                                 factor, 
-                                 levels=values,
-                                 ordered = TRUE,
-                                 exclude="")
-
-# convert frequency questions into ordered factors
-values <- c("Frequently", "Occasionally", "Rarely", "Never")
-questions <- c("Q14_1", "Q14_2", "Q14_3", "Q14_4", "Q14_5", "Q14_6", "Q14_7", "Q14_8", "Q14_9", "Q14_10", "Q14_11", "Q14_12")
-survey_resp[questions] <- lapply(survey_resp[questions], 
-                                 factor, 
-                                 levels=values,
-                                 ordered = TRUE,
-                                 exclude="")
-
[…]

### 2023-01-11 docs/manuscript/manuscript.tex

@@
 \newtheorem{notation}{Notation}
+
+\usepackage{tabularx}
+\usepackage{booktabs,caption}
+\usepackage{threeparttable}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+\begin{description}
+\setlength{\itemindent}{0ex}
+    \item[\textbf{(Q1)}] How do geographic researchers define reproduciblity?
+    \item[\textbf{(Q2)}] How familiar are geographic researchers with different reproducible research practices?
+    \item[\textbf{(Q3)}] How often do geographic researchers use different reproducibile research practices when conducting their own studies? 
+    \item[\textbf{(Q4)}] What factors hinder the reproduction of geographic research?
+\end{description}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \subsection*{Survey Response Demographics}
-A total of \textit{n}=215 of the authors we contacted completed the online survey with information sufficient for analysis. 
+A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
 The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. 
@@
 
+\newpage
+
 %%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Statistical Analyses}
+\subsection*{Statistical Methods}
+We conduct two statistical analyses of the survey response. 
+First, we use descriptive statistical summaries to address our four questions about how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
+To assess the familiarity of geographic researchers with reproducible and open science research practices, we created a single aggregate variable by recoding and then summing these measures. 
+This procedure produced a single aggregate variable with a minimum value of 0 and a maximum value of 5.
+
+We also examine group-wise differences in each aggregated measure by disciplinary subfield and methodological approach to identify variation across the discipline's many traditions.
+This analysis is based on our full sample (\textit{n}=218), but excludes 29 participants who did not provide complete responses to the relevant survey questions.
+
+Second, we conduct an analysis of the experience of geographic researchers who have attempted reproductions of prior work. 
+We examine what motivates geographic researchers to attempt to reproduce another study and how successful researcher attempting reproductions were at recreating existing results. 
+We also investigate why
+
+The full methodological details of our statistical analyses, and a complete history of our response coding a variable construction is included in the Github repository linked to OSF repository that accompanies this paper.
+All of the results presented in this paper can be reproduced using the materials in that repository.
 
@@
 This subsection will pivot on Table 9 that has rows representing aggregate measures of 1) definition, 2) Familiarity 3) Experience, 4) Barriers and two groups of columns representing (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).
+
+\begin{table}[h]
+    \centering
+    \begin{threeparttable}
+    \caption{Descriptive summary of survey results}
+    \begin{tabular}{l c c c c c c c c c c}
+         \hline
+                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & \\
+         Measure    & HU & PH & NS & GIS            & & QNT & QUL & MIX              & & Overall \\
+         \hline
+         Definition  &  & & & & & & & & & \\
+         Familiarity &  \begin{tabular}[c]{@{}c@{}}2.35\\ (1.36)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}3.71\\ (0.98)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}2.28\\ (1.76)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}3.97\\ (0.86)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}3.75\\ (0.98)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}1.75\\ (1.30)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}3.56\\ (1.22)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}3.26\\ (1.36)\end{tabular}\\
+
+         Experience  &  \begin{tabular}[c]{@{}c@{}}0.60\\ (0.80)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}2.06\\ (1.18)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.18\\ (0.96)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}1.85\\ (1.38)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}1.63\\ (1.32)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}0.48\\ (0.68)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}1.69\\ (1.24)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}1.44\\ (1.28)\end{tabular}\\
+
+         Barriers    &  \begin{tabular}[c]{@{}c@{}}7.32\\ (3.57)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}8.31\\ (3.00)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}7.44\\ (3.20)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}9.31\\ (2.79)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}8.78\\ (2.80)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}5.97\\ (3.83)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}8.58\\ (2.96)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}8.20\\ (3.24)\end{tabular}\\
+                     & & & & & & & & & &\\
+         N           & 67 & 65 & 22 & 61 & & 92 & 40 & 85 & & 218 \\
+         Missing     & 14 & 4  & 4  & 6  & & 6 & 9 & 14 & & 29 \\
+        \hline
+    \end{tabular}
+    \begin{tablenotes}
+        \footnotesize
+        \item \textit{HU} Human Geography, \textit{PH} Physical Geography, \textit{NS} Nature and Society, \textit{GIS} GIScience and Methods; \textit{QNT} Quantitative, \textit{QUL} Qualitative, \textit{MIX} Mixed Methods.
+    \end{tablenotes}
+    \label{tab:overview}
+    \end{threeparttable}
+\end{table}
 

### 2023-01-11 docs/manuscript/manuscript.tex
Update results

@@
 We conduct two statistical analyses of the survey response. 
-First, we use descriptive statistical summaries to address our four questions about how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
-To assess the familiarity of geographic researchers with reproducible and open science research practices, we created a single aggregate variable by recoding and then summing these measures. 
-This procedure produced a single aggregate variable with a minimum value of 0 and a maximum value of 5.
+First, we used descriptive statistical summaries of the participant response to address our four questions about how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
+For each question, we created a single variable that aggregates a participant's response across a subset of survey questions related to that issue.
+
+We measured each participant's definition of reproducibility relative to the definition provided by the \citet{NASEM2019}. 
+Before being provided a standardized definition, each participant was asked to provide their own definition of reproducibility. 
+We coded these text responses along four dimensions of data, procedure, result, and context similarity.  
+To assess researcher familiarity with reproducible practices, we created a single variable, \textit{Familiarity}, that counts the number of practices a researcher was 'somewhat' or 'very' familiar with.
+To assess researcher experience with reproducible practices, we created a single variable, \textit{Experience}, that counts the number of practices a researcher use 'most of the time' or 'always' when conducting their own research.
+Our \textit{Familiarity} and \textit{Experience} variables both range from 0-5. 
+We similarly created a single measure, \textit{Barriers} that counts the number of factors a researcher believe 'frequently' or 'occasionally' contributed to a lack of reproducibility. 
+This \textit{Barriers} variable ranges from 0-12.
 
@@
 Second, we conduct an analysis of the experience of geographic researchers who have attempted reproductions of prior work. 
+A total of \textit{n}=102 of the authors we contacted reported attempting to reproduce a prior study. 
 We examine what motivates geographic researchers to attempt to reproduce another study and how successful researcher attempting reproductions were at recreating existing results. 
-We also investigate why
+We also investigate why researchers were unable to reproduce results.
 
@@
 \subsubsection*{Definition of Reproducibility}
+Coded definitions are relative to the NASEM definition. The NASEM state SAME data, procedures, and results and implies SAME context because data is not recollected. 
 \begin{itemize}
@@
 %%%%%%%%%%%
-\subsubsection*{Familiarity with Reproduciblity Practices}
-
-%%%%%%%%%%%
-\subsubsection*{Frequency of Reproduciblity Practices}
-Q9 will feather in to contextualize the measure
-
-%%%%%%%%%%%
-\subsubsection*{Barriers to Reproduction}
-Discussion of details from Q14
+\subsubsection*{Reproducible Research Practices and Barriers to Reproducibility}
+This will be a discussion of how subfields differ on the specific questions used to create the aggregate variables presented above. 
+The purpose is to enrich the overall picture by identifying differences within the aggregate measures.
+\begin{itemize}
+    \item Use Q9 to contextualize the frequency measure.
+    \item Use details from Q14 to enrich the discussion of barriers
+\end{itemize}
 
@@
 \subsection*{Actual Reproductions}
+A total of \textit{n}=102 of the authors we contacted reported attempting to reproduce a prior study.
+
 Start with the outline of what the population is here because not all respondents answered these questions.

### 2023-01-12 docs/manuscript/manuscript.tex
Update survey summary in results

@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Survey Design}
+\subsection*{Sampling Frame}
 Our target population of interest is researchers who have recently published in the field of geography. 
@@
 
+\subsection*{Survey Instrument}
 The survey instrument used in this study is available through the Survey of Reproducibility in Geographic Research Repository.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Survey Response Demographics}
-A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
-The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. 
-The refusal rate was 3.1 percent.\endnote{All outcome rates are reported using \citet{aaporstandards} standards.
-The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
-Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
-The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
-Respondents were similarly well balanced across the disciplinary subfields - Human Geography (30.7\%), Physical Geography (29.8\%), Nature and Society (10.1\%), Geographic Methods and GISci (28.0\%); and methodological approaches - quantitative (42.2\%), qualitative (18.3\%), and mixed-methods (39.0\%) research.
-
-\newpage
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Statistical Methods}
-We conduct two statistical analyses of the survey response. 
-First, we used descriptive statistical summaries of the participant response to address our four questions about how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
+\subsection*{Analytical Approach}
+We conduct two statistical analyses of the survey response
+\endnote{The full methodological details of our statistical analyses, and a complete history of our response coding a variable construction is included in the Github repository linked to OSF repository that accompanies this paper.
+All of the results presented in this paper can be independently reproduced using the materials in that repository.}.
+First, we used descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
 For each question, we created a single variable that aggregates a participant's response across a subset of survey questions related to that issue.
@@
 We also examine group-wise differences in each aggregated measure by disciplinary subfield and methodological approach to identify variation across the discipline's many traditions.
-This analysis is based on our full sample (\textit{n}=218), but excludes 29 participants who did not provide complete responses to the relevant survey questions.
 
 Second, we conduct an analysis of the experience of geographic researchers who have attempted reproductions of prior work. 
-A total of \textit{n}=102 of the authors we contacted reported attempting to reproduce a prior study. 
 We examine what motivates geographic researchers to attempt to reproduce another study and how successful researcher attempting reproductions were at recreating existing results. 
 We also investigate why researchers were unable to reproduce results.
-
-The full methodological details of our statistical analyses, and a complete history of our response coding a variable construction is included in the Github repository linked to OSF repository that accompanies this paper.
-All of the results presented in this paper can be reproduced using the materials in that repository.
 
@@
 %%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Survey Response Demographics}
+A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
+The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. 
+The refusal rate was 3.1 percent.
+\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
+The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
+Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
+The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
+Respondents were similarly well balanced across the disciplinary subfields - human geography (30.7\%), physical geography (29.8\%), nature and society (10.1\%), geographic methods and GIScience (28.0\%); and methodological approaches - quantitative (42.2\%), qualitative (18.3\%), and mixed-methods (39.0\%) research.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
 \subsection*{Aggregate Measures Along 4-Dimensions}
-This subsection will pivot on Table 9 that has rows representing aggregate measures of 1) definition, 2) Familiarity 3) Experience, 4) Barriers and two groups of columns representing (Quant, Qual, Mixed) and (Human, Physical, GIS/Methods, NS).
+Of our 218 respondents, \textit{$n_{1}$}=217 (99.5\%) provided information sufficient for our first analysis of geographic researchers' understanding and perception of reproducibility.
 
@@
 \subsection*{Actual Reproductions}
-A total of \textit{n}=102 of the authors we contacted reported attempting to reproduce a prior study.
+A total of \textit{$n_{2}$}=102 (46.7\%) of the authors that responded to our survey reported attempting to reproduce a study in the past two years.
+This subset of participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions.
+Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (42.2\%) and geographic methods and GIScience (35.3\%).
+Respondents attempting reproductions were also focused on quantitative (52.0\%) and mixed-methods (46.1\%) approaches. 
+Only two respondents that self-identified as qualitative researchers attempted to reproduce a study in the past two years.
 

### 2023-01-18 procedure/code/201b_Q6_coding.R
Code for comparing Q6 coding.

@@ -1,0 +1,49 @@
+# list of required packages
+packages = c("here","tidyverse","table1","officer","readxl")
+
+# load and install required packages
+package.check <- lapply(
+  packages,
+  FUN = function(x) {
+    if (!require(x, character.only = TRUE)) {
+      install.packages(x, dependencies = TRUE)
+      library(x, character.only = TRUE)
+    }
+  }
+)
+
+# save the R processing environment to r_environment.txt
+writeLines(capture.output(sessionInfo()),here("procedure","environment","r_environment.txt"))
+
+sb_coding <- read_excel(here("data","derived","public","analysis_Q6_coding.xlsx"))
+pk_coding <- read_excel(here("data","derived","public","pk_analysis_Q6_coding.xlsx"))
+
+combined <- left_join(sb_coding,pk_coding,by="ResponseId") 
+## NOTE: PK deleted cases that were blank rather than coding as Missing
+
+#Replace NA values with 0 and create logical statements to identify discrepancies
+combined <- mutate_all(combined, ~replace_na(.,0)) %>% 
+                         mutate(diff_data_same = (data_same.x != data_same.y),
+                                diff_data_sim = (data_similar.x != data_similar.y),
+                                diff_pro_same = (procedure_same.x != procedure_same.y),
+                                diff_pro_sim = procedure_similar.x != procedure_similar.y, 
+                                diff_res_same = results_same.x != results_same.y,
+                                diff_res_sim = results_similar.x != results_similar.y,
+                                diff_con_same = context_same.x != context_same.y,
+                                diff_con_sim = context_similar.x != context_similar.y,
+                                diff_rp_rej = rp_rejection.x != rp_rejection.y ,
+                                diff_miss = Missing.x != Missing.y) %>%
+                         rowwise %>%
+                         mutate(diff_any = if_any(.cols = contains('diff_'), isTRUE)) %>%
+                         ungroup
+
+#Check results of flagging
+combined %>% select(c(data_similar.x,data_similar.y,diff_data_sim))                                
+
+check <- combined %>% 
+          select(starts_with("diff_"))
+sapply(check, sum)
+
+discrepancies <- combined %>% filter(diff_any == T)
+write.csv(discrepancies,here("data","derived","public","discrepancies_Q6_coding.csv"))
+write.csv(combined,here("data","derived","public","full_Q6_coding.csv"))

### 2023-01-19 docs/manuscript/manuscript.tex

@@
 All of the results presented in this paper can be independently reproduced using the materials in that repository.}.
-First, we used descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
-For each question, we created a single variable that aggregates a participant's response across a subset of survey questions related to that issue.
+First, we create descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
+Each of these topics is linked to a subset of survey questions, which we examine individually.
+As a summary measure for each topic, we created a single variable that aggregates individual responses to the subset of questions linked to that topic.
+Each of these measures is described below.
 
-We measured each participant's definition of reproducibility relative to the definition provided by the \citet{NASEM2019}. 
-Before being provided a standardized definition, each participant was asked to provide their own definition of reproducibility. 
-We coded these text responses along four dimensions of data, procedure, result, and context similarity.  
-To assess researcher familiarity with reproducible practices, we created a single variable, \textit{Familiarity}, that counts the number of practices a researcher was 'somewhat' or 'very' familiar with.
-To assess researcher experience with reproducible practices, we created a single variable, \textit{Experience}, that counts the number of practices a researcher use 'most of the time' or 'always' when conducting their own research.
-Our \textit{Familiarity} and \textit{Experience} variables both range from 0-5. 
-We similarly created a single measure, \textit{Barriers} that counts the number of factors a researcher believe 'frequently' or 'occasionally' contributed to a lack of reproducibility. 
-This \textit{Barriers} variable ranges from 0-12.
+We measured the similarity of each participant's definition of reproducibility relative to the definition of adopted by the \citet{NASEM2019}. 
+The NASEM defines reproducibile research as having four characteristics --- same data, same procedure, same results, same context.
+Before being provided this standardized definition, each participant was asked to provide their own definition of reproducibility.
+Two of the authors independently coded these text responses for the presence/absence of each of the four characteristics included in the NASEM definition.
+Disagreements were resolved through discussion between the two authors. 
+As a final check, the third author reviewed the final list in light of the four dimensions.
+The coded response for each participant was then summed across the four characteristics creating the variable, \textit{DEF} with domain [0---no characteristics shared, 4---all characteristics shared].
 
-We also examine group-wise differences in each aggregated measure by disciplinary subfield and methodological approach to identify variation across the discipline's many traditions.
+We measured participant familiarity and experience with five reproduciblity enhancing research practices --- open source software, research notebooks, data sharing, code sharing, and pre-registration.
+We created a summary measure of research familiarity, \textit{f}, with these practices by summing the number of reproducible and open science practices a researcher was 'somewhat' or 'very' familiar with.
+To assess researcher experience with reproducible practices, we similarly created a summary variable, \textit{p}, that counts the number of reproducible practices a researcher uses 'most of the time' or 'always' when conducting their own research.
+Both \textit{f} and \textit{p} have domains [0,5]. 
+Finally, we created a variable, \textit{b}, that counts the number of factors a researcher believe 'frequently' or 'occasionally' contributed to a lack of reproducibility in the discipline. 
+This variable aggregated participant response across 12 questions and ranges and has domain [0,12].
+Given the topical and epistemological variation that exists among geographic researchers, we also examined group-wise differences in each aggregated measure by disciplinary subfield and methodological approach.
 
-Second, we conduct an analysis of the experience of geographic researchers who have attempted reproductions of prior work. 
-We examine what motivates geographic researchers to attempt to reproduce another study and how successful researcher attempting reproductions were at recreating existing results. 
+Second, we conducted an analysis of the experience of geographic researchers who have attempted reproductions of prior work. 
+We examine what motivates geographic researchers to attempt to reproductions and how successful researchers attempting reproductions were at recreating existing results. 
 We also investigate why researchers were unable to reproduce results.
+ADD DETAILS ABOUT HOW WE ANALYZE.
 
@@
 \subsection*{Aggregate Measures Along 4-Dimensions}
-Of our 218 respondents, \textit{$n_{1}$}=217 (99.5\%) provided information sufficient for our first analysis of geographic researchers' understanding and perception of reproducibility.
+A primary aim of our survey was to establish the current level of knowledge and experience geographic researchers have with reproducibility and reproducibility enhancing research practices.
+Table 1 presents our summary measures for each topic, as well as those measures by subgroup.
 
@@
                     & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & \\
-         Measure    & HU & PH & NS & GIS            & & QNT & QUL & MIX              & & Overall \\
+         Measure    & HU & PH & NS & MT            & & QN & QL & MX              & & Overall \\
          \hline
-         Definition  &  & & & & & & & & & \\
-         Familiarity &  \begin{tabular}[c]{@{}c@{}}2.35\\ (1.36)\end{tabular} & 
+         \textit{DEF}: Definition   &  & & & & & & & & & \\
+         Familiarity (\textit{f}) &  \begin{tabular}[c]{@{}c@{}}2.35\\ (1.36)\end{tabular} & 
                         \begin{tabular}[c]{@{}c@{}}3.71\\ (0.98)\end{tabular} & 
@@
 
-         Experience  &  \begin{tabular}[c]{@{}c@{}}0.60\\ (0.80)\end{tabular} & 
+         Experience (\textit{p}) &  \begin{tabular}[c]{@{}c@{}}0.60\\ (0.80)\end{tabular} & 
                         \begin{tabular}[c]{@{}c@{}}2.06\\ (1.18)\end{tabular} & 
@@
 
-         Barriers    &  \begin{tabular}[c]{@{}c@{}}7.32\\ (3.57)\end{tabular} & 
+         Barriers (\textit{b})   &  \begin{tabular}[c]{@{}c@{}}7.32\\ (3.57)\end{tabular} & 
                         \begin{tabular}[c]{@{}c@{}}8.31\\ (3.00)\end{tabular} & 
@@
         \footnotesize
-        \item \textit{HU} Human Geography, \textit{PH} Physical Geography, \textit{NS} Nature and Society, \textit{GIS} GIScience and Methods; \textit{QNT} Quantitative, \textit{QUL} Qualitative, \textit{MIX} Mixed Methods.
+        \item \textit{HU} Human Geography, \textit{PH} Physical Geography, \textit{NS} Nature and Society, \textit{MT} GIScience and Methods; \textit{QN} Quantitative, \textit{QL} Qualitative, \textit{MX} Mixed Methods.
     \end{tablenotes}
@@
 
+%%%%%%%%%%%
+\subsubsection*{Reproducible Research Practices and Barriers to Reproducibility}
+Geographic researchers are on average familiar with multiple reproducible research practices ($\overline{f}=3.26$), but reported limited use of these practices in their own work ($\overline{p}=1.44$).
+More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\% ).
+However, while familiar with these practice, a far smaller number of researchers reported using these practices regularly in their own work. 
+Less than half of the researchers surveyed reported sharing their data (44.5\%), using open source software (38.1\%), or using field or lab notebooks to record their work (40.0\%), or sharing their code (18.8\%) most or all of the time.
+Only a small subset of researchers reported familiarity with the pre-registration of research designs and protocols (27.5\%), or regular use of this practice (2.7\%).
+
+Researcher familiarity and use of reproducible research practices also varied by disciplinary subfield and methodological approach. 
+Researchers that identified as physical geographers ($\overline{f_{PH}}=3.71$) or methodologists and GIScientists ($\overline{f_{MT}}=3.97$) reported being familiar with more reproducible researcher practices than human  geographers ($\overline{f_{HU}}=2.35$) and those focused on nature and society ($\overline{f_{NS}}=2.28$).
+Researcher practices similarly diverged by subfield, but no subset of researchers reported using on average more than two of these practices regularly in their work.  
+When grouped by methodological approach, Quantitative and mixed-methods researchers reported substantially greater familiarity ($\overline{f_{QN}}=3.75$, $\overline{f_{MX}}=3.56$) and use ($\overline{p_{QN}}=1.63$, $\overline{p_{MX}}=1.69$) of reproducible researcher practices than qualitative researchers ($\overline{f_{QL}}=1.75$, $\overline{p_{QL}}=0.48$).
+
+Differences in practice familiarity and use across subfields and approaches were greatest for practices more typical of quantitative workflows. 
+For example, quantitiative and mixed-methods researchers reported familiarity with open source software (QNT=96.7\%, MIX=89.5\%) and code sharing (QNT=81.5\%, MIX=55.7\%).
+In contrast, a smaller percentage of qualitative researchers reported familiarity with these same practices (OS=52.5\%, Code=12.5\%).
+
+Even among quantitiative and mixed-methods researchers familiarity with reproducible research practices did not translate into regular use of those practices.
+For example, just over half of quantitative (51.2\%) and mixed-methods (51.8\%) researchers reported sharing their data most of the time.
+Less than a third of these researchers reported sharing their code most of the time. 
+These rates were lower for qualitative geographers, of which only a small subset reported using open source software (10.0\%) or field notes (20.0\%), or sharing data (12.5\%) and code (5.0\%) most of the time.
+
 \begin{itemize}
-    \item Overall story is that collectively geographers are aware of reproducible research practices, but don't have a matching amount of direct experience using those practices.
-There are also many perceived barriers to conducting reproducible research.
-    \item High - Low gradient across all aggregate measures from Quant-MM-Qual.
-    \item High - Low familiarity gradient Method-Physs-NS-H
-    \item Likely need to comment on survey including many reproducible research practices that center on, or are easier to accomplish with, when using quantitative data and methods.
-This reality may automatically deflate the aggregate measures of certain sub-group.
-We can use the response to Q8f as a filter to explore this issue.
-\textcolor{red}{For conclusions - Points to the emphasis on quantitative, particularly computational, focus in the reproducibility literature.
-Suggests a meed to examine what reproducibility means in the context of geography's qual, NS, and human traditions.}
+    \item Use Q9 to contextualize the frequency measure.
+    \item Use details from Q14 to enrich the discussion of barriers
 \end{itemize}
@@
     \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
-\end{itemize}
-
-%%%%%%%%%%%
-\subsubsection*{Reproducible Research Practices and Barriers to Reproducibility}
-This will be a discussion of how subfields differ on the specific questions used to create the aggregate variables presented above. 
-The purpose is to enrich the overall picture by identifying differences within the aggregate measures.
-\begin{itemize}
-    \item Use Q9 to contextualize the frequency measure.
-    \item Use details from Q14 to enrich the discussion of barriers
 \end{itemize}
@@
 This emphasis necessarily carried over into our survey instrument, which may automatically lower response scores for researchers not working in these areas (e.g., qualitative, human geography).
+This reality may automatically deflate the aggregate measures of certain sub-group.
+We can use the response to Q8f as a filter to explore this issue.
 These scores do reflect their present level of understanding, but the practices may not be relevant to their methods or epistomologies.
@@
 \section*{Conclusion}
+
+\begin{itemize}
+    \item Overall story is that collectively geographers are aware of reproducible research practices, but don't have a matching amount of direct experience using those practices.
+There are also many perceived barriers to conducting reproducible research.
+\end{itemize}
 

### 2023-01-23 docs/manuscript/manuscript.tex

@@
 %%%%%%%%%%%
-\subsubsection*{Reproducible Research Practices and Barriers to Reproducibility}
-Geographic researchers are on average familiar with multiple reproducible research practices ($\overline{f}=3.26$), but reported limited use of these practices in their own work ($\overline{p}=1.44$).
-More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\% ).
-However, while familiar with these practice, a far smaller number of researchers reported using these practices regularly in their own work. 
-Less than half of the researchers surveyed reported sharing their data (44.5\%), using open source software (38.1\%), or using field or lab notebooks to record their work (40.0\%), or sharing their code (18.8\%) most or all of the time.
-Only a small subset of researchers reported familiarity with the pre-registration of research designs and protocols (27.5\%), or regular use of this practice (2.7\%).
-
-Researcher familiarity and use of reproducible research practices also varied by disciplinary subfield and methodological approach. 
-Researchers that identified as physical geographers ($\overline{f_{PH}}=3.71$) or methodologists and GIScientists ($\overline{f_{MT}}=3.97$) reported being familiar with more reproducible researcher practices than human  geographers ($\overline{f_{HU}}=2.35$) and those focused on nature and society ($\overline{f_{NS}}=2.28$).
-Researcher practices similarly diverged by subfield, but no subset of researchers reported using on average more than two of these practices regularly in their work.  
-When grouped by methodological approach, Quantitative and mixed-methods researchers reported substantially greater familiarity ($\overline{f_{QN}}=3.75$, $\overline{f_{MX}}=3.56$) and use ($\overline{p_{QN}}=1.63$, $\overline{p_{MX}}=1.69$) of reproducible researcher practices than qualitative researchers ($\overline{f_{QL}}=1.75$, $\overline{p_{QL}}=0.48$).
-
-Differences in practice familiarity and use across subfields and approaches were greatest for practices more typical of quantitative workflows. 
-For example, quantitiative and mixed-methods researchers reported familiarity with open source software (QNT=96.7\%, MIX=89.5\%) and code sharing (QNT=81.5\%, MIX=55.7\%).
-In contrast, a smaller percentage of qualitative researchers reported familiarity with these same practices (OS=52.5\%, Code=12.5\%).
-
-Even among quantitiative and mixed-methods researchers familiarity with reproducible research practices did not translate into regular use of those practices.
-For example, just over half of quantitative (51.2\%) and mixed-methods (51.8\%) researchers reported sharing their data most of the time.
-Less than a third of these researchers reported sharing their code most of the time. 
-These rates were lower for qualitative geographers, of which only a small subset reported using open source software (10.0\%) or field notes (20.0\%), or sharing data (12.5\%) and code (5.0\%) most of the time.
-
-\begin{itemize}
-    \item Use Q9 to contextualize the frequency measure.
-    \item Use details from Q14 to enrich the discussion of barriers
-\end{itemize}
-
-%%%%%%%%%%%
 \subsubsection*{Definition of Reproducibility}
@@
 
+%%%%%%%%%%%
+\subsubsection*{Familiarity and use of Reproducible Research Practices}
+The reproducibility of research is on the minds of geographic researchers. 
+The majority of survey respondents reported thinking about the reproducibility of their own research (80.7\%), discussing reproducibility with a colleague (70.6\%), and questioning the reproducibility of published work (57.3\%) in the past two years.
+More than half of the researchers we surveyed (52.8\%) also reported considering reproducibility while peer reviewing a grant proposal or publication during the same time frame.
+
+Geographic researchers are on average familiar with multiple reproducible research practices ($\overline{f}=3.26$, Table \ref{tab:overview}), but reported limited use of these practices in their own work ($\overline{p}=1.44$).
+More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\% ).
+However, while familiar with these practice, a far smaller number of researchers reported using these practices regularly in their own work. 
+Less than half of the researchers surveyed reported sharing their data (44.5\%), using open source software (38.1\%), or using field or lab notebooks to record their work (40.0\%), or sharing their code (18.8\%) most or all of the time.
+Only a small subset of researchers reported familiarity with the pre-registration of research designs and protocols (27.5\%), or regular use of this practice (2.7\%).
+
+Researcher familiarity and use of reproducible research practices also varied by disciplinary subfield and methodological approach. 
+Researchers that identified as physical geographers ($\overline{f_{PH}}=3.71$) or methodologists and GIScientists ($\overline{f_{MT}}=3.97$) reported being familiar with more reproducible researcher practices than human  geographers ($\overline{f_{HU}}=2.35$) and those focused on nature and society ($\overline{f_{NS}}=2.28$).
+Researcher practices similarly diverged by subfield, but no subset of researchers reported using on average more than two of these practices regularly in their work.  
+When grouped by methodological approach, quantitative and mixed-methods researchers reported substantially greater familiarity ($\overline{f_{QN}}=3.75$, $\overline{f_{MX}}=3.56$) and use ($\overline{p_{QN}}=1.63$, $\overline{p_{MX}}=1.69$) of reproducible researcher practices than qualitative researchers ($\overline{f_{QL}}=1.75$, $\overline{p_{QL}}=0.48$).
+
+Differences in researcher familiarity and use of specific reproducible research practices across subfields and approaches were greatest for practices more typical of quantitative workflows. 
+For example, quantitiative and mixed-methods researchers reported familiarity with open source software (QT=96.7\%, MX=89.5\%) and code sharing (QT=81.5\%, MX=55.7\%).
+In contrast, a smaller percentage of qualitative researchers reported familiarity with these same practices (OS=52.5\%, Code=12.5\%).
+However, even among quantitiative and mixed-methods researchers familiarity with reproducible research practices did not translate into regular use of those practices.
+Just over half of quantitative (51.2\%) and mixed-methods (51.8\%) researchers reported sharing their data most of the time.
+Less than a third of these same researchers reported sharing their code most of the time. 
+These rates were lower for qualitative geographers, of which only a small subset reported using open source software (10.0\%) or field notes (20.0\%), or sharing data (12.5\%) and code (5.0\%) most of the time.
+
+\subsubsection*{Barriers to Reproducible Research}
+Aligning with the differences we observed between researcher familiarity with reproducibility enhancing research practices and researcher use of those same practices, respondents to our survey identified numerous factors contributing to a lack or reproducible research across the discipline ($\overline{b}=8.20$).
+Geographic researchers working in different subfields and with different methodological approaches each identified a similar number of barriers to reproducibility (Table \ref{tab:overview}).
+Qualitative geographers may be the one group that deviates from this consistent pattern. 
+These researchers identified fewer barriers to reproducibility on average, but with a greater variance that left us unable to distinguish this group from any other ($\overline{b_{QL}}=5.97, \sigma_{QL}=3.83$).
+To examine differences in researcher beliefs about specific factors potentially hindering reproducibility in the discipline, we divided the 12 factors we examined into three groups --- those related to the research environment, the availability of research artifacts, and study-specific characteristics (Table \ref{tab:barriers}).
+
+\begin{table}[h]
+    \centering
+    \begin{threeparttable}
+    \caption{Barriers to Reproducibility}
+    \begin{tabular}{l c c c c c c c c c c}
+         \hline
+                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & \\
+         Barrier    & HU & PH & NS & MT            & & QN & QL & MX              & & Overall \\
+         \hline
+         \textit{Research Environment}      & & & & & & & & & & \\
+         Pressure to Publish                & 61.2\% & 83.1\% & 54.5\% & 75.0\% & & & & & & 71.5\% \\
+         Insufficient oversight             & 56.7\% & 81.6\% & 63.6\% & 82.0\% & & & & & & 71.1\% \\
+         Fraud                              & 22.4\% & 32.3\% & 9.1\%  & 39.3\% & & & & & & 28.4\% \\
+                                            & & & & & & & & & &\\
+         \textit{Artifact Availability}     & & & & & & & & & & \\
+         Insufficient metadata              & 62.6\% & 76.9\% & 59.1\% & 78.7\% & & & & & & 80.2\% \\
+         Unavailable Data                   & 65.7\% & 89.3\% & 59.1\% & 78.6\% & & & & & & 75.2\% \\
+         Unavailable protocol/code          & 59.7\% & 77.0\% & 50.0\% & 86.9\% & & & & & & 71.1\% \\
+         Published incomplete results       & 56.7\% & 73.8\% & 63.7\% & 78.7\% & & & & & & 68.4\% \\
+         Use restricted data/software       & 44.8\% & 56.9\% & 40.9\% & 82.0\% & & & & & & 57.8\% \\
+                                            & & & & & & & & & &\\
+         \textit{Study Characteristics}     & & & & & & & & & & \\
+         Geographic variation               & 61.2\% & 80.0\% & 81.8\% & 72.2\% & & & & & & 71.5\% \\
+         Researcher positionality           & 70.2\% & 50.8\% & 72.8\% & 70.5\% & & & & & & 64.2\% \\
+         Chance                             & 55.2\% & 66.2\% & 68.2\% & 65.6\% & & & & & & 62.3\% \\
+         Different computation              & 38.8\% & 53.8\% & 31.8\% & 68.9\% & & & & & & 50.9\% \\
+                                            & & & & & & & & & &\\
+         N                                  & 67 & 65 & 22 & 61 & & 92 & 40 & 85 & & 218 \\
+        \hline
+    \end{tabular}
+    \begin{tablenotes}
+        \footnotesize
+        \item \textit{HU} Human Geography, \textit{PH} Physical Geography, \textit{NS} Nature and Society, \textit{MT} GIScience and Methods; \textit{QN} Quantitative, \textit{QL} Qualitative, \textit{MX} Mixed Methods.
+        \item Percentage of respondents reporting each factor frequently or occasionally contributed to a lack of reproducibility in geographic research
+    \end{tablenotes}
+    \label{tab:barriers}
+    \end{threeparttable}
+\end{table}
+
+Geographic researchers identified the incentive structure of the researcher environment as an important barrier to reproducibility in the discipline.
+A majority of geographic researchers identified both the pressure to publish (71.5\%) and insufficient oversight of the research process (71.1\%) as barriers to reproducibility.
+A high percentage of physical, methods-focused, and quantitative geographers identified these factors as barriers. 
+Qualtiative geographers were least concerned with these factors, but a majority of these researchers still identified both factors as barriers to reproducibility in the field.
+Contrary to alarms raised in some of the reproducibility literature, a minority of geographic researchers (28.4\%) believe that the fabrication of data, the manipulation of research results, and similar forms of fraud are a cause of irreproducibility in the discipline.
+
+Researchers identified the unavailability of research artifacts (e.g., data, code) as a barrier to reproducibility, but the importance placed on different artifacts varied by subfield and methodological approach.
+A higher percentage physical and methods-focused researchers identified all five of the artifacts we investigated as common barriers to reproducibility than did human and nature-society researchers.
+A similar gap existed between qualitative and mixed-methods researchers and qualtiative researchers. 
+The largest differences between these groups existed in researchers beliefs about how often the availability of research protocols/code and the use of restricted data or software impacted reproducibility.
+More than three-quarters of physical (77.0\%) and methods-focused (86.9\%) geographers identified the availability of protocols/code as contributing to irreproducibility, whereas less than two-thirds of human (59.7\%) and nature-society (50.0\%) identified this same factor.
+Only a large percentage of methods-focused researchers (82.0\%) identified the use of restricted data/software as a common contributor to irreproducibility in the discipline.
+
+A majority of researchers identified geographic variation (71.5\%), researcher positionality (64.2\%), and chance (62.3\%) as study-specific factors limiting the reproducibility of geographic research.
+Minor variations in the emphasis placed on these factors exist across subfields and approaches. 
+A higher percentage of nature-society (81.8\%) and physical (80.0\%) researchers emphasized the important role the spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researcher across subfields and approaches.
+A smaller percentage of physical geographers placed less emphasis on the impact of researcher positionality may have on reproducibility (50.8\%) when compared to all other subfields.  
+Differences between the computational environment used to conduct and original study and a reproduction attempt was generally not seen as a common factor contributing to a lack of reproducibility in the discipline.
+The exception being methods-focused (68.9\%) and quantitative researchers (\%), which aligns with the research practices used in these areas of research.
+
 %%%%%%%%%%%%%%%%%%%%%%%%
@@
 
-Start with the outline of what the population is here because not all respondents answered these questions.
-Start with descriptives that show this sub-sample of respondents.
-Summary discussion of Q10-Q12.
+WHY DID RESEARCHERS ATTEMPT REPRODUCTION - Q10
+
+ACCESS MATERIALS - Q12.
+The majority of researchers (82/102) that attempted reproductions were able to access at least some of the data used in the original study, but only (27/102) could access all of the original data.
+
+OUTCOME - Q11 AND OUTCOME BY ACCESS Q12
+Geographic researchers report being able to recreate some the results they attempt to reproduce, but few researchers report being able to identically recreate all results (20/102).
 

### 2023-01-25 docs/manuscript/manuscript.tex
Draft repro attempts

@@
 Only two respondents that self-identified as qualitative researchers attempted to reproduce a study in the past two years.
+Approximately half (49\%) of the researchers attempting reproductions reported submitting their findings for publication.
 
@@
 
-ACCESS MATERIALS - Q12.
-The majority of researchers (82/102) that attempted reproductions were able to access at least some of the data used in the original study, but only (27/102) could access all of the original data.
+In most instances, researchers reported some ability to access to the research artifacts used in the study they were attempting to reproduce and the ability to recreate at least some of the results of that study.
+The majority of researchers that attempted reproductions (82\%) were able to access at least some of the data used in the original study, but few researchers (27\%) reported access to all of the original data.
+Researchers also reported the ability to access at least some information about study procedures (69\%) and its computational environment (60\%), but limited ability to access all procedural (20\%) and computational information (15\%).
+Less than half of researchers (38\%) reported being able to at least partially reproduce all of the results from an original study.
+Similarly, nearly all researchers (96\%) reported at least partially reproducing some results, but less than half (38\%) reported being able to at least partially reproduce all results.
+Few researchers (20\%) reported the ability to identically reproduce all results.
 
 OUTCOME - Q11 AND OUTCOME BY ACCESS Q12
-Geographic researchers report being able to recreate some the results they attempt to reproduce, but few researchers report being able to identically recreate all results (20/102).
+\begin{itemize}
+    \item If geographic researchers had access to at least some of the data and procedures used in the original study they reported the ability to at least partially reproducing some results in all cases.
+This indirectly supports researcher beliefs that fraud is not prevalent in the discipline.
+    \item Access to data and procedures seems to be equally important to being able to at least partially reproduce all results
+    \item Having access to all of the data and all of the procedures used in an original study double the probability that a research would be able to at least partially reproduce all results.
+$P(C|D=A)=66.7\%$ while $P(C|D=\neg A)=27.4\%$.
+$P(C|P=A)=70.0\%$ while $P(C|P=\neg A)=30.0\%$.
+    \item Same story, given at least some access to whatever is not being modulated.
+$P(C|D=S,A;P=A)=14/20=0.7$ with $P(C|D=S,A;P=S)=13/43=0.30$ compared to $P(C|D=A;P=S,A)=16/23=0.695$ with $P(C|D=S;P=S,A)=11/40=0.275$
+    \item Reverse conditional maybe...
+\end{itemize}
 

### 2023-01-26 procedure/code/202_preprocess.R
Updated Q8 Tables.

@@ -257,7 +257,8 @@ table1::label(survey_resp$Q14_12) <- "Researcher positionality"
 
 Q3_table8 <- table1::table1(~Q14_1 + Q14_2 + Q14_3 + Q14_4 + Q14_5 + Q14_6 + Q14_7 + Q14_8 + 
                               Q14_9 + Q14_10 + Q14_11 + Q14_12 | Q3_recoded, data = survey_resp)
-Q4_table8 <- table1::table1(~Q11_1 + Q11_2 + Q11_3 + Q12_1 + Q12_2 + Q12_3 + Q12_4 | Q4, data = survey_resp)
+Q4_table8 <- table1::table1(~Q14_1 + Q14_2 + Q14_3 + Q14_4 + Q14_5 + Q14_6 + Q14_7 + Q14_8 + 
+                              Q14_9 + Q14_10 + Q14_11 + Q14_12 | Q4, data = survey_resp)
 
 # Output tables using write table and flextable
 write.table(Q3_table8 , here("results","tables","Table8_Barriers_discipline.csv"), col.names = T, row.names=F, append= T, sep=',')

### 2023-01-26 docs/manuscript/manuscript.tex
Updates from Overleaf

--- 2023-01-23 docs/manuscript/manuscript.tex
@@
 \subsection*{Aggregate Measures Along 4-Dimensions}
-A primary aim of our survey was to establish the current level of knowledge and experience geographic researchers have with reproducibility and reproducibility enhancing research practices.
+A primary aim of our survey was to establish the current level of knowledge and experience geographic researchers have with reproducibility enhancing research practices.
 Table 1 presents our summary measures for each topic, as well as those measures by subgroup.
@@
 %%%%%%%%%%%
-\subsubsection*{Definition of Reproducibility}
+\subsubsection*{Definitions and Importance of Reproducibility}
 Coded definitions are relative to the NASEM definition. The NASEM state SAME data, procedures, and results and implies SAME context because data is not recollected. 
@@
 \end{itemize}
+
+In aggregate, respondents identified reproducibility as an important means of achieving numerous epistemic goals in geographic research (Q17).
+\begin{itemize}
+    \item reducing the risk of persistent errors (77.5\%)
+    \item preventing duplication of research efforts (63.3\%)
+    \item communicating results to academics (68.8\%)
+    \item communicating results to practitioners (64.7\%)
+    \item Researchers also view attempting reproductions as an important part of student training (75.7\%). 
+\end{itemize}
+
+Qualitative researchers identified reproducibility as playing a much smaller role in the research process when compared to quantitiative or mixed-methods researchers.
 
@@
          \textit{Research Environment}      & & & & & & & & & & \\
-         Pressure to Publish                & 61.2\% & 83.1\% & 54.5\% & 75.0\% & & & & & & 71.5\% \\
-         Insufficient oversight             & 56.7\% & 81.6\% & 63.6\% & 82.0\% & & & & & & 71.1\% \\
-         Fraud                              & 22.4\% & 32.3\% & 9.1\%  & 39.3\% & & & & & & 28.4\% \\
+         Pressure to Publish                & 61.2\% & 83.1\% & 54.5\% & 75.0\% & & 77.3\% & 47.5\% & 75.3\% & & 71.5\% \\
+         Insufficient oversight             & 56.7\% & 81.6\% & 63.6\% & 82.0\% & & 82.6\% & 40.0\% & 74.2\% & & 71.1\% \\
+         Fraud                              & 22.4\% & 32.3\% & 9.1\%  & 39.3\% & & 29.4\% & 20.0\% & 31.8\% & & 28.4\% \\
                                             & & & & & & & & & &\\
          \textit{Artifact Availability}     & & & & & & & & & & \\
-         Insufficient metadata              & 62.6\% & 76.9\% & 59.1\% & 78.7\% & & & & & & 80.2\% \\
-         Unavailable Data                   & 65.7\% & 89.3\% & 59.1\% & 78.6\% & & & & & & 75.2\% \\
-         Unavailable protocol/code          & 59.7\% & 77.0\% & 50.0\% & 86.9\% & & & & & & 71.1\% \\
-         Published incomplete results       & 56.7\% & 73.8\% & 63.7\% & 78.7\% & & & & & & 68.4\% \\
-         Use restricted data/software       & 44.8\% & 56.9\% & 40.9\% & 82.0\% & & & & & & 57.8\% \\
+         Insufficient metadata              & 62.6\% & 76.9\% & 59.1\% & 78.7\% & & 79.4\% & 45.0\% & 72.9\% & & 80.2\% \\
+         Unavailable Data                   & 65.7\% & 89.3\% & 59.1\% & 78.6\% & & 87.0\% & 42.5\% & 81.2\% & & 75.2\% \\
+         Unavailable protocol/code          & 59.7\% & 77.0\% & 50.0\% & 86.9\% & & 87.0\% & 37.5\% & 70.6\% & & 71.1\% \\
+         Published incomplete results       & 56.7\% & 73.8\% & 63.7\% & 78.7\% & & 78.2\% & 37.2\% & 72.9\% & & 68.4\% \\
+         Use restricted data/software       & 44.8\% & 56.9\% & 40.9\% & 82.0\% & & 70.7\% & 32.5\% & 56.5\% & & 57.8\% \\
                                             & & & & & & & & & &\\
          \textit{Study Characteristics}     & & & & & & & & & & \\
-         Geographic variation               & 61.2\% & 80.0\% & 81.8\% & 72.2\% & & & & & & 71.5\% \\
-         Researcher positionality           & 70.2\% & 50.8\% & 72.8\% & 70.5\% & & & & & & 64.2\% \\
-         Chance                             & 55.2\% & 66.2\% & 68.2\% & 65.6\% & & & & & & 62.3\% \\
-         Different computation              & 38.8\% & 53.8\% & 31.8\% & 68.9\% & & & & & & 50.9\% \\
+         Geographic variation               & 61.2\% & 80.0\% & 81.8\% & 72.2\% & & 79.4\% & 40.0\% & 74.1\% & & 71.5\% \\
+         Researcher positionality           & 70.2\% & 50.8\% & 72.8\% & 70.5\% & & 56.5\% & 80.0\% & 65.9\% & & 64.2\% \\
+         Chance                             & 55.2\% & 66.2\% & 68.2\% & 65.6\% & & 67.4\% & 52.5\% & 64.4\% & & 62.3\% \\
+         Different computation              & 38.8\% & 53.8\% & 31.8\% & 68.9\% & & 63.1\% & 25.0\% & 56.5\% & & 50.9\% \\
                                             & & & & & & & & & &\\
@@
 A majority of geographic researchers identified both the pressure to publish (71.5\%) and insufficient oversight of the research process (71.1\%) as barriers to reproducibility.
-A high percentage of physical, methods-focused, and quantitative geographers identified these factors as barriers. 
+A high percentage of physical, methods-focused, quantitative, and mixed-methods researchers identified these factors as barriers. 
 Qualtiative geographers were least concerned with these factors, but a majority of these researchers still identified both factors as barriers to reproducibility in the field.
@@
 Researchers identified the unavailability of research artifacts (e.g., data, code) as a barrier to reproducibility, but the importance placed on different artifacts varied by subfield and methodological approach.
-A higher percentage physical and methods-focused researchers identified all five of the artifacts we investigated as common barriers to reproducibility than did human and nature-society researchers.
-A similar gap existed between qualitative and mixed-methods researchers and qualtiative researchers. 
+A higher percentage physical and methods-focused researchers identified all five of the artifacts we investigated as common barriers to reproducibility as compared to human and nature-society researchers.
+A similar gap existed between qualitative researchers and those identifying as mixed-methods researchers or quantitative researchers. 
 The largest differences between these groups existed in researchers beliefs about how often the availability of research protocols/code and the use of restricted data or software impacted reproducibility.
@@
 Only a large percentage of methods-focused researchers (82.0\%) identified the use of restricted data/software as a common contributor to irreproducibility in the discipline.
+A similar gap existed between qualitative researchers, a minority of which identified code availability or the use of restricted data/software as contributing to irreproducibility, and quantiative and mixed-methods researchers, the majority of which saw these factors as frequent causes of irreproducibility.
 
@@
 Minor variations in the emphasis placed on these factors exist across subfields and approaches. 
-A higher percentage of nature-society (81.8\%) and physical (80.0\%) researchers emphasized the important role the spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researcher across subfields and approaches.
-A smaller percentage of physical geographers placed less emphasis on the impact of researcher positionality may have on reproducibility (50.8\%) when compared to all other subfields.  
-Differences between the computational environment used to conduct and original study and a reproduction attempt was generally not seen as a common factor contributing to a lack of reproducibility in the discipline.
-The exception being methods-focused (68.9\%) and quantitative researchers (\%), which aligns with the research practices used in these areas of research.
+A higher percentage of nature-society (81.8\%) and physical (80.0\%) researchers emphasized the important role the spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researchers across subfields and approaches.
+A smaller percentage of physical geographers placed emphasis on the impact of researcher positionality may have on reproducibility (50.8\%) when compared to all other subfields.  
+Differences between the computational environment used to conduct an original study and a reproduction attempt was generally not seen as a factor contributing to a lack of reproducibility in the discipline.
+The exception being methods-focused (68.9\%) and quantitative researchers (63.1\%\%), which aligns with the research practices used in these areas of research.
 
@@
 Only two respondents that self-identified as qualitative researchers attempted to reproduce a study in the past two years.
+Approximately half (49\%) of the researchers attempting reproductions reported submitting their findings for publication.
 
 WHY DID RESEARCHERS ATTEMPT REPRODUCTION - Q10
+\begin{itemize}
+    \item to check results - surprising, as part of peer-review, of related interest
+    \item to check their own results and make them more accessible
+    \item to learn more about methods and/or transfer them into their own work
+\end{itemize}
 
-ACCESS MATERIALS - Q12.
-The majority of researchers (82/102) that attempted reproductions were able to access at least some of the data used in the original study, but only (27/102) could access all of the original data.
+In most instances, researchers reported some ability to access the research artifacts used in the study they were attempting to reproduce and the ability to recreate at least some of the results of that study.
+The majority of researchers that attempted reproductions (82\%) were able to access at least some of the data used in the original study, but few researchers (27\%) reported access to all of the original data.
+Researchers also reported the ability to access at least some information about study procedures (69\%) and its computational environment (60\%), but limited ability to access all procedural (20\%) and computational information (15\%).
+Nearly all researchers reported at least partially reproducing some results (96\%), but less than half reported being able to at least partially reproduce all results (38\%).
+Few researchers were able to identically reproduce all results (20\%).
 
-OUTCOME - Q11 AND OUTCOME BY ACCESS Q12
-Geographic researchers report being able to recreate some the results they attempt to reproduce, but few researchers report being able to identically recreate all results (20/102).
+How much access researchers had to study data and procedural information impacted their ability to reproduce results. 
+If geographic researchers had access to at least some of the data and procedures used in the study they were attempting to reproduce, they were able to at least partially reproduce some results in all cases, but were able at least partially reproduce all results less than half of the time (42.9\%).
+With complete access to all data and procedures, researchers reported the ability to at least partially reproduce all results 68.4 percent of the time.
+Accessibility to data and procedures appears to be equally important in raising the chances of reproducing all results. 
+Given access to some or all procedural information, having access to all data doubled a researcher's chances of reproducing all results (69.5\%) when compared to having access to only some of the data (27.5\%).
+We observed the same doubling effect when reversing this relationship. 
+Given access to some or all of a study's data, having access to all the procedural information doubled a researcher's chances of reproducing all results (70.0\%) when compared to having access to only some of the procedures (30.0\%).
 

### 2023-01-27 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 \subsection*{Aggregate Measures Along 4-Dimensions}
-A primary aim of our survey was to establish the current level of knowledge and experience geographic researchers have with reproducibility enhancing research practices.
+A primary aim of our survey was to establish how geographic researchers conceptualize reproducibility and their current level of knowledge and experience with reproducibility enhancing research practices.
+Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%) with half reporting being very familiar with the term (53.6\%).
+A majority of researchers also believe reproducibility is compatible with epistemologies used in discipline (72.0\%). 
+However, researchers estimated that only half of the results published in the discipline were reproducible ($\overline{rep}=50.6\%$, $\sigma=24.7\%$) and reported limited familiarity with and use of many reproducible research practices.
+Few respondents reported attempting to reproduce the work of other researchers (\%) with fewer still attempting to publish those reproduction studies (\%).
+
 Table 1 presents our summary measures for each topic, as well as those measures by subgroup.
@@
          \hline
-         \textit{DEF}: Definition   &  & & & & & & & & & \\
+         Definition (\textit{d}) & \begin{tabular}[c]{@{}c@{}}1.76\\ (1.17)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.68\\ (1.12)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.97\\ (1.08)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}1.77\\ (1.10)\end{tabular} & 
+                        & 
+                        \begin{tabular}[c]{@{}c@{}}1.89\\ (1.14)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.53\\ (1.28)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.78\\ (1.06)\end{tabular} & 
+                        & 
+                        \begin{tabular}[c]{@{}c@{}}1.77\\ (1.15)\end{tabular} \\
          Familiarity (\textit{f}) &  \begin{tabular}[c]{@{}c@{}}2.35\\ (1.36)\end{tabular} & 
@@
 \subsubsection*{Definitions and Importance of Reproducibility}
-Coded definitions are relative to the NASEM definition. The NASEM state SAME data, procedures, and results and implies SAME context because data is not recollected. 
-\begin{itemize}
-    \item Self-reported definition (Q6) analysis: Qualitative analysis that will present a typology of definitions by combination of the Q,Q,M and M,P,NS,H splits that match on the 8 category coding of the provided definitions.
-    \item Interpretations (Q8) and Importance (Q17) of reproductions: Develop a split that distinguishes between Qs that focus on epistemology Q8a+Q8b+Q8f+17a, as these provide the most direct information about how a respondent processes the evidence provided by a reproduction; and Qs that focus on reproducibility as a quality of a study Q8e+Q8c+17c+17e+17f.
-We will explore how these question groups crosstab with the typologies we draw from Q6.
-Initial assumption is that many will support reproduction as a study characteristic or label, and less will link it with epistomological function.
-Examine by subfields and methods, which we expect to align with typologies from Q6.
-    \item Importance of reproducibility (Q17) - Reproducibility was/wasn't seen as important for other open science goals - error reduction (17b), effort duplication (17d), scientific communication (17g, 17h), training (17i, 8d).
-    \item Reproducibility Estimate (Q13) - \textcolor{red}{What is the state of the summaries on this dimension?}
-\end{itemize}
+Geographic researchers provided definitions of reproducibility that generally explicitly included one to two of the four characteristics ($\overline{d}=1.77$) from the definition adopted by the NASEM.
+This level of inclusion was consistent across subfields and methodological approaches.
+The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
+Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
+This patterns was also consistent across subfields and approaches, with a slightly greater emphasis on data and procedural consistency and availability amongst quantitative and methods focused researchers.
+The lower inclusion of data and context in definitions matched the conflation of reproduction and replication by a minority of researchers (\%).
 
-In aggregate, respondents identified reproducibility as an important means of achieving numerous epistemic goals in geographic research (Q17).
-\begin{itemize}
-    \item reducing the risk of persistent errors (77.5\%)
-    \item preventing duplication of research efforts (63.3\%)
-    \item communicating results to academics (68.8\%)
-    \item communicating results to practitioners (64.7\%)
-    \item Researchers also view attempting reproductions as an important part of student training (75.7\%). 
-\end{itemize}
+Researchers defined reproducibility in relation to two epistemic functions.
+Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies.
+Nearly all other researchers (40.9\%) tied reproducibilty to the need for transparency in research so others could independently expand upon past studies.
+Both of these functions were supported by respondents across our sample. 
+Overall, a majority of researchers also identified reproducibility as an important for validating (75.2\%) and establishing the credibility (72.5\%) of research.  
+Respondents also saw reproducing studies as important to reducing the presence of persistent errors in the discipline (77.5\%) and to increasing trust in research findings (78.45\%).
+Matching the emphasis placed on research transparency, respondents identified reproducibility as important to research efficiency (63.3\%) and the communication of findings to academics (68.8\%) and practitioners (64.7\%).
+Half of the respondents (50.9\%) also agreed that when researchers don't share their data they have less trust in a study.
+Researchers also view attempting reproductions as an important part of student training (75.7\%).
 
-Qualitative researchers identified reproducibility as playing a much smaller role in the research process when compared to quantitiative or mixed-methods researchers.
+Despite wide recognition of reproducibility as epistemically important, researchers collectively advocated caution when drawing conclusions from a single reproduction attempts. 
+A minority of researchers agreed that an inability to reproduce a result implies that the result is false (26.2\%). 
+A larger, but still minority, percentage of researchers believed that an inability to reproduce a result detracts from the validity of a study (41.7\%).
+
+Qualitative researchers identified reproducibility as playing a much smaller role in the research process when compared to the discipline as a whole. 
+A majority of the respondents that identified as qualitative researchers believe that reproducibility is incompatible with the epistomologies used in their subfield (75.0\%).
+Qualitative researchers did not believe reproducibility to be important to assessing prior work and correcting errors in the literature. 
+A small percentage or these respondents agree that reproducibility is important for validating (25.0\%) or establishing the credibility (20.0\%) of qualitative research.
+Qualitative geographers similarly placed less emphasis on reproducibility as a means of increasing the accessibility and expansion of research.
+Few qualitative researchers had less trust in a study when researchers did not share their data (27.5\%), or saw reproducibility as important to sharing research with academics (27.5\%).
 

### 2023-01-27 procedure/code/201_clean.R
New Q10 coding workbook and associated code updates.

@@ -267,7 +267,12 @@ sapply(int_hegs_rpr, class)
 
 saveRDS(int_hegs_rpr, here("data","derived","public","analysis_hegs_rpr.rds"))
 
-#-Export open response definitions to .csv for further coding
+#-Export open response definitions and reproductions to .csv for further coding
 analysis_Q6_coding <- int_hegs_rpr %>% select(c(ResponseId,Q3_recoded,Q4,Q6))
-
 write.csv(analysis_Q6_coding,here("data","derived","public","analysis_Q6_coding.csv"))
+
+analysis_Q10_coding  <- int_hegs_rpr %>% 
+                  filter(Q9_7 == "Yes") %>% 
+                  select(c(ResponseId,Q3_recoded,Q4,Q10))
+write.csv(analysis_Q10_coding,here("data","derived","public","analysis_10_coding.csv"))
+

### 2023-02-01 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 %%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Aggregate Measures Along 4-Dimensions}
+\subsection*{Researcher Perspectives on Reproducibility}
 A primary aim of our survey was to establish how geographic researchers conceptualize reproducibility and their current level of knowledge and experience with reproducibility enhancing research practices.
@@
 A majority of researchers also believe reproducibility is compatible with epistemologies used in discipline (72.0\%). 
-However, researchers estimated that only half of the results published in the discipline were reproducible ($\overline{rep}=50.6\%$, $\sigma=24.7\%$) and reported limited familiarity with and use of many reproducible research practices.
+However, researchers estimated that only half of the results published in the discipline were reproducible, albeit with wide variance ($\overline{rep}=50.6\%$, $\sigma=24.7\%$), and reported limited familiarity with and use of many reproducible research practices.
 Few respondents reported attempting to reproduce the work of other researchers (\%) with fewer still attempting to publish those reproduction studies (\%).
@@
 \subsubsection*{Definitions and Importance of Reproducibility}
-Geographic researchers provided definitions of reproducibility that generally explicitly included one to two of the four characteristics ($\overline{d}=1.77$) from the definition adopted by the NASEM.
+Geographic researchers provided definitions of reproducibility that generally explicitly included one to two ($\overline{d}=1.77$) of the four characteristics from the definition adopted by the NASEM.
 This level of inclusion was consistent across subfields and methodological approaches.
@@
 
-Researchers identified the unavailability of research artifacts (e.g., data, code) as a barrier to reproducibility, but the importance placed on different artifacts varied by subfield and methodological approach.
+Researchers identified the unavailability of research artifacts (e.g., data, code) as a second barrier to reproducibility, but the importance placed on different artifacts varied by subfield and methodological approach.
 A higher percentage physical and methods-focused researchers identified all five of the artifacts we investigated as common barriers to reproducibility as compared to human and nature-society researchers.
@@
 \begin{itemize}
+    \item Geographic researcher closely link replication and reproduction.
+This isn't surprising as geographic researchers often have training from other disciplines and variation in the use of the two term, and their outright reversal in meaning, is well documented.
+It is likely that this is the root of the conflation.
+This muddling of the definition has important implications ...
     \item The reproducibility literature emphasizes quantitative, particularly computational, forms of research.

### 2023-02-01 procedure/code/201c_Q10_coding.R
Cleaned up analysis folder structure to create Q6 and Q10 subfolders and move associated coding workbooks to relevant locations. Created a full_Q10_coding.csv that includes all 3 of our codings and a couple flag variables to capture any discrepancies across our 3 coding workbooks.

@@ -1,0 +1,54 @@
+# list of required packages
+packages = c("here","tidyverse","table1","officer","readxl")
+
+# load and install required packages
+package.check <- lapply(
+  packages,
+  FUN = function(x) {
+    if (!require(x, character.only = TRUE)) {
+      install.packages(x, dependencies = TRUE)
+      library(x, character.only = TRUE)
+    }
+  }
+)
+
+# save the R processing environment to r_environment.txt
+writeLines(capture.output(sessionInfo()),here("procedure","environment","r_environment.txt"))
+
+sb_coding <- read_excel(here("data","derived","public","Q10","sb_analysis_10_coding.xlsx"))
+pk_coding <- read.csv(here("data","derived","public","Q10","analysis_10_coding_pk.csv"))
+jh_coding <- read.csv(here("data","derived","public","Q10","analysis_10_coding_jh.csv"))
+
+
+
+table(sb_coding$rp_intent)
+sb_coding <- sb_coding %>% transmute(ResponseId,
+                                     SB_notes = notes,
+                                     sb_rp_intent = 
+                                       ifelse(rp_intent == "Missing", 5,
+                                       ifelse(rp_intent == "Replication", 3,
+                                       ifelse(rp_intent == "Self-Check/Promote transparency of own work", 2,
+                                       ifelse(rp_intent == "Teaching/Learning", 4,
+                                       ifelse(rp_intent == "Verification/Peer-Review", 1, 5))))))
+table(sb_coding$sb_rp_intent)
+
+pk_coding <- pk_coding %>% transmute(ResponseId,
+                                     PK_notes = notes,
+                                     pk_rp_intent = rp_intent)
+
+combined_sb_pk <- merge(sb_coding,pk_coding,by="ResponseId")
+combined_all <- merge(jh_coding,combined_sb_pk,by="ResponseId")
+
+#Replace NA values with 0 and create logical statements to identify discrepancies
+combined_all <- combined_all %>%
+                         mutate(any_diff = ifelse(rp_intent != sb_rp_intent | rp_intent != pk_rp_intent, 1, 0),
+                                no_agreement = ifelse(rp_intent != sb_rp_intent & rp_intent != pk_rp_intent & sb_rp_intent != pk_rp_intent, 1, 0)) %>%
+                         select(X, ResponseId, Q3_recoded, Q4, Q10, rp_intent, sb_rp_intent, pk_rp_intent, 
[…]

### 2023-02-01 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 In a direct assessment of reproducibility, an independent team(s) of researchers repeats the analytical steps of a previous study using the same data and then evaluates the consistency of the two sets of results\footnote{Insert paragraph on the difficulty of developing in using consistency criteria}.
-By contrast, during an indirect assessment of reproducibility, a research team gathers information about the transparency of a study and the availability of the research components (e.g., data and code) needed to recreate that study, but does not directly attempt to recreate the results.
-Indirect assessments also often take the form of surveys in which researchers are asked about their research practices, incentives, and motivations.
+Direct reproducibility assessments aim to establish whether the data and analysis presented in support of a result do in fact support that result.
+By contrast, indirect assessments of reproducibility aim to establish whether study data and procedures are presented with sufficient transparency and clarity that research results could be subjected to a direct assessment.
+During an indirect assessment of reproducibility, a research team gathers information about the transparency of a study and the availability of the research components (e.g., data and code) needed to recreate that study, but does not directly attempt to recreate the results.
+Indirect assessments also often take the form of surveys in which researchers are asked about their research practices, incentives, and motivations to measure the transparency and practices of a subset if researchers.
 
 Direct and indirect reproducibility assessments present a trade off between the depth and breadth of evaluation.  
-A direct assessment that carefully reproduces a study can provide insight into how a particular study was conducted and why a consistent result could, or could not, be obtained.  
+A direct assessment can provide insight into how a particular study was conducted and why a consistent result could, or could not, be obtained.  
 However, such assessments are resource and time intensive, which makes them difficult to scale to a large number of studies. 
 Constrained to a limited number of studies, direct assessments offer only suggestive evidence about the reproducibility of unevaluated studies and the prevalence of reproducible research practices. 
-In contrast, comparatively less resource intensive indirect assessments that catalog reproducible research practices can be more easily scaled.
+In contrast, comparatively less resource intensive indirect assessments that simply catalog reproducible research practices can be more easily scaled.
 By evaluating many studies, indirect assessments provide evidence of how common reproducible research practices are and, by extension, how reproducible work in a field of study is likely to be.
@@
 Reproduction attempts remain relatively rare, and those that do exist \citep[see][]{chang2015economics, moraila2014measuring} have selectively targeted publications in high-impact journals and conference papers series in a limited number of disciplines that are not representative of many forms of research.
-Indirect reproducibility assessments that catalog the availability of research components similarly focus on conveniently accessible archives, such as conference paper series \citep{gundersen2018state, ostermann2017}, or target specific journals and disciplinary repositories \citep{stodden2018empirical, stodden2018enabling, byrne_2017}.
+Indirect reproducibility assessments similarly focus on conveniently accessible archives, such as conference paper series \citep{gundersen2018state, ostermann2017}, or target specific journals and disciplinary repositories \citep{stodden2018empirical, stodden2018enabling, byrne_2017}.
 These assessments have also tended to focus on evaluating the computational components of research such as data and code availability, as this information is easier to identify and assess at scale when compared to components like field procedures or qualitative analysis that may be included only in text.
-Surveys of researcher practices and attitudes on reproducibility face similar challenges to their generalizability. 
-Rather than carefully defining researcher populations of interest, prior surveys have drawn data non-randomly from self-selecting populations that are convenient to survey (e.g., members of professional association, conference attendees), but are not necessarily representative of researchers active in a particular field.
+Surveys of researcher practices and attitudes on reproducibility face similar challenges. 
+Rather than carefully defining researcher populations of interest, existing surveys have drawn data non-randomly from self-selecting populations that are convenient to survey (e.g., members of professional association, conference attendees), but are not necessarily representative of researchers active in a particular field.
 These surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response.
 
-While it may not be possible to determine the extent of irreproducibility across or within disciplines, it is possible to draw lessons about potential sources of irreproducibility from available studies.
-The evidence available from direct and indirect reproducibility assessments suggests inadequate record keeping, opaque reporting, unavailable research components, and a lack of incentives are important factors contributing to the irreproducibility of research \citep{NASEM2019}.
+While it may not be possible to determine the extent of irreproducibility across or within disciplines from available studies, it is possible to draw lessons about potential sources of irreproducibility.
+The available evidence suggests inadequate record keeping, opaque reporting, unavailable research components, and a lack of incentives are likely important factors contributing to the irreproducibility of research \citep{NASEM2019}.
 Prominent attempts to reproduce research in economics \citep{chang2015economics}, computer science \citep{moraila2014measuring}, and psychology \citep{open2015estimating} have all been able to reproduce only a small portion of studies because original authors did not share data or adequate information about their procedures.
-Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread, as the majority of articles reviewed did not share data adequate for reproducibility.
-
-Surveys of researchers about reproducibility issues and related research practices paint a similar picture. 
+Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread, 
+Reproducibility surveys paint a similar picture. 
 Recent surveys suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
 Moreover, a sizable portion of the researchers responding to these surveys admit to engaging in questionable research practices linked to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
-For example, in a survey of 807 ecologists and evolutionary biologists, 64 percent admitted to failing to report non-significant results and 51 percent admitted to presenting unexpected findings as if they been hypothesized from the start of the research \citep{fraser2018questionable}.
-These findings also match researcher perceptions, which link irreproducibility to causes ranging from natural variation to outright fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}.
+For example, in a survey of 807 ecologists and evolutionary biologists, 64 percent admitted to failing to report non-significant results and 51 percent admitted to presenting unexpected findings as if they had been hypothesized from the start of the research \citep{fraser2018questionable}.
+These findings match researcher perceptions, which link irreproducibility to causes ranging from natural variation to outright fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}.
 
@@
 For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort.
-A related effort to reproduce 31 papers published in the conference series of the Association of Geographic Information Laboratories in Europe \citep{Nust_AGILE_2020, Nust2021AGILE, Nust_AGILE_2022} similarly identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results.
+A related effort to reproduce 31 papers published in the conference series of the Association of Geographic Information Laboratories in Europe \citep{Nust_AGILE_2020, Nust2021AGILE, Nust_AGILE_2022} identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results.
 \citet{konkol2019}'s attempt to reproduce of 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves).
@@
 The survey instrument used in this study is available through the Survey of Reproducibility in Geographic Research Repository.
-The survey consists of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reprodicibility.
+The survey consists of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reprodicibility, and (iv) experience conducting independent reproductions.
 Survey questions were developed following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature.
+All researchers were presented questions about their definition of reproducibility, familiarity with and use of reproducible practices, and perceptions of barriers to reproducibility. 
+However, a subset of researchers that reported attempting to reproduce a study in the past two years were given an additional set of questions about their experience conducting that work.
+
 Because this survey had not been previously fielded, we pilot tested the instrument with a subset of \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background.
@@
 \subsection*{Analytical Approach}
-We conduct two statistical analyses of the survey response
-\endnote{The full methodological details of our statistical analyses, and a complete history of our response coding a variable construction is included in the Github repository linked to OSF repository that accompanies this paper.
+We conduct two statistical analyses of the survey response\endnote{The full methodological details of our statistical analyses, and a complete history of our response coding a variable construction is included in the Github repository linked to OSF repository that accompanies this paper.
 All of the results presented in this paper can be independently reproduced using the materials in that repository.}.
 First, we create descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
-Each of these topics is linked to a subset of survey questions, which we examine individually.
-As a summary measure for each topic, we created a single variable that aggregates individual responses to the subset of questions linked to that topic.
-Each of these measures is described below.
+Second, we conducted an analysis of the experience of the subset of geographic researchers who reported attempting independent reproductions of prior work during the last two years that identified what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
 
-We measured the similarity of each participant's definition of reproducibility relative to the definition of adopted by the \citet{NASEM2019}. 
-The NASEM defines reproducibile research as having four characteristics --- same data, same procedure, same results, same context.
-Before being provided this standardized definition, each participant was asked to provide their own definition of reproducibility.
-Two of the authors independently coded these text responses for the presence/absence of each of the four characteristics included in the NASEM definition.
-Disagreements were resolved through discussion between the two authors. 
-As a final check, the third author reviewed the final list in light of the four dimensions.
-The coded response for each participant was then summed across the four characteristics creating the variable, \textit{DEF} with domain [0---no characteristics shared, 4---all characteristics shared].
+%%%%%%%%%%%
+\subsubsection*{Variable Construction}
+For our first analysis, we constructed summary measures that aggregated researcher responses to questions linked to 1) definitions of reproducibility, 2) familiarity with and 3) use of reproducible research practices, and 4) potential barriers to reproducibility.
 
-We measured participant familiarity and experience with five reproduciblity enhancing research practices --- open source software, research notebooks, data sharing, code sharing, and pre-registration.
-We created a summary measure of research familiarity, \textit{f}, with these practices by summing the number of reproducible and open science practices a researcher was 'somewhat' or 'very' familiar with.
-To assess researcher experience with reproducible practices, we similarly created a summary variable, \textit{p}, that counts the number of reproducible practices a researcher uses 'most of the time' or 'always' when conducting their own research.
+\textit{Definition:} Before providing a common definition, we asked each participant to provide their own definition of reproducibility.
+We measured the similarity of the definition provided by each participant to the definition of adopted by the \citet{NASEM2019}. 
+The NASEM defines reproducibile research as having four characteristics --- same data, same procedure, same results, and same context.
+To make this comparison, two of the authors independently coded the definition provided by each respondent for the presence/absence of each of the four characteristics included in the NASEM definition.
+Disagreements in the assignment of codes were resolved through discussion between the two authors. 
+As a final check, the third author reviewed rectified coding and resolved any remaining disputes.
+To create an aggregate measure of agreement the final coded response for each participant was then summed across the four characteristics, creating definition similarity \textit{d} with domain [0, 4].
+
+\textit{Familiarity and Experience:} We measured participant familiarity and experience with five reproduciblity enhancing research practices; the use of --- open source software, research notebooks, data sharing, code sharing, and pre-registration.
+We created a summary measure of research familiarity with these practices, \textit{f}, by summing the number of reproducible practices a researcher was 'somewhat' or 'very' familiar with.
+To assess researcher experience with reproducible practices, we created \textit{p}, which counts the number of reproducible practices a researcher reported using 'most of the time' or 'always' when conducting their own research.
 Both \textit{f} and \textit{p} have domains [0,5].
-Finally, we created a variable, \textit{b}, that counts the number of factors a researcher believe 'frequently' or 'occasionally' contributed to a lack of reproducibility in the discipline. 
-This variable aggregated participant response across 12 questions and ranges and has domain [0,12].
-Given the topical and epistemological variation that exists among geographic researchers, we also examined group-wise differences in each aggregated measure by disciplinary subfield and methodological approach.
+
+\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 factors contributed to a lack of reproducibility in the discipline. 
+From those responses, we created a summary measure, \textit{b} with domain [0,12], of the number of barriers a researcher believes 'frequently' or 'occasionally' contributed to irreproducibility.
+
+Our second analysis examines only researchers that reported attempting a reproduction in the past two years. 
+We asked each of these researchers what motivated their reproduction attempt.
+
+%%%%%%%%%%%
+\subsubsection*{Analytical Methods}
+Given the topical and epistemological variation that exists among geographic researchers, we examined group-wise differences in each aggregated measure by disciplinary subfield and methodological approach.
 
@@
 We also investigate why researchers were unable to reproduce results.
-ADD DETAILS ABOUT HOW WE ANALYZE.
 

### 2023-02-02 docs/manuscript/manuscript.tex

@@
 \begin{abstract}
-While the number of reproduction and replication studies undertaken in the social and behavioural sciences continues to rise, such studies have not yet become commonplace in geography. 
+While the number of reproduction and replication studies undertaken in the social and behavioral sciences continues to rise, such studies have not yet become commonplace in geography. 
 Existing attempts to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 

### 2023-02-11 procedure/code/201_clean.R
Cleaned up results folder to remove unnecessary tables, updated cleaning and analysis programs to recalculate definitions row to be among all individuals who reported some familiarity with the term reproducibility regardless of validity of definition provided, and regenerated Table 9 results.

@@ -279,7 +279,7 @@ q10_coding <- read.csv(here("data","derived","public","final_full_q10_coding.csv
 q10_coding <- q10_coding  %>% select(ResponseId, consensus, starts_with("X"))
 
 q6_coding <- read.csv(here("data","derived","public","final_full_q6_coding.csv"))
-q6_coding <- q6_coding  %>% select(ResponseId, ends_with("_rec"), Rejection, Missing.x)
+q6_coding <- q6_coding  %>% select(ResponseId, ends_with("_rec"), Rejection, label)
 
 #-Merge qualitative coding back to main analysis file and construct additional variables
 survey_resp <- left_join(int_hegs_rpr,q10_coding, by ="ResponseId")
@@ -292,7 +292,8 @@ survey_resp <- survey_resp %>% mutate(rp_conservative = ifelse(Q11_1 == "All" | 
                                       access_some_data_code = ifelse(access_some_code == 1 & access_some_data == 1, 1, 0),
                                       access_all_data_code = ifelse(Q12_1 == "Yes, all" & Q12_2 == "Yes, all",1,0),
                                       Q10_recoded = as.factor(consensus),
-                                      definition_sum = dat_rec + pro_rec + res_rec + con_rec)
+                                      definition_sum = ifelse(label == "Omit", NA, dat_rec + pro_rec + res_rec + con_rec),
+                                      definition_label = label)
 levels(survey_resp$Q10_recoded) <- c("Verification/Peer-Review",
                                      "Self-check",
                                      "Replication",

### 2023-02-11 procedure/code/202_preprocess.R

@@ -269,35 +269,6 @@ t1flex(rp_table7) %>%
   save_as_docx(path = here("results","tables","MSWord","Table7_RP_reasons.docx"),
                pr_section = sect_properties)
 
-#- Exploratory analysis about access to data and code with respect to reproduction results
-all_partial_reproduction <- reproduction_analysis %>% filter(Q11_2 == "All")
-some_partial_reproduction <- reproduction_analysis %>% filter(Q11_2 == "Some")
-all_identical_reproduction <- reproduction_analysis %>% filter(Q11_1 == "All")
-some_identical_reproduction <- reproduction_analysis %>% filter(Q11_1 == "Some")
-
-table1::label(all_partial_reproduction$Q12_1) <- "Access to study's data"
-table1::label(some_partial_reproduction$Q12_1) <- "Access to study's data"
-table1::label(all_identical_reproduction$Q12_1) <- "Access to study's data"
-table1::label(some_identical_reproduction$Q12_1) <- "Access to study's data"
-
-table1::label(all_partial_reproduction$Q12_2) <- "Access to study's code"
-table1::label(some_partial_reproduction$Q12_2) <- "Access to study's code"
-table1::label(all_identical_reproduction$Q12_2) <- "Access to study's code"
-table1::label(some_identical_reproduction$Q12_2) <- "Access to study's code"
-
-all_partial <- table1::table1(~Q12_1 | Q12_2 , data = all_partial_reproduction) 
-some_partial <- table1::table1(~Q12_1 | Q12_2 , data = some_partial_reproduction)
-all_identical <- table1::table1(~Q12_1 | Q12_2 , data = all_identical_reproduction)
-some_identical <- table1::table1(~Q12_1 | Q12_2 , data = some_identical_reproduction)
-
-
-write.table(all_partial, here("results","tables","Data_Code_Matrix_all_partial.csv"), col.names = T, row.names=F, append= T, sep=',')
-write.table(some_partial, here("results","tables","Data_Code_Matrix_some_partial.csv"), col.names = T, row.names=F, append= T, sep=',')
-write.table(all_identical, here("results","tables","Data_Code_Matrix_all_identical.csv"), col.names = T, row.names=F, append= T, sep=',')
-write.table(some_identical, here("results","tables","Data_Code_Matrix_some_identical.csv"), col.names = T, row.names=F, append= T, sep=',')
-
-
-
 #---------------------------------------------------------------------------------------
[…]

### 2023-02-11 procedure/code/201_clean.R
Created new Table 10 tables to describe types of definitions provided by respondents and updated cleaning and analysis programs accordingly.

@@ -292,14 +292,20 @@ survey_resp <- survey_resp %>% mutate(rp_conservative = ifelse(Q11_1 == "All" | 
                                       access_some_data_code = ifelse(access_some_code == 1 & access_some_data == 1, 1, 0),
                                       access_all_data_code = ifelse(Q12_1 == "Yes, all" & Q12_2 == "Yes, all",1,0),
                                       Q10_recoded = as.factor(consensus),
-                                      definition_sum = ifelse(label == "Omit", NA, dat_rec + pro_rec + res_rec + con_rec),
+                                      definition_sum = ifelse(Q5 == "Not at all", NA, dat_rec + pro_rec + res_rec + con_rec),
                                       definition_label = label)
+
+
 levels(survey_resp$Q10_recoded) <- c("Verification/Peer-Review",
                                      "Self-check",
                                      "Replication",
                                      "Teaching/Learning",
                                      "Missing")
 
+#Check coding
+# ensure no responses wher Q5= "Not at all" are included in def_sum
+table(survey_resp$definition_sum,survey_resp$Q5) 
+# confirm that 3 individuals neither achieved a conservative nor liberal reproduction
 table(survey_resp$rp_conservative,survey_resp$rp_liberal)
 survey_resp %>% 
   select(Q11_1,Q11_2) %>% 

### 2023-02-11 procedure/code/202_preprocess.R

@@ -397,7 +397,13 @@ table(survey_resp$familiar)
 table(survey_resp$practices)
 table(survey_resp$barriers)
 
-table1::label(survey_resp$defimitions) <- "Definition of reproducibility"
+table(survey_resp$Q5,survey_resp$definition_sum)
+table(survey_resp$label,survey_resp$definition_sum)
+
+survey_resp %>% filter(label=="Omit") %>% select(definition_sum)
+
+
+table1::label(survey_resp$definitions) <- "Definition of reproducibility"
 table1::label(survey_resp$familiar) <-  "Familiarity with reproducible practices"
 table1::label(survey_resp$practices) <- "Experience with reproducible practices"
 table1::label(survey_resp$barriers) <-  "Barriers to reproducibility"
@@ -420,4 +426,19 @@ t1flex(Q4_table9) %>%
 
 #---------------------------------------------------------------------------------------
 
+def_sample <- survey_resp %>% filter(Q5 != "Not at all")
+table1::label(def_sample$definition_label) <- "Type of definition"
 
+Q3_table10 <- table1::table1(~definition_label | Q3_recoded , data = def_sample)
+Q4_table10 <- table1::table1(~definition_label | Q4, data = def_sample)
+
+write.table(Q3_table10 , here("results","tables","Table10_def_types_discipline.csv"), col.names = T, row.names=F, append= T, sep=',')
+write.table(Q4_table10 , here("results","tables","Table10_def_types_method.csv"), col.names = T, row.names=F, append= T, sep=',')
+
+t1flex(Q3_table10) %>% 
+  save_as_docx(path = here("results","tables","MSWord","Table10_def_type_discipline.docx"),
+               pr_section = sect_properties)
+
+t1flex(Q4_table10) %>% 
+  save_as_docx(path = here("results","tables","MSWord","Table10_def_type_method.docx"),
+               pr_section = sect_properties)

### 2023-02-14 docs/manuscript/manuscript.tex

@@
 \usepackage{threeparttable}
+
+\usepackage{lscape}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \section*{Introduction}
 Reproducibility as a characteristic of a study that lends it credibility v. Reproducibility as a error correcting function of science.
-
-\newpage
 
@@
 By evaluating many studies, indirect assessments provide evidence of how common reproducible research practices are and, by extension, how reproducible work in a field of study is likely to be.
-The trade off being that indirect assessments do not offer as detailed a look into why a particular result in a specific instance could, or could not, be obtained.
 
@@
 Prominent attempts to reproduce research in economics \citep{chang2015economics}, computer science \citep{moraila2014measuring}, and psychology \citep{open2015estimating} have all been able to reproduce only a small portion of studies because original authors did not share data or adequate information about their procedures.
-Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread, 
+Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread. 
 Reproducibility surveys paint a similar picture. 
@@
 \subsection*{Analytical Approach}
+
+%%%%%%%%%%%
+\subsubsection*{Statistical Approach}
 We conduct two statistical analyses of the survey response\endnote{The full methodological details of our statistical analyses, and a complete history of our response coding a variable construction is included in the Github repository linked to OSF repository that accompanies this paper.
@@
 Second, we conducted an analysis of the experience of the subset of geographic researchers who reported attempting independent reproductions of prior work during the last two years that identified what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
+Given the topical and epistemological variation that exists among geographic researchers, we examined differences by disciplinary subfield and methodological approach as part of each analysis.
 
@@
 
-\textit{Definition:} Before providing a common definition, we asked each participant to provide their own definition of reproducibility.
-We measured the similarity of the definition provided by each participant to the definition of adopted by the \citet{NASEM2019}. 
-The NASEM defines reproducibile research as having four characteristics --- same data, same procedure, same results, and same context.
-To make this comparison, two of the authors independently coded the definition provided by each respondent for the presence/absence of each of the four characteristics included in the NASEM definition.
+\textit{Definition:} Before providing a common definition of reproducibility, we asked each participant to provide their own definition.
+We measured the similarity of each provided definition to the definition of adopted by the \citet{NASEM2019}. 
+The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same context.
+To make this comparison, two of the authors independently coded each provided definition for the presence/absence of each of the four characteristics included in the NASEM definition.
 Disagreements in the assignment of codes were resolved through discussion between the two authors. 
@@
 We created a summary measure of research familiarity with these practices, \textit{f}, by summing the number of reproducible practices a researcher was 'somewhat' or 'very' familiar with.
-To assess researcher experience with reproducible practices, we created \textit{p}, which counts the number of reproducible practices a researcher reported using 'most of the time' or 'always' when conducting their own research.
+To assess researcher experience with these same five practices, we created \textit{p}, which counts the number of practices a researcher reported using 'most of the time' or 'always' when conducting their own research.
 Both \textit{f} and \textit{p} have domains [0,5].
@@
 We asked each of these researchers what motivated their reproduction attempt. 
-
-%%%%%%%%%%%
-\subsubsection*{Analytical Methods}
-Given the topical and epistemological variation that exists among geographic researchers, we examined group-wise differences in each aggregated measure by disciplinary subfield and methodological approach.
-
-Second, we conducted an analysis of the experience of geographic researchers who have attempted reproductions of prior work. 
-We examine what motivates geographic researchers to attempt to reproductions and how successful researchers attempting reproductions were at recreating existing results. 
-We also investigate why researchers were unable to reproduce results.
+Two of the authors independently assigned these responses to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and increase the transparency of their work, ii) a desire to learn from past work, or use the reproduction in teaching.
+Some authors provided motivation linked to the replication of results in new geographic contexts. 
+Because these responses did not match our provided definition of reproduction, we removed these from the subsample. 
+We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
 
@@
 The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. 
-The refusal rate was 3.1 percent.
-\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
-The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}
+The refusal rate was 3.1 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
+The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
 Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
@@
 Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%) with half reporting being very familiar with the term (53.6\%).
-A majority of researchers also believe reproducibility is compatible with epistemologies used in discipline (72.0\%). 
+A majority of researchers also believe reproducibility is compatible with epistemologies used in the discipline (58.2\%). 
 However, researchers estimated that only half of the results published in the discipline were reproducible, albeit with wide variance ($\overline{rep}=50.6\%$, $\sigma=24.7\%$), and reported limited familiarity with and use of many reproducible research practices.
-Few respondents reported attempting to reproduce the work of other researchers (\%) with fewer still attempting to publish those reproduction studies (\%).
+Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%).
 
-Table 1 presents our summary measures for each topic, as well as those measures by subgroup.
+Table \ref{tab:overview} summarizes how  researchers define reproducibility (\textit{d}), their familiarity with (\textit{f}) and use of (\textit{p}) reproducible research practices, and the factors they see as barriers (\textit{b}) to reproducibility in geography.
+We present the mean and standard deviation for the overall sample and for each subfield and methodological approach.
+The following sub-sections discuss each of these topics in turn.
 
-\begin{table}[h]
-    \centering
-    \begin{threeparttable}
-    \caption{Descriptive summary of survey results}
-    \begin{tabular}{l c c c c c c c c c c}
-         \hline
-                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & \\
-         Measure    & HU & PH & NS & MT            & & QN & QL & MX              & & Overall \\
-         \hline
-         Definition (\textit{d}) & \begin{tabular}[c]{@{}c@{}}1.76\\ (1.17)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}1.68\\ (1.12)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}1.97\\ (1.08)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}1.77\\ (1.10)\end{tabular} & 
-                        & 
-                        \begin{tabular}[c]{@{}c@{}}1.89\\ (1.14)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}1.53\\ (1.28)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}1.78\\ (1.06)\end{tabular} & 
-                        & 
-                        \begin{tabular}[c]{@{}c@{}}1.77\\ (1.15)\end{tabular} \\
-         Familiarity (\textit{f}) &  \begin{tabular}[c]{@{}c@{}}2.35\\ (1.36)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}3.71\\ (0.98)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}2.28\\ (1.76)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}3.97\\ (0.86)\end{tabular} &
-                        &
-                        \begin{tabular}[c]{@{}c@{}}3.75\\ (0.98)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}1.75\\ (1.30)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}3.56\\ (1.22)\end{tabular} &
-                        &
-                        \begin{tabular}[c]{@{}c@{}}3.26\\ (1.36)\end{tabular}\\
-
-         Experience (\textit{p}) &  \begin{tabular}[c]{@{}c@{}}0.60\\ (0.80)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}2.06\\ (1.18)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}1.18\\ (0.96)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}1.85\\ (1.38)\end{tabular} &
-                        &
-                        \begin{tabular}[c]{@{}c@{}}1.63\\ (1.32)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}0.48\\ (0.68)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}1.69\\ (1.24)\end{tabular} &
-                        &
-                        \begin{tabular}[c]{@{}c@{}}1.44\\ (1.28)\end{tabular}\\
-
-         Barriers (\textit{b})   &  \begin{tabular}[c]{@{}c@{}}7.32\\ (3.57)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}8.31\\ (3.00)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}7.44\\ (3.20)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}9.31\\ (2.79)\end{tabular} &
-                        &
-                        \begin{tabular}[c]{@{}c@{}}8.78\\ (2.80)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}5.97\\ (3.83)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}8.58\\ (2.96)\end{tabular} &
-                        &
-                        \begin{tabular}[c]{@{}c@{}}8.20\\ (3.24)\end{tabular}\\
-                     & & & & & & & & & &\\
-         N           & 67 & 65 & 22 & 61 & & 92 & 40 & 85 & & 218 \\
-         Missing     & 14 & 4  & 4  & 6  & & 6 & 9 & 14 & & 29 \\
-        \hline
-    \end{tabular}
-    \begin{tablenotes}
-        \footnotesize
-        \item \textit{HU} Human Geography, \textit{PH} Physical Geography, \textit{NS} Nature and Society, \textit{MT} GIScience and Methods; \textit{QN} Quantitative, \textit{QL} Qualitative, \textit{MX} Mixed Methods.
-    \end{tablenotes}
-    \label{tab:overview}
-    \end{threeparttable}
-\end{table}
+\begin{center}
+\textbf{Insert Table \ref{tab:overview} About Here}
+\end{center}
 
@@
 \subsubsection*{Definitions and Importance of Reproducibility}
-Geographic researchers provided definitions of reproducibility that generally explicitly included one to two ($\overline{d}=1.77$) of the four characteristics from the definition adopted by the NASEM.
+A total of \textit{$n_{d}$}=181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
+On average, geographic researchers provided definitions of reproducibility that generally explicitly included one to two ($\overline{d}=1.83$) of the four characteristics from the definition adopted by the NASEM.
 This level of inclusion was consistent across subfields and methodological approaches.
@@
 This patterns was also consistent across subfields and approaches, with a slightly greater emphasis on data and procedural consistency and availability amongst quantitative and methods focused researchers.
-The lower inclusion of data and context in definitions matched the conflation of reproduction and replication by a minority of researchers (\%).
+The lower inclusion of data and context in definitions matched the conflation of reproduction and replication by a minority of researchers (20.4\%).
 
-Researchers defined reproducibility in relation to two epistemic functions.
-Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies.
+Researchers definitions of reproducibility were connected to two epistemic functions.
+Just under half of respondents (45.9\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies.
 Nearly all other researchers (40.9\%) tied reproducibilty to the need for transparency in research so others could independently expand upon past studies.
-Both of these functions were supported by respondents across our sample. 
+Identification of reproducibility with both of these functions was supported by responses to related questions from our entire sample. 
 Overall, a majority of researchers also identified reproducibility as an important for validating (75.2\%) and establishing the credibility (72.5\%) of research.  
@@
 
-Geographic researchers are on average familiar with multiple reproducible research practices ($\overline{f}=3.26$, Table \ref{tab:overview}), but reported limited use of these practices in their own work ($\overline{p}=1.44$).
+Geographic researchers are on average familiar with multiple reproducible research practices ($\overline{f}=3.26$), but reported limited use of these practices in their own work ($\overline{p}=1.44$).
 More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\% ).
@@
 For example, quantitiative and mixed-methods researchers reported familiarity with open source software (QT=96.7\%, MX=89.5\%) and code sharing (QT=81.5\%, MX=55.7\%).
-In contrast, a smaller percentage of qualitative researchers reported familiarity with these same practices (OS=52.5\%, Code=12.5\%).
+In contrast, a smaller percentage of qualitative researchers reported familiarity with open source software (52.5\%) and code sharing (12.5\%).
 However, even among quantitiative and mixed-methods researchers familiarity with reproducible research practices did not translate into regular use of those practices.
@@
 Aligning with the differences we observed between researcher familiarity with reproducibility enhancing research practices and researcher use of those same practices, respondents to our survey identified numerous factors contributing to a lack or reproducible research across the discipline ($\overline{b}=8.20$).
-Geographic researchers working in different subfields and with different methodological approaches each identified a similar number of barriers to reproducibility (Table \ref{tab:overview}).
+Geographic researchers working in different subfields and with different methodological approaches each identified a similar number of barriers to reproducibility.
 Qualitative geographers may be the one group that deviates from this consistent pattern. 
 These researchers identified fewer barriers to reproducibility on average, but with a greater variance that left us unable to distinguish this group from any other ($\overline{b_{QL}}=5.97, \sigma_{QL}=3.83$).
-To examine differences in researcher beliefs about specific factors potentially hindering reproducibility in the discipline, we divided the 12 factors we examined into three groups --- those related to the research environment, the availability of research artifacts, and study-specific characteristics (Table \ref{tab:barriers}).
+To examine differences in researcher beliefs about specific factors potentially hindering reproducibility in the discipline, we divided the 12 factors we examined into three groups --- those related to the research environment, the availability of research artifacts, and study-specific characteristics.
 
+\begin{center}
+\textbf{Insert Table \ref{tab:barriers} About Here}
+\end{center}
+
+Geographic researchers identified the incentive structure of the researcher environment as an important barrier to reproducibility in the discipline.
+A majority of geographic researchers identified both the pressure to publish (71.5\%) and insufficient oversight of the research process (71.1\%) as barriers to reproducibility.
+A high percentage of physical, methods-focused, quantitative, and mixed-methods researchers identified these factors as barriers. 
+Qualtiative geographers were least concerned with these factors, but a majority of these researchers still identified both factors as barriers to reproducibility in the field.
+Contrary to alarms raised in some of the reproducibility literature, a minority of geographic researchers (28.4\%) believe that the fabrication of data, the manipulation of research results, and similar forms of fraud are a cause of irreproducibility in the discipline.
+
+Researchers identified the unavailability of research artifacts (e.g., data, code) as a second barrier to reproducibility, but the importance placed on different artifacts varied by subfield and methodological approach.
+A higher percentage physical and methods-focused researchers identified all five of the artifacts we investigated as common barriers to reproducibility as compared to human and nature-society researchers.
+A similar gap existed between qualitative researchers and those identifying as mixed-methods researchers or quantitative researchers. 
+The largest differences between these groups existed in researchers beliefs about how often the availability of research protocols/code and the use of restricted data or software impacted reproducibility.
+More than three-quarters of physical (77.0\%) and methods-focused (86.9\%) geographers identified the availability of protocols/code as contributing to irreproducibility, whereas less than two-thirds of human (59.7\%) and nature-society (50.0\%) identified this same factor.
+Only a large percentage of methods-focused researchers (82.0\%) identified the use of restricted data/software as a common contributor to irreproducibility in the discipline.
+A similar gap existed between qualitative researchers, a minority of which identified code availability or the use of restricted data/software as contributing to irreproducibility, and quantiative and mixed-methods researchers, the majority of which saw these factors as frequent causes of irreproducibility.
+
+A majority of researchers identified geographic variation (71.5\%), researcher positionality (64.2\%), and chance (62.3\%) as study-specific factors limiting the reproducibility of geographic research.
+Minor variations in the emphasis placed on these factors exist across subfields and approaches. 
+A higher percentage of nature-society (81.8\%) and physical (80.0\%) researchers emphasized the important role the spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researchers across subfields and approaches.
+A smaller percentage of physical geographers placed emphasis on the impact of researcher positionality may have on reproducibility (50.8\%) when compared to all other subfields.  
+Differences between the computational environment used to conduct an original study and a reproduction attempt was generally not seen as a factor contributing to a lack of reproducibility in the discipline.
+The exception being methods-focused (68.9\%) and quantitative researchers (63.1\%\%), which aligns with the research practices used in these areas of research.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Attempted Reproductions}
+A total of 102 of the researchers that responded to our survey (46.8\%) reported attempting a reproduction study during the past two years.
+However, 23 of those reported reproduction attempts were of the researcher own work, while another 13 were in fact replications of prior work in new locations.
+In the end, only \textit{$n_{a}$}=32 (14.7\%) of all respondents reported attempting to reproduce a study originally conducted by another researcher during the past two years.
+
+This subset of 32 participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions of the work of others.
+Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (43.8\%) and geographic methods and Methods (37.5\%).
+Respondents attempting reproductions were also focused on quantitative (68.8\%) and mixed-methods (41.2\%) approaches. 
+Only a quarter (25\%) of the researchers attempting reproductions reported submitting any of their findings for publication.
+
+In most instances, researchers reported some ability to access the research artifacts used in the study they were attempting to reproduce and the ability to recreate at least some of the results of that study.
+The majority of researchers that attempted reproductions (87.5\%) were able to access at least some of the data used in the original study, but few researchers (12.5\%) reported access to all of the original data.
+Researchers also reported the ability to access at least some information about study procedures (68.8\%) and its computational environment (59.4\%), but limited ability to access all procedural (9.4\%) and computational information (12.5\%).
+Despite these limitations, nearly all researchers reported at least partially reproducing some results (81.3\%), but less than half reported being able to at least partially reproduce all results (21.9\%).
+Few researchers were able to identically reproduce all results (9.4\%).
+
+How much access researchers had to study data and procedural information impacted their ability to reproduce results. 
+If geographic researchers had access to at least some of the data and procedures used in the study they were attempting to reproduce, they were able to at least partially reproduce some results in nearly all cases (90.5\%), but were able at least partially reproduce all results only a fraction of the time (14.3\%).
+Accessibility to data and procedures appears to be equally important in raising the chances of reproducing all results. 
+Given access to some or all procedural information, having access to all data doubled a researcher's chances of reproducing all results (69.5\%) when compared to having access to only some of the data (27.5\%).
+We observed the same doubling effect when reversing this relationship. 
+Given access to some or all of a study's data, having access to all the procedural information doubled a researcher's chances of reproducing all results (70.0\%) when compared to having access to only some of the procedures (30.0\%).
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Discussion}
+
+\begin{itemize}
+    \item Geographic researcher closely link replication and reproduction.
+This isn't surprising as geographic researchers often have training from other disciplines and variation in the use of the two term, and their outright reversal in meaning, is well documented.
+It is likely that this is the root of the conflation.
+This muddling of the definition has important implications ...
+    \item The reproducibility literature emphasizes quantitative, particularly computational, forms of research.
+This emphasis necessarily carried over into our survey instrument, which may automatically lower response scores for researchers not working in these areas (e.g., qualitative, human geography).
+This reality may automatically deflate the aggregate measures of certain sub-group.
+We can use the response to Q8f as a filter to explore this issue.
+These scores do reflect their present level of understanding, but the practices may not be relevant to their methods or epistomologies.
+This fact suggests a meed to examine what reproducibility means in the context of geography's qual, NS, and human traditions.
+    \item A standing question is how should geographic research approaches be designed to efficiently generate reliable knowledge.
+    \item Add discussion about limitation of creating strata for the sample frame being limited so we could not post-stratify.
+\end{itemize}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Conclusion}
+
+\begin{itemize}
+    \item Overall story is that collectively geographers are aware of reproducible research practices, but don't have a matching amount of direct experience using those practices.
+There are also many perceived barriers to conducting reproducible research.
+\end{itemize}
+
+\theendnotes
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\section*{Acknowledgement(s)}
+We thank Tyler Hoffman for providing technical assistance in the development and execution of a set of trial queries using the Scopus API.
+
+\section*{Funding}
+This material is based on work supported by the National Science Foundation under Grant No. \textbf{BCS-2049837}.
+
+\section*{Notes on contributor(s)}
+\textbf{Kedron:} Conceptualization, Methodology, Writing - Original Draft, Writing - Review and Editing, Supervision, Project Administration, Funding Acquisition.
+\textbf{Holler:} Conceptualization, Methodology, Data Curation, Writing - Review and Editing, Funding Acquisition.
+\textbf{Bardin:} Conceptualization, Methodology, Writing - Original Draft, Writing - Review and Editing, Data Curation, Software.
+
+\newpage
+\bibliography{references}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{landscape}
+\begin{table}[h]
+    \centering
+    \begin{threeparttable}
+    \caption{Descriptive summary of survey results}
+    \begin{tabular}{l c c c c c c c c c c c c}
+         \hline
+                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & &         &   & \\
+         Measure    & HU & PH & NS & MT             & & QN & QL & MX                 & & Overall & N & Missing \\
+         \hline
+         Definition (\textit{d}) & \begin{tabular}[c]{@{}c@{}}1.84\\ (1.14)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.73\\ (1.11)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.86\\ (1.06)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}2.00\\ (1.09)\end{tabular} & 
+                        & 
+                        \begin{tabular}[c]{@{}c@{}}1.91\\ (1.13)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.69\\ (1.26)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.82\\ (1.04)\end{tabular} & 
+                        & 
+                        \begin{tabular}[c]{@{}c@{}}1.83\\ (1.12)\end{tabular} &
+                        181 &
+                        30 \\
+         Familiarity (\textit{f}) &  \begin{tabular}[c]{@{}c@{}}2.36\\ (1.36)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}3.71\\ (0.98)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}2.82\\ (1.76)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}3.97\\ (0.86)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}3.75\\ (0.98)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}1.75\\ (1.30)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}3.46\\ (1.22)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}3.26\\ (1.36)\end{tabular} &
+                        218 &
+                        0 \\
+         Experience (\textit{p}) &  \begin{tabular}[c]{@{}c@{}}0.60\\ (0.80)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}2.06\\ (1.18)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.18\\ (0.96)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}1.85\\ (1.38)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}1.63\\ (1.32)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}0.48\\ (0.68)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}1.69\\ (1.24)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}1.44\\ (1.28)\end{tabular}
+                        &
+                        218 &
+                        0 \\         
+         Barriers (\textit{b})   &  \begin{tabular}[c]{@{}c@{}}7.32\\ (3.57)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}8.31\\ (3.00)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}7.44\\ (3.20)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}9.31\\ (2.79)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}8.78\\ (2.80)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}5.97\\ (3.83)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}8.58\\ (2.96)\end{tabular} &
+                        &
+                        \begin{tabular}[c]{@{}c@{}}8.20\\ (3.24)\end{tabular} &
+                        182 &
+                        29 \\
+        \hline
+    \end{tabular}
+    \begin{tablenotes}
+        \footnotesize
+        \item \textit{HU} Human Geography, \textit{PH} Physical Geography, \textit{NS} Nature and Society, \textit{MT} GIScience and Methods; \textit{QN} Quantitative, \textit{QL} Qualitative, \textit{MX} Mixed Methods.
+    \end{tablenotes}
+    \label{tab:overview}
+    \end{threeparttable}
+\end{table}
+\end{landscape}
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
 \begin{table}[h]
@@
 \end{table}
-
-Geographic researchers identified the incentive structure of the researcher environment as an important barrier to reproducibility in the discipline.
-A majority of geographic researchers identified both the pressure to publish (71.5\%) and insufficient oversight of the research process (71.1\%) as barriers to reproducibility.
-A high percentage of physical, methods-focused, quantitative, and mixed-methods researchers identified these factors as barriers. 
-Qualtiative geographers were least concerned with these factors, but a majority of these researchers still identified both factors as barriers to reproducibility in the field.
-Contrary to alarms raised in some of the reproducibility literature, a minority of geographic researchers (28.4\%) believe that the fabrication of data, the manipulation of research results, and similar forms of fraud are a cause of irreproducibility in the discipline.
-
-Researchers identified the unavailability of research artifacts (e.g., data, code) as a second barrier to reproducibility, but the importance placed on different artifacts varied by subfield and methodological approach.
-A higher percentage physical and methods-focused researchers identified all five of the artifacts we investigated as common barriers to reproducibility as compared to human and nature-society researchers.
-A similar gap existed between qualitative researchers and those identifying as mixed-methods researchers or quantitative researchers. 
-The largest differences between these groups existed in researchers beliefs about how often the availability of research protocols/code and the use of restricted data or software impacted reproducibility.
-More than three-quarters of physical (77.0\%) and methods-focused (86.9\%) geographers identified the availability of protocols/code as contributing to irreproducibility, whereas less than two-thirds of human (59.7\%) and nature-society (50.0\%) identified this same factor.
-Only a large percentage of methods-focused researchers (82.0\%) identified the use of restricted data/software as a common contributor to irreproducibility in the discipline.
-A similar gap existed between qualitative researchers, a minority of which identified code availability or the use of restricted data/software as contributing to irreproducibility, and quantiative and mixed-methods researchers, the majority of which saw these factors as frequent causes of irreproducibility.
-
-A majority of researchers identified geographic variation (71.5\%), researcher positionality (64.2\%), and chance (62.3\%) as study-specific factors limiting the reproducibility of geographic research.
-Minor variations in the emphasis placed on these factors exist across subfields and approaches. 
-A higher percentage of nature-society (81.8\%) and physical (80.0\%) researchers emphasized the important role the spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researchers across subfields and approaches.
-A smaller percentage of physical geographers placed emphasis on the impact of researcher positionality may have on reproducibility (50.8\%) when compared to all other subfields.  
-Differences between the computational environment used to conduct an original study and a reproduction attempt was generally not seen as a factor contributing to a lack of reproducibility in the discipline.
-The exception being methods-focused (68.9\%) and quantitative researchers (63.1\%\%), which aligns with the research practices used in these areas of research.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Actual Reproductions}
-A total of \textit{$n_{2}$}=102 (46.7\%) of the authors that responded to our survey reported attempting to reproduce a study in the past two years.
-This subset of participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions.
-Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (42.2\%) and geographic methods and GIScience (35.3\%).
-Respondents attempting reproductions were also focused on quantitative (52.0\%) and mixed-methods (46.1\%) approaches. 
-Only two respondents that self-identified as qualitative researchers attempted to reproduce a study in the past two years.
-Approximately half (49\%) of the researchers attempting reproductions reported submitting their findings for publication.
-
-WHY DID RESEARCHERS ATTEMPT REPRODUCTION - Q10
-\begin{itemize}
-    \item to check results - surprising, as part of peer-review, of related interest
-    \item to check their own results and make them more accessible
-    \item to learn more about methods and/or transfer them into their own work
-\end{itemize}
-
-In most instances, researchers reported some ability to access the research artifacts used in the study they were attempting to reproduce and the ability to recreate at least some of the results of that study.
-The majority of researchers that attempted reproductions (82\%) were able to access at least some of the data used in the original study, but few researchers (27\%) reported access to all of the original data.
-Researchers also reported the ability to access at least some information about study procedures (69\%) and its computational environment (60\%), but limited ability to access all procedural (20\%) and computational information (15\%).
-Nearly all researchers reported at least partially reproducing some results (96\%), but less than half reported being able to at least partially reproduce all results (38\%).
-Few researchers were able to identically reproduce all results (20\%).
-
-How much access researchers had to study data and procedural information impacted their ability to reproduce results. 
-If geographic researchers had access to at least some of the data and procedures used in the study they were attempting to reproduce, they were able to at least partially reproduce some results in all cases, but were able at least partially reproduce all results less than half of the time (42.9\%).
-With complete access to all data and procedures, researchers reported the ability to at least partially reproduce all results 68.4 percent of the time.
-Accessibility to data and procedures appears to be equally important in raising the chances of reproducing all results. 
-Given access to some or all procedural information, having access to all data doubled a researcher's chances of reproducing all results (69.5\%) when compared to having access to only some of the data (27.5\%).
-We observed the same doubling effect when reversing this relationship. 
-Given access to some or all of a study's data, having access to all the procedural information doubled a researcher's chances of reproducing all results (70.0\%) when compared to having access to only some of the procedures (30.0\%).
-
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-
-\begin{itemize}
-    \item Geographic researcher closely link replication and reproduction.
-This isn't surprising as geographic researchers often have training from other disciplines and variation in the use of the two term, and their outright reversal in meaning, is well documented.
-It is likely that this is the root of the conflation.
-This muddling of the definition has important implications ...
-    \item The reproducibility literature emphasizes quantitative, particularly computational, forms of research.
-This emphasis necessarily carried over into our survey instrument, which may automatically lower response scores for researchers not working in these areas (e.g., qualitative, human geography).
-This reality may automatically deflate the aggregate measures of certain sub-group.
-We can use the response to Q8f as a filter to explore this issue.
-These scores do reflect their present level of understanding, but the practices may not be relevant to their methods or epistomologies.
-This fact suggests a meed to examine what reproducibility means in the context of geography's qual, NS, and human traditions.
-    \item A standing question is how should geographic research approaches be designed to efficiently generate reliable knowledge.
-\end{itemize}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Conclusion}
-
-\begin{itemize}
-    \item Overall story is that collectively geographers are aware of reproducible research practices, but don't have a matching amount of direct experience using those practices.
-There are also many perceived barriers to conducting reproducible research.
-\end{itemize}
-
-\theendnotes
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Acknowledgement(s)}
-We thank Tyler Hoffman for providing technical assistance in the development and execution of a set of trial queries using the Scopus API.
-
-\section*{Funding}
-This material is based on work supported by the National Science Foundation under Grant No. \textbf{BCS-2049837}.
-
-\section*{Notes on contributor(s)}
-\textbf{Kedron:} Conceptualization, Methodology, Writing - Original Draft, Writing - Review and Editing, Supervision, Project Administration, Funding Acquisition.
-\textbf{Holler:} Conceptualization, Methodology, Data Curation, Writing - Review and Editing, Funding Acquisition.
-\textbf{Bardin:} Conceptualization, Methodology, Writing - Original Draft, Writing - Review and Editing, Data Curation, Software.
-
-\newpage
-\bibliography{references}
-
 \newpage

### 2023-04-24 docs/manuscript/manuscript.tex
Edit current evidence sections

@@
 \section*{Introduction}
+Reproducibility is important for geography for the same reason it is important in other fields - one-off studies 
 Reproducibility as a characteristic of a study that lends it credibility v. Reproducibility as a error correcting function of science.
+
+While geographers continue to debate the role of reproduction studies in the discipline \citep{kedron2022replication}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, kedron2021GA}, and build the infrastructure needed to support reproducible research \citep{wilson2021}, no one has conducted a systematic survey of the use of reproducible research practices in the discipline.
+
+Within geography, reproduction efforts have identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results. 
+Irreproducibility has also been linked to conceptual and methodological transparency as researchers make decisions about the handling of spatial forms of uncertainty \citep{kedron2021GA}. 
+While these efforts have produced useful reproducibility guidance for geographic researchers \citep{hofer2019reproducible, wilson2021} they have not been systematic surveys of the discipline as a whole.
 
@@
 \section*{Assessing the Reproducibility of Research}
-The reproducibility of research can be assessed directly or indirectly. 
-In a direct assessment of reproducibility, an independent team(s) of researchers repeats the analytical steps of a previous study using the same data and then evaluates the consistency of the two sets of results\footnote{Insert paragraph on the difficulty of developing in using consistency criteria}.
-Direct reproducibility assessments aim to establish whether the data and analysis presented in support of a result do in fact support that result.
-By contrast, indirect assessments of reproducibility aim to establish whether study data and procedures are presented with sufficient transparency and clarity that research results could be subjected to a direct assessment.
-During an indirect assessment of reproducibility, a research team gathers information about the transparency of a study and the availability of the research components (e.g., data and code) needed to recreate that study, but does not directly attempt to recreate the results.
-Indirect assessments also often take the form of surveys in which researchers are asked about their research practices, incentives, and motivations to measure the transparency and practices of a subset if researchers.
 
-Direct and indirect reproducibility assessments present a trade off between the depth and breadth of evaluation.  
-A direct assessment can provide insight into how a particular study was conducted and why a consistent result could, or could not, be obtained.  
-However, such assessments are resource and time intensive, which makes them difficult to scale to a large number of studies. 
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{The Evidence Currently Available from Reproducibility Assessments}
+The reproducibility of research can be assessed directly by attempting to recreate the results of selected studies, or indirectly by reviewing the availability of the research components (e.g., data and code) or surveying those working in that field about their research practices.
+Direct assessments of reproducibility provide insight into how a particular study was conducted and why a consistent result could, or could not, be obtained.  
+However, such assessments are resource and time intensive, which makes it difficult to gather information from numerous studies. 
 Constrained to a limited number of studies, direct assessments offer only suggestive evidence about the reproducibility of unevaluated studies and the prevalence of reproducible research practices. 
-In contrast, comparatively less resource intensive indirect assessments that simply catalog reproducible research practices can be more easily scaled.
-By evaluating many studies, indirect assessments provide evidence of how common reproducible research practices are and, by extension, how reproducible work in a field of study is likely to be.
+In contrast, comparatively less resource intensive indirect assessments that catalog reproducible research practices across many studies offer less insight into individual studies, but provide evidence of how common reproducible research practices are and, by extension, how reproducible work in a field of study is likely to be.
 
-Despite their growing number, the available body of direct and indirect reproducibility assessments currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically \citep{NASEM2019}.
-This knowledge gap exists because neither direct nor indirect reproducibility assessments have been designed so the results of the sample of studies evaluated can be extended to the population of research as a whole.
-Reproduction attempts remain relatively rare, and those that do exist \citep[see][]{chang2015economics, moraila2014measuring} have selectively targeted publications in high-impact journals and conference papers series in a limited number of disciplines that are not representative of many forms of research.
-Indirect reproducibility assessments similarly focus on conveniently accessible archives, such as conference paper series \citep{gundersen2018state, ostermann2017}, or target specific journals and disciplinary repositories \citep{stodden2018empirical, stodden2018enabling, byrne_2017}.
+Across many disciplines, direct reproduction attempts remain relatively rare \citep[see][]{chang2015economics, moraila2014measuring, iqbal2016reproducible,sumner2020reproducibility}.
+However, prominent attempts to reproduce research in economics \citep{chang2015economics}, computer science \citep{moraila2014measuring}, and psychology \citep{open2015estimating} have all been able to reproduce only a small portion of studies because original authors did not share data or adequate information about their procedures.
+
+Within geography, the small number of available reproduction attempts similarly suggest that many studies cannot be fully reproduced, or are simply missing the components needed to attempt a reproduction \citep{nust2018, Kedron2021ssrn, konkol2019, ostermann2021, Nust_AGILE_2022}.
+For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort.
+\citet{konkol2019}'s attempt to reproduce 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves).
+A series of reproduction attempts by \citet{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP} and \citet{paez2022reproducibility} show that the issues hindering the reproduction of results extend beyond computation and into the conceptualization and design of geographic research.
+Nonetheless, like reproduction attempts in other disciplines these studies provide only suggestive evidence of underlying problems, not a comprehensive assessment of the prevalence or sources of these issues.
+
+Indirect reproducibility assessments offer a wider view of what and how common these underlying issues may be. 
+The available evidence for study reviews suggests inadequate record keeping, opaque reporting, unavailable research components, and a lack of incentives are likely important factors contributing to the irreproducibility of research \citep{NASEM2019}.
+Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread. 
+Reproducibility surveys paint a similar picture. 
+Recent surveys suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
+Moreover, a sizable portion of the researchers responding to these surveys admit to engaging in questionable research practices linked to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
+These findings match researcher perceptions, which link irreproducibility to causes ranging from natural variation to outright fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}.
+
+To date only a handful studies have attempted to indirectly measure the reproducibility of geographic research.
+In a survey of remote sensing editors and working group officers of the International Society for Photogrammetry and Remote Sensing, \citet{balz2020reproducibility} asked respondents whether they believe a reproducibility crises existed in their sub-field, but not what the causes of such a crisis might be.
+In a richer treatment of the issue, \citet{konkol2019} survied of participants from the 2016 European Geosciences Union General Assembly to assess the frequency with which researchers published their work in ways that enabled computational reproducibility.
+Those authors found that only 33 percent of respondents included links to the data used in their analyses and only 12 percent provided their analytical code. 
+The authors also found that only seven percent of respondents ever attempted to reproduce the work of other researchers.
+Similarly, in a literature review of volunteered geographic information research, \citet{ostermann2017} found the computational reproducibility of work in the sub-field limited by the availability of original data, metadata, source code, or pseudocode.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Limitations of the Currently Available Evidence}
+While it may not be possible to determine the extent of irreproducibility across or within disciplines from available studies, it is possible to draw lessons about potential sources of irreproducibility.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Current State of Knowledge}
+
+Most indirect assessments sample studies for review from conveniently accessible archives, such as conference paper series \citep{gundersen2018state, ostermann2017}, or target specific journals and disciplinary repositories \citep{stodden2018empirical, stodden2018enabling, byrne_2017}.
 These assessments have also tended to focus on evaluating the computational components of research such as data and code availability, as this information is easier to identify and assess at scale when compared to components like field procedures or qualitative analysis that may be included only in text.
@@
 
-While it may not be possible to determine the extent of irreproducibility across or within disciplines from available studies, it is possible to draw lessons about potential sources of irreproducibility.
-The available evidence suggests inadequate record keeping, opaque reporting, unavailable research components, and a lack of incentives are likely important factors contributing to the irreproducibility of research \citep{NASEM2019}.
-Prominent attempts to reproduce research in economics \citep{chang2015economics}, computer science \citep{moraila2014measuring}, and psychology \citep{open2015estimating} have all been able to reproduce only a small portion of studies because original authors did not share data or adequate information about their procedures.
-Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread. 
-Reproducibility surveys paint a similar picture. 
-Recent surveys suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
-Moreover, a sizable portion of the researchers responding to these surveys admit to engaging in questionable research practices linked to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
-For example, in a survey of 807 ecologists and evolutionary biologists, 64 percent admitted to failing to report non-significant results and 51 percent admitted to presenting unexpected findings as if they had been hypothesized from the start of the research \citep{fraser2018questionable}.
-These findings match researcher perceptions, which link irreproducibility to causes ranging from natural variation to outright fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}.
+Across many disciplines, direct reproduction attempts remain relatively rare, and those that do exist \citep[see][]{chang2015economics, moraila2014measuring, iqbal2016reproducible,sumner2020reproducibility} have selectively targeted publications in high-impact journals and conference papers series in a limited number of disciplines that are not representative of many forms of research.
 
-\subsection*{Assessing the Reproducibility of Geographic Research}
-To date, only a small number of studies have attempted to reproduce geographic research.
-The reproductions that are available within the discipline suggest that many studies cannot be fully reproduced \citep{Kedron2021ssrn, nust2018, ostermann2021}, or are simply missing the components needed to attempt a reproduction \citep{Kedron_VijayanRP, konkol2019, ostermann2021}.
+Despite their growing number, the available body of both direct and indirect reproducibility assessments currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically \citep{NASEM2019}.
+This knowledge gap exists because neither direct nor indirect reproducibility assessments have been designed so the results of the sample of studies evaluated can be extended to the population of research as a whole.
 
-For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort.
-A related effort to reproduce 31 papers published in the conference series of the Association of Geographic Information Laboratories in Europe \citep{Nust_AGILE_2020, Nust2021AGILE, Nust_AGILE_2022} identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results.
-\citet{konkol2019}'s attempt to reproduce of 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves).
+Overall, we have yet to assess the use of reproducible research practices across the discipline's diverse research traditions, or identify the factors that have barred geographers from adopting practices that foster reproducibility or from conducting more reproduction studies.
+Our knowledge and systems remain incomplete because
 
-Moving past the question of whether the computational results of a study can be recreated using the same data and code, a handful of geographic researchers are using the reproduction process as a way of examining not only the execution of a prior study, but its conceptualization and inferences \citep{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP}.
-While this form of the direct approach to reproduction opens a new door to the critical evaluation of geographic research, it primarily provides evidence about a particular research study and the phenomenon that study investigates.
-Similarly, while computationally focused reproductions have produced useful guidelines \citep{hofer2019reproducible, wilson2021} and moved forward the development of the computational and institutional infrastructure \citep{Kedron_Holler_Bardin_Hilgendorf_2022, nust2019, nust2021,}\textbf{ADD SHAOWEN} needed to foster reproducibility in the field, they have not yet assessed the use of reproducible research practices across the disciplines diverse research traditions, or identified the factors that have barred geographers from adopting practices that foster reproducibility or from conducting more reproduction studies.
+the evidence available from direct and indirect assessments of reproducibility suggests that studies are often not reproducible because researchers do provide the information or materials others need to recreate their work.
 
-To date only a handful studies have tried to indirectly measure the reproducibility of geographic research.
-In a survey of participants from the 2016 European Geosciences Union General Assembly, \citet{konkol2019} assessed the frequency with which researchers published their work in ways that enabled computational reproducibility.
-Those authors found that only 33 percent of respondents included links to the data used in their analyses and only 12 percent provided their analytical code. 
-The authors also found that only seven percent of respondents ever attempted to reproduce the work of other researchers.
-For example, \citet{ostermann2017} use a literature review of volunteered geographic information research publications to assess computational reproducibility based on availability of original data, metadata, source code, or pseudocode.
-Remote Sensing survey.
-
-\subsubsection*{Research Summary to Transition}
-The evidence available from direct and indirect assessments of reproducibility suggests that studies are often not reproducible because researchers do provide the information or materials others need to recreate their work.
-
-However, may of our indirect assessment are on shaky methodological grounds and we have not studied this in geography.
+Which leaves a set of basic questions about the reproducibility of geographic research unanswered.
 
@@
 \section*{Data and Methods}
-Complete documentation of the procedures and materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
-That repository connects to a Github repository which hosts the anonymized dataset and code used to create all results and supplemental materials and along with a complete history of their development.
+Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
+That repository connects to a Github repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
+All of the results presented in this paper can be independently reproduced using the materials in that repository.
 Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
-We later amended that plan to reflect a change in stopping rule we used to end the survey and to include additional statistical analyses we conducted after viewing the survey response.
-
 The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.
-All approved documentation, study protocols, and consent materials are available through the above repository.
 
@@
 Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication.
-Because our intention is to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = "Article"} and removed all other publication types (e.g., editorials, book reviews) from our article database.
+Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = "Article"} and removed all other publication types (e.g., editorials, book reviews) from our article database.
 We also removed articles with missing authorship information.
 
-Third, we next moved to the author level to create a condensed list of corresponding authors. 
-We chose to focus on corresponding authors for two reasons. 
+Third, we created a list of researchers and their published articles, focusing on corresponding authors for two reasons.
 (1) Corresponding authorship is one indicator of the level of involvement an individual had in a given work. 
@@
 
-Fourth, we associated each corresponding author with their contact email address and deduplicated to create a single record for each corresponding author. 
-To maximize our chance or response, we retained the latest available contact information for each author by sorting the initial list by author-id and publication year (descending) and keeping the latest available entry for each author-id.
-For authors who had two or more distinct emails in the latest year of publication, we deduplicated by giving a ranked preference to .edu, .gov, and then .org extensions.
+Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
+We determined uniqueness by grouping researchers by their author-id, and we selected for the most recent contact information by selecting records associated with the most recent year of publication. 
+For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.
 
-Applying these criteria yielded a sampling frame of 29,828 authors. 
+Applying these criteria yielded a sampling frame of 29,828 researchers. 
 On average, these authors published 2.7 articles in geography journals meeting our criteria between 2017 and 2021. 
-Roughly one-third (33 percent) were most recently a corresponding author for an article published in a general geography journal. 
-A similar proportion (32 percent) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions in the social sciences and cultural geography (20 percent and 16 percent, respectively).
+Roughly one-third (33.0\%) were most recently a corresponding author for an article published in a general geography journal. 
+A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).
 
 \subsection*{Survey Instrument}
-The survey instrument used in this study is available through the Survey of Reproducibility in Geographic Research Repository.
-The survey consists of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reprodicibility, and (iv) experience conducting independent reproductions.
+The survey consisted of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reproducibility, and (iv) experience conducting independent reproductions.
 Survey questions were developed following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature.
 All researchers were presented questions about their definition of reproducibility, familiarity with and use of reproducible practices, and perceptions of barriers to reproducibility. 
-However, a subset of researchers that reported attempting to reproduce a study in the past two years were given an additional set of questions about their experience conducting that work.
+A subset of researchers that reported attempting to reproduce a study in the past two years were given an additional set of questions about their experience conducting that work.
 
-Because this survey had not been previously fielded, we pilot tested the instrument with a subset of \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background.
+We pilot tested the survey instrument with a subset of \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
 After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.
@@
 \subsubsection*{Statistical Approach}
-We conduct two statistical analyses of the survey response\endnote{The full methodological details of our statistical analyses, and a complete history of our response coding a variable construction is included in the Github repository linked to OSF repository that accompanies this paper.
-All of the results presented in this paper can be independently reproduced using the materials in that repository.}.
-First, we create descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practice, and the barriers to reproducibility they perceive in the discipline.
-Second, we conducted an analysis of the experience of the subset of geographic researchers who reported attempting independent reproductions of prior work during the last two years that identified what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
+We conduct two statistical analyses of the survey response.
+First, we create descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practices, and the barriers to reproducibility they perceive in the discipline.
+Second, we conducted an analysis of the experience of the subset of geographic researchers who reported attempting independent reproductions of prior work during the last two years.
+That analysis identified what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
 Given the topical and epistemological variation that exists among geographic researchers, we examined differences by disciplinary subfield and methodological approach as part of each analysis.
@@
 
-\textit{Definition:} Before providing a common definition of reproducibility, we asked each participant to provide their own definition.
-We measured the similarity of each provided definition to the definition of adopted by the \citet{NASEM2019}. 
-The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same context.
-To make this comparison, two of the authors independently coded each provided definition for the presence/absence of each of the four characteristics included in the NASEM definition.
-Disagreements in the assignment of codes were resolved through discussion between the two authors. 
-As a final check, the third author reviewed rectified coding and resolved any remaining disputes.
+\textit{Definition:} Before providing a common definition of reproducibility, we asked each participant to provide their own definition of the term.
+We coded these definitions following two procedures.
+First, we measured the similarity of each provided definition to the definition of adopted by the \citet{NASEM2019}. 
+The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same conditions.
+To make this comparison, each of the authors independently coded each respondent definition for the presence/absence of each of the four characteristics included in the NASEM definition.
+Disagreements in the assignment of codes were resolved through discussion between the three authors.
 To create an aggregate measure of agreement the final coded response for each participant was then summed across the four characteristics, creating definition similarity \textit{d} with domain [0, 4].
 
-\textit{Familiarity and Experience:} We measured participant familiarity and experience with five reproduciblity enhancing research practices; the use of --- open source software, research notebooks, data sharing, code sharing, and pre-registration.
-We created a summary measure of research familiarity with these practices, \textit{f}, by summing the number of reproducible practices a researcher was 'somewhat' or 'very' familiar with.
-To assess researcher experience with these same five practices, we created \textit{p}, which counts the number of practices a researcher reported using 'most of the time' or 'always' when conducting their own research.
+Second, we coded each definition to one of three motivations for ensuring the reproducibility of a study--- to facilitate the assessment of prior work, to improve transparency and facilitate further extension of work, and to improve the transparency and consistency of study data.
+We derived this coding from common themes in the authors response and our own reading of the reproducibility literature.
+As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.
+
+\textit{Familiarity and Experience:} We measured participant familiarity and use of five reproduciblity enhancing research practices; the adoption of--- open-source software, research notebooks, data sharing, code sharing, and research plan preregistration.
+We created a summary measure of familiarity with these practices, \textit{f}, by summing the number of reproducible practices a researcher was 'somewhat' or 'very' familiar with.
+To assess experience with these same five practices, we created \textit{p}, which counts the number of practices a researcher reported using 'most of the time' or 'always' when conducting their own research.
 Both \textit{f} and \textit{p} have domains [0,5].
@@
 
-Our second analysis examines only researchers that reported attempting a reproduction in the past two years. 
+Our second analysis examined only researchers that reported attempting a reproduction in the past two years. 
 We asked each of these researchers what motivated their reproduction attempt. 
-Two of the authors independently assigned these responses to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and increase the transparency of their work, ii) a desire to learn from past work, or use the reproduction in teaching.
-Some authors provided motivation linked to the replication of results in new geographic contexts. 
-Because these responses did not match our provided definition of reproduction, we removed these from the subsample. 
+Two of the authors independently assigned these responses to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and increase the transparency of their work, iii) replication of a study with new data, and iv) a desire to learn from past work, or use the reproduction in teaching.
 We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
+We selected groups i) and iv) for further analysis of reproduction attempts, as these motivations most closely matched our definition of reproduction.
 
@@
 A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
-The contact rate for the survey was 13.9 percent, the response rate was 10.8 percent, yielding a cooperation rate of 77.6 percent. 
+The contact rate for the survey was 13.9 percent and the cooperation rate was 77.6 percent, yielding an overall response rate of 10.8 percent. 
 The refusal rate was 3.1 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
@@
 A majority of researchers also believe reproducibility is compatible with epistemologies used in the discipline (58.2\%). 
-However, researchers estimated that only half of the results published in the discipline were reproducible, albeit with wide variance ($\overline{rep}=50.6\%$, $\sigma=24.7\%$), and reported limited familiarity with and use of many reproducible research practices.
+However, researchers estimated that only 50.6 percent of the results published in the discipline were reproducible, albeit with a large standard deviation of 24.7 percent that suggests great uncertainty about the true value.
 Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%).
 
-Table \ref{tab:overview} summarizes how  researchers define reproducibility (\textit{d}), their familiarity with (\textit{f}) and use of (\textit{p}) reproducible research practices, and the factors they see as barriers (\textit{b}) to reproducibility in geography.
+Table \ref{tab:overview} summarizes how researchers define reproducibility (\textit{d}), their familiarity with (\textit{f}) and use of reproducible research practices (\textit{u}), and the factors they see as barriers (\textit{b}) to reproducibility in geography.
 We present the mean and standard deviation for the overall sample and for each subfield and methodological approach.
-The following sub-sections discuss each of these topics in turn.
+In aggregate, the data reveal trends in definition, familiarity, practices, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
+Respondents that self-identified as specializing in physical geography and geographic methods consistently report higher indicators than those working nature and society and human geography.
+Similarly, respondents that identified as primarily using quantitative and mixed methods approaches consistently report higher indicators than those using qualitative methods.
+The following sub-sections present detailed results for each of these topics, highlighting the principal sources of difference between sub-disciplines and methodological approaches.
 
@@
 A total of \textit{$n_{d}$}=181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
-On average, geographic researchers provided definitions of reproducibility that generally explicitly included one to two ($\overline{d}=1.83$) of the four characteristics from the definition adopted by the NASEM.
+On average, geographic researchers provided definitions of reproducibility that explicitly included one or two ($\overline{d}=1.83$) of the four characteristics from the definition adopted by the NASEM.
 This level of inclusion was consistent across subfields and methodological approaches.
@@
 Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
-This patterns was also consistent across subfields and approaches, with a slightly greater emphasis on data and procedural consistency and availability amongst quantitative and methods focused researchers.
-The lower inclusion of data and context in definitions matched the conflation of reproduction and replication by a minority of researchers (20.4\%).
+This pattern was consistent across subfields and approaches, with a slightly greater emphasis on data and procedural consistency and availability amongst quantitative and methods focused researchers.
+The lower inclusion of data and context in definitions can be explained by researchers understanding reproducibility in terms of the formal NASEM definition of "replicability"--- a pattern evident in at least 20.4\% of respondents' definitions.
+For example, one respondent defines reproducibility as, "The extent to which the research design can be replicated in different geographical contexts."
 
-Researchers definitions of reproducibility were connected to two epistemic functions.
-Just under half of respondents (45.9\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies.
-Nearly all other researchers (40.9\%) tied reproducibilty to the need for transparency in research so others could independently expand upon past studies.
-Identification of reproducibility with both of these functions was supported by responses to related questions from our entire sample. 
-Overall, a majority of researchers also identified reproducibility as an important for validating (75.2\%) and establishing the credibility (72.5\%) of research.  
+Researchers' definitions of reproducibility were primarily connected to two epistemic functions.
+Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies.
+Nearly all other researchers (40.9\%) tied reproducibility to the need for transparency in research so others could independently expand upon past studies.
+Identification of reproducibility with both of these functions was supported by responses to related questions from our entire sample (\textit{n}=218). 
+A majority of researchers identified reproducibility as important for validating (75.2\%) and establishing the credibility (72.5\%) of research.  
 Respondents also saw reproducing studies as important to reducing the presence of persistent errors in the discipline (77.5\%) and to increasing trust in research findings (78.45\%).
-Matching the emphasis placed on research transparency, respondents identified reproducibility as important to research efficiency (63.3\%) and the communication of findings to academics (68.8\%) and practitioners (64.7\%).
-Half of the respondents (50.9\%) also agreed that when researchers don't share their data they have less trust in a study.
-Researchers also view attempting reproductions as an important part of student training (75.7\%).
+In parallel with the need for openness and transparency in science, most respondents agreed with the importance of reproducibility for research efficiency (63.3\%), communication with academics (68.8\%) and practitioners (64.7\%), and training students (75.7\%).
 
-Despite wide recognition of reproducibility as epistemically important, researchers collectively advocated caution when drawing conclusions from a single reproduction attempts. 
-A minority of researchers agreed that an inability to reproduce a result implies that the result is false (26.2\%). 
-A larger, but still minority, percentage of researchers believed that an inability to reproduce a result detracts from the validity of a study (41.7\%).
+Despite wide recognition of reproducibility as epistemically important, respondents were cautious about drawing conclusions from a single study or reproduction attempt. 
+Half of the respondents (50.9\%) agreed that when researchers don't share their data they have less trust in a study.
+41.7 percent agreed that inability to reproduce a result detracts from the validity of a study, and a smaller minority agreed that such inability implies that the result is false (26.2\%).
 
-Qualitative researchers identified reproducibility as playing a much smaller role in the research process when compared to the discipline as a whole. 
-A majority of the respondents that identified as qualitative researchers believe that reproducibility is incompatible with the epistomologies used in their subfield (75.0\%).
-Qualitative researchers did not believe reproducibility to be important to assessing prior work and correcting errors in the literature. 
-A small percentage or these respondents agree that reproducibility is important for validating (25.0\%) or establishing the credibility (20.0\%) of qualitative research.
+Qualitative researchers identified reproducibility as playing a much smaller epistemic role compared to the discipline as a whole. 
+A majority of the qualitative researchers responded that reproducibility is incompatible with the epistomologies used in their subfield (75.0\%).
+Accordingly small percentage of qualitative researchers agreed that reproducibility is important for validating (25.0\%) or establishing the credibility (20.0\%) of research.
 Qualitative geographers similarly placed less emphasis on reproducibility as a means of increasing the accessibility and expansion of research.
-Few qualitative researchers had less trust in a study when researchers did not share their data (27.5\%), or saw reproducibility as important to sharing research with academics (27.5\%).
+Few qualitative researchers had less trust in a study when researchers did not share their data (27.5\%), or saw reproducibility as important for sharing research with academics (27.5\%).
 
 %%%%%%%%%%%
-\subsubsection*{Familiarity and use of Reproducible Research Practices}
+\subsubsection*{Familiarity and Use of Reproducible Research Practices}
 The reproducibility of research is on the minds of geographic researchers. 
@@
 
-Geographic researchers are on average familiar with multiple reproducible research practices ($\overline{f}=3.26$), but reported limited use of these practices in their own work ($\overline{p}=1.44$).
+Geographic researchers are on average familiar with multiple reproducible research practices ($\overline{f}=3.26$), but reported limited use of these practices in their own work ($\overline{u}=1.44$).
 More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\% ).
-However, while familiar with these practice, a far smaller number of researchers reported using these practices regularly in their own work. 
-Less than half of the researchers surveyed reported sharing their data (44.5\%), using open source software (38.1\%), or using field or lab notebooks to record their work (40.0\%), or sharing their code (18.8\%) most or all of the time.
+However, while familiar with these practices, a far smaller number of researchers reported using these practices regularly in their own work. 
+Less than half of the researchers surveyed reported sharing their data (44.5\%), using open source software (38.1\%), using field or lab notebooks to record their work (40.0\%), or sharing their code (18.8\%) most or all of the time.
 Only a small subset of researchers reported familiarity with the pre-registration of research designs and protocols (27.5\%), or regular use of this practice (2.7\%).
@@
 Researcher familiarity and use of reproducible research practices also varied by disciplinary subfield and methodological approach. 
-Researchers that identified as physical geographers ($\overline{f_{PH}}=3.71$) or methodologists and GIScientists ($\overline{f_{MT}}=3.97$) reported being familiar with more reproducible researcher practices than human  geographers ($\overline{f_{HU}}=2.35$) and those focused on nature and society ($\overline{f_{NS}}=2.28$).
+Researchers that identified as physical geographers or methodologists and GIScientists reported being familiar with one to two more reproducible researcher practices than human  geographers and those focused on nature and society.
 Researcher practices similarly diverged by subfield, but no subset of researchers reported using on average more than two of these practices regularly in their work.  
-When grouped by methodological approach, quantitative and mixed-methods researchers reported substantially greater familiarity ($\overline{f_{QN}}=3.75$, $\overline{f_{MX}}=3.56$) and use ($\overline{p_{QN}}=1.63$, $\overline{p_{MX}}=1.69$) of reproducible researcher practices than qualitative researchers ($\overline{f_{QL}}=1.75$, $\overline{p_{QL}}=0.48$).
+When grouped by methodological approach, quantitative and mixed-methods researchers on average reported familiarity with and use of two more reproducible research practices when compared to qualitative researchers.
 
-Differences in researcher familiarity and use of specific reproducible research practices across subfields and approaches were greatest for practices more typical of quantitative workflows. 
-For example, quantitiative and mixed-methods researchers reported familiarity with open source software (QT=96.7\%, MX=89.5\%) and code sharing (QT=81.5\%, MX=55.7\%).
-In contrast, a smaller percentage of qualitative researchers reported familiarity with open source software (52.5\%) and code sharing (12.5\%).
+Differences in researcher familiarity and use of specific reproducible research practices across subfields and approaches was greatest for practices more typical of quantitative workflows. 
+For example, 96.7 percent of quantitative and 89.5 percent of mixed-methods researchers reported familiarity with open source software, while 52.5 percent of qualitative researchers with the same resources.
+These differences were greater for code sharing practices. 
+Just 12.5 percent of qualitative researchers reported familiarity with code sharing, while 81.5 percent of quantitative and 55.7 percent of mixed-methods researchers reported familiarity with the same practice.
 However, even among quantitiative and mixed-methods researchers familiarity with reproducible research practices did not translate into regular use of those practices.
@@
 
-\subsubsection*{Barriers to Reproducible Research}
+\subsubsection*{Perceived Barriers to Reproducible Research}
 Aligning with the differences we observed between researcher familiarity with reproducibility enhancing research practices and researcher use of those same practices, respondents to our survey identified numerous factors contributing to a lack or reproducible research across the discipline ($\overline{b}=8.20$).
@@
 Qualitative geographers may be the one group that deviates from this consistent pattern. 
-These researchers identified fewer barriers to reproducibility on average, but with a greater variance that left us unable to distinguish this group from any other ($\overline{b_{QL}}=5.97, \sigma_{QL}=3.83$).
+These researchers identified fewer barriers to reproducibility on average, but with a greater variance that left us unable to distinguish this group from any other.
 To examine differences in researcher beliefs about specific factors potentially hindering reproducibility in the discipline, we divided the 12 factors we examined into three groups --- those related to the research environment, the availability of research artifacts, and study-specific characteristics.
@@
 This subset of 32 participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions of the work of others.
-Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (43.8\%) and geographic methods and Methods (37.5\%).
+Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (43.8\%) and geographic methods (37.5\%).
 Respondents attempting reproductions were also focused on quantitative (68.8\%) and mixed-methods (41.2\%) approaches. 
-Only a quarter (25\%) of the researchers attempting reproductions reported submitting any of their findings for publication.
+Only eight of the researchers that attempted reproductions reported submitting any of their findings for publication.
 
@@
 
-How much access researchers had to study data and procedural information impacted their ability to reproduce results. 
+How much access researchers had to study data and procedural information may impact their ability to reproduce results. 
 If geographic researchers had access to at least some of the data and procedures used in the study they were attempting to reproduce, they were able to at least partially reproduce some results in nearly all cases (90.5\%), but were able at least partially reproduce all results only a fraction of the time (14.3\%).
-Accessibility to data and procedures appears to be equally important in raising the chances of reproducing all results. 
-Given access to some or all procedural information, having access to all data doubled a researcher's chances of reproducing all results (69.5\%) when compared to having access to only some of the data (27.5\%).
-We observed the same doubling effect when reversing this relationship. 
-Given access to some or all of a study's data, having access to all the procedural information doubled a researcher's chances of reproducing all results (70.0\%) when compared to having access to only some of the procedures (30.0\%).
+When researchers had access to some of the data from the original study, they reported being able to at least partially reproduce all results in 6 of 24 instances. 
+That success rate rose to 3 of 4 when researchers reported access to all data. 
+We observed a similar increase in researcher ability to at least partially reproduce all results when researchers reported access to all procedural information. 
+Having access to all procedures was linked to partial reproduction of all results in 3 of 3 instances, compared to just 6 of 19 instances when researchers could only access some procedural information.
+The small number of total reproduction of independent work reported makes it difficult to draw definitive conclusions on the relative importance of data or procedures when attempting a reproduction of geographic work.
 
@@
 \section*{Discussion}
+The results of our survey collectively suggest that while geographic researchers are aware of reproducibility
+
+Geographic researchers have yet to adopt a common definition of reproducibility and in some instances use the term to refer to very different types of research.  
+When asked to define reproducibility, researchers provided definitions that contained different requirements for similarity across studies in terms of data, procedures, and results. 
+As importantly, a minority of the geographic researchers define reproducibility as what the NASEM defines as replicability.
+Interchangable use of reproducibility and replicability or an outright reversal of the meaning attached to each term has been documented across the sciences. 
+Given that many geographic researchera are trained in realted disciplinary traditions and that geography has no established standard use of either term, it is likely that researchers link their definitions to those prominent in their cognate fields.
+These conflicting terminologies may lead to confusion.
+
+Researchers that self identified as primarily using qualitative methods have a very different perspective of reproducibility. 
+Many outright rejected that reproducibility was compatible with the epistemology of their subfield/approach.
+Focused instead on what one qualitative researcher termed 'transferability', the desire to know that what they have discovered is relevant in other similar contexts. 
+This idea is much more closely aligned with replication. 
+Perhaps the way forward here is to focus on Wainwright argument that reproducibility can be though of not as a absolute standard, but a means of clarifying for others what was was done and why conclusions were drawn as they were.
+This perspective productively moves the conversation away from over focus on exactly recreating numerical results, and back to the deeper function of attempting a reproduction - assessing the argument and claims made by a researcher.
+
+Our survey instrument may not provide the range of option necessary to capture the practices of certain geographic subfields or methodological approaches. 
+Our survey instrument was built following a review of prior instruments and our own reading of issues in the reproducibility literature. 
+However, that literature over represents the sciences and also computationally intesive research. 
+Indeed, the NASEM report on reproducibility and replicability quickly narrows its focus to computational reproducibility to make a report tractable. 
+This emphasis necessarily carried over into our survey instrument, which may automatically lower response scores for researchers not working in these areas (e.g., qualitative, human geography). 
+This reality may automatically deflate the aggregate measures of certain sub-group.
+These scores do reflect their present level of understanding, but the practices may not be relevant to their methods or epistomologies. 
+This fact suggests a need to more closely examine reproducibility in the context of geography's qual, NS, and human traditions.
+I don't think the gap is as wide as it may seem, as qualitative respondents focused on replication of claims across space presents one possible bridge to build on.
+
+We just don't value or do reproductions.
 
@@
 This fact suggests a meed to examine what reproducibility means in the context of geography's qual, NS, and human traditions.
-    \item A standing question is how should geographic research approaches be designed to efficiently generate reliable knowledge.
-    \item Add discussion about limitation of creating strata for the sample frame being limited so we could not post-stratify.
 \end{itemize}
@@
                     & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & &         &   & \\
-         Measure    & HU & PH & NS & MT             & & QN & QL & MX                 & & Overall & N & Missing \\
+         Measure    & PH & MT & NS & HU             & & QN & MX & QL                 & & Overall & N & Missing \\
          \hline
-         Definition (\textit{d}) & \begin{tabular}[c]{@{}c@{}}1.84\\ (1.14)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}1.73\\ (1.11)\end{tabular} & 
+         Definition (\textit{d}) & \begin{tabular}[c]{@{}c@{}}1.73\\ (1.11)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}2.00\\ (1.09)\end{tabular} & 
                         \begin{tabular}[c]{@{}c@{}}1.86\\ (1.06)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}2.00\\ (1.09)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.84\\ (1.14)\end{tabular} & 
                         & 
                         \begin{tabular}[c]{@{}c@{}}1.91\\ (1.13)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}1.82\\ (1.04)\end{tabular} &
                         \begin{tabular}[c]{@{}c@{}}1.69\\ (1.26)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}1.82\\ (1.04)\end{tabular} & 
                         & 
@@
                         181 &
-                        30 \\
-         Familiarity (\textit{f}) &  \begin{tabular}[c]{@{}c@{}}2.36\\ (1.36)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}3.71\\ (0.98)\end{tabular} & 
+                        37 \\
+         Familiarity (\textit{f}) &  \begin{tabular}[c]{@{}c@{}}3.71\\ (0.98)\end{tabular} & 
+                        \begin{tabular}[c]{@{}c@{}}3.97\\ (0.86)\end{tabular} & 
                         \begin{tabular}[c]{@{}c@{}}2.82\\ (1.76)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}3.97\\ (0.86)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}2.36\\ (1.36)\end{tabular} &
                         &
                         \begin{tabular}[c]{@{}c@{}}3.75\\ (0.98)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}3.46\\ (1.22)\end{tabular} &
                         \begin{tabular}[c]{@{}c@{}}1.75\\ (1.30)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}3.46\\ (1.22)\end{tabular} &
                         &
@@
                         0 \\
-         Experience (\textit{p}) &  \begin{tabular}[c]{@{}c@{}}0.60\\ (0.80)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}2.06\\ (1.18)\end{tabular} & 
+         Practices (\textit{u}) & \begin{tabular}[c]{@{}c@{}}2.06\\ (1.18)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}1.85\\ (1.38)\end{tabular} & 
                         \begin{tabular}[c]{@{}c@{}}1.18\\ (0.96)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}1.85\\ (1.38)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}0.60\\ (0.80)\end{tabular} &
                         &
                         \begin{tabular}[c]{@{}c@{}}1.63\\ (1.32)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}1.69\\ (1.24)\end{tabular} &
                         \begin{tabular}[c]{@{}c@{}}0.48\\ (0.68)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}1.69\\ (1.24)\end{tabular} &
                         &
@@
                         0 \\         
-         Barriers (\textit{b})   &  \begin{tabular}[c]{@{}c@{}}7.32\\ (3.57)\end{tabular} & 
-                        \begin{tabular}[c]{@{}c@{}}8.31\\ (3.00)\end{tabular} & 
+         Barriers (\textit{b}) & \begin{tabular}[c]{@{}c@{}}8.31\\ (3.00)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}9.31\\ (2.79)\end{tabular} & 
                         \begin{tabular}[c]{@{}c@{}}7.44\\ (3.20)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}9.31\\ (2.79)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}7.32\\ (3.57)\end{tabular} &
                         &
                         \begin{tabular}[c]{@{}c@{}}8.78\\ (2.80)\end{tabular} &
+                        \begin{tabular}[c]{@{}c@{}}8.58\\ (2.96)\end{tabular} &
                         \begin{tabular}[c]{@{}c@{}}5.97\\ (3.83)\end{tabular} &
-                        \begin{tabular}[c]{@{}c@{}}8.58\\ (2.96)\end{tabular} &
                         &
@@
                         182 &
-                        29 \\
+                        36 \\
         \hline
@@
         \footnotesize
-        \item \textit{HU} Human Geography, \textit{PH} Physical Geography, \textit{NS} Nature and Society, \textit{MT} GIScience and Methods; \textit{QN} Quantitative, \textit{QL} Qualitative, \textit{MX} Mixed Methods.
+        \item Acronyms indicate: \textit{PH} Physical Geography, \textit{MT} GIScience and Methods, \textit{NS} Nature and Society, \textit{HU} Human Geography; \textit{QN} Quantitative, \textit{MX} Mixed Methods, \textit{QL} Qualitative.
     \end{tablenotes}
@@
 \newpage
+\begin{landscape}
 \begin{table}[h]
@@
                     & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & \\
-         Barrier    & HU & PH & NS & MT            & & QN & QL & MX              & & Overall \\
+         Barrier    & PH & MT & NS & HU            & & QN & MX & QL              & & Overall \\
          \hline
          \textit{Research Environment}      & & & & & & & & & & \\
-         Pressure to Publish                & 61.2\% & 83.1\% & 54.5\% & 75.0\% & & 77.3\% & 47.5\% & 75.3\% & & 71.5\% \\
-         Insufficient oversight             & 56.7\% & 81.6\% & 63.6\% & 82.0\% & & 82.6\% & 40.0\% & 74.2\% & & 71.1\% \\
-         Fraud                              & 22.4\% & 32.3\% & 9.1\%  & 39.3\% & & 29.4\% & 20.0\% & 31.8\% & & 28.4\% \\
+         Pressure to Publish                & 83.1\% & 75.0\% & 54.5\% & 61.2\% & & 77.3\% & 75.3\% & 47.5\% & & 71.5\% \\
+         Insufficient oversight             & 81.6\% & 82.0\% & 63.6\% & 56.7\% & & 82.6\% & 74.2\% & 40.0\% & & 71.1\% \\
+         Fraud                              & 32.3\% & 39.3\% & 9.1\%  & 22.4\% & & 29.4\% & 31.8\% & 20.0\% & & 28.4\% \\
                                             & & & & & & & & & &\\
          \textit{Artifact Availability}     & & & & & & & & & & \\
-         Insufficient metadata              & 62.6\% & 76.9\% & 59.1\% & 78.7\% & & 79.4\% & 45.0\% & 72.9\% & & 80.2\% \\
-         Unavailable Data                   & 65.7\% & 89.3\% & 59.1\% & 78.6\% & & 87.0\% & 42.5\% & 81.2\% & & 75.2\% \\
-         Unavailable protocol/code          & 59.7\% & 77.0\% & 50.0\% & 86.9\% & & 87.0\% & 37.5\% & 70.6\% & & 71.1\% \\
-         Published incomplete results       & 56.7\% & 73.8\% & 63.7\% & 78.7\% & & 78.2\% & 37.2\% & 72.9\% & & 68.4\% \\
-         Use restricted data/software       & 44.8\% & 56.9\% & 40.9\% & 82.0\% & & 70.7\% & 32.5\% & 56.5\% & & 57.8\% \\
+         Insufficient metadata              & 76.9\% & 78.7\% & 59.1\% & 62.6\% & & 79.4\% & 72.9\% & 45.0\% & & 80.2\% \\
+         Unavailable Data                   & 89.3\% & 78.6\% & 59.1\% & 65.7\% & & 87.0\% & 81.2\% & 42.5\% & & 75.2\% \\
+         Unavailable protocol/code          & 77.0\% & 86.9\% & 50.0\% & 59.7\% & & 87.0\% & 70.6\% & 37.5\% & & 71.1\% \\
+         Published incomplete results       & 73.8\% & 78.7\% & 63.7\% & 56.7\% & & 78.2\% & 72.9\% & 37.2\% & & 68.4\% \\
+         Use restricted data/software       & 56.9\% & 82.0\% & 40.9\% & 44.8\% & & 70.7\% & 56.5\% & 32.5\% & & 57.8\% \\
                                             & & & & & & & & & &\\
          \textit{Study Characteristics}     & & & & & & & & & & \\
-         Geographic variation               & 61.2\% & 80.0\% & 81.8\% & 72.2\% & & 79.4\% & 40.0\% & 74.1\% & & 71.5\% \\
-         Researcher positionality           & 70.2\% & 50.8\% & 72.8\% & 70.5\% & & 56.5\% & 80.0\% & 65.9\% & & 64.2\% \\
-         Chance                             & 55.2\% & 66.2\% & 68.2\% & 65.6\% & & 67.4\% & 52.5\% & 64.4\% & & 62.3\% \\
-         Different computation              & 38.8\% & 53.8\% & 31.8\% & 68.9\% & & 63.1\% & 25.0\% & 56.5\% & & 50.9\% \\
+         Geographic variation               & 80.0\% & 72.2\% & 81.8\% & 61.2\% & & 79.4\% & 74.1\% & 40.0\% &  & 71.5\% \\
+         Researcher positionality           & 50.8\% & 70.5\% & 72.8\% & 70.2\% & & 56.5\% & 65.9\% & 80.0\% &  & 64.2\% \\
+         Chance                             & 66.2\% & 65.6\% & 68.2\% & 55.2\% & & 67.4\% & 64.4\% & 52.5\% &  & 62.3\% \\
+         Different computation              & 53.8\% & 68.9\% & 31.8\% & 38.8\% & & 63.1\% & 56.5\% & 25.0\% &  & 50.9\% \\
                                             & & & & & & & & & &\\
-         N                                  & 67 & 65 & 22 & 61 & & 92 & 40 & 85 & & 218 \\
+         N                                  & 65 & 61 & 22 & 67 & & 92 & 85 & 40 & & 218 \\
         \hline
@@
         \footnotesize
-        \item \textit{HU} Human Geography, \textit{PH} Physical Geography, \textit{NS} Nature and Society, \textit{MT} GIScience and Methods; \textit{QN} Quantitative, \textit{QL} Qualitative, \textit{MX} Mixed Methods.
-        \item Percentage of respondents reporting each factor frequently or occasionally contributed to a lack of reproducibility in geographic research
+        \item Cells report the percentage of respondents reporting each factor frequently, occasionally, or always contributed to a lack of reproducibility in geographic research.
+Acronyms indicate: \textit{PH} Physical Geography, \textit{MT} GIScience and Methods, \textit{NS} Nature and Society, \textit{HU} Human Geography; \textit{QN} Quantitative, \textit{MX} Mixed Methods, \textit{QL} Qualitative.
     \end{tablenotes}
@@
 \end{table}
+\end{landscape}
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-05-08 docs/manuscript/manuscript.tex
Add intro and discussion

@@
 \section*{Introduction}
-Reproducibility is important for geography for the same reason it is important in other fields - one-off studies 
-Reproducibility as a characteristic of a study that lends it credibility v. Reproducibility as a error correcting function of science.
+Reproducibility is important for geographic research for the same reason it is important in other areas of research. 
+In principle, reproducible research publicly discloses the evidence used to support claims made in prior work which facilitates the independent verification of those claims and the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009} .
+While reproducibility is not a guarantee of scientific or practical usefulness, it does provide a strong basis for the collective evaluation of ideas.
+Nonetheless, research across disciplines suggests that the results of many studies cannot be independently recreated \citep[see][]{moraila2014measuring, chang2015economics, open2015estimating, iqbal2016reproducible} and that few researchers are attempting to independently reproduce the work of others \citep{baker20161, boulbes2018survey}.
+The available evidence links the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details of to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
+At the same time a sizable portion of the researchers admit engaging in questionable research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
 
-While geographers continue to debate the role of reproduction studies in the discipline \citep{kedron2022replication}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, kedron2021GA}, and build the infrastructure needed to support reproducible research \citep{wilson2021}, no one has conducted a systematic survey of the use of reproducible research practices in the discipline.
+Although not yet systematically measured, many of these same factors may be impacting the reproducibility of geographic research.
+The small number of reproduction studies available within the discipline suggest that many studies cannot be fully reproduced, or are simply missing the components needed to attempt a reproduction \citep[see][]{ Kedron2021ssrn, konkol2019, Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021, paez2022reproducibility}.
+The available surveys of research practices in the discipline also support this conclusion as few researchers report sharing their data, metadata, or source code \citep{balz2020reproducibility, konkol2019, ostermann2017}.
+At the same time, recent reproduction attempts by \citet{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.
 
-Within geography, reproduction efforts have identified the inaccessibility of data, code, and information about the computational environment as key barriers to recreating results. 
-Irreproducibility has also been linked to conceptual and methodological transparency as researchers make decisions about the handling of spatial forms of uncertainty \citep{kedron2021GA}. 
-While these efforts have produced useful reproducibility guidance for geographic researchers \citep{hofer2019reproducible, wilson2021} they have not been systematic surveys of the discipline as a whole.
+Despite these suggestive findings, the available literature currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically.
+This knowledge gap exists because researchers conducting reproducibility assessments have not defined clear target populations or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
+Attempts to reproduce past results typically focus on recreating the results of one or a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}.
+Attempted reproductions of geographic research for example focus on the computational reproducibility of conference papers \citep{Nust-AGILE_2018} or specific topics such as COVID-19 \citep{Holler2023disability,kedron2021GA, paez2022reproducibility}.
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Assessing the Reproducibility of Research}
+More broadly, attempts to catalog or survey reproducible research practices have drawn data non-randomly from conveniently accessible archives such as conference paper series, specific journals, and disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2018empirical, stodden2018enabling}, or from self-selecting populations such as authors in specific journals, members of professional associations, and conference attendees \citep{baker20161} that are not necessarily representative of researchers active in a particular field.
+Like attempts to reproduce specific studies, reproducibility surveys also focus on evaluating the computational components of research such as data and code availability over less accessible information like field procedures or qualitative analysis that may only be included in text.
+Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use.
+The few available surveys of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017} face these same challenges.
 
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{The Evidence Currently Available from Reproducibility Assessments}
-The reproducibility of research can be assessed directly by attempting to recreate the results of selected studies, or indirectly by reviewing the availability of the research components (e.g., data and code) or surveying those working in that field about their research practices.
-Direct assessments of reproducibility provide insight into how a particular study was conducted and why a consistent result could, or could not, be obtained.  
-However, such assessments are resource and time intensive, which makes it difficult to gather information from numerous studies. 
-Constrained to a limited number of studies, direct assessments offer only suggestive evidence about the reproducibility of unevaluated studies and the prevalence of reproducible research practices. 
-In contrast, comparatively less resource intensive indirect assessments that catalog reproducible research practices across many studies offer less insight into individual studies, but provide evidence of how common reproducible research practices are and, by extension, how reproducible work in a field of study is likely to be.
+While geographers continue to debate the role of reproduction studies in the discipline \citep{brunsdon2016, goodchild2021Annals, kedron2022replication, kedron2021IJGIS, singleton2016, sui2021}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, ostermann2021}, and build the infrastructure needed to support reproducible research \citep{nust2019, wilson2021, yin2019cybergis}, we have yet to systematically assess the use of reproducible research practices across the discipline's diverse research traditions, or identify the factors that have hindered geographers from adopting reproducible research practices and conducting reproduction studies.
+Without answers to these questions it is unclear what actions geographers should take if they wish to improve the reproducibility of work in the discipline.
 
-Across many disciplines, direct reproduction attempts remain relatively rare \citep[see][]{chang2015economics, moraila2014measuring, iqbal2016reproducible,sumner2020reproducibility}.
-However, prominent attempts to reproduce research in economics \citep{chang2015economics}, computer science \citep{moraila2014measuring}, and psychology \citep{open2015estimating} have all been able to reproduce only a small portion of studies because original authors did not share data or adequate information about their procedures.
-
-Within geography, the small number of available reproduction attempts similarly suggest that many studies cannot be fully reproduced, or are simply missing the components needed to attempt a reproduction \citep{nust2018, Kedron2021ssrn, konkol2019, ostermann2021, Nust_AGILE_2022}.
-For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be reproduced, or could only be reproduced with significant effort.
-\citet{konkol2019}'s attempt to reproduce 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves).
-A series of reproduction attempts by \citet{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP} and \citet{paez2022reproducibility} show that the issues hindering the reproduction of results extend beyond computation and into the conceptualization and design of geographic research.
-Nonetheless, like reproduction attempts in other disciplines these studies provide only suggestive evidence of underlying problems, not a comprehensive assessment of the prevalence or sources of these issues.
-
-Indirect reproducibility assessments offer a wider view of what and how common these underlying issues may be. 
-The available evidence for study reviews suggests inadequate record keeping, opaque reporting, unavailable research components, and a lack of incentives are likely important factors contributing to the irreproducibility of research \citep{NASEM2019}.
-Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread. 
-Reproducibility surveys paint a similar picture. 
-Recent surveys suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
-Moreover, a sizable portion of the researchers responding to these surveys admit to engaging in questionable research practices linked to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
-These findings match researcher perceptions, which link irreproducibility to causes ranging from natural variation to outright fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}.
-
-To date only a handful studies have attempted to indirectly measure the reproducibility of geographic research.
-In a survey of remote sensing editors and working group officers of the International Society for Photogrammetry and Remote Sensing, \citet{balz2020reproducibility} asked respondents whether they believe a reproducibility crises existed in their sub-field, but not what the causes of such a crisis might be.
-In a richer treatment of the issue, \citet{konkol2019} survied of participants from the 2016 European Geosciences Union General Assembly to assess the frequency with which researchers published their work in ways that enabled computational reproducibility.
-Those authors found that only 33 percent of respondents included links to the data used in their analyses and only 12 percent provided their analytical code. 
-The authors also found that only seven percent of respondents ever attempted to reproduce the work of other researchers.
-Similarly, in a literature review of volunteered geographic information research, \citet{ostermann2017} found the computational reproducibility of work in the sub-field limited by the availability of original data, metadata, source code, or pseudocode.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Limitations of the Currently Available Evidence}
-While it may not be possible to determine the extent of irreproducibility across or within disciplines from available studies, it is possible to draw lessons about potential sources of irreproducibility.
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Current State of Knowledge}
-
-Most indirect assessments sample studies for review from conveniently accessible archives, such as conference paper series \citep{gundersen2018state, ostermann2017}, or target specific journals and disciplinary repositories \citep{stodden2018empirical, stodden2018enabling, byrne_2017}.
-These assessments have also tended to focus on evaluating the computational components of research such as data and code availability, as this information is easier to identify and assess at scale when compared to components like field procedures or qualitative analysis that may be included only in text.
-Surveys of researcher practices and attitudes on reproducibility face similar challenges. 
-Rather than carefully defining researcher populations of interest, existing surveys have drawn data non-randomly from self-selecting populations that are convenient to survey (e.g., members of professional association, conference attendees), but are not necessarily representative of researchers active in a particular field.
-These surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response.
-
-Across many disciplines, direct reproduction attempts remain relatively rare, and those that do exist \citep[see][]{chang2015economics, moraila2014measuring, iqbal2016reproducible,sumner2020reproducibility} have selectively targeted publications in high-impact journals and conference papers series in a limited number of disciplines that are not representative of many forms of research.
-
-Despite their growing number, the available body of both direct and indirect reproducibility assessments currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically \citep{NASEM2019}.
-This knowledge gap exists because neither direct nor indirect reproducibility assessments have been designed so the results of the sample of studies evaluated can be extended to the population of research as a whole.
-
-Overall, we have yet to assess the use of reproducible research practices across the discipline's diverse research traditions, or identify the factors that have barred geographers from adopting practices that foster reproducibility or from conducting more reproduction studies.
-Our knowledge and systems remain incomplete because
-
-the evidence available from direct and indirect assessments of reproducibility suggests that studies are often not reproducible because researchers do provide the information or materials others need to recreate their work.
-
-Which leaves a set of basic questions about the reproducibility of geographic research unanswered.
-
-\begin{description}
-\setlength{\itemindent}{0ex}
-    \item[\textbf{(Q1)}] How do geographic researchers define reproduciblity?
-    \item[\textbf{(Q2)}] How familiar are geographic researchers with different reproducible research practices?
-    \item[\textbf{(Q3)}] How often do geographic researchers use different reproducibile research practices when conducting their own studies? 
-    \item[\textbf{(Q4)}] What factors hinder the reproduction of geographic research?
-\end{description}
+To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, familiarity and use of reproducible research practices, and the factors they see as barriers to reproducibile research using a probability sampling scheme designed to capture the breadth of geographic research.
+In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
+We then present the results of our survey first focusing on researcher perceptions and use of reproducible research practices, then analyzing researcher experiences attempting to reproduce prior work.
+We then discuss the implications of our survey results. 
+Finally, we conclude by presenting a current snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here. 
+Excluding data that could be used to identify participants, all of the materials, methods, and code used to conduct and analyze our survey are available in online repositories with persistent links and identifiers.
+We encourage interested readers to critically evaluate and build on these materials through their own work.
 
@@
 A majority of researchers also believe reproducibility is compatible with epistemologies used in the discipline (58.2\%). 
-However, researchers estimated that only 50.6 percent of the results published in the discipline were reproducible, albeit with a large standard deviation of 24.7 percent that suggests great uncertainty about the true value.
+However, researchers estimated that only 50.6 percent of the results published in the discipline were reproducible, albeit with a large standard deviation of 24.7 percent that suggests a great deal of uncertainty about the true value.
 Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%).
@@
 In aggregate, the data reveal trends in definition, familiarity, practices, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
-Respondents that self-identified as specializing in physical geography and geographic methods consistently report higher indicators than those working nature and society and human geography.
+Respondents that self-identified as specializing in physical geography and geographic methods consistently report higher indicators than those working in nature and society and human geography.
 Similarly, respondents that identified as primarily using quantitative and mixed methods approaches consistently report higher indicators than those using qualitative methods.
@@
 Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
-This pattern was consistent across subfields and approaches, with a slightly greater emphasis on data and procedural consistency and availability amongst quantitative and methods focused researchers.
-The lower inclusion of data and context in definitions can be explained by researchers understanding reproducibility in terms of the formal NASEM definition of "replicability"--- a pattern evident in at least 20.4\% of respondents' definitions.
+This pattern was consistent across subfields and approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and methods focused researchers.
+The lower inclusion of data and context in definitions may be explained by researchers conceptualizing reproducibility as the formal NASEM definition of replicability, which emphasizes the testing of similar questions and procedures in new contexts with new data.
 For example, one respondent defines reproducibility as, "The extent to which the research design can be replicated in different geographical contexts."
+We observed this alternative definition of reproducibility in 20.4\% of respondents' definitions.
 
@@
 Half of the respondents (50.9\%) agreed that when researchers don't share their data they have less trust in a study.
-41.7 percent agreed that inability to reproduce a result detracts from the validity of a study, and a smaller minority agreed that such inability implies that the result is false (26.2\%).
+A similar percentage (41.7\%) agreed that inability to reproduce a result detracts from the validity of a study, and a smaller minority agreed that such inability implies that the result is false (26.2\%).
 
@@
 A majority of the qualitative researchers responded that reproducibility is incompatible with the epistomologies used in their subfield (75.0\%).
-Accordingly small percentage of qualitative researchers agreed that reproducibility is important for validating (25.0\%) or establishing the credibility (20.0\%) of research.
+Accordingly a small percentage of qualitative researchers agreed that reproducibility is important for validating (25.0\%) or establishing the credibility (20.0\%) of research.
 Qualitative geographers similarly placed less emphasis on reproducibility as a means of increasing the accessibility and expansion of research.
@@
 Geographic researchers are on average familiar with multiple reproducible research practices ($\overline{f}=3.26$), but reported limited use of these practices in their own work ($\overline{u}=1.44$).
-More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\% ).
+More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\%).
 However, while familiar with these practices, a far smaller number of researchers reported using these practices regularly in their own work. 
@@
 Aligning with the differences we observed between researcher familiarity with reproducibility enhancing research practices and researcher use of those same practices, respondents to our survey identified numerous factors contributing to a lack or reproducible research across the discipline ($\overline{b}=8.20$).
-Geographic researchers working in different subfields and with different methodological approaches each identified a similar number of barriers to reproducibility.
+Geographic researchers working in different subfields and with different methodological approaches each identified a similar number of barriers to reproducibility (Table \ref{tab:barriers}).
 Qualitative geographers may be the one group that deviates from this consistent pattern. 
@@
 A total of 102 of the researchers that responded to our survey (46.8\%) reported attempting a reproduction study during the past two years.
-However, 23 of those reported reproduction attempts were of the researcher own work, while another 13 were in fact replications of prior work in new locations.
+However, 23 of those reported reproduction attempts were of the researcher's own work, while another 13 were in fact replications of prior work in new locations.
 In the end, only \textit{$n_{a}$}=32 (14.7\%) of all respondents reported attempting to reproduce a study originally conducted by another researcher during the past two years.
@@
 
-How much access researchers had to study data and procedural information may impact their ability to reproduce results. 
+How much access researchers had to study data and procedural information seems to impact their ability to reproduce results. 
 If geographic researchers had access to at least some of the data and procedures used in the study they were attempting to reproduce, they were able to at least partially reproduce some results in nearly all cases (90.5\%), but were able at least partially reproduce all results only a fraction of the time (14.3\%).
@@
 Having access to all procedures was linked to partial reproduction of all results in 3 of 3 instances, compared to just 6 of 19 instances when researchers could only access some procedural information.
-The small number of total reproduction of independent work reported makes it difficult to draw definitive conclusions on the relative importance of data or procedures when attempting a reproduction of geographic work.
+We report counts in these cases, becasuse the small number of total independent reproduction attempts makes it difficult to draw definitive conclusions on the relative importance of data or procedures when attempting a reproduction of geographic work.
 
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion}
-The results of our survey collectively suggest that while geographic researchers are aware of reproducibility
+\section*{Discussion and Conclusion}
 
-Geographic researchers have yet to adopt a common definition of reproducibility and in some instances use the term to refer to very different types of research.  
-When asked to define reproducibility, researchers provided definitions that contained different requirements for similarity across studies in terms of data, procedures, and results. 
-As importantly, a minority of the geographic researchers define reproducibility as what the NASEM defines as replicability.
-Interchangable use of reproducibility and replicability or an outright reversal of the meaning attached to each term has been documented across the sciences. 
-Given that many geographic researchera are trained in realted disciplinary traditions and that geography has no established standard use of either term, it is likely that researchers link their definitions to those prominent in their cognate fields.
-These conflicting terminologies may lead to confusion.
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Discussion}
+Overall, the results of our survey collectively suggest that geographic researchers are aware of reproducible research practices, but have yet to incorporate many of those practices into their own work.
+We also found that few researchers report attempting to independently reproduce the work of others. 
+In alignment with the broader reproducibility literature, a majority of respondents identified a lack methodological transparency and the unavailability of data and procedural information, particularly code, as key barriers to reproducibility in the discipline.
+Our results also suggest the existence of an incentive problem within the discipline, as pressure to publish original research and a lack of oversight create the opportunity to publish irreproducibile work and limited reward for attempting and publishing reproduction studies.
 
-Researchers that self identified as primarily using qualitative methods have a very different perspective of reproducibility. 
-Many outright rejected that reproducibility was compatible with the epistemology of their subfield/approach.
-Focused instead on what one qualitative researcher termed 'transferability', the desire to know that what they have discovered is relevant in other similar contexts. 
-This idea is much more closely aligned with replication. 
-Perhaps the way forward here is to focus on Wainwright argument that reproducibility can be though of not as a absolute standard, but a means of clarifying for others what was was done and why conclusions were drawn as they were.
-This perspective productively moves the conversation away from over focus on exactly recreating numerical results, and back to the deeper function of attempting a reproduction - assessing the argument and claims made by a researcher.
+Our findings also suggest that geographic research do not share a single definition of the reproducibility. 
+In fact, our results show that while researchers share beliefs about the epistemological functions of independent reproductions, they provide definitions that contained different requirements for similarity across studies in terms of data, procedures, results, and context.
+Moreover, a subset of researchers define reproducibility as what the NASEM \citet{NASEM2019} defines as replicability - the ability to obtain consistent results across studies designed to answer the same question, each of which has obtained its own data.
+The interchangeable use of reproducibility and replicability, or the outright reversal of definitions we observed in our sample, has also been documented across the sciences \citep{barba2018terminologies, plesser2018reproducibility}.
+Given that geography has no established standard use of either term and that many geographic researchers are also trained in other disciplines, it is likely that researchers at least partially inform their definition of reproducibility using concepts prominent in their cognate fields.
+More broadly, our observed variation in terminology is important for at least two reasons.
 
-Our survey instrument may not provide the range of option necessary to capture the practices of certain geographic subfields or methodological approaches. 
-Our survey instrument was built following a review of prior instruments and our own reading of issues in the reproducibility literature. 
-However, that literature over represents the sciences and also computationally intesive research. 
-Indeed, the NASEM report on reproducibility and replicability quickly narrows its focus to computational reproducibility to make a report tractable. 
-This emphasis necessarily carried over into our survey instrument, which may automatically lower response scores for researchers not working in these areas (e.g., qualitative, human geography). 
-This reality may automatically deflate the aggregate measures of certain sub-group.
-These scores do reflect their present level of understanding, but the practices may not be relevant to their methods or epistomologies. 
-This fact suggests a need to more closely examine reproducibility in the context of geography's qual, NS, and human traditions.
-I don't think the gap is as wide as it may seem, as qualitative respondents focused on replication of claims across space presents one possible bridge to build on.
+First, if researchers lock into a debate about the definition of reproducibility rather than a shared understanding of its potential functions, the community as a whole may hinder a more productive discussion about the role independent reproductions and open science practices can or should play in the discipline.
+Second, variation in geographic researchers' understanding of reproducibility reflects the discipline diverse traditions and ways of knowing. 
+Acknowledging this diversity as a strength of the discipline, productive discussions about reproducibility should consider how the reproducible research practice fits into different traditions and what common understanding exists across traditions.
+Our findings point to potentially productive pathways for such a discussion. 
+Even among the subset of respondents most uncertain about the role of reproducibility in geographic research, qualitative geographers, we observed recognition of the value reproducible research practices bring to the transparency of research, with a particular emphasis on the sharing of methods and procedures.
 
-We just don't value or do reproductions.
+However, our results also show that self-identified qualitative researchers have a different perspective on the role or reproducibility in geographic research when compared to other subgroups of respondents.
+The extent to which we can generalize this perspective is limited by the size of our sample of qualitative researchers (\textit{$n_{ql}$}=40).  
+Nonetheless, the majority of our qualitatively-focused respondents believe reproducibility is incompatible with their epistemological approach.  
+The definitions these researcher provided suggest this belief may be rooted in the role researcher positionality can play in the collection and interpretation of qualitative data. 
+Several respondents questioned whether an independent researcher could ever collect the same data from the same set of participants, or even given the same data would bring their own unique interpretive lens making the recreation of exact result impossible.
+Several qualitative respondents also focused on what one researcher termed 'transferability', the desire to know that what they have discovered is relevant in other similar contexts. 
+These are all relevant questions, but also raise issues that are more closely associated with what the NASEM defines as replicability.
+
+Recognizing this variation in the conceptualization of reproducibility not only reinforces our prior point, it suggests further ways to productively discuss and work toward reproducibility. 
+Perhaps one way forward is initiate a conversation that highlights how reproducibility is not an absolute standard or determinant of research quality, but instead a means of clarifying for others what was was done in a study and why conclusions were drawn as they were.
+Even if a researcher believes their positionality influences the data they collect and the interpretations and claims they ultimately make to the point where an independent research could not recreate those results, using reproducible research practices where appropriate may help convey that researcher's position and its impact on outcomes.
+To our knowledge there is little explicit discussion in the reproducibility literature about how researcher positionality can or should be recorded and conveyed to other researchers. 
+Introducing existing discussions of this issue from that tradition to the reproducibility literature may be a fruitful collaborative path.  
+This perspective may move the conversation about reproducibility away from a current focus on exactly recreating numerical results, and back to the practice's deeper function - independently assessing the arguments of another researcher.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Limitations}
+To our knowledge, our work is the first systematic attempt to survey geographic researchers about reproducibility. 
+To draw a reliable and generalizable understanding of this issue, we developed a sampling frame using recent publications in indexed journals to gather information from our target population of individuals actively publishing geographic research.
+One limitation of our approach is that geographic researchers publish in a range of journals that are not necessarily indexed as geography by the Web of Science. 
+Our sampling frame and strategy would not capture these individuals. 
+However, we believe the number of individuals falling into this category will be small as most active geographic researchers are likely to publish at least one study in a geography journal over a 5-year period.
+
+A related concern is that our survey response may suffer from self-selection bias. 
+It may be the case that geographic researchers more familiar with reproducible research practices, or those working in subfields more involved with the current reproduciblity debate (e.g., quantitative, computational research) are more likely to respond to our survey.
+Conversely, it may also be the case that researchers working in subfields traditionally associated with critiques of a positivist scientific approach (e.g., qualitative, human geography) are less likely to participate in our survey.
+Two means of addressing these concerns would be to stratify our initial sampling or to poststratify our final sample.
+Startification divides potential subjects into subgoups based on common characteristcs, while poststratification adjusts a non-representative sample using predictors known to characterize strata that are likewise known to have different response characteristics.
+We initially considered balancing our sampling across strata meaningful to reproducibility. 
+However, the existing lack of knowledge about the researcher characteristics that might meaningfully differentiate strata, and our inability to accurately measure those characteristics led use to adopt a simple random sampling scheme.
+
+Relatedly, we do not currently have sufficient knowledge of the predictors of differences in response or good measures of key researcher characteristics across the population to inform a meaningful poststratification adjustment.
+In this circumstance, if we were to poststratify our data we would have no way of knowing whether our actions increased or decreased the bias in our results. 
+Considering this challenge, our results could be viewed as an exploratory analysis identifying researcher characteristics that might differentiate subgroups with similar understandings of reproducibility that could then be used to stratify or poststratify future reproducibility related research in geography.
+
+While self-selection may exist in our data, it may also be less of a concern because the forms of self-selection we have discussed are likely to only amplify some of our key findings. 
+Namely, that reproducible research practices have yet to be widely adopted in the field and that relatively few geographers are attempting and sharing independent reproduction studies.
+However, we think that concern about self-selection should motivate a closer examination of reproducibility in the context of geography's qualitative, human, and nature society traditions.  
+It would be interesting to not only know how to better document and share components of qualitative research designs and research positions, but whether reproducibility could be used as a lens for the investigation of
+whether certain elements of those approaches and positions appear to be stable across researchers and contexts.
+
+Another potential limitation of our research is that we based our survey instrument on a review of prior reproducibility surveys and our identification of practices and barriers discussed in the reproducibility literature.
+To the extent that this literature over represents perspectives from selected disciplines, experimental research designs, and computationally-intensive research approaches our survey may reflect this bias.
+If this were the case, our survey may not gather data on practices and barriers important to the reproducibility of types of geographic research not like the work conducted in those disciplines that are well represented in the existing literature.
+To address this concern, we incorporated into our survey instrument questions informed by a parallel review of the reproducibility literature available within geography and a review of critiques of positivist science made by social scientists and human geographers.
+We also provided the option for an open ended text response to questions about reproducible research practices, researcher familiarity with those practices, and barriers to reproducibility in an attempt to identify factor and issues we did not anticipate during instrument construction.
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\subsection*{Conclusion}
 
 \begin{itemize}
-    \item Geographic researcher closely link replication and reproduction.
-This isn't surprising as geographic researchers often have training from other disciplines and variation in the use of the two term, and their outright reversal in meaning, is well documented.
-It is likely that this is the root of the conflation.
-This muddling of the definition has important implications ...
-    \item The reproducibility literature emphasizes quantitative, particularly computational, forms of research.
-This emphasis necessarily carried over into our survey instrument, which may automatically lower response scores for researchers not working in these areas (e.g., qualitative, human geography).
-This reality may automatically deflate the aggregate measures of certain sub-group.
-We can use the response to Q8f as a filter to explore this issue.
-These scores do reflect their present level of understanding, but the practices may not be relevant to their methods or epistomologies.
-This fact suggests a meed to examine what reproducibility means in the context of geography's qual, NS, and human traditions.
+    \item We created a base t build on. everything is available. Please, Reproduce our survey! Replicate our survey! Improve our survey!
 \end{itemize}
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Conclusion}
-
 \begin{itemize}
+    \item essential interpretation based on key findings
+    \item unanswered questions and potential future work
     \item Overall story is that collectively geographers are aware of reproducible research practices, but don't have a matching amount of direct experience using those practices.

### 2023-05-08 docs/manuscript/saved_text.tex
Add intro and discussion

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Assessing the Reproducibility of Research}

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{The Evidence Currently Available from Reproducibility Assessments}
The reproducibility of research can be assessed directly by attempting to recreate the results of selected studies, or indirectly by reviewing the availability of the research components (e.g., data and code) or surveying those working in that field about their research practices. 
Direct assessments of reproducibility provide insight into how a particular study was conducted and why a consistent result could, or could not, be obtained.  
However, such assessments are resource and time intensive, which makes it difficult to gather information from numerous studies. 
Constrained to a limited number of studies, direct assessments offer only suggestive evidence about the reproducibility of unevaluated studies and the prevalence of reproducible research practices. 
In contrast, comparatively less resource intensive indirect assessments that catalog reproducible research practices across many studies offer less insight into individual studies, but provide evidence of how common reproducible research practices are and, by extension, how reproducible work in a field of study is likely to be.

Across many disciplines, direct assessments of reproducibility remain relatively rare and attempted reproductions in the biomedical sciences \citep{iqbal2016reproducible}, economics \citep{chang2015economics}, computer science \citep{moraila2014measuring}, and psychology \citep{open2015estimating} have all been able to recreate only a portion of results. 
Within geography, the small number of available reproduction attempts similarly suggest that many studies cannot be fully reproduced, or are simply missing the components needed to attempt a reproduction \citep{nust2018, Kedron2021ssrn, konkol2019, ostermann2021, Nust_AGILE_2022}.
For example, \citet{ostermann2021}'s attempt to reproduce the computational analyses of 75 papers published in the GIScience conference series found that most results could not be recreated, or could only be recreated with significant effort. 
\citet{konkol2019}'s attempt to reproduce 41 geocomputational studies likewise found that 39 of the papers had coding issues that hindered reproduction and that 47 percent of the figures created using the original data and code deviated from the those published in some significant way (e.g., graphs with different curves). 
A series of reproduction attempts by \citet{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP} and \citet{paez2022reproducibility} show that the issues hindering the reproduction of results extend beyond computation and into the conceptualization and design of geographic research.
While indicative, these studies provide only suggestive evidence of underlying problems, not a comprehensive assessment of the prevalence or sources of these issues.

Indirect reproducibility assessments offer a wider view of what and how common these underlying issues may be. 
The available evidence from reviews of studies across the sciences suggests inadequate record keeping, opaque reporting, unavailable research components, and a lack of incentives are likely important factors contributing to the irreproducibility of research \citep{NASEM2019}. 
Systematic reviews of publications in prominent outlets \citep{byrne_2017,stodden2018empirical} suggest these issues are likely widespread. 
Reproducibility surveys paint a similar picture. 
Recent surveys suggest that the majority of scientists have either not tried, or tried and failed to reproduce another scientist's work \citep{baker20161, boulbes2018survey}. 
Moreover, a sizable portion of the researchers responding to these surveys admit to engaging in questionable research practices linked to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
These findings match researcher perceptions, which link irreproducibility to causes ranging from natural variation to outright fraud \citep{ranstam2000fraud, anderson2007normative, baker20161}.

To date only a handful studies have attempted to indirectly measure the reproducibility of geographic research.
In a survey of remote sensing editors and working group officers of the International Society for Photogrammetry and Remote Sensing, \citet{balz2020reproducibility} asked respondents whether they believe a reproducibility crises existed in their sub-field, but not what the causes of such a crisis might be.
In a richer treatment of the issue, \citet{konkol2019} surveyed of participants from the 2016 European Geosciences Union General Assembly to assess the frequency with which researchers published their work in ways that enabled computational reproducibility. 
Those authors found that only 33 percent of respondents included links to the data used in their analyses and only 12 percent provided their analytical code. 
The authors also found that only seven percent of respondents ever attempted to reproduce the work of other researchers.
Similarly, in a literature review of volunteered geographic information research, \citet{ostermann2017} found the computational reproducibility of work in the sub-field limited by the availability of original data, metadata, source code, or pseudocode.

%%%%%%%%%%%%%%%%%%%%%%%%
\subsection*{Limitations of the Currently Available Evidence}
Despite their growing number, the available body of reproducibility assessments currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically \citep{NASEM2019}.
This knowledge gap exists because neither direct nor indirect reproducibility assessments have been designed so the results obtained from the sample of studies evaluated can be extended to the population of research as a whole.
Most reproducibility reviews sample studies from conveniently accessible archives, such as conference paper series \citep{gundersen2018state, ostermann2017}, or target specific journals and disciplinary repositories \citep{stodden2018empirical, stodden2018enabling, byrne_2017}.
These assessments have also tended to focus on evaluating the computational components of research such as data and code availability, as this information is easier to identify and assess at scale when compared to components like field procedures or qualitative analysis that may be included only in text.

Surveys of researcher practices and attitudes on reproducibility face similar challenges. 
Rather than carefully defining researcher populations of interest, existing surveys have drawn data non-randomly from self-selecting populations that are convenient to survey (e.g., members of professional association, conference attendees), but are not necessarily representative of researchers active in a particular field. 
These surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response.

### 2023-05-18 docs/manuscript/manuscript.tex

@@
 This study addresses each of these questions by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
-We find ...
-CONClUSION...
+Our results identify a clear division in perception of reproducibility among geographic sub-fields. 
+We also find varying levels of familiarity with reproducible research practices and a perceived lack of incentives to attempt and publish reproduction studies. 
+In contrast, many researchers did report attempting to reproduce their own work but not publishing those efforts, which suggests a foundation exists for the examination and expansion of reproducibility in the field.
 
@@
 \section*{Introduction}
-Reproducibility is important for geographic research for the same reason it is important in other areas of research. 
-In principle, reproducible research publicly discloses the evidence used to support claims made in prior work which facilitates the independent verification of those claims and the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009} .
+Reproducible research publicly discloses the evidence used to support claims made in prior work, facilitates the independent verification of those claims, and the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009}.
 While reproducibility is not a guarantee of scientific or practical usefulness, it does provide a strong basis for the collective evaluation of ideas.
-Nonetheless, research across disciplines suggests that the results of many studies cannot be independently recreated \citep[see][]{moraila2014measuring, chang2015economics, open2015estimating, iqbal2016reproducible} and that few researchers are attempting to independently reproduce the work of others \citep{baker20161, boulbes2018survey}.
-The available evidence links the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details of to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
-At the same time a sizable portion of the researchers admit engaging in questionable research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
+Nonetheless, reviews of published research papers reveal a lack of data and code for reproducibility \citep{moraila2014measuring, iqbal2016reproducible} and attempts to reproduce published research papers frequently fail \citep[see][]{raghupathi2022reproducibility, chang2015economics}.
+Previous studies consistently link the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details or to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
+Surveys of researchers find that few researchers are attempting to independently reproduce the work of others \citep{baker20161, boulbes2018survey}.
+At the same time, a sizable portion of researchers admit engaging in questionable research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
 
-Although not yet systematically measured, many of these same factors may be impacting the reproducibility of geographic research.
-The small number of reproduction studies available within the discipline suggest that many studies cannot be fully reproduced, or are simply missing the components needed to attempt a reproduction \citep[see][]{ Kedron2021ssrn, konkol2019, Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021, paez2022reproducibility}.
+Many of these same factors may be impacting the reproducibility of geographic research, but they have yet to be systematically measured.
+The small number of reproduction studies available within the discipline suggest that most studies are missing the components needed to attempt a reproduction; and of the studies with the needed components, many cannot be fully reproduced \citep[see][]{Kedron2022dimaggio, konkol2019, Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021, paez2022reproducibility}.
 The available surveys of research practices in the discipline also support this conclusion as few researchers report sharing their data, metadata, or source code \citep{balz2020reproducibility, konkol2019, ostermann2017}.
@@
 Attempts to reproduce past results typically focus on recreating the results of one or a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}.
-Attempted reproductions of geographic research for example focus on the computational reproducibility of conference papers \citep{Nust-AGILE_2018} or specific topics such as COVID-19 \citep{Holler2023disability,kedron2021GA, paez2022reproducibility}.
+For example, reproductions of geographic research have focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2022} or on specific topics such as COVID-19 \citep{Holler2023disability, kedron2021GA, paez2022reproducibility}.
 
-More broadly, attempts to catalog or survey reproducible research practices have drawn data non-randomly from conveniently accessible archives such as conference paper series, specific journals, and disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2018empirical, stodden2018enabling}, or from self-selecting populations such as authors in specific journals, members of professional associations, and conference attendees \citep{baker20161} that are not necessarily representative of researchers active in a particular field.
-Like attempts to reproduce specific studies, reproducibility surveys also focus on evaluating the computational components of research such as data and code availability over less accessible information like field procedures or qualitative analysis that may only be included in text.
+More broadly, attempts to catalog or survey reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}, or have drawn samples of researchers from specific journals, members of professional associations, or conference attendees \citep{baker20161}.
+These samples of researcher surveys and research papers have been convenient, but are not guaranteed to be representative of researchers and research activity in a particular field through random sampling.
+Like attempts to reproduce specific studies, reproducibility surveys have also focused on evaluating the computational components of research such as data and code availability over less accessible information like field procedures or qualitative analysis that may only be included in text.
 Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use.
@@
 
-While geographers continue to debate the role of reproduction studies in the discipline \citep{brunsdon2016, goodchild2021Annals, kedron2022replication, kedron2021IJGIS, singleton2016, sui2021}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, ostermann2021}, and build the infrastructure needed to support reproducible research \citep{nust2019, wilson2021, yin2019cybergis}, we have yet to systematically assess the use of reproducible research practices across the discipline's diverse research traditions, or identify the factors that have hindered geographers from adopting reproducible research practices and conducting reproduction studies.
+Geographers continue to debate the role of reproduction studies in the discipline \citep{brunsdon2016, goodchild2021Annals, kedron2022replication, kedron2021IJGIS, singleton2016, sui2021, Wainwright2021}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, ostermann2021}, and build the infrastructure needed to support reproducible research \citep{nust2019, wilson2021, yin2019cybergis}.
+And yet, we still have not systematically assessed the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have hindered geographers from adopting reproducible research practices and conducting reproduction studies.
 Without answers to these questions it is unclear what actions geographers should take if they wish to improve the reproducibility of work in the discipline.
 
-To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, familiarity and use of reproducible research practices, and the factors they see as barriers to reproducibile research using a probability sampling scheme designed to capture the breadth of geographic research.
+To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, familiarity and use of reproducible research practices, and the factors they see as barriers to reproducible research using a probability sampling scheme designed to capture the breadth of geographic research.
 In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
-We then present the results of our survey first focusing on researcher perceptions and use of reproducible research practices, then analyzing researcher experiences attempting to reproduce prior work.
-We then discuss the implications of our survey results. 
-Finally, we conclude by presenting a current snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here. 
-Excluding data that could be used to identify participants, all of the materials, methods, and code used to conduct and analyze our survey are available in online repositories with persistent links and identifiers.
-We encourage interested readers to critically evaluate and build on these materials through their own work.
+We then present the results of our survey, first focusing on researcher perceptions and use of reproducible research practices, and then analyzing researcher experiences attempting to reproduce prior work.
+Finally, we discuss the implications of our survey results and conclude by presenting a current snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here.
 
@@
 Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
-That repository connects to a Github repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
+The OSF repository connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development.
 All of the results presented in this paper can be independently reproduced using the materials in that repository.
+We encourage interested readers to critically evaluate and build on these materials through their own work.
 Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
@@
 \subsection*{Survey Instrument}
-The survey consisted of 23 questions that assess (i) perceptions of the reproducibility of geographic research, (ii) familiarity and use of reproducible research practices, and (iii) beliefs about barriers to reproducibility, and (iv) experience conducting independent reproductions.
-Survey questions were developed following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature.
-All researchers were presented questions about their definition of reproducibility, familiarity with and use of reproducible practices, and perceptions of barriers to reproducibility. 
-A subset of researchers that reported attempting to reproduce a study in the past two years were given an additional set of questions about their experience conducting that work.
+The survey first established eligibility based on age and geographic research activity in the past five years and asked researchers to report their primary subfield and methodology.
+We asked each participant to assess their familiarity with the term ``reproducibility'' and to provide their own definition. 
+We then provided a definition based on the \citet{NASEM2019} to establish a common understanding of reproducibility for the remainder of the survey.
+Remaining questions assessed familiarity and use of reproducible research practices (22 questions), perceptions of the reproducibility of geographic research (2 questions), and beliefs about reproducibility with regards to its significance (17 questions) and barriers (13 questions).
+For researchers who reported attempting reproductions, we asked researcher to elaborate on their motivations and outcomes (9 questions).
 
-We pilot tested the survey instrument with a subset of \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
+We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature.
+We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
 After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.
@@
 
+The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
 Participation in the survey was entirely voluntary. 
 Each researcher that opted to participate in the survey was provided with IRB approved consent documentation and linked to the internet survey instrument. 
-Participants were also given the option to enter a random prize draw. 
-The total possible compensation a participant was eligible to receive was 90 US dollars, awarded as a prepaid credit card.
-Three prize winners were selected at random from those electing to enter the prize draw at the end of the data collection period.
-
-The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
-Each question on the survey was presented as a unique page. 
-Adaptive questioning, conditionally displaying items based on responses to other items, was used to reduce the number of complexity of questions.
-Participating researchers had the option to exit and re-enter the survey and were also able to review and/or change their answers using a back button as they progressed through the survey.
-
+Participants were also given the option to provide an email address for eligibility for one of three  prizes of 90 US\$, selected randomly after the data collection period.
+Participating researchers had the option to exit and re-enter the survey and were also able to review and change their answers using a back button as they progressed through the survey.
 At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
-Responses were downloaded from Qualtrics, anonymized, and stored in a password-protected databases.
-We used a unique key to link this data with participant information (e.g., citation history) stored in a separate database during our statistical analyses. 
-To preserve participant privacy that connection was severed at the end of our analysis.
-We have only shared the anonymized response file through our public repository. 
-As a result some of the result presented below cannot be directly replicated. 
-We have indicated throughout our results section which analysis can and cannot be replicated using the data files and code share through our public repository.
+Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium (self-identifying reference removed).
 
@@
 
-%%%%%%%%%%%
-\subsubsection*{Statistical Approach}
-We conduct two statistical analyses of the survey response.
-First, we create descriptive statistical summaries of the participant response to address how geographic researchers define reproducibility, their familiarity and experience with reproducible research practices, and the barriers to reproducibility they perceive in the discipline.
-Second, we conducted an analysis of the experience of the subset of geographic researchers who reported attempting independent reproductions of prior work during the last two years.
-That analysis identified what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
-Given the topical and epistemological variation that exists among geographic researchers, we examined differences by disciplinary subfield and methodological approach as part of each analysis.
+%%%%%%%
+\subsubsection*{Analyzing Researcher Perspectives on Reproducibility}
+\noindent We conducted two statistical analyses of the survey responses.
+First, we created descriptive statistical summaries of the participant response to assess how geographic researchers define reproducibility, their familiarity and experience with reproducible research practices, and the barriers to reproducibility they perceive in the discipline.
 
-%%%%%%%%%%%
-\subsubsection*{Variable Construction}
-For our first analysis, we constructed summary measures that aggregated researcher responses to questions linked to 1) definitions of reproducibility, 2) familiarity with and 3) use of reproducible research practices, and 4) potential barriers to reproducibility.
-
-\textit{Definition:} Before providing a common definition of reproducibility, we asked each participant to provide their own definition of the term.
-We coded these definitions following two procedures.
-First, we measured the similarity of each provided definition to the definition of adopted by the \citet{NASEM2019}. 
+\textit{Definition:} 
+We coded participants' qualitative definitions of ``reproducibility'' following two procedures.
+First, we measured the similarity of each provided definition to the definition adopted by the \citet{NASEM2019}. 
 The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same conditions.
@@
 Disagreements in the assignment of codes were resolved through discussion between the three authors.
-To create an aggregate measure of agreement the final coded response for each participant was then summed across the four characteristics, creating definition similarity \textit{d} with domain [0, 4].
+We created an aggregate measure of definition similarity for the final coded response for each participant by counting the presence of each NASEM definition characteristic, resulting in a measure with the domain [0, 4].
 
-Second, we coded each definition to one of three motivations for ensuring the reproducibility of a study--- to facilitate the assessment of prior work, to improve transparency and facilitate further extension of work, and to improve the transparency and consistency of study data.
+Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study--- (i) to facilitate the assessment of prior work, (ii) assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
 We derived this coding from common themes in the authors response and our own reading of the reproducibility literature.
@@
 
-\textit{Familiarity and Experience:} We measured participant familiarity and use of five reproduciblity enhancing research practices; the adoption of--- open-source software, research notebooks, data sharing, code sharing, and research plan preregistration.
-We created a summary measure of familiarity with these practices, \textit{f}, by summing the number of reproducible practices a researcher was 'somewhat' or 'very' familiar with.
-To assess experience with these same five practices, we created \textit{p}, which counts the number of practices a researcher reported using 'most of the time' or 'always' when conducting their own research.
-Both \textit{f} and \textit{p} have domains [0,5].
+\textit{Familiarity and Experience:} We measured participant familiarity and experience with five reproducibility enhancing research practices: the adoption of open-source software, research notebooks, data sharing, code sharing, and research plan preregistration.
+We created a measure of familiarity by counting the variety of practices a researcher was 'somewhat' or 'very' familiar with.
+We measured experience by counting the variety of practices a researcher reported using 'most of the time' or 'always' when conducting their own research. 
+Both measures have domains [0, 5].
 
-\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 factors contributed to a lack of reproducibility in the discipline. 
-From those responses, we created a summary measure, \textit{b} with domain [0,12], of the number of barriers a researcher believes 'frequently' or 'occasionally' contributed to irreproducibility.
+\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in the discipline. 
+From those responses, we created a measure of perceived barriers by counting the number of factors a researcher believes 'frequently' or 'occasionally' contributed to irreproducibility, resulting in a measure with domain [0, 12].
 
-Our second analysis examined only researchers that reported attempting a reproduction in the past two years. 
-We asked each of these researchers what motivated their reproduction attempt. 
-Two of the authors independently assigned these responses to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and increase the transparency of their work, iii) replication of a study with new data, and iv) a desire to learn from past work, or use the reproduction in teaching.
+To examine variation in researcher understanding of reproducibility across disciplinary subfields and methodological traditions, we cross tabulated these summary measures and responses to individual questions for these subgroups.
+We then compared response frequencies cross subgroups.
+
+%%%%%%%
+\subsubsection*{Analyzing Researcher Reproduction Attempts}
+\noindent Our second analysis examined only the responses of researchers that reported attempting a reproduction in the past two years to understand what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
+
+\textit{Motivations:} To assess what motivated researchers to attempt reproductions, two of the authors independently assigned participants text-based response to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and/or increase the transparency of their work, iii) replication of a study with new data, and iv) a desire to learn from past work, or use the reproduction in teaching.
 We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
@@
 
+\textit{Success and Barriers:} To analyze participant success, we create statistical summaries for a series of questions that asked researcher to identify whether they were able to partially or completely recreate some or all results of the target study.
+We similarly analyzed barriers to the reproduction of results by creating statistical summaries of participants ability to access key study artifacts (e.g., data, procedural information, code).
+
+Given the topical and epistemological variation that exists among geographic researchers, we again used cross-tabulation to examine differences in response by disciplinary subfield and methodological approach.
+However, the size of our sub-sample for this analysis limited number of cross-tabulations we could pursue.
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \section*{Results}
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Survey Response Demographics}
 A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
@@
 Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
-The majority of respondents were also academics, but were well balanced across career levels as no one category made up more that 30 percent of the sample.
-Respondents were similarly well balanced across the disciplinary subfields - human geography (30.7\%), physical geography (29.8\%), nature and society (10.1\%), geographic methods and GIScience (28.0\%); and methodological approaches - quantitative (42.2\%), qualitative (18.3\%), and mixed-methods (39.0\%) research.
+The majority of respondents were academics, and they were balanced across career levels from graduate students to full professors as no one career level made up more that 30 percent of the sample.
+Respondents were balanced across the disciplinary subfields--- physical geography (29.8\%), geographic methods and GIScience (28.0\%), nature and society (10.1\%), and human geography (30.7\%); and methodological approaches---quantitative (42.2\%), mixed methods (39.0\%), and qualitative (18.3\%).
 
@@
 \subsection*{Researcher Perspectives on Reproducibility}
-A primary aim of our survey was to establish how geographic researchers conceptualize reproducibility and their current level of knowledge and experience with reproducibility enhancing research practices.
-Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%) with half reporting being very familiar with the term (53.6\%).
-A majority of researchers also believe reproducibility is compatible with epistemologies used in the discipline (58.2\%). 
+Reproducibility is on the minds of geographic researchers.
+Nearly all researchers reported being at least somewhat familiar with the term reproducibility (89.0\%), with half reporting being very familiar with the term (53.6\%).
+More pointedly, the majority of survey respondents reported thinking about the reproducibility of their own research (80.7\%), discussing reproducibility with a colleague (70.6\%), and questioning the reproducibility of published work (57.3\%) in the past two years.
+More than half of the researchers we surveyed (52.8\%) also reported considering reproducibility while peer reviewing a grant proposal or publication during the same time frame. 
 However, researchers estimated that only 50.6 percent of the results published in the discipline were reproducible, albeit with a large standard deviation of 24.7 percent that suggests a great deal of uncertainty about the true value.
 Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%). 
+Strikingly, only a small majority of respondents believe reproducibility is compatible with epistemologies used in the discipline (58.2\%).
 
-Table \ref{tab:overview} summarizes how researchers define reproducibility (\textit{d}), their familiarity with (\textit{f}) and use of reproducible research practices (\textit{u}), and the factors they see as barriers (\textit{b}) to reproducibility in geography.
+Table \ref{tab:overview} summarizes how researchers define reproducibility, their familiarity with reproducible research practices and experience using them, and the factors they see as barriers to reproducibility in geography.
 We present the mean and standard deviation for the overall sample and for each subfield and methodological approach.
-In aggregate, the data reveal trends in definition, familiarity, practices, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
+In aggregate, the data reveal trends in definition, familiarity, experience, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
 Respondents that self-identified as specializing in physical geography and geographic methods consistently report higher indicators than those working in nature and society and human geography.
@@
 \subsubsection*{Definitions and Importance of Reproducibility}
-A total of \textit{$n_{d}$}=181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
-On average, geographic researchers provided definitions of reproducibility that explicitly included one or two ($\overline{d}=1.83$) of the four characteristics from the definition adopted by the NASEM.
+A total of 181 (83.0\%) of our survey respondents provided an interpretable definition of reproducibility.  
+Geographic researchers provided definitions of reproducibility that explicitly included an average of 1.83 of the four characteristics from the definition adopted by the NASEM.
 This level of inclusion was consistent across subfields and methodological approaches.
@@
 Researchers' definitions of reproducibility were primarily connected to two epistemic functions.
-Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies.
-Nearly all other researchers (40.9\%) tied reproducibility to the need for transparency in research so others could independently expand upon past studies.
+Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies through comparison of original results to results from an attempted reproduction.
+These ranged from rigid bitwise quantitative interpretations, as in the "ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which "other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results".
+Responses included definitions with a focus on experimental science, as in "an ability to produce consistent results when an experiment is repeated!"
+
+Nearly all other researchers (40.9\%) tied reproducibility to the need for transparency in research so that others could independently expand upon past studies.
+For example a quantitative geographers stated: "The methods should provide sufficient information to be able to reproduce the results.
+In quantitative science this should, at minimum, provide all the equations and algorithms used for any calculation.
+In the interest of increasing transparency in science, the practice of sharing the code should be encouraged.
+For others, open science did not necessarily need to result in identical results: "As a qualitative researcher doing in-depth case study research, my studies can not be perfectly reproduced.
+But reproducibility sits in the openness about methods and data collection practices, as well as critical reflection about strengths and weaknesses of my research.
+When we write about those things in the methods section in our papers and theses, their reproducibility is increased."
+The remainder of responses (6.6\%) emphasized repeatable and/or reliable data observation over all other dimensions of reproducibility.
+For example, "As a historical geographer, working with qualitative research methods, I understand reproducibility more in terms of sources than of methods.
+I see reproducible research as being that which makes clear the origin and location of its data."
+A physical geographer similarly emphasized data observations: "Data/observations of some variable can be recovered repeatedly by different observers/methods"
+
+Responses to related Likert questions from the full survey sample (\textit{n}=218) support the results from the subsample of 181 qualitative definitions analyzed above.
 Identification of reproducibility with both of these functions was supported by responses to related questions from our entire sample (\textit{n}=218). 
@@
 Despite wide recognition of reproducibility as epistemically important, respondents were cautious about drawing conclusions from a single study or reproduction attempt. 
-Half of the respondents (50.9\%) agreed that when researchers don't share their data they have less trust in a study.
-A similar percentage (41.7\%) agreed that inability to reproduce a result detracts from the validity of a study, and a smaller minority agreed that such inability implies that the result is false (26.2\%).
+Only half of the respondents (50.9\%) agreed that when researchers don't share their data they have less trust in a study.
+A smaller percentage (41.7\%) agreed that inability to reproduce a result detracts from the validity of a study, and an even smaller minority agreed that such inability implies that the result is false (26.2\%).
 
 Qualitative researchers identified reproducibility as playing a much smaller epistemic role compared to the discipline as a whole. 
-A majority of the qualitative researchers responded that reproducibility is incompatible with the epistomologies used in their subfield (75.0\%).
-Accordingly a small percentage of qualitative researchers agreed that reproducibility is important for validating (25.0\%) or establishing the credibility (20.0\%) of research.
-Qualitative geographers similarly placed less emphasis on reproducibility as a means of increasing the accessibility and expansion of research.
+A majority of the qualitative researchers responded that reproducibility is incompatible with the epistemologies used in their subfield (75.0\%).
+Accordingly, a small percentage of qualitative researchers agreed that reproducibility is important for validating research (25.0\%) or establishing its credibility (20.0\%).
+Qualitative geographers similarly placed less emphasis on reproducibility as a means of increasing the accessibility and extensibility of research.
 Few qualitative researchers had less trust in a study when researchers did not share their data (27.5\%), or saw reproducibility as important for sharing research with academics (27.5\%).
@@
 %%%%%%%%%%%
-\subsubsection*{Familiarity and Use of Reproducible Research Practices}
-The reproducibility of research is on the minds of geographic researchers. 
-The majority of survey respondents reported thinking about the reproducibility of their own research (80.7\%), discussing reproducibility with a colleague (70.6\%), and questioning the reproducibility of published work (57.3\%) in the past two years.
-More than half of the researchers we surveyed (52.8\%) also reported considering reproducibility while peer reviewing a grant proposal or publication during the same time frame.
-
-Geographic researchers are on average familiar with multiple reproducible research practices ($\overline{f}=3.26$), but reported limited use of these practices in their own work ($\overline{u}=1.44$).
+\subsubsection*{Familiarity and Experience with Reproducible Research Practices}
+Geographic researchers were familiar with an average of 3.26 different reproducible research practices, but only reported experience using an average of 1.44 of these practices in their own work.
 More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\%).
@@
 Just 12.5 percent of qualitative researchers reported familiarity with code sharing, while 81.5 percent of quantitative and 55.7 percent of mixed-methods researchers reported familiarity with the same practice.
-However, even among quantitiative and mixed-methods researchers familiarity with reproducible research practices did not translate into regular use of those practices.
+However, even among quantitiative and mixed-methods researchers, familiarity with reproducible research practices did not translate into regular use of those practices.
 Just over half of quantitative (51.2\%) and mixed-methods (51.8\%) researchers reported sharing their data most of the time.
@@
 \subsubsection*{Perceived Barriers to Reproducible Research}
-Aligning with the differences we observed between researcher familiarity with reproducibility enhancing research practices and researcher use of those same practices, respondents to our survey identified numerous factors contributing to a lack or reproducible research across the discipline ($\overline{b}=8.20$).
+Aligning with the differences we observed between researcher familiarity with reproducibility enhancing research practices and researcher use of those same practices, respondents to our survey identified an average of 8.20 factors contributing to a lack or reproducible research across the discipline.
 Geographic researchers working in different subfields and with different methodological approaches each identified a similar number of barriers to reproducibility (Table \ref{tab:barriers}).
@@
 These researchers identified fewer barriers to reproducibility on average, but with a greater variance that left us unable to distinguish this group from any other.
-To examine differences in researcher beliefs about specific factors potentially hindering reproducibility in the discipline, we divided the 12 factors we examined into three groups --- those related to the research environment, the availability of research artifacts, and study-specific characteristics.
+To examine differences in researcher beliefs about specific factors potentially hindering reproducibility in the discipline, we divided the 12 factors we examined into three groups---those related to the research environment, the availability of research artifacts, and study-specific characteristics.
 
@@
 Geographic researchers identified the incentive structure of the researcher environment as an important barrier to reproducibility in the discipline.
-A majority of geographic researchers identified both the pressure to publish (71.5\%) and insufficient oversight of the research process (71.1\%) as barriers to reproducibility.
+A majority of geographic researchers identified both the pressure to publish original research (71.5\%) and insufficient oversight of the research process (71.1\%) as barriers to reproducibility.
 A high percentage of physical, methods-focused, quantitative, and mixed-methods researchers identified these factors as barriers. 
-Qualtiative geographers were least concerned with these factors, but a majority of these researchers still identified both factors as barriers to reproducibility in the field.
-Contrary to alarms raised in some of the reproducibility literature, a minority of geographic researchers (28.4\%) believe that the fabrication of data, the manipulation of research results, and similar forms of fraud are a cause of irreproducibility in the discipline.
+Qualitative geographers were least concerned with these factors, but a majority of these researchers still identified both factors as barriers to reproducibility in the field.
+A minority of geographic researchers (28.4\%) believe that the fabrication of data, the manipulation of research results, and similar forms of fraud are a cause of irreproducibility in the discipline.
+These percentage is roughly aligned with values reported elsewhere in the reproducibility literature \citep{fanelli2009many, baker20161}.
 
@@
 Only a large percentage of methods-focused researchers (82.0\%) identified the use of restricted data/software as a common contributor to irreproducibility in the discipline.
-A similar gap existed between qualitative researchers, a minority of which identified code availability or the use of restricted data/software as contributing to irreproducibility, and quantiative and mixed-methods researchers, the majority of which saw these factors as frequent causes of irreproducibility.
+A similar gap existed between qualitative researchers, a minority of which identified code availability or the use of restricted data/software as contributing to irreproducibility, and quantitative and mixed-methods researchers, the majority of which saw these factors as frequent causes of irreproducibility.
 
@@
 
-In most instances, researchers reported some ability to access the research artifacts used in the study they were attempting to reproduce and the ability to recreate at least some of the results of that study.
-The majority of researchers that attempted reproductions (87.5\%) were able to access at least some of the data used in the original study, but few researchers (12.5\%) reported access to all of the original data.
+Most of the 32 researchers that attempted to reproduce a prior study reported at least some success in accessing data and procedures and in reproducing the prior study results.   
+The majority of researchers (87.5\%) were able to access some of the data used in the original study, but few researchers (12.5\%) reported access to all of the original data.
 Researchers also reported the ability to access at least some information about study procedures (68.8\%) and its computational environment (59.4\%), but limited ability to access all procedural (9.4\%) and computational information (12.5\%).
-Despite these limitations, nearly all researchers reported at least partially reproducing some results (81.3\%), but less than half reported being able to at least partially reproduce all results (21.9\%).
-Few researchers were able to identically reproduce all results (9.4\%).
+Nearly all researchers reported at least partially reproducing some results (81.3\%), but only seven (21.9\%) reported being able to at least partially reproduce all results.
+For the purposes of this survey, ``Partially reproduce'' was defined as producing slightly different results as the prior study, but with the same overall conclusions.
+Only three researchers (9.4\%) were able to identically reproduce all results.
 
-How much access researchers had to study data and procedural information seems to impact their ability to reproduce results. 
-If geographic researchers had access to at least some of the data and procedures used in the study they were attempting to reproduce, they were able to at least partially reproduce some results in nearly all cases (90.5\%), but were able at least partially reproduce all results only a fraction of the time (14.3\%).
+Access to prior study data and procedural information appears to impact the ability to reproduce prior study results. 
 When researchers had access to some of the data from the original study, they reported being able to at least partially reproduce all results in 6 of 24 instances. 
@@
 We observed a similar increase in researcher ability to at least partially reproduce all results when researchers reported access to all procedural information. 
-Having access to all procedures was linked to partial reproduction of all results in 3 of 3 instances, compared to just 6 of 19 instances when researchers could only access some procedural information.
-We report counts in these cases, becasuse the small number of total independent reproduction attempts makes it difficult to draw definitive conclusions on the relative importance of data or procedures when attempting a reproduction of geographic work.
+When researchers had access to some of the procedural information from the original study, they reported being able to at least partially reproduce all results in 6 of 19 instances.
+That success rate rose to 3 of 3 when researchers reported access to all procedural information and all code.
+The small number of reproduction study attempts reported in the survey results make it difficult to draw broad conclusions.
+However, the results are internally consistent and intuitively support the importance of available data and procedures for successful reproductions of geographic research.
 
@@
 \subsection*{Discussion}
-Overall, the results of our survey collectively suggest that geographic researchers are aware of reproducible research practices, but have yet to incorporate many of those practices into their own work.
-We also found that few researchers report attempting to independently reproduce the work of others. 
-In alignment with the broader reproducibility literature, a majority of respondents identified a lack methodological transparency and the unavailability of data and procedural information, particularly code, as key barriers to reproducibility in the discipline.
+Overall, the results of our survey indicate that geographic researchers are aware of reproducibility and reproducible research practices, but have yet to incorporate many of those practices into their own work.
+We found that few researchers attempt to independently reproduce the work of others, or to publish the reproduction attempts they do undertake.
+In alignment with the broader reproducibility literature, geographic researchers identify the lack methodological transparency and the unavailability of data and procedural information, particularly code, as key barriers to reproducibility in the discipline.
 Our results also suggest the existence of an incentive problem within the discipline, as pressure to publish original research and a lack of oversight create the opportunity to publish irreproducibile work and limited reward for attempting and publishing reproduction studies.
+These findings empirically confirm prior speculations about the reproducibility of geographic research --- on the whole geographers have yet to make reproducible research practices and reproduction attempts a regular part of disciplinary practice.
 
-Our findings also suggest that geographic research do not share a single definition of the reproducibility. 
-In fact, our results show that while researchers share beliefs about the epistemological functions of independent reproductions, they provide definitions that contained different requirements for similarity across studies in terms of data, procedures, results, and context.
-Moreover, a subset of researchers define reproducibility as what the NASEM \citet{NASEM2019} defines as replicability - the ability to obtain consistent results across studies designed to answer the same question, each of which has obtained its own data.
+Our findings also suggest that geographic researchers do not share a single definition of the reproducibility. 
+While researchers share beliefs about the epistemological functions of independent reproductions, they provide definitions that contained different requirements for similarity across studies in terms of data, procedures, results, and context.
+Moreover, a subset of researchers define reproducibility as what the \citet{NASEM2019} defines as replicability - the ability to obtain consistent results across studies designed to answer the same question, each of which has obtained its own data.
 The interchangeable use of reproducibility and replicability, or the outright reversal of definitions we observed in our sample, has also been documented across the sciences \citep{barba2018terminologies, plesser2018reproducibility}.
 Given that geography has no established standard use of either term and that many geographic researchers are also trained in other disciplines, it is likely that researchers at least partially inform their definition of reproducibility using concepts prominent in their cognate fields.
+
 More broadly, our observed variation in terminology is important for at least two reasons. 
+First, if researchers lock into an ontological debate about the definition of reproducibility rather than a shared understanding of its potential functions, the community as a whole may hinder a more productive discussion about the epistemological role independent reproductions and open science practices can or should play in the discipline.
+Second, variation in geographic researchers' understanding of reproducibility reflects the discipline's diverse traditions and ways of knowing. 
+Acknowledging this diversity as a strength of the discipline, productive discussions about reproducibility should consider how reproducible research practice fits into different traditions and what common understanding exists across traditions.
+Our findings point to potentially productive pathways for such a discussion. 
+Even among the subset of respondents most uncertain about the role of reproducibility in geographic research--- qualitative geographers---we observed recognition of the value reproducible research practices bring to the transparency of research, with a particular emphasis on the sharing of methods and procedures.
 
-First, if researchers lock into a debate about the definition of reproducibility rather than a shared understanding of its potential functions, the community as a whole may hinder a more productive discussion about the role independent reproductions and open science practices can or should play in the discipline.
-Second, variation in geographic researchers' understanding of reproducibility reflects the discipline diverse traditions and ways of knowing. 
-Acknowledging this diversity as a strength of the discipline, productive discussions about reproducibility should consider how the reproducible research practice fits into different traditions and what common understanding exists across traditions.
-Our findings point to potentially productive pathways for such a discussion. 
-Even among the subset of respondents most uncertain about the role of reproducibility in geographic research, qualitative geographers, we observed recognition of the value reproducible research practices bring to the transparency of research, with a particular emphasis on the sharing of methods and procedures.
-
-However, our results also show that self-identified qualitative researchers have a different perspective on the role or reproducibility in geographic research when compared to other subgroups of respondents.
+Our results suggest that qualitative researchers have a different perspective on the role or reproducibility in geographic research when compared to other subgroups.
 The extent to which we can generalize this perspective is limited by the size of our sample of qualitative researchers (\textit{$n_{ql}$}=40).  
 Nonetheless, the majority of our qualitatively-focused respondents believe reproducibility is incompatible with their epistemological approach.  
-The definitions these researcher provided suggest this belief may be rooted in the role researcher positionality can play in the collection and interpretation of qualitative data. 
-Several respondents questioned whether an independent researcher could ever collect the same data from the same set of participants, or even given the same data would bring their own unique interpretive lens making the recreation of exact result impossible.
-Several qualitative respondents also focused on what one researcher termed 'transferability', the desire to know that what they have discovered is relevant in other similar contexts. 
-These are all relevant questions, but also raise issues that are more closely associated with what the NASEM defines as replicability.
+The reproducibility definitions these researchers provided suggest this belief may be rooted in the role researcher positionality plays in the collection and interpretation of qualitative data. 
+Several respondents questioned whether an independent researcher analyzing the same data through their unique interpretive could come to the exact same results. 
+Respondents also focused on what one researcher termed 'transferability', the desire to know that what they have discovered is relevant in other similar contexts.
 
-Recognizing this variation in the conceptualization of reproducibility not only reinforces our prior point, it suggests further ways to productively discuss and work toward reproducibility. 
+Engaging qualitative researchers and integrating their perspectives and knowledge has the potential address issues in the reproducibility literature.  
 Perhaps one way forward is initiate a conversation that highlights how reproducibility is not an absolute standard or determinant of research quality, but instead a means of clarifying for others what was was done in a study and why conclusions were drawn as they were.
-Even if a researcher believes their positionality influences the data they collect and the interpretations and claims they ultimately make to the point where an independent research could not recreate those results, using reproducible research practices where appropriate may help convey that researcher's position and its impact on outcomes.
-To our knowledge there is little explicit discussion in the reproducibility literature about how researcher positionality can or should be recorded and conveyed to other researchers. 
-Introducing existing discussions of this issue from that tradition to the reproducibility literature may be a fruitful collaborative path.  
-This perspective may move the conversation about reproducibility away from a current focus on exactly recreating numerical results, and back to the practice's deeper function - independently assessing the arguments of another researcher.
+Even if a researcher believes positionality influences data collection and interpretation, using reproducible research practices may help convey that position and its impact on study results.
+To our knowledge, there is little explicit discussion in the reproducibility literature about how researcher positionality can or should be recorded and conveyed to other researchers. 
+It would also be interesting to know whether certain elements of researcher positions appear stable across researchers and contexts.
+Such work could also move the conversation about reproducibility away from a current focus on exactly recreating numerical results, and back to the practice's deeper function---independently assessing the arguments of another researcher.
 
@@
 To draw a reliable and generalizable understanding of this issue, we developed a sampling frame using recent publications in indexed journals to gather information from our target population of individuals actively publishing geographic research.
-One limitation of our approach is that geographic researchers publish in a range of journals that are not necessarily indexed as geography by the Web of Science. 
-Our sampling frame and strategy would not capture these individuals. 
-However, we believe the number of individuals falling into this category will be small as most active geographic researchers are likely to publish at least one study in a geography journal over a 5-year period.
+Ideally, we would stratify this set of potential respondents into subgroups based on common characteristics meaningful to their knowledge of reproducibility and use of reproducibile research practices, and then randomly draw participants from these subgroups to create a balanced and representative sample.
+If our resulting sample was imbalanced across subgroups, we would then use a post-stratification procedure to adjust the non-representative sample using the predictors known to characterize the strata and response.
 
-A related concern is that our survey response may suffer from self-selection bias. 
-It may be the case that geographic researchers more familiar with reproducible research practices, or those working in subfields more involved with the current reproduciblity debate (e.g., quantitative, computational research) are more likely to respond to our survey.
-Conversely, it may also be the case that researchers working in subfields traditionally associated with critiques of a positivist scientific approach (e.g., qualitative, human geography) are less likely to participate in our survey.
-Two means of addressing these concerns would be to stratify our initial sampling or to poststratify our final sample.
-Startification divides potential subjects into subgoups based on common characteristcs, while poststratification adjusts a non-representative sample using predictors known to characterize strata that are likewise known to have different response characteristics.
-We initially considered balancing our sampling across strata meaningful to reproducibility. 
-However, the existing lack of knowledge about the researcher characteristics that might meaningfully differentiate strata, and our inability to accurately measure those characteristics led use to adopt a simple random sampling scheme.
+We could not follow this approach for three reasons. 
+First, meaningful stratification and post-stratification require knowledge of what predicts differences in response.
+Given the currently limited understanding of reproducibility within geography, we can only speculate about the researcher characteristics predictive or different level of familiarity and experience with reproducible research.
+We do not the foundational knowledge needed to identify reliable predictors.   
+Second, even if predictors could be selected to be used in stratification or post-stratification, they must be measured for the population of geographic researchers.
+We are not aware of any census of geographic researchers that could be used to identify and classify all those working in the field.
+Third, given population wide measures of key predictors, potential respondents would also have to a assigned to specific measures, which can be difficult within geography.
+For example, divisions between subfields and approaches in geography are often unclear and researchers often identify in with multiple subfields and approaches. 
+Without this knowledge and data, we have no way of knowing if an adjustment to our sample is likely to increase or decrease bias in our results.
 
-Relatedly, we do not currently have sufficient knowledge of the predictors of differences in response or good measures of key researcher characteristics across the population to inform a meaningful poststratification adjustment.
-In this circumstance, if we were to poststratify our data we would have no way of knowing whether our actions increased or decreased the bias in our results. 
-Considering this challenge, our results could be viewed as an exploratory analysis identifying researcher characteristics that might differentiate subgroups with similar understandings of reproducibility that could then be used to stratify or poststratify future reproducibility related research in geography.
+Being unable to meaningfully differentiate subgroups for either stratification or post-stratification, we adopted a simple random sampling scheme and provide our data to facilitate transparency and reanalysis of our sample.
+Considering these challenges, our results could be viewed as an exploratory analysis that identifies researcher characteristics that might differentiate subgroups with similar understandings of reproducibility, which could be used to stratify or post-stratify future reproducibility related research in geography.
+Nonetheless, because we were unable to assess the representativeness of our sample our results may be subject to at least three forms of bias.
 
-While self-selection may exist in our data, it may also be less of a concern because the forms of self-selection we have discussed are likely to only amplify some of our key findings. 
+\textit{Exclusion Bias:} One limitation of our approach is that geographic researchers publish in a range of journals that are not necessarily indexed as geography by the Web of Science. 
+Geographic researchers that have only published outside these indexed journals would not be captured in our sampling frame creating non-coverage errors in our sample. 
+However, we believe the number of individuals falling into this category will be small as most active geographic researchers are likely to publish at least one study in one of the X geography journals used in our sampling frame over a 5-year period.
+
+\textit{Self-selection Bias}.
+A related concern is that it may be the case that geographic researchers more familiar with reproducible research practices, or those working in subfields more involved with the current reproduciblity debate (e.g., quantitative, computational research) were more likely to respond to our survey.
+Conversely, it may also be the case that researchers working in subfields traditionally associated with critiques of a positivist scientific approach (e.g., qualitative, human geography) were less likely to participate in our survey.
+While self-selection bias may shape our data, we believe its presence is a limited concern because it is likely to only amplify some of our key findings. 
 Namely, that reproducible research practices have yet to be widely adopted in the field and that relatively few geographers are attempting and sharing independent reproduction studies.
-However, we think that concern about self-selection should motivate a closer examination of reproducibility in the context of geography's qualitative, human, and nature society traditions.  
-It would be interesting to not only know how to better document and share components of qualitative research designs and research positions, but whether reproducibility could be used as a lens for the investigation of
-whether certain elements of those approaches and positions appear to be stable across researchers and contexts.
+Nonetheless, we believe concerns about self-selection should motivate a closer examination of reproducibility within the subfields and approaches for which we obtained the smallest samples --- qualitative, human geography, and nature society.
 
-Another potential limitation of our research is that we based our survey instrument on a review of prior reproducibility surveys and our identification of practices and barriers discussed in the reproducibility literature.
+\textit{Questionnare Bias:} Another potential limitation of our research is that we based our survey instrument on a review of prior reproducibility surveys and our identification of practices and barriers discussed in the reproducibility literature.
 To the extent that this literature over represents perspectives from selected disciplines, experimental research designs, and computationally-intensive research approaches our survey may reflect this bias.
@@
 \subsection*{Conclusion}
+Reproducibility remains an emerging topic in the geographic literature. 
+In this study, we provide the first systematic survey of the use of reproducible research practices across geography's diverse research traditions. 
+Our results make clear that geographic researchers are aware or reproducible research practices, but lack direct experience using those practices.
+Academic incentive systems and the inaccessibility of key components of prior research hinder reproducibility, and a small percentage of researchers are attempting to independently reproduce past work.
 
-\begin{itemize}
-    \item We created a base t build on. everything is available. Please, Reproduce our survey! Replicate our survey! Improve our survey!
-\end{itemize}
+Our work also creates a foundation for the further empirical investigation of reproducibility within geography and across the discipline's many traditions. 
+We have made all the materials used in the development and execution of this research openly available so others can critique and extend our work.
+We urge other researchers to replicate our research, improve our sampling frame and survey instrument, and progressively create a deeper understanding of questions we only begin to address in this work.
 
-\begin{itemize}
-    \item essential interpretation based on key findings
-    \item unanswered questions and potential future work
-    \item Overall story is that collectively geographers are aware of reproducible research practices, but don't have a matching amount of direct experience using those practices.
-There are also many perceived barriers to conducting reproducible research.
-\end{itemize}
-
+%%%%%%%%%%%%%%%%%%%%%%%%
 \theendnotes
@@
          \hline
-         Definition (\textit{d}) & \begin{tabular}[c]{@{}c@{}}1.73\\ (1.11)\end{tabular} &
+         Definition & \begin{tabular}[c]{@{}c@{}}1.73\\ (1.11)\end{tabular} &
                         \begin{tabular}[c]{@{}c@{}}2.00\\ (1.09)\end{tabular} & 
@@
                         37 \\
-         Familiarity (\textit{f}) &  \begin{tabular}[c]{@{}c@{}}3.71\\ (0.98)\end{tabular} & 
+         Familiarity &  \begin{tabular}[c]{@{}c@{}}3.71\\ (0.98)\end{tabular} & 
                         \begin{tabular}[c]{@{}c@{}}3.97\\ (0.86)\end{tabular} & 
@@
                         0 \\
-         Practices (\textit{u}) & \begin{tabular}[c]{@{}c@{}}2.06\\ (1.18)\end{tabular} &
+         Experience & \begin{tabular}[c]{@{}c@{}}2.06\\ (1.18)\end{tabular} &
                         \begin{tabular}[c]{@{}c@{}}1.85\\ (1.38)\end{tabular} & 
@@
                         0 \\         
-         Barriers (\textit{b}) & \begin{tabular}[c]{@{}c@{}}8.31\\ (3.00)\end{tabular} &
+         Barriers & \begin{tabular}[c]{@{}c@{}}8.31\\ (3.00)\end{tabular} &
                         \begin{tabular}[c]{@{}c@{}}9.31\\ (2.79)\end{tabular} & 
@@
         \footnotesize
-        \item Cells report the percentage of respondents reporting each factor frequently, occasionally, or always contributed to a lack of reproducibility in geographic research.
+        \item Cells report the percentage of respondents reporting each factor occasionally or frequently contributed to a lack of reproducibility in geographic research.
 Acronyms indicate: \textit{PH} Physical Geography, \textit{MT} GIScience and Methods, \textit{NS} Nature and Society, \textit{HU} Human Geography; \textit{QN} Quantitative, \textit{MX} Mixed Methods, \textit{QL} Qualitative.

### 2023-05-18 procedure/code/200_deidentify.R
incomplete surveys & survey questions
added code to 200_deidentify to save plain text file of questions and modified 201_clean to 201_clean_analyze_drops.R to isolate incomplete responses and added

@@ -50,6 +50,11 @@ hegs_rpr_deidentified <- raw_rpr_responses %>%
                                 DistributionChannel,
                                 UserLanguage))
 
+# save plain text file of questions
+sink(here("data", "metadata", "questions.txt"))
+print(raw_rpr_survey_questions, n=1000)
+sink()
+
 saveRDS(hegs_rpr_deidentified, here("data","raw","public","raw_hegs_rpr.rds"))
 
                         

### 2023-05-18 procedure/code/201_clean_analyze_drops.R

@@ -1,0 +1,327 @@
+# list of required packages
+packages = c("here","tidyverse","table1","officer")
+
+# load and install required packages
+package.check <- lapply(
+  packages,
+  FUN = function(x) {
+    if (!require(x, character.only = TRUE)) {
+      install.packages(x, dependencies = TRUE)
+      library(x, character.only = TRUE)
+    }
+  }
+)
+
+# save the R processing environment to r_environment.txt
+writeLines(capture.output(sessionInfo()),here("procedure","environment","r_environment.txt"))
+
+#--------------------------------------------#
+
+#- Read in data file to completes -#
+
+#--------------------------------------------#
+raw_hegs_rpr <- readRDS(here("data","raw","public","raw_hegs_rpr.rds"))
+
+
+#------------------------------------#
+
+#- Backcode other specify responses -#
+
+#------------------------------------#
+  
+table(toupper(raw_hegs_rpr$Q3_5_TEXT))
+
+#-Open response areas of specialization to recode-#
+hum_list  <- c("ECONOMIC GEOGRAPHY","POLITICAL GEOGRAPHY", "POLITICAL SCIENCE", "SOCIO-ANTHROPOLOGY", "MOBILITIES",
+              "SOCIOLOGY","TRANSPORT GEOGRAPHY","TRANSPORTATION","TRANSPORTATION ENGINEERING", "URBAN GEOGRAPHY",
+              "GEOGRAPHY OF INNOVATION")
+
+phys_list <- c("BIOGEOGRAPHY","PALEOBOTANY","PALEOCLIMATOLOGY")
+
+nat_list  <- c("CITY PLANNING, SUSTAINABILITY TRANSFORMATIONS","ENVIRONMENTAL ARCHAEOLOGY","ARCHAEOLOGY")
+
+gis_list  <- c("GEOSPATIAL INFORMATION SCIENCE", "SPATIAL ECONOMETRICS", "CARTOGRAPHY","REMOTE SENSING",
+              "REMOTE SENSING OF ENVIRONMENT")
+
+int_hegs_rpr <- raw_hegs_rpr %>% 
+                  mutate(Q3_recoded = as.factor(ifelse(toupper(Q3_5_TEXT) %in% hum_list, 1, 
+                                        ifelse(toupper(Q3_5_TEXT) %in% phys_list, 2, 
+                                            ifelse(toupper(Q3_5_TEXT) %in% nat_list, 3, 
[…]

### 2023-05-19 procedure/code/201_clean_analyze_drops.R
export incomplete responses

@@ -65,7 +65,8 @@ int_hegs_rpr <- int_hegs_rpr %>%
                           0))
 
 # isolate incomplete surveys
-unfinished <- filter(int_hegs_rpr, include == 0) %>% select(Q3, Q3_5_TEXT, Q3_recoded)
+unfinished <- filter(int_hegs_rpr, include == 0) %>% select(Q3, Q3_5_TEXT, Q3_recoded, Q4)
+write.csv(unfinished, here("data", "derived", "public", "incomplete_responses.csv"))
 
 int_hegs_rpr <- raw_hegs_rpr %>% filter(include == 1)
 summary(int_hegs_rpr$Progress)

### 2023-05-19 docs/manuscript/manuscript.tex

@@
 
+\usepackage{doi}
 \usepackage{natbib}
@@
 The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
+Another \textit{$n_{nc}$}=40 authors started the survey, but did not complete enough of the survey to be included in the analysis.
+
 Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
@@
 Conversely, it may also be the case that researchers working in subfields traditionally associated with critiques of a positivist scientific approach (e.g., qualitative, human geography) were less likely to participate in our survey.
-While self-selection bias may shape our data, we believe its presence is a limited concern because it is likely to only amplify some of our key findings. 
+We attempted to partially quantify this issue by examining the characteristics of the 40 researchers who started our survey but did not complete enough of the survey to be included in the final analysis.
+The percentage of incomplete responses for each disciplinary subfield and methodological approach broadly matched the percentages we observed for each subgroup in our completed responses.
+The only deviation we observed from the complete survey percentages was for researchers that identified as geographic methods and GIScience (28.3\%) and quantiative (22.5\%) researchers. 
+These values suggest that, at least among researchers that stated the survey, self-selection was not a significant issue.
+This analysis of course does not measure researchers who elected to never start the survey.
+
+While we cannot definitively eliminate the possibility of self-selection bias from our survey, we believe its presence may be a limited concern because it is likely to only amplify some of our key findings.
 Namely, that reproducible research practices have yet to be widely adopted in the field and that relatively few geographers are attempting and sharing independent reproduction studies.
@@
 
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 \newpage
 \bibliography{references}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

### 2023-05-29 docs/manuscript/manuscript.tex

--- 2023-05-18 docs/manuscript/manuscript.tex
@@
 Existing attempts to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 
-Despite this suggestive evidence, we have not yet systematically assessed geographers' perceptions of reproducibility, the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have kept geographers from conducting more reproduction studies.
-This study addresses each of these questions by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
+Despite this suggestive evidence, we have not yet systematically assessed geographers' perceptions of reproducibility or the use of reproducible research practices across the discipline's diverse research traditions; nor have we identified the factors that keep geographers from conducting more reproduction studies.
+We address each of these questions by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
 Our results identify a clear division in perception of reproducibility among geographic sub-fields. 
 We also find varying levels of familiarity with reproducible research practices and a perceived lack of incentives to attempt and publish reproduction studies. 
-In contrast, many researchers did report attempting to reproduce their own work but not publishing those efforts, which suggests a foundation exists for the examination and expansion of reproducibility in the field.
+Despite many barriers to reproducibility and divisions between subfields, we also find common foundations for examining and expanding reproducibility in the field.
+These include interest in publishing transparent and reproducible methods, and in reproducing other researchers' studies for a variety of motivations including learning, checking the validity of a prior study, or extending the prior study.
 
@@
 While reproducibility is not a guarantee of scientific or practical usefulness, it does provide a strong basis for the collective evaluation of ideas.
-Nonetheless, reviews of published research papers reveal a lack of data and code for reproducibility \citep{moraila2014measuring, iqbal2016reproducible} and attempts to reproduce published research papers frequently fail \citep[see][]{raghupathi2022reproducibility, chang2015economics}.
+Nonetheless, systematic reviews \citep{moraila2014measuring, iqbal2016reproducible} of published research papers reveal a lack of data and code for reproducibility  and attempts to reproduce published research papers \citep{raghupathi2022reproducibility, chang2015economics} frequently fail.
 Previous studies consistently link the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details or to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
@@
 
-Many of these same factors may be impacting the reproducibility of geographic research, but they have yet to be systematically measured.
-The small number of reproduction studies available within the discipline suggest that most studies are missing the components needed to attempt a reproduction; and of the studies with the needed components, many cannot be fully reproduced \citep[see][]{Kedron2022dimaggio, konkol2019, Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021, paez2022reproducibility}.
-The available surveys of research practices in the discipline also support this conclusion as few researchers report sharing their data, metadata, or source code \citep{balz2020reproducibility, konkol2019, ostermann2017}.
-At the same time, recent reproduction attempts by \citet{Kedron_MollaloRP, Kedron_SaffaryRP, Kedron_VijayanRP} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.
+Despite these concerns, the available literature currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically.
+This knowledge gap exists because researchers conducting reproducibility assessments, surveys of researcher practices, and reproduction attempts have not defined clear target populations for inference, or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
+Attempts to reproduce past results typically focus on recreating the results of one or a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}.
+Attempts to catalog or survey reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}, or have drawn samples of researchers from specific journals, members of professional associations, or conference attendees \citep{baker20161}.
+These samples are convenient, but are not guaranteed to be representative of researchers and research activity in a particular field. 
+Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use.
+Finally, both reproduction attempts and reproducibility surveys have focused on evaluating the computational components of past studies such as data and code availability rather than all aspects of research design and execution.
 
-Despite these suggestive findings, the available literature currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically.
-This knowledge gap exists because researchers conducting reproducibility assessments have not defined clear target populations or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
-Attempts to reproduce past results typically focus on recreating the results of one or a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}.
-For example, reproductions of geographic research have focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2022} or on specific topics such as COVID-19 \citep{Holler2023disability, kedron2021GA, paez2022reproducibility}.
-
-More broadly, attempts to catalog or survey reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}, or have drawn samples of researchers from specific journals, members of professional associations, or conference attendees \citep{baker20161}.
-These samples of researcher surveys and research papers have been convenient, but are not guaranteed to be representative of researchers and research activity in a particular field through random sampling.
-Like attempts to reproduce specific studies, reproducibility surveys have also focused on evaluating the computational components of research such as data and code availability over less accessible information like field procedures or qualitative analysis that may only be included in text.
-Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use.
-The few available surveys of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017} face these same challenges.
+Reproducibility surveys and reproduction attempts in the geographic literature face these same challenges. 
+The few available reproducibility surveys in the discipline have relied on convenience samples drawn from specialist conferences and have only focused on computationally intensive forms of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017}.
+The small number of published attempts to reproduction geographic research similarly have focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021,} or on specific topics such as COVID-19 \citep{Holler2023disability, Kedron2022dimaggio, Kedron2023Beyond, paez2022reproducibility}.
+More recent reproduction attempts by \citet{Kedron2023Beyond} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.
 
@@
 
-To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, familiarity and use of reproducible research practices, and the factors they see as barriers to reproducible research using a probability sampling scheme designed to capture the breadth of geographic research.
+To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, perception of reproducibility in their sub-fields,  familiarity and use of reproducible research practices, and the factors they see as barriers to reproducible research.
+To support generalization, we used a probability sampling scheme designed to capture the breadth of geographic research.
 In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
 We then present the results of our survey, first focusing on researcher perceptions and use of reproducible research practices, and then analyzing researcher experiences attempting to reproduce prior work.
-Finally, we discuss the implications of our survey results and conclude by presenting a current snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here.
+Finally, we discuss the implications of our survey results and conclude by presenting a snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here.
 
@@
 Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication.
-Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = "Article"} and removed all other publication types (e.g., editorials, book reviews) from our article database.
+Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = ``Article''} and removed all other publication types (e.g., editorials, book reviews) from our article database.
 We also removed articles with missing authorship information.
@@
 Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
-We determined uniqueness by grouping researchers by their author-id, and we selected for the most recent contact information by selecting records associated with the most recent year of publication. 
+We determined uniqueness by grouping researchers by their author-id, and we determined the most recent contact information by selecting records associated with the most recent year of publication. 
 For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.
@@
 Roughly one-third (33.0\%) were most recently a corresponding author for an article published in a general geography journal. 
-A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).
+A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions had published in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).
 
@@
 We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
-After pilot testing we removed these individuals from our sampling frame to ensure they would not be included in our final sample.
+After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.
 
@@
 
-%%%%%%%
+We conducted two statistical analyses of the survey responses.
+First, we analyzed researcher perspectives on reproducibility by coding and calculating summary variables and statistics for three themes: how geographic researchers define reproducibility, familiarity and experience with reproducible research practices, and perceived barriers to reproducibility.
+Second, we analyzed researchers' experiences with reproducing prior studies, for those who had done so, including their motivations and experience of successes and barriers.
+
 \subsubsection*{Analyzing Researcher Perspectives on Reproducibility}
-\noindent We conducted two statistical analyses of the survey responses.
-First, we created descriptive statistical summaries of the participant response to assess how geographic researchers define reproducibility, their familiarity and experience with reproducible research practices, and the barriers to reproducibility they perceive in the discipline.
 
-\textit{Definition:} 
+\noindent For our first set of analyses, we examined the full set of survey responses.
+
+\textit{Defining Reproducibility:} 
 We coded participants' qualitative definitions of ``reproducibility'' following two procedures.
@@
 
-Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study--- (i) to facilitate the assessment of prior work, (ii) assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
-We derived this coding from common themes in the authors response and our own reading of the reproducibility literature.
+Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study: (i) to facilitate the assessment of prior work, (ii) assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
+We derived this coding from common themes in the responses and our own reading of the reproducibility literature.
 As above, each definition was independently coded by each author before code assignments across authors were compared with disagreements resolved through discussion.
@@
 \textit{Familiarity and Experience:} We measured participant familiarity and experience with five reproducibility enhancing research practices: the adoption of open-source software, research notebooks, data sharing, code sharing, and research plan preregistration.
-We created a measure of familiarity by counting the variety of practices a researcher was 'somewhat' or 'very' familiar with.
-We measured experience by counting the variety of practices a researcher reported using 'most of the time' or 'always' when conducting their own research. 
+We created a measure of familiarity by counting the variety of practices a researcher was `somewhat' or `very' familiar with.
+We measured experience by counting the variety of practices a researcher reported using `most of the time' or `always' when conducting their own research. 
 Both measures have domains [0, 5].
@@
 \textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in the discipline. 
-From those responses, we created a measure of perceived barriers by counting the number of factors a researcher believes 'frequently' or 'occasionally' contributed to irreproducibility, resulting in a measure with domain [0, 12].
+From those responses, we created a measure of perceived barriers by counting the number of factors a researcher believes `frequently' or `occasionally' contributed to irreproducibility, resulting in a measure with domain [0, 12].
 
 To examine variation in researcher understanding of reproducibility across disciplinary subfields and methodological traditions, we cross tabulated these summary measures and responses to individual questions for these subgroups.
-We then compared response frequencies cross subgroups.
+We then compared response frequencies across subgroups.
 
@@
 \subsubsection*{Analyzing Researcher Reproduction Attempts}
-\noindent Our second analysis examined only the responses of researchers that reported attempting a reproduction in the past two years to understand what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
+\noindent For our second set of analyses, we examined only the responses of researchers who reported attempting a reproduction in the past two years to understand what motivated reproduction attempts, how successful those attempts were, and what factors hindered success.
 
-\textit{Motivations:} To assess what motivated researchers to attempt reproductions, two of the authors independently assigned participants text-based response to groups with the following motivations - i) verification/check of published research, ii) an internal check of their own research to verify their work and/or increase the transparency of their work, iii) replication of a study with new data, and iv) a desire to learn from past work, or use the reproduction in teaching.
+\textit{Motivations:} To assess what motivated researchers to attempt reproductions, two of the authors independently assigned participants text-based response to groups with the following motivations: i) verify/check published research, ii) learn from published research for extension or teaching, iii) internally check their own research to verify their work and/or increase the transparency of their work, and iv) replicate a study with new data.
 We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
-We selected groups i) and iv) for further analysis of reproduction attempts, as these motivations most closely matched our definition of reproduction.
+We selected groups i) and ii) for further analysis of reproduction attempts, as these motivations most closely matched our definition of reproduction.
 
 \textit{Success and Barriers:} To analyze participant success, we create statistical summaries for a series of questions that asked researcher to identify whether they were able to partially or completely recreate some or all results of the target study.
-We similarly analyzed barriers to the reproduction of results by creating statistical summaries of participants ability to access key study artifacts (e.g., data, procedural information, code).
-
-Given the topical and epistemological variation that exists among geographic researchers, we again used cross-tabulation to examine differences in response by disciplinary subfield and methodological approach.
-However, the size of our sub-sample for this analysis limited number of cross-tabulations we could pursue.
+We similarly analyzed barriers to the reproduction of results by creating statistical summaries of participants' ability to access key study artifacts (e.g., data, procedural information, code).
 
@@
 The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
+Another \textit{n}=40 authors started the survey, but did not complete enough of the survey to be included in the analysis.
+
 Respondents were predominantly male (65.1\%) and between the ages of 35 and 55 (62.4\%). 
-The majority of respondents were academics, and they were balanced across career levels from graduate students to full professors as no one career level made up more that 30 percent of the sample.
-Respondents were balanced across the disciplinary subfields--- physical geography (29.8\%), geographic methods and GIScience (28.0\%), nature and society (10.1\%), and human geography (30.7\%); and methodological approaches---quantitative (42.2\%), mixed methods (39.0\%), and qualitative (18.3\%).
+The majority of respondents were academics, and they were balanced across career levels from graduate students to full professors with no one career level comprising more that 30 percent of the sample.
+Respondents identified with each of the four major disciplinary subfields---physical geography (29.8\%), geographic methods and GIScience (28.0\%), nature and society (10.1\%), and human geography (30.7\%); and three major methodological approaches---quantitative (42.2\%), mixed methods (39.0\%), and qualitative (18.3\%).
 
@@
 Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%). 
-Strikingly, only a small majority of respondents believe reproducibility is compatible with epistemologies used in the discipline (58.2\%).
+Strikingly, only a small majority of respondents believe reproducibility is compatible with epistemologies used in their disciplinary subfields (58.2\%).
 
@@
 Geographic researchers provided definitions of reproducibility that explicitly included an average of 1.83 of the four characteristics from the definition adopted by the NASEM.
-This level of inclusion was consistent across subfields and methodological approaches.
 The availability and use of the same research procedures (80.7\%) and results (74.0\%) were the characteristics of reproducibility most frequently identified by researchers. 
 Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
-This pattern was consistent across subfields and approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and methods focused researchers.
+The pattern of similarity to the NASEM definition and each of its components was consistent across subfields and methodological approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and methods-focused researchers.
 The lower inclusion of data and context in definitions may be explained by researchers conceptualizing reproducibility as the formal NASEM definition of replicability, which emphasizes the testing of similar questions and procedures in new contexts with new data.
-For example, one respondent defines reproducibility as, "The extent to which the research design can be replicated in different geographical contexts."
+For example, one respondent defines reproducibility as, ``the extent to which the research design can be replicated in different geographical contexts."
 We observed this alternative definition of reproducibility in 20.4\% of respondents' definitions.
@@
 Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies through comparison of original results to results from an attempted reproduction.
-These ranged from rigid bitwise quantitative interpretations, as in the "ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which "other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results".
-Responses included definitions with a focus on experimental science, as in "an ability to produce consistent results when an experiment is repeated!"
+These ranged from rigid bitwise quantitative interpretations, as in the ``ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which ``other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results."
+Responses included definitions with a focus on experimental science, as in ``an ability to produce consistent results when an experiment is repeated!"
 
 Nearly all other researchers (40.9\%) tied reproducibility to the need for transparency in research so that others could independently expand upon past studies.
-For example a quantitative geographers stated: "The methods should provide sufficient information to be able to reproduce the results.
+For example a quantitative geographer stated: ``The methods should provide sufficient information to be able to reproduce the results.
 In quantitative science this should, at minimum, provide all the equations and algorithms used for any calculation.
-In the interest of increasing transparency in science, the practice of sharing the code should be encouraged.
-For others, open science did not necessarily need to result in identical results: "As a qualitative researcher doing in-depth case study research, my studies can not be perfectly reproduced.
+In the interest of increasing transparency in science, the practice of sharing the code should be encouraged."
+For others, open science did not necessarily need to result in identical results, reflected in this definition: ``As a qualitative researcher doing in-depth case study research, my studies can not be perfectly reproduced.
 But reproducibility sits in the openness about methods and data collection practices, as well as critical reflection about strengths and weaknesses of my research.
 When we write about those things in the methods section in our papers and theses, their reproducibility is increased."
-The remainder of responses (6.6\%) emphasized repeatable and/or reliable data observation over all other dimensions of reproducibility.
-For example, "As a historical geographer, working with qualitative research methods, I understand reproducibility more in terms of sources than of methods.
+
+The remainder of responses (6.6\%) emphasized repeatable or reliable data observation over all other dimensions of reproducibility.
+For example, ``As a historical geographer, working with qualitative research methods, I understand reproducibility more in terms of sources than of methods.
 I see reproducible research as being that which makes clear the origin and location of its data."
-A physical geographer similarly emphasized data observations: "Data/observations of some variable can be recovered repeatedly by different observers/methods"
+A physical geographer similarly emphasized data observations: ``Data/observations of some variable can be recovered repeatedly by different observers/methods."
 
 Responses to related Likert questions from the full survey sample (\textit{n}=218) support the results from the subsample of 181 qualitative definitions analyzed above.
-Identification of reproducibility with both of these functions was supported by responses to related questions from our entire sample (\textit{n}=218). 
 A majority of researchers identified reproducibility as important for validating (75.2\%) and establishing the credibility (72.5\%) of research.  
-Respondents also saw reproducing studies as important to reducing the presence of persistent errors in the discipline (77.5\%) and to increasing trust in research findings (78.45\%).
+Respondents also saw reproducing studies as important to reducing the presence of persistent errors in the discipline (77.5\%) and to increasing trust in research findings (78.5\%).
 In parallel with the need for openness and transparency in science, most respondents agreed with the importance of reproducibility for research efficiency (63.3\%), communication with academics (68.8\%) and practitioners (64.7\%), and training students (75.7\%).
@@
 
+The data from our sample of researchers has shown broad recognition of reproducibility and its importance in geography with three caveats---confusion between reproducibility and replicability, different perspectives from researchers using qualitative methods, and caution about judging the trustworthiness or validity published research based on its reproducibility.
+In this context, are individual researchers aware of the research practices needed to enhance reproducibility, and have these practices already been adopted for use in research?
+
 %%%%%%%%%%%
@@
 More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\%).
-However, while familiar with these practices, a far smaller number of researchers reported using these practices regularly in their own work. 
+However, a far smaller number of researchers reported using these ``familiar" practices regularly in their own work. 
 Less than half of the researchers surveyed reported sharing their data (44.5\%), using open source software (38.1\%), using field or lab notebooks to record their work (40.0\%), or sharing their code (18.8\%) most or all of the time.
@@
 
-Researcher familiarity and use of reproducible research practices also varied by disciplinary subfield and methodological approach. 
+Researcher familiarity and use of reproducible research practices varied by disciplinary subfield and methodological approach. 
 Researchers that identified as physical geographers or methodologists and GIScientists reported being familiar with one to two more reproducible researcher practices than human geographers and those focused on nature and society.
@@
 A minority of geographic researchers (28.4\%) believe that the fabrication of data, the manipulation of research results, and similar forms of fraud are a cause of irreproducibility in the discipline.
-These percentage is roughly aligned with values reported elsewhere in the reproducibility literature \citep{fanelli2009many, baker20161}.
+This percentage is consistent with large surveys and meta-analyses of research on scientific fraud across other scientific disciplines \citep{fanelli2009many, baker20161}.
 
@@
 A higher percentage physical and methods-focused researchers identified all five of the artifacts we investigated as common barriers to reproducibility as compared to human and nature-society researchers.
-A similar gap existed between qualitative researchers and those identifying as mixed-methods researchers or quantitative researchers. 
 The largest differences between these groups existed in researchers beliefs about how often the availability of research protocols/code and the use of restricted data or software impacted reproducibility.
-More than three-quarters of physical (77.0\%) and methods-focused (86.9\%) geographers identified the availability of protocols/code as contributing to irreproducibility, whereas less than two-thirds of human (59.7\%) and nature-society (50.0\%) identified this same factor.
+More than three-quarters of physical (77.0\%) and methods-focused (86.9\%) geographers identified the availability of protocols/code as contributing to irreproducibile results, whereas less than two-thirds of human (59.7\%) and nature-society (50.0\%) identified this same factor.
 Only a large percentage of methods-focused researchers (82.0\%) identified the use of restricted data/software as a common contributor to irreproducibility in the discipline.
-A similar gap existed between qualitative researchers, a minority of which identified code availability or the use of restricted data/software as contributing to irreproducibility, and quantitative and mixed-methods researchers, the majority of which saw these factors as frequent causes of irreproducibility.
+Intuitively, a similar gap existed between qualitative researchers and mixed-methods or quantitative researchers with regards to identifying code availability or the use of restricted dara/software as contributing to irreproducibility.
 
@@
 Minor variations in the emphasis placed on these factors exist across subfields and approaches. 
-A higher percentage of nature-society (81.8\%) and physical (80.0\%) researchers emphasized the important role the spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researchers across subfields and approaches.
+A higher percentage of nature-society (81.8\%) and physical (80.0\%) researchers emphasized the important role that spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researchers across subfields and approaches.
 A smaller percentage of physical geographers placed emphasis on the impact of researcher positionality may have on reproducibility (50.8\%) when compared to all other subfields.  
 Differences between the computational environment used to conduct an original study and a reproduction attempt was generally not seen as a factor contributing to a lack of reproducibility in the discipline.
-The exception being methods-focused (68.9\%) and quantitative researchers (63.1\%\%), which aligns with the research practices used in these areas of research.
+Of all subgroups, only a majority of methods-focused (68.9\%) and quantitative researchers (63.1\%) were concerned with computational environments, reflecting research practices used in their areas of research.
 
@@
 A total of 102 of the researchers that responded to our survey (46.8\%) reported attempting a reproduction study during the past two years.
-However, 23 of those reported reproduction attempts were of the researcher's own work, while another 13 were in fact replications of prior work in new locations.
-In the end, only \textit{$n_{a}$}=32 (14.7\%) of all respondents reported attempting to reproduce a study originally conducted by another researcher during the past two years.
+However, 23 of those researchers were reproducing their own research results, while another 13 were replicating prior studies in new locations.
+In the end, only \textit{n}=32 (14.7\%) of all respondents reported attempting to reproduce a study originally conducted by another researcher during the past two years.
 
 This subset of 32 participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions of the work of others.
-Reproduction attempts were predominantly made by geographic researchers that self-identified as working in physical geography (43.8\%) and geographic methods (37.5\%).
+Reproduction attempts were predominantly made by geographic researchers that self-identified with the physical geography (43.8\%) or geographic methods (37.5\%) subfields.
 Respondents attempting reproductions were also focused on quantitative (68.8\%) and mixed-methods (41.2\%) approaches. 
@@
 The majority of researchers (87.5\%) were able to access some of the data used in the original study, but few researchers (12.5\%) reported access to all of the original data.
-Researchers also reported the ability to access at least some information about study procedures (68.8\%) and its computational environment (59.4\%), but limited ability to access all procedural (9.4\%) and computational information (12.5\%).
+Researchers also reported the ability to access at least some information about the study procedures (68.8\%) and computational environment (59.4\%), but limited ability to access all procedural (9.4\%) and computational environment information (12.5\%).
+
+Reproduction attempts may produce results for comparison to \textit{some} or \textit{all} of the results in a prior study.
+A reproduction may be \textit{identical} by finding the exact same results, or may be \textit{partial} by finding slightly different results that still support the same conclusions.
 Nearly all researchers reported at least partially reproducing some results (81.3\%), but only seven (21.9\%) reported being able to at least partially reproduce all results.
-For the purposes of this survey, ``Partially reproduce'' was defined as producing slightly different results as the prior study, but with the same overall conclusions.
 Only three researchers (9.4\%) were able to identically reproduce all results.
@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\section*{Discussion and Conclusion}
-
-%%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Discussion}
-Overall, the results of our survey indicate that geographic researchers are aware of reproducibility and reproducible research practices, but have yet to incorporate many of those practices into their own work.
+\section*{Discussion and Limitations}
+Our survey results indicate that geographic researchers are aware of reproducibility and reproducible research practices, but have yet to incorporate many of those practices into their own work. 
 We found that few researchers attempt to independently reproduce the work of others, or to publish the reproduction attempts they do undertake.
-In alignment with the broader reproducibility literature, geographic researchers identify the lack methodological transparency and the unavailability of data and procedural information, particularly code, as key barriers to reproducibility in the discipline.
+In alignment with the broader reproducibility literature, geographic researchers identify the lack methodological transparency and the unavailability of data and procedural information---particularly code---as key barriers to reproducibility in the discipline.
 Our results also suggest the existence of an incentive problem within the discipline, as pressure to publish original research and a lack of oversight create the opportunity to publish irreproducibile work and limited reward for attempting and publishing reproduction studies.
-These findings empirically confirm prior speculations about the reproducibility of geographic research --- on the whole geographers have yet to make reproducible research practices and reproduction attempts a regular part of disciplinary practice.
+These findings empirically confirm prior speculations about the reproducibility of geographic research---on the whole, geographers have yet to make reproducible research practices and reproduction attempts a regular part of disciplinary practice.
 
@@
 While researchers share beliefs about the epistemological functions of independent reproductions, they provide definitions that contained different requirements for similarity across studies in terms of data, procedures, results, and context.
-Moreover, a subset of researchers define reproducibility as what the \citet{NASEM2019} defines as replicability - the ability to obtain consistent results across studies designed to answer the same question, each of which has obtained its own data.
+Moreover, a subset of researchers define reproducibility as what the \citet{NASEM2019} defines as replicability---the ability to obtain consistent results across studies designed to answer the same question, each of which has obtained its own data.
 The interchangeable use of reproducibility and replicability, or the outright reversal of definitions we observed in our sample, has also been documented across the sciences \citep{barba2018terminologies, plesser2018reproducibility}.
@@
 
-More broadly, our observed variation in terminology is important for at least two reasons. 
-First, if researchers lock into an ontological debate about the definition of reproducibility rather than a shared understanding of its potential functions, the community as a whole may hinder a more productive discussion about the epistemological role independent reproductions and open science practices can or should play in the discipline.
-Second, variation in geographic researchers' understanding of reproducibility reflects the discipline's diverse traditions and ways of knowing. 
+More broadly, the observed variation in terminology we observed is important for at least two reasons. 
+First, variation in geographic researchers' understanding of reproducibility reflects the discipline's diverse traditions and ways of knowing. 
 Acknowledging this diversity as a strength of the discipline, productive discussions about reproducibility should consider how reproducible research practice fits into different traditions and what common understanding exists across traditions.
+Second, if researchers lock into an ontological debate about the definition of reproducibility, the community may hinder a more productive discussion about the epistemological role independent reproductions and open science practices can or should play in the discipline.
+
 Our findings point to potentially productive pathways for such a discussion. 
-Even among the subset of respondents most uncertain about the role of reproducibility in geographic research--- qualitative geographers---we observed recognition of the value reproducible research practices bring to the transparency of research, with a particular emphasis on the sharing of methods and procedures.
+Even among the subset of respondents most uncertain about the role of reproducibility in geographic research---qualitative geographers---we observed recognition of the value reproducible research practices bring to the transparency of research, with a particular emphasis on the sharing of methods and procedures.
+Even acknowledging that spatial heterogeneity and the uniqueness of places can complicate how reproduction and replication studies can be used to build geographic knowledge, conversations to address that challenge likely best begins with some common understanding of what role they are meant to play in that process.
 
 Our results suggest that qualitative researchers have a different perspective on the role or reproducibility in geographic research when compared to other subgroups.
-The extent to which we can generalize this perspective is limited by the size of our sample of qualitative researchers (\textit{$n_{ql}$}=40).  
+The extent to which we can generalize this perspective is limited by the size of our sample of qualitative researchers (\textit{n}=40).  
 Nonetheless, the majority of our qualitatively-focused respondents believe reproducibility is incompatible with their epistemological approach.  
@@
 Engaging qualitative researchers and integrating their perspectives and knowledge has the potential address issues in the reproducibility literature.  
-Perhaps one way forward is initiate a conversation that highlights how reproducibility is not an absolute standard or determinant of research quality, but instead a means of clarifying for others what was was done in a study and why conclusions were drawn as they were.
-Even if a researcher believes positionality influences data collection and interpretation, using reproducible research practices may help convey that position and its impact on study results.
+Perhaps one way forward is to initiate a conversation that highlights how reproducibility is not an absolute standard or determinant of research quality, but instead a means of clarifying for others what was was done in a study and why conclusions were drawn as they were.
+Even if a researcher believes positionality influences data collection and interpretation, using reproducible research practices to control all variables of research design \textit{except} researcher positionality may help convey that position and its impact on study results.
 To our knowledge, there is little explicit discussion in the reproducibility literature about how researcher positionality can or should be recorded and conveyed to other researchers. 
 It would also be interesting to know whether certain elements of researcher positions appear stable across researchers and contexts.
-Such work could also move the conversation about reproducibility away from a current focus on exactly recreating numerical results, and back to the practice's deeper function---independently assessing the arguments of another researcher.
+Such work could also move the conversation about reproducibility away from a current focus on exactly recreating numerical results, and back to the practice's deeper function---independently assessing the claims of prior research.
 
@@
 First, meaningful stratification and post-stratification require knowledge of what predicts differences in response.
-Given the currently limited understanding of reproducibility within geography, we can only speculate about the researcher characteristics predictive or different level of familiarity and experience with reproducible research.
-We do not the foundational knowledge needed to identify reliable predictors.   
+Given the currently limited understanding of reproducibility within geography, we can only speculate about the researcher characteristics predictive of different levels of familiarity and experience with reproducible research, e.g.
+subfield, methodological approach, or career position.
+We do not have the foundational knowledge needed to identify reliable predictors.
+Inverting the issue our survey as the first discilpine-wide measurement of these issues contributes to the development of this foundational knowledge to support future studies.
 Second, even if predictors could be selected to be used in stratification or post-stratification, they must be measured for the population of geographic researchers.
 We are not aware of any census of geographic researchers that could be used to identify and classify all those working in the field.
-Third, given population wide measures of key predictors, potential respondents would also have to a assigned to specific measures, which can be difficult within geography.
-For example, divisions between subfields and approaches in geography are often unclear and researchers often identify in with multiple subfields and approaches. 
-Without this knowledge and data, we have no way of knowing if an adjustment to our sample is likely to increase or decrease bias in our results.
+Third, given population-wide measures of key predictors, it would be necessary to have measures of those predictors for potential respondents, which can be difficult within geography.
+For example, divisions between subfields and approaches in geography are often unclear and researchers often identify with multiple subfields and approaches.
 
-Being unable to meaningfully differentiate subgroups for either stratification or post-stratification, we adopted a simple random sampling scheme and provide our data to facilitate transparency and reanalysis of our sample.
-Considering these challenges, our results could be viewed as an exploratory analysis that identifies researcher characteristics that might differentiate subgroups with similar understandings of reproducibility, which could be used to stratify or post-stratify future reproducibility related research in geography.
-Nonetheless, because we were unable to assess the representativeness of our sample our results may be subject to at least three forms of bias.
+Given the limitations to stratifying or balancing a survey on reproducibility in geography, our study should be viewed as an exploratory analysis with random sampling and a transparent, reproducible methodology for sample frame construction.
 
-\textit{Exclusion Bias:} One limitation of our approach is that geographic researchers publish in a range of journals that are not necessarily indexed as geography by the Web of Science. 
-Geographic researchers that have only published outside these indexed journals would not be captured in our sampling frame creating non-coverage errors in our sample. 
-However, we believe the number of individuals falling into this category will be small as most active geographic researchers are likely to publish at least one study in one of the X geography journals used in our sampling frame over a 5-year period.
-
-\textit{Self-selection Bias}.
-A related concern is that it may be the case that geographic researchers more familiar with reproducible research practices, or those working in subfields more involved with the current reproduciblity debate (e.g., quantitative, computational research) were more likely to respond to our survey.
-Conversely, it may also be the case that researchers working in subfields traditionally associated with critiques of a positivist scientific approach (e.g., qualitative, human geography) were less likely to participate in our survey.
-While self-selection bias may shape our data, we believe its presence is a limited concern because it is likely to only amplify some of our key findings. 
-Namely, that reproducible research practices have yet to be widely adopted in the field and that relatively few geographers are attempting and sharing independent reproduction studies.
-Nonetheless, we believe concerns about self-selection should motivate a closer examination of reproducibility within the subfields and approaches for which we obtained the smallest samples --- qualitative, human geography, and nature society.
-
-\textit{Questionnare Bias:} Another potential limitation of our research is that we based our survey instrument on a review of prior reproducibility surveys and our identification of practices and barriers discussed in the reproducibility literature.
-To the extent that this literature over represents perspectives from selected disciplines, experimental research designs, and computationally-intensive research approaches our survey may reflect this bias.
-If this were the case, our survey may not gather data on practices and barriers important to the reproducibility of types of geographic research not like the work conducted in those disciplines that are well represented in the existing literature.
-To address this concern, we incorporated into our survey instrument questions informed by a parallel review of the reproducibility literature available within geography and a review of critiques of positivist science made by social scientists and human geographers.
-We also provided the option for an open ended text response to questions about reproducible research practices, researcher familiarity with those practices, and barriers to reproducibility in an attempt to identify factor and issues we did not anticipate during instrument construction.
+Absent stratification, we have taken steps to reduce exclusion bias by including in our sampling frame all researchers publishing as corresponding authors in any one of X geography journals over a five year period.
+While we cannot eliminate the possibility of self-selection bias from our survey, we attempted to quantify potential self-selection by examining the characteristics of researchers who started our survey but did not complete the full survey.
+For 29 researchers who reported their subfield but did not complete the full survey, completion rates for all subfields were between 84 and 87 percent, except slightly higher rates for methods / GIScience (96.8\%).
+Considering 31 researchers who reported their method but did not complete the full survey, completion rates were 84.2 percent for mixed methods, 87.0 percent for qualitative methods, and 91.1 percent for quantitative methods.
+These values suggest that self-selection was not a significant issue.
+Finally, we attempted to mitigate the potential for questionnaire bias, which could be caused by partially basing our survey instrument on prior studies that over-represent perspectives from the computational and experimental sciences.
+To address this concern, we incorporated into our survey questions from a parallel review  of the reproducibility literature available within geography and a review of critiques of positivist science made by social scientists and human geographers, and included space for qualitative responses in each survey theme, and pilot tested out instrument with a diverse set of geographers.
 
 %%%%%%%%%%%%%%%%%%%%%%%%
-\subsection*{Conclusion}
+\section*{Conclusion}
 Reproducibility remains an emerging topic in the geographic literature. 
 In this study, we provide the first systematic survey of the use of reproducible research practices across geography's diverse research traditions. 
-Our results make clear that geographic researchers are aware or reproducible research practices, but lack direct experience using those practices.
+Our results make clear that geographic researchers are aware of reproducible research practices, but lack direct experience using those practices.
 Academic incentive systems and the inaccessibility of key components of prior research hinder reproducibility, and a small percentage of researchers are attempting to independently reproduce past work.
+
+Arising from survey results, we see two major opportunities for geographers to contribute to the interdisciplinary challenges and debates surrounding reproducibility.
+Geographers may use the methodological and epistemological diversity in our discipline to pragmatically de-emphasize target fixation on computational reproducibility and refocus debates about reproducibility on practical ways in which attempting to reproduce the findings of prior studies may enhance the accumulation of knowledge and learning across different epistemologies.
+By extension, such a pragmatic debate would naturally extend back to approaches to designing and communicating geographic research to facilitate meaningful reproducibility across methodologies and disciplines and beyond the limited scope of computational reproducibility.
+Across subfields and methods, geographers are aware of the challenges that spatial heterogeneity and uniqueness of place may pose for reproducibility, and thus we are well-positioned to infuse the theory and practice of reproducibility with geographic context.
+Both of these contributions are particularly salient in the context of convergence research addressing the most urgent challenges facing humanity, including global health, climate change, poverty, conflict, and resilience and transformation in rapidly changing environments.
 

### 2023-05-29 docs/manuscript/manuscript.tex

@@
 A total of \textit{n}=218 of the authors we contacted completed the online survey with information sufficient for analysis. 
-The contact rate for the survey was 13.9 percent and the cooperation rate was 77.6 percent, yielding an overall response rate of 10.8 percent. 
-The refusal rate was 3.1 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
+The contact rate for the survey was 13.9 percent and the cooperation rate was 78.7 percent, yielding an overall response rate of 10.9 percent. 
+The refusal rate was 2.9 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
 The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
@@
 Few respondents reported attempting to reproduce the work of other researchers (14.7\%) with fewer still attempting to publish those reproduction studies (6.8\%).
-Strikingly, only a small majority of respondents believe reproducibility is compatible with epistemologies used in their disciplinary subfields (58.2\%).
+
+Strikingly, only 58 percent of respondents believe reproducibility is compatible with the epistemologies used in their disciplinary subfields.
+In total, 28 percent of respondents indicated that reproducibility was incompatible with the epistemologies of their subfields, with an additional 12 percent of respondents indicated that they did not know whether reproducibility was epistomologically compatible.
+About half of the respondents specializing in human geography (49\%) and nature and society (50\%) indicated that reproducibility was incompatible with the epistomologies of their subfields. 
+Respondents conducting primarily qualitative research were similarly skeptical of the epistemological role of reproducibility in their subfields.
+75 percent of qualitative researchers indicated that reproducibility was incompatible with the epistomologies of their subfields.
 
@@
 Geographic researchers were familiar with an average of 3.26 different reproducible research practices, but only reported experience using an average of 1.44 of these practices in their own work.
+Table \ref{tab:familar-use} presents researcher familiarity and use of five different reproducible research practices.
 More than half of all researchers reported familiarity with with data sharing (86.7\%), open source software (85.3\%), field and lab notebooks (67.0\%), and code sharing (59.2\%).
@@
 Only a small subset of researchers reported familiarity with the pre-registration of research designs and protocols (27.5\%), or regular use of this practice (2.7\%).
+
+\begin{center}
+\textbf{Insert Table \ref{tab:familar-use} About Here}
+\end{center}
 
@@
 Differences in researcher familiarity and use of specific reproducible research practices across subfields and approaches was greatest for practices more typical of quantitative workflows. 
-For example, 96.7 percent of quantitative and 89.5 percent of mixed-methods researchers reported familiarity with open source software, while 52.5 percent of qualitative researchers with the same resources.
+For example, 96.7 percent of quantitative and 89.5 percent of mixed-methods researchers reported familiarity with open source software, while 52.5 percent of qualitative researchers reported familiarity with the same resources.
 These differences were greater for code sharing practices. 
@@
     \caption{Barriers to Reproducibility}
-    \begin{tabular}{l c c c c c c c c c c}
+    \begin{tabular}{l c c c c c c c c c c c}
          \hline
-                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & \\
-         Barrier    & PH & MT & NS & HU            & & QN & MX & QL              & & Overall \\
+                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & & \\
+         Barrier                            & PH & MT & NS & HU                   & & QN & MX & QL           & & Overall & Missing \\
          \hline
-         \textit{Research Environment}      & & & & & & & & & & \\
-         Pressure to Publish                & 83.1\% & 75.0\% & 54.5\% & 61.2\% & & 77.3\% & 75.3\% & 47.5\% & & 71.5\% \\
-         Insufficient oversight             & 81.6\% & 82.0\% & 63.6\% & 56.7\% & & 82.6\% & 74.2\% & 40.0\% & & 71.1\% \\
-         Fraud                              & 32.3\% & 39.3\% & 9.1\%  & 22.4\% & & 29.4\% & 31.8\% & 20.0\% & & 28.4\% \\
-                                            & & & & & & & & & &\\
-         \textit{Artifact Availability}     & & & & & & & & & & \\
-         Insufficient metadata              & 76.9\% & 78.7\% & 59.1\% & 62.6\% & & 79.4\% & 72.9\% & 45.0\% & & 80.2\% \\
-         Unavailable Data                   & 89.3\% & 78.6\% & 59.1\% & 65.7\% & & 87.0\% & 81.2\% & 42.5\% & & 75.2\% \\
-         Unavailable protocol/code          & 77.0\% & 86.9\% & 50.0\% & 59.7\% & & 87.0\% & 70.6\% & 37.5\% & & 71.1\% \\
-         Published incomplete results       & 73.8\% & 78.7\% & 63.7\% & 56.7\% & & 78.2\% & 72.9\% & 37.2\% & & 68.4\% \\
-         Use restricted data/software       & 56.9\% & 82.0\% & 40.9\% & 44.8\% & & 70.7\% & 56.5\% & 32.5\% & & 57.8\% \\
-                                            & & & & & & & & & &\\
-         \textit{Study Characteristics}     & & & & & & & & & & \\
-         Geographic variation               & 80.0\% & 72.2\% & 81.8\% & 61.2\% & & 79.4\% & 74.1\% & 40.0\% &  & 71.5\% \\
-         Researcher positionality           & 50.8\% & 70.5\% & 72.8\% & 70.2\% & & 56.5\% & 65.9\% & 80.0\% &  & 64.2\% \\
-         Chance                             & 66.2\% & 65.6\% & 68.2\% & 55.2\% & & 67.4\% & 64.4\% & 52.5\% &  & 62.3\% \\
-         Different computation              & 53.8\% & 68.9\% & 31.8\% & 38.8\% & & 63.1\% & 56.5\% & 25.0\% &  & 50.9\% \\
-                                            & & & & & & & & & &\\
-         N                                  & 65 & 61 & 22 & 67 & & 92 & 85 & 40 & & 218 \\
+         \textit{Open Source Software}      & & & & & & & & & & & \\
+         Familiarity with                   & 90.8\% & 100.0\% & 72.7\% & 71.7\% & & 96.7\% & 89.5\% & 52.5\% & & 85.3\% & 0 \\
+         Use of                             & 47.4\% & 59.0\% & 31.8\% & 13.4\% & & 47.8\% & 41.1\% & 10.0\% & & 36.1\% & 0 \\
+                                            & & & & & & & & & & &\\
+         \textit{Lab and Field Notebooks}   & & & & & & & & & & & \\
+         Familiarity with                   & 90.8\% & 78.0\% & 63.7\% & 35.8\% & & 75.0\% & 71.8\% & 40.0\% & & 67.0\% & 0 \\
+         Use of                             & 63.0\% & 44.2\% & 40.9\% & 14.9\% & & 40.2\% & 39.4\% & 20.0\% & & 40.0\% & 2 \\
+                                            & & & & & & & & & & & \\
+         \textit{Sharing and Archiving Data}     & & & & & & & & & & & \\
+         Familiarity with                   & 95.4\% & 95.4\% & 72.7\% & 71.7\% & & 93.5\% & 92.9\% & 57.5\% & & 86.7\% & 0 \\
+         Use of                             & 63.0\% & 44.2\% & 40.9\% & 20.9\% & & 51.1\% & 51.8\% & 13.0\% & & 44.5\% & 0 \\
+                                            & & & & & & & & & & & \\
+         \textit{Sharing of Code/Scripts}     & & & & & & & & & & & \\
+         Familiarity with                   & 64.6\% & 83.6\% & 45.4\% & 38.8\% & & 71.5\% & 57.7\% & 12.5\% & & 59.2\% & 0 \\
+         Use of                             & 20.0\% & 32.8\% & 4.5\% & 10.5\% & & 22.8\% & 21.1\% & 5.0\% & & 18.8\% & 1 \\
+                                            & & & & & & & & & & & \\
+         \textit{Research Pre-registration}     & & & & & & & & & & & \\
+         Familiarity with                   & 29.2\% & 27.2\% & 29.2\% & 17.9\% & & 28.3\% & 34.2\% & 12.5\% &  & 27.5\% & 0\\
+         Use of                             & 4.6\% & 4.9\% & 0.0\% & 0.0\% & & 1.1\% & 5.9\% & 0.0\% &  & 2.7\% & 0 \\
+                                            & & & & & & & & & & & \\
+         N                                  & 65 & 61 & 22 & 67 & & 92 & 85 & 40 & & 218 & 0 \\
+        \hline
+    \end{tabular}
+    \begin{tablenotes}
+        \footnotesize
+        \item Cells report the percentage of respondents reporting being `somewhat' or `very' familiar with a reproducible research practice, or using those practices `most of the time' of `always'.
+Acronyms indicate: \textit{PH} Physical Geography, \textit{MT} GIScience and Methods, \textit{NS} Nature and Society, \textit{HU} Human Geography; \textit{QN} Quantitative, \textit{MX} Mixed Methods, \textit{QL} Qualitative.
+    \end{tablenotes}
+    \label{tab:familar-use}
+    \end{threeparttable}
+\end{table}
+\end{landscape}
+
+%%%%%%%%%%%%%%%%%%%%%%%%
+\newpage
+\begin{landscape}
+\begin{table}[h]
+    \centering
+    \begin{threeparttable}
+    \caption{Barriers to Reproducibility}
+    \begin{tabular}{l c c c c c c c c c c c}
+         \hline
+                    & \multicolumn{4}{1}{Subfield}  & & \multicolumn{3}{1}{Approach} & & &\\
+         Barrier    & PH & MT & NS & HU            & & QN & MX & QL              & & Overall & Missing\\
+         \hline
+         \textit{Research Environment}      & & & & & & & & & & &\\
+         Pressure to Publish                & 83.1\% & 75.0\% & 54.5\% & 61.2\% & & 77.3\% & 75.3\% & 47.5\% & & 71.5\% & 11 \\
+         Insufficient oversight             & 81.6\% & 82.0\% & 63.6\% & 56.7\% & & 82.6\% & 74.2\% & 40.0\% & & 71.1\% & 13 \\
+         Fraud                              & 32.3\% & 39.3\% & 9.1\%  & 22.4\% & & 29.4\% & 31.8\% & 20.0\% & & 28.4\% & 13 \\
+                                            & & & & & & & & & & &\\
+         \textit{Artifact Availability}     & & & & & & & & & & &\\
+         Insufficient metadata              & 76.9\% & 78.7\% & 59.1\% & 62.6\% & & 79.4\% & 72.9\% & 45.0\% & & 80.2\% & 15\\
+         Unavailable Data                   & 89.3\% & 78.6\% & 59.1\% & 65.7\% & & 87.0\% & 81.2\% & 42.5\% & & 75.2\% & 15 \\
+         Unavailable protocol/code          & 77.0\% & 86.9\% & 50.0\% & 59.7\% & & 87.0\% & 70.6\% & 37.5\% & & 71.1\% & 14 \\
+         Published incomplete results       & 73.8\% & 78.7\% & 63.7\% & 56.7\% & & 78.2\% & 72.9\% & 37.2\% & & 68.4\% & 14 \\
+         Use restricted data/software       & 56.9\% & 82.0\% & 40.9\% & 44.8\% & & 70.7\% & 56.5\% & 32.5\% & & 57.8\% & 19\\
+                                            & & & & & & & & & & &\\
+         \textit{Study Characteristics}     & & & & & & & & & & &\\
+         Geographic variation               & 80.0\% & 72.2\% & 81.8\% & 61.2\% & & 79.4\% & 74.1\% & 40.0\% &  & 71.5\% & 16 \\
+         Researcher positionality           & 50.8\% & 70.5\% & 72.8\% & 70.2\% & & 56.5\% & 65.9\% & 80.0\% &  & 64.2\% & 19\\
+         Chance                             & 66.2\% & 65.6\% & 68.2\% & 55.2\% & & 67.4\% & 64.4\% & 52.5\% &  & 62.3\% & 19 \\
+         Different computation              & 53.8\% & 68.9\% & 31.8\% & 38.8\% & & 63.1\% & 56.5\% & 25.0\% &  & 50.9\% & 18 \\
+                                            & & & & & & & & & & &\\
+         N                                  & 65 & 61 & 22 & 67 & & 92 & 85 & 40 & & 218 & 0 \\
         \hline

### 2023-05-31 docs/manuscript/saved_text.tex

@@
 These surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response.
+
+% Some saved language about survey biases from limitations (from Peter)
+Without this knowledge and data, we have no way of knowing if an adjustment to our sample is likely to increase or decrease bias in our results.
+
+Being unable to meaningfully differentiate subgroups for either stratification or post-stratification, we adopted a simple random sampling scheme and provide our data to facilitate transparency and reanalysis of our sample.
+Considering these challenges, our results could be viewed as an exploratory analysis that identifies researcher characteristics that might differentiate subgroups with similar understandings of reproducibility, which could be used to stratify or post-stratify future reproducibility related research in geography.
+Nonetheless, because we were unable to assess the representativeness of our sample our results may be subject to at least three forms of bias.
+
+\textit{Exclusion Bias:} One limitation of our approach is that geographic researchers publish in a range of journals that are not necessarily indexed as geography by the Web of Science. 
+Geographic researchers that have only published outside these indexed journals would not be captured in our sampling frame creating non-coverage errors in our sample. 
+However, we believe the number of individuals falling into this category will be small as most active geographic researchers are likely to publish at least one study in one of the X geography journals used in our sampling frame over a 5-year period.
+
+\textit{Self-selection Bias}.
+A related concern is that it may be the case that geographic researchers more familiar with reproducible research practices, or those working in subfields more involved with the current reproduciblity debate (e.g., quantitative, computational research) were more likely to respond to our survey.
+Conversely, it may also be the case that researchers working in subfields traditionally associated with critiques of a positivist scientific approach (e.g., qualitative, human geography) were less likely to participate in our survey.
+We attempted to partially quantify this issue by examining the characteristics of the 40 researchers who started our survey but did not complete enough of the survey to be included in the final analysis.
+Taking into account 29 researchers who reported their subfield but did not complete the full survey, completion rates for all subfields were between 84 and 87 percent, except slightly higher rates for methods / GIScience (96.8\%).
+Considering 31 researchers who reported their method but did not complete the full survey, completion rates were 84.2 percent for mixed methods, 87.0 percent for qualitative methods, and 91.1 percent for quantitative methods.
+These values suggest that self-selection was not a significant issue.
+This analysis of course does not measure researchers who elected to never start the survey.
+
+While we cannot definitively eliminate the possibility of self-selection bias from our survey, we believe its presence may be a limited concern because it is likely to only amplify some of our key findings.
+Namely, that reproducible research practices have yet to be widely adopted in the field and that relatively few geographers are attempting and sharing independent reproduction studies.
+Nonetheless, we believe concerns about self-selection should motivate a closer examination of reproducibility within the subfields and approaches for which we obtained the smallest samples --- qualitative, human geography, and nature society.
+
+\textit{Questionnare Bias:} Another potential limitation of our research is that we based our survey instrument on a review of prior reproducibility surveys and our identification of practices and barriers discussed in the reproducibility literature.
+To the extent that this literature over represents perspectives from selected disciplines, experimental research designs, and computationally-intensive research approaches our survey may reflect this bias.
+If this were the case, our survey may not gather data on practices and barriers important to the reproducibility of types of geographic research not like the work conducted in those disciplines that are well represented in the existing literature.
+To address this concern, we incorporated into our survey instrument questions informed by a parallel review of the reproducibility literature available within geography and a review of critiques of positivist science made by social scientists and human geographers.
+We also provided the option for an open ended text response to questions about reproducible research practices, researcher familiarity with those practices, and barriers to reproducibility in an attempt to identify factor and issues we did not anticipate during instrument construction.

### 2023-05-31 docs/manuscript/manuscript.tex
Updates from Overleaf

@@
 \usepackage{natbib}
+%\bibliographystyle{natbib}
 \bibliographystyle{chicago}
@@
 \begin{abstract}
-While the number of reproduction and replication studies undertaken in the social and behavioral sciences continues to rise, such studies have not yet become commonplace in geography. 
+The number of reproduction and replication studies undertaken across the sciences continues to rise, however such studies have not yet become commonplace in geography. 
 Existing attempts to reproduce geographic research suggest that many studies cannot be fully reproduced, or are simply missing components needed to attempt a reproduction. 
 Despite this suggestive evidence, we have not yet systematically assessed geographers' perceptions of reproducibility or the use of reproducible research practices across the discipline's diverse research traditions; nor have we identified the factors that keep geographers from conducting more reproduction studies.
-We address each of these questions by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
-Our results identify a clear division in perception of reproducibility among geographic sub-fields. 
+We address each of these needs by surveying active geographic researchers selected using probability sampling techniques from a rigorously constructed sampling frame.
+We identify a clear division in perceptions of reproducibility among geographic subfields. 
 We also find varying levels of familiarity with reproducible research practices and a perceived lack of incentives to attempt and publish reproduction studies. 
 Despite many barriers to reproducibility and divisions between subfields, we also find common foundations for examining and expanding reproducibility in the field.
-These include interest in publishing transparent and reproducible methods, and in reproducing other researchers' studies for a variety of motivations including learning, checking the validity of a prior study, or extending the prior study.
+These include interest in publishing transparent and reproducible methods, and in reproducing other researchers' studies for a variety of motivations including learning, assessing the internal validity of a study, or extending prior work.
 
@@
 \section*{Introduction}
-Reproducible research publicly discloses the evidence used to support claims made in prior work, facilitates the independent verification of those claims, and the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009}.
+Reproducible research publicly discloses the evidence used to support claims made in prior work, facilitates the independent verification of those claims, and enables the extension of that work by the broader research community \citep{earp2015, nosek2012scientific, Schmidt2009}.
 While reproducibility is not a guarantee of scientific or practical usefulness, it does provide a strong basis for the collective evaluation of ideas.
-Nonetheless, systematic reviews \citep{moraila2014measuring, iqbal2016reproducible} of published research papers reveal a lack of data and code for reproducibility  and attempts to reproduce published research papers \citep{raghupathi2022reproducibility, chang2015economics} frequently fail.
+Nonetheless, systematic reviews of published research papers reveal a lack reproducibility \citep{moraila2014measuring, iqbal2016reproducible}; and furthermore, attempts to reproduce published research papers frequently fail \citep{raghupathi2022reproducibility, chang2015economics}.
 Previous studies consistently link the irreproducibility of research to inadequate record keeping, opaque reporting, the inaccessibility of research components, and a lack of incentives to share research details or to attempt reproduction studies \citep{ranstam2000fraud, anderson2007normative, NASEM2019}.
 Surveys of researchers find that few researchers are attempting to independently reproduce the work of others \citep{baker20161, boulbes2018survey}.
-At the same time, a sizable portion of researchers admit engaging in questionable research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
+At the same time, a sizable portion of survey respondents report knowing of instances in which researchers engaged in questionable or biased research practices tied to the publication of false positive results and low reproducibility rates \citep{fanelli2009many, fraser2018questionable}.
 
 Despite these concerns, the available literature currently provides insufficient evidence to conclusively evaluate the reproducibility of research generally, or disciplinary research specifically.
-This knowledge gap exists because researchers conducting reproducibility assessments, surveys of researcher practices, and reproduction attempts have not defined clear target populations for inference, or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
-Attempts to reproduce past results typically focus on recreating the results of one or a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}.
-Attempts to catalog or survey reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}, or have drawn samples of researchers from specific journals, members of professional associations, or conference attendees \citep{baker20161}.
-These samples are convenient, but are not guaranteed to be representative of researchers and research activity in a particular field. 
+This knowledge gap exists because researchers conducting reproducibility assessments and surveys of researcher practices have not defined clear target populations for inference, or used probability sampling techniques structured by well-defined sampling frames that support generalization \citep{NASEM2019}.
+Attempts to reproduce published studies typically focus on recreating the results of a small number of studies selected based on topical interest or researcher familiarity \citep{camerer2016evaluating, camerer2018evaluating, open2015estimating}.
+Attempts to catalog reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}.
+Surveys of researchers have drawn samples from authors in specific journals, members of professional associations, or conference attendees \citep{baker20161}.
+All of these sampling frames are convenient, but are not guaranteed to be representative of researchers and research activity in a particular field. 
 Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use.
-Finally, both reproduction attempts and reproducibility surveys have focused on evaluating the computational components of past studies such as data and code availability rather than all aspects of research design and execution.
+Finally, reproducibility assessments have focused on evaluating the computational components of past studies, such as data and code availability, rather than all aspects of research design and execution.
 
 Reproducibility surveys and reproduction attempts in the geographic literature face these same challenges. 
-The few available reproducibility surveys in the discipline have relied on convenience samples drawn from specialist conferences and have only focused on computationally intensive forms of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017}.
-The small number of published attempts to reproduction geographic research similarly have focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021,} or on specific topics such as COVID-19 \citep{Holler2023disability, Kedron2022dimaggio, Kedron2023Beyond, paez2022reproducibility}.
+The few available reproducibility surveys in the discipline have relied on convenience samples drawn from specialist conferences and have only focused on computationally-intensive forms of geographic research \citep{balz2020reproducibility, konkol2019, ostermann2017}.
+The small number of published attempts to reproduce geographic research have similarly focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021} or on specific topics such as COVID-19 \citep{Holler2023disability, Kedron2022dimaggio, Kedron2023Beyond, paez2022reproducibility}.
 More recent reproduction attempts by \citet{Kedron2023Beyond} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.
 
-Geographers continue to debate the role of reproduction studies in the discipline \citep{brunsdon2016, goodchild2021Annals, kedron2022replication, kedron2021IJGIS, singleton2016, sui2021, Wainwright2021}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, ostermann2021}, and build the infrastructure needed to support reproducible research \citep{nust2019, wilson2021, yin2019cybergis}.
+Geographers continue to debate the role of reproduction studies in the discipline \citep{brunsdon2016, goodchild2021Annals, kedron2022replication, kedron2021IJGIS, singleton2016, sui2021, Wainwright2021}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, ostermann2021}, and build the infrastructure needed to support reproducible research \citep{nust2019, wilson2021, yin2019cybergis, Kedron_Holler_Bardin_Hilgendorf_2022}.
 And yet, we still have not systematically assessed the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have hindered geographers from adopting reproducible research practices and conducting reproduction studies.
@@
 
-To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, perception of reproducibility in their sub-fields,  familiarity and use of reproducible research practices, and the factors they see as barriers to reproducible research.
-To support generalization, we used a probability sampling scheme designed to capture the breadth of geographic research.
+To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, perception of reproducibility in their subfields, familiarity and use of reproducible research practices, and barriers to reproducibility.
+To support generalization, we design a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.
 In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
 We then present the results of our survey, first focusing on researcher perceptions and use of reproducible research practices, and then analyzing researcher experiences attempting to reproduce prior work.
-Finally, we discuss the implications of our survey results and conclude by presenting a snapshot of geographic researcher perceptions of reproducibility and where the discipline may go from here.
+Finally, we discuss the implications of our survey results and limitation of our work, and conclude by proposing where the geography may go from here and how the discipline may contribute to reproducibility across the sciences.
 
@@
 \section*{Data and Methods}
-Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research Repository (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
-The OSF repository connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development.
+Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research project (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
+The OSF project connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
 All of the results presented in this paper can be independently reproduced using the materials in that repository.
-We encourage interested readers to critically evaluate and build on these materials through their own work.
+We encourage interested readers to critically evaluate and build on these materials.
 Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
@@
 
-First, beginning at the publication level, we identified journals indexed as either geography or physical geography by the \href{https://access.clarivate.com/}{Web of Science's Journal Citation Reports} that also had a 5-year impact factor greater than 1.5.
+First, beginning at the publication level, we identified journals indexed as either geography or physical geography by the Web of Science's Journal Citation Reports that also had a 5-year impact factor greater than 1.5.
 From those journals, we created a database of all articles published between 2017 and 2021.
 
-Second, we used Arizona State University's institutional subscription to the \href{https://www.scopus.com/home.uri}{Scopus Database} to extract journal information (e.g., subject area, ranking), article information (e.g., abstract, citation counts), and author information (e.g., corresponding status, email) for each publication.
-Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = ``Article''} and removed all other publication types (e.g., editorials, book reviews) from our article database.
+Second, we used Arizona State University's institutional subscription to the \citet{Scopus} to extract journal information (e.g., subject area), article information (e.g., citation counts), and author information (e.g., corresponding status) for each publication.
+Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = ``Article''} and removed all other publication types (e.g., editorials) from our article database.
 We also removed articles with missing authorship information.
@@
 Third, we created a list of researchers and their published articles, focusing on corresponding authors for two reasons.
-(1) Corresponding authorship is one indicator of the level of involvement an individual had in a given work. 
+First, corresponding authorship is one indicator of the level of involvement an individual had in a given work. 
 While imperfect, it was the best available indicator in the Scopus database as across journals there is no commonly adopted policy for declarations of author work (e.g., CRediT Statements).
-(2) Scopus maintains email contact information for all corresponding authors, which gave us a means of contacting researchers in our sampling frame.
-Scopus also maintains a unique identifier for each author (author-id) across time, which allowed us to identify authors across publications.
+Second, Scopus maintains email contact information for all corresponding authors, which gave us a means of contacting researchers in our sampling frame.
+Scopus also maintains a unique identifier for each author (\textit{author-id}) across time, which allowed us to identify authors across publications.
 
 Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
-We determined uniqueness by grouping researchers by their author-id, and we determined the most recent contact information by selecting records associated with the most recent year of publication. 
+We determined uniqueness by grouping researchers by their \textit{author-id}, and we determined the most recent contact information by selecting records associated with the most recent year of publication.
 For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.
@@
 Roughly one-third (33.0\%) were most recently a corresponding author for an article published in a general geography journal. 
-A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions had published in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).
+A similar proportion (32.0\%) were most recently a corresponding author for an article published in an earth sciences journal, and smaller proportions published in the social sciences and cultural geography (20.0\% and 16.0\%, respectively).
 
@@
 Remaining questions assessed familiarity and use of reproducible research practices (22 questions), perceptions of the reproducibility of geographic research (2 questions), and beliefs about reproducibility with regards to its significance (17 questions) and barriers (13 questions).
-For researchers who reported attempting reproductions, we asked researcher to elaborate on their motivations and outcomes (9 questions).
+For researchers who reported attempting reproductions, we asked them to elaborate on their motivations and outcomes (9 questions).
 
 We developed the survey questions following a review of prior reproducibility surveys \citep[e.g.,][]{fanelli2009many,baker20161, konkol2019} and our own reading of recurring issues in the reproducibility literature.
-We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, topical focus, and methodological background. 
+We pilot tested the survey instrument with \textit{n}=19 graduate students and geography faculty with differing levels of experience, disciplinary subfields, and methodological background. 
 After pilot testing, we removed these individuals from our sampling frame to ensure they would not be included in our final sample.
@@
 Participation in the survey was entirely voluntary. 
-Each researcher that opted to participate in the survey was provided with IRB approved consent documentation and linked to the internet survey instrument. 
-Participants were also given the option to provide an email address for eligibility for one of three  prizes of 90 US\$, selected randomly after the data collection period.
+Each researcher that opted to participate in the survey was provided with IRB-approved consent documentation and linked to the internet survey instrument. 
+Participants were also given the option to provide an email address for eligibility for one of three  prizes of 90 USD, selected randomly after the data collection period.
 Participating researchers had the option to exit and re-enter the survey and were also able to review and change their answers using a back button as they progressed through the survey.
 At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
-Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium (self-identifying reference removed).
+Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium.
 
@@
 First, we analyzed researcher perspectives on reproducibility by coding and calculating summary variables and statistics for three themes: how geographic researchers define reproducibility, familiarity and experience with reproducible research practices, and perceived barriers to reproducibility.
-Second, we analyzed researchers' experiences with reproducing prior studies, for those who had done so, including their motivations and experience of successes and barriers.
+Second, we analyzed researchers' experiences with reproducing prior studies including their motivations and experience of successes and barriers.
 
@@
 
-Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study: (i) to facilitate the assessment of prior work, (ii) assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
+Second, we coded each definition to one of four motivations for ensuring the reproducibility of a study: (i) to facilitate the assessment of prior work, (ii) to assess experimental research, (iii) to improve transparency and facilitate further extension of work, and (iv) to improve the transparency and consistency of data collection.
 We derived this coding from common themes in the responses and our own reading of the reproducibility literature.
@@
 
-\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in the discipline. 
+\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in their subfield. 
 From those responses, we created a measure of perceived barriers by counting the number of factors a researcher believes `frequently' or `occasionally' contributed to irreproducibility, resulting in a measure with domain [0, 12].
 
-To examine variation in researcher understanding of reproducibility across disciplinary subfields and methodological traditions, we cross tabulated these summary measures and responses to individual questions for these subgroups.
+To examine variation in researcher understanding of reproducibility, we cross tabulated responses to individual questions and these summary measures by disciplinary subfields and methodological traditions.
 We then compared response frequencies across subgroups.
@@
 We identified disagreements in motivation assignments, and the third author again resolved all disputes in consultation with the two assigning authors.
-We selected groups i) and ii) for further analysis of reproduction attempts, as these motivations most closely matched our definition of reproduction.
+We selected groups i) and ii) for further analysis of reproduction attempts, as these motivations most closely matched the NASEM definition of reproducibility.
 
-\textit{Success and Barriers:} To analyze participant success, we create statistical summaries for a series of questions that asked researcher to identify whether they were able to partially or completely recreate some or all results of the target study.
-We similarly analyzed barriers to the reproduction of results by creating statistical summaries of participants' ability to access key study artifacts (e.g., data, procedural information, code).
+\textit{Success and Barriers:} To analyze participant success, we created statistical summaries for a series of questions that asked researchers to identify whether they were able to partially or completely recreate some or all results of the target study.
+We similarly analyzed barriers to the reproduction of results by creating statistical summaries of participants' ability to access key study artifacts (e.g., data, procedural information, and code).
 
@@
 
-Strikingly, only 58 percent of respondents believe reproducibility is compatible with the epistemologies used in their disciplinary subfields.
-In total, 28 percent of respondents indicated that reproducibility was incompatible with the epistemologies of their subfields, with an additional 12 percent of respondents indicated that they did not know whether reproducibility was epistomologically compatible.
+Strikingly, only 58 percent of respondents believe reproducibility is compatible with the epistemologies used in their disciplinary subfield.
+An additional 28 percent of respondents reported that reproducibility was incompatible with the epistemologies of their subfields, and  12 percent of respondents indicated that they did not know whether reproducibility was epistemologically compatible.
 About half of the respondents specializing in human geography (49\%) and nature and society (50\%) indicated that reproducibility was incompatible with the epistomologies of their subfields. 
-Respondents conducting primarily qualitative research were similarly skeptical of the epistemological role of reproducibility in their subfields.
-75 percent of qualitative researchers indicated that reproducibility was incompatible with the epistomologies of their subfields.
+Respondents conducting primarily qualitative research were similarly skeptical of the epistemological role of reproducibility in their subfield.
+75 percent of qualitative researchers indicated that reproducibility was incompatible with the epistemologies of their subfield.
 
@@
 We present the mean and standard deviation for the overall sample and for each subfield and methodological approach.
-In aggregate, the data reveal trends in definition, familiarity, experience, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
+In aggregate, the data reveal consistent trends in definition, familiarity, experience, and barriers of reproducibility between the sub-disciplines and methodological approaches. 
 Respondents that self-identified as specializing in physical geography and geographic methods consistently report higher indicators than those working in nature and society and human geography.
 Similarly, respondents that identified as primarily using quantitative and mixed methods approaches consistently report higher indicators than those using qualitative methods.
-The following sub-sections present detailed results for each of these topics, highlighting the principal sources of difference between sub-disciplines and methodological approaches.
+The following sub-sections present detailed results for each of these topics, highlighting the principal sources of difference between subfields and methodological approaches.
 
@@
 Less than half of respondents explicitly included use of the same data (38.1\%) or the need to work in the same context (17.7\%) in their definitions. 
-The pattern of similarity to the NASEM definition and each of its components was consistent across subfields and methodological approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and methods-focused researchers.
+The pattern of similarity to the NASEM definition and each of its components was consistent across subfields and methodological approaches, with a slightly greater emphasis on data and procedural availability amongst quantitative and geographic methods and GIS researchers.
 The lower inclusion of data and context in definitions may be explained by researchers conceptualizing reproducibility as the formal NASEM definition of replicability, which emphasizes the testing of similar questions and procedures in new contexts with new data.
@@
 Just over half of respondents (52.5\%) defined reproducibility as a means of assessing prior work for errors or inconsistencies through comparison of original results to results from an attempted reproduction.
-These ranged from rigid bitwise quantitative interpretations, as in the ``ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which ``other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results."
+These comparisons ranged from rigid bitwise quantitative interpretations, as in the ``ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which ``other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results."
 Responses included definitions with a focus on experimental science, as in ``an ability to produce consistent results when an experiment is repeated!"
@@
 Qualitative researchers identified reproducibility as playing a much smaller epistemic role compared to the discipline as a whole. 
-A majority of the qualitative researchers responded that reproducibility is incompatible with the epistemologies used in their subfield (75.0\%).
-Accordingly, a small percentage of qualitative researchers agreed that reproducibility is important for validating research (25.0\%) or establishing its credibility (20.0\%).
+A small percentage of qualitative researchers agreed that reproducibility is important for validating research (25.0\%) or establishing its credibility (20.0\%).
 Qualitative geographers similarly placed less emphasis on reproducibility as a means of increasing the accessibility and extensibility of research.
@@
 
-The data from our sample of researchers has shown broad recognition of reproducibility and its importance in geography with three caveats---confusion between reproducibility and replicability, different perspectives from researchers using qualitative methods, and caution about judging the trustworthiness or validity published research based on its reproducibility.
+The data from our sample of researchers has shown broad recognition of reproducibility and its importance in geography with three caveats---confusion between reproducibility and replicability, different perspectives from researchers using qualitative methods, and caution about judging the trustworthiness or validity of published research based on its reproducibility.
 In this context, are individual researchers aware of the research practices needed to enhance reproducibility, and have these practices already been adopted for use in research?
@@
 Researcher familiarity and use of reproducible research practices varied by disciplinary subfield and methodological approach. 
-Researchers that identified as physical geographers or methodologists and GIScientists reported being familiar with one to two more reproducible researcher practices than human geographers and those focused on nature and society.
+Researchers that identified as physical geographers or methodologists and GIScientists reported being familiar with one to two more reproducible research practices than human geographers and those focused on nature and society.
 Researcher practices similarly diverged by subfield, but no subset of researchers reported using on average more than two of these practices regularly in their work.  
-When grouped by methodological approach, quantitative and mixed-methods researchers on average reported familiarity with and use of two more reproducible research practices when compared to qualitative researchers.
+Quantitative and mixed-methods researchers reported familiarity with and use of an average of two more reproducible research practices when compared to qualitative researchers.
 
 Differences in researcher familiarity and use of specific reproducible research practices across subfields and approaches was greatest for practices more typical of quantitative workflows. 
-For example, 96.7 percent of quantitative and 89.5 percent of mixed-methods researchers reported familiarity with open source software, while 52.5 percent of qualitative researchers reported familiarity with the same resources.
-These differences were greater for code sharing practices. 
-Just 12.5 percent of qualitative researchers reported familiarity with code sharing, while 81.5 percent of quantitative and 55.7 percent of mixed-methods researchers reported familiarity with the same practice.
+When compared to qualitative researchers, quantitative and mixed-methods researchers reported greater familiarity with all reproducible research practices.
+For example, just 12.5 percent of qualitative researchers reported familiarity with code sharing, while 81.5 percent of quantitative and 57.7 percent of mixed-methods researchers reported familiarity with the same practice.
 However, even among quantitiative and mixed-methods researchers, familiarity with reproducible research practices did not translate into regular use of those practices.
-Just over half of quantitative (51.2\%) and mixed-methods (51.8\%) researchers reported sharing their data most of the time.
-Less than a third of these same researchers reported sharing their code most of the time. 
-These rates were lower for qualitative geographers, of which only a small subset reported using open source software (10.0\%) or field notes (20.0\%), or sharing data (12.5\%) and code (5.0\%) most of the time.
+Just over half of quantitative and mixed-methods researchers reported regularly sharing their data.
+Less than a quarter of these same researchers reported regularly sharing their code. 
+These rates were lower for qualitative geographers, of which only a small subset reported using open source software or field notes, or sharing data and code most of the time or always.
 
 \subsubsection*{Perceived Barriers to Reproducible Research}
-Aligning with the differences we observed between researcher familiarity with reproducibility enhancing research practices and researcher use of those same practices, respondents to our survey identified an average of 8.20 factors contributing to a lack or reproducible research across the discipline.
-Geographic researchers working in different subfields and with different methodological approaches each identified a similar number of barriers to reproducibility (Table \ref{tab:barriers}).
+Aligning with the differences we observed between researcher familiarity with reproducibility enhancing research practices and researcher use of those same practices, respondents to our survey identified an average of 8.20 factors contributing to a lack or reproducible research.
+Geographic researchers working in different subfields and with different methodological approaches each identified a similar number of barriers to reproducibility, as shown in Table \ref{tab:barriers}.
 Qualitative geographers may be the one group that deviates from this consistent pattern. 
 These researchers identified fewer barriers to reproducibility on average, but with a greater variance that left us unable to distinguish this group from any other.
-To examine differences in researcher beliefs about specific factors potentially hindering reproducibility in the discipline, we divided the 12 factors we examined into three groups---those related to the research environment, the availability of research artifacts, and study-specific characteristics.
+To examine differences in the specific factors researchers believe hinder reproducibility in the discipline, we divided the 12 factors into three groups---those related to the research environment, the availability of research artifacts, and study-specific characteristics.
 
@@
 
-Geographic researchers identified the incentive structure of the researcher environment as an important barrier to reproducibility in the discipline.
-A majority of geographic researchers identified both the pressure to publish original research (71.5\%) and insufficient oversight of the research process (71.1\%) as barriers to reproducibility.
-A high percentage of physical, methods-focused, quantitative, and mixed-methods researchers identified these factors as barriers. 
-Qualitative geographers were least concerned with these factors, but a majority of these researchers still identified both factors as barriers to reproducibility in the field.
+Geographic researchers identified the incentive structure of the researcher environment as an important barrier to reproducibility.
+A majority of geographic researchers identified both the pressure to publish original research (71.5\%) and insufficient oversight of the research process (71.1\%) as barriers.
+A minority of qualitative researchers identified both factors as barriers, but a majority of researchers in all other approaches and subfields identified both factors as barriers to reproducibility.
+Physical, methods-focused, and quantitative researchers identified these factors as barriers in higher numbers. 
 A minority of geographic researchers (28.4\%) believe that the fabrication of data, the manipulation of research results, and similar forms of fraud are a cause of irreproducibility in the discipline.
-This percentage is consistent with large surveys and meta-analyses of research on scientific fraud across other scientific disciplines \citep{fanelli2009many, baker20161}.
+This percentage is consistent with concerning results from large surveys and meta-analyses of research on scientific fraud across other scientific disciplines \citep{fanelli2009many, baker20161}.
 
-Researchers identified the unavailability of research artifacts (e.g., data, code) as a second barrier to reproducibility, but the importance placed on different artifacts varied by subfield and methodological approach.
+Researchers identified the unavailability of research artifacts (e.g., data) as a second barrier to reproducibility, but the importance placed on different artifacts varied by subfield and methodological approach.
 A higher percentage physical and methods-focused researchers identified all five of the artifacts we investigated as common barriers to reproducibility as compared to human and nature-society researchers.
-The largest differences between these groups existed in researchers beliefs about how often the availability of research protocols/code and the use of restricted data or software impacted reproducibility.
-More than three-quarters of physical (77.0\%) and methods-focused (86.9\%) geographers identified the availability of protocols/code as contributing to irreproducibile results, whereas less than two-thirds of human (59.7\%) and nature-society (50.0\%) identified this same factor.
-Only a large percentage of methods-focused researchers (82.0\%) identified the use of restricted data/software as a common contributor to irreproducibility in the discipline.
-Intuitively, a similar gap existed between qualitative researchers and mixed-methods or quantitative researchers with regards to identifying code availability or the use of restricted dara/software as contributing to irreproducibility.
+The largest differences between these groups existed in researchers' beliefs about how often the availability of research protocols/code and the use of restricted data or software impacted reproducibility.
+A similar gap existed between qualitative researchers and mixed-methods or quantitative researchers with regards to identifying code availability or the use of restricted data/software as contributing to irreproducibility.
 
-A majority of researchers identified geographic variation (71.5\%), researcher positionality (64.2\%), and chance (62.3\%) as study-specific factors limiting the reproducibility of geographic research.
+A majority of researchers identified the complexity and variability of a system (71.5\%), researcher positionality (64.2\%), and chance (62.3\%) as study-specific factors limiting the reproducibility of geographic research.
 Minor variations in the emphasis placed on these factors exist across subfields and approaches. 
-A higher percentage of nature-society (81.8\%) and physical (80.0\%) researchers emphasized the important role that spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researchers across subfields and approaches.
-A smaller percentage of physical geographers placed emphasis on the impact of researcher positionality may have on reproducibility (50.8\%) when compared to all other subfields.  
-Differences between the computational environment used to conduct an original study and a reproduction attempt was generally not seen as a factor contributing to a lack of reproducibility in the discipline.
-Of all subgroups, only a majority of methods-focused (68.9\%) and quantitative researchers (63.1\%) were concerned with computational environments, reflecting research practices used in their areas of research.
+A higher percentage of nature-society and physical researchers emphasized the important role that spatial variation and complexity of geographic processes can play when attempting to reproduce geographic research, but this factor was also recognized by researchers across subfields and approaches.
+A smaller percentage of physical geographers placed emphasis on the impact of researcher positionality may have on reproducibility when compared to all other subfields.  
+Differences between the computational environment (computer hardware and software) used to conduct an original study and a reproduction attempt was generally not seen as a factor contributing to a lack of reproducibility in the discipline.
+Of all subgroups, only a majority of methods-focused and quantitative researchers were concerned with computational environments, reflecting research practices used in their areas of research.
 
@@
 A total of 102 of the researchers that responded to our survey (46.8\%) reported attempting a reproduction study during the past two years.
-However, 23 of those researchers were reproducing their own research results, while another 13 were replicating prior studies in new locations.
+However, 23 of those researchers were reproducing their own research results, while another 13 were in fact replicating prior studies in new locations.
 In the end, only \textit{n}=32 (14.7\%) of all respondents reported attempting to reproduce a study originally conducted by another researcher during the past two years.
 
-This subset of 32 participants formed the basis for our second analysis of researcher practices and experiences when attempting reproductions of the work of others.
-Reproduction attempts were predominantly made by geographic researchers that self-identified with the physical geography (43.8\%) or geographic methods (37.5\%) subfields.
+This subset of 32 participants formed the basis for our analysis of researcher practices and experiences when attempting reproductions of the work of others.
+Reproduction attempts were predominantly made by geographic researchers that self-identified with the physical geography (43.8\%) or geographic methods and GIS (37.5\%) subfields.
 Respondents attempting reproductions were also focused on quantitative (68.8\%) and mixed-methods (41.2\%) approaches. 
@@
 That success rate rose to 3 of 4 when researchers reported access to all data. 
-We observed a similar increase in researcher ability to at least partially reproduce all results when researchers reported access to all procedural information. 
+Procedural information and code appears to matter as much as data.
 When researchers had access to some of the procedural information from the original study, they reported being able to at least partially reproduce all results in 6 of 19 instances.
 That success rate rose to 3 of 3 when researchers reported access to all procedural information and all code.
+
 The small number of reproduction study attempts reported in the survey results make it difficult to draw broad conclusions.
-However, the results are internally consistent and intuitively support the importance of available data and procedures for successful reproductions of geographic research.
+However, the results are internally consistent and intuitively support the importance of available data and procedures for the reproducibility of geographic research.
 
@@
 We found that few researchers attempt to independently reproduce the work of others, or to publish the reproduction attempts they do undertake.
-In alignment with the broader reproducibility literature, geographic researchers identify the lack methodological transparency and the unavailability of data and procedural information---particularly code---as key barriers to reproducibility in the discipline.
-Our results also suggest the existence of an incentive problem within the discipline, as pressure to publish original research and a lack of oversight create the opportunity to publish irreproducibile work and limited reward for attempting and publishing reproduction studies.
-These findings empirically confirm prior speculations about the reproducibility of geographic research---on the whole, geographers have yet to make reproducible research practices and reproduction attempts a regular part of disciplinary practice.
+In alignment with the broader reproducibility literature, geographic researchers identify the lack of methodological transparency and the unavailability of data and procedural information as key barriers to reproducibility in the discipline.
+Our results also suggest the need to change the culture of research, publication, and promotion within the discipline, to one that recognizes, values, and rewards attempting and publishing reproduction studies and original researcher that is reproducible.
+On the whole, awareness of reproducible research practices and the infrastructure to attempt reproductions and publish reproducible work exist within the discipline, but geographers have yet to make either a regular part of disciplinary practice.
 
-Our findings also suggest that geographic researchers do not share a single definition of the reproducibility. 
-While researchers share beliefs about the epistemological functions of independent reproductions, they provide definitions that contained different requirements for similarity across studies in terms of data, procedures, results, and context.
+Our findings also suggest that geographic researchers do not share a single definition of reproducibility. 
+While researchers share beliefs about the epistemological functions of independent reproductions, they provide definitions that contain different requirements for similarity across studies in terms of data, procedures, results, and context.
 Moreover, a subset of researchers define reproducibility as what the \citet{NASEM2019} defines as replicability---the ability to obtain consistent results across studies designed to answer the same question, each of which has obtained its own data.
@@
 
-More broadly, the observed variation in terminology we observed is important for at least two reasons. 
+More broadly, the variation in terminology we observed is important for at least two reasons. 
 First, variation in geographic researchers' understanding of reproducibility reflects the discipline's diverse traditions and ways of knowing. 
@@
 Our findings point to potentially productive pathways for such a discussion. 
-Even among the subset of respondents most uncertain about the role of reproducibility in geographic research---qualitative geographers---we observed recognition of the value reproducible research practices bring to the transparency of research, with a particular emphasis on the sharing of methods and procedures.
-Even acknowledging that spatial heterogeneity and the uniqueness of places can complicate how reproduction and replication studies can be used to build geographic knowledge, conversations to address that challenge likely best begins with some common understanding of what role they are meant to play in that process.
+For example, qualitative geographers are subset of respondents that most frequently diverged from other respondents using other approaches and working in other subfields.
+This subset of respondents had much less familiarity and use of reproducible research practices and more frequently disagreed that reproducibility was compatible with their epistemological approach.
+These differences may also explain their lower rates of reporting barriers to reproducibility. 
+However, our qualitative respondents did consistently value particular epistemic functions of reproducibility at higher rates than their disagreement with reproducibility on epistemological grounds suggests.
+This contradiction suggests that qualitative methodologists and reproducibility researcher have yet to meaningfully engage despite sharing some common values.
+One commonly held value that could serve as a platform for such an engagement is the shared belief in the importance of transparency and precise communication in research.
 
-Our results suggest that qualitative researchers have a different perspective on the role or reproducibility in geographic research when compared to other subgroups.
-The extent to which we can generalize this perspective is limited by the size of our sample of qualitative researchers (\textit{n}=40).  
-Nonetheless, the majority of our qualitatively-focused respondents believe reproducibility is incompatible with their epistemological approach.  
-The reproducibility definitions these researchers provided suggest this belief may be rooted in the role researcher positionality plays in the collection and interpretation of qualitative data. 
-Several respondents questioned whether an independent researcher analyzing the same data through their unique interpretive could come to the exact same results. 
-Respondents also focused on what one researcher termed 'transferability', the desire to know that what they have discovered is relevant in other similar contexts.
-
-Engaging qualitative researchers and integrating their perspectives and knowledge has the potential address issues in the reproducibility literature.  
+Qualitative researchers may also have much to contribute to the reproducibility literature owing to their unique perspective and different approach to research.  
+For example, qualitative researchers are more concerned that any other group that research positionality is a barrier to reproducibility, but other groups also recognize the impact researcher position and experience can have on research.
 Perhaps one way forward is to initiate a conversation that highlights how reproducibility is not an absolute standard or determinant of research quality, but instead a means of clarifying for others what was was done in a study and why conclusions were drawn as they were.
-Even if a researcher believes positionality influences data collection and interpretation, using reproducible research practices to control all variables of research design \textit{except} researcher positionality may help convey that position and its impact on study results.
+Even if a researcher believes positionality influences data collection and interpretation, using reproducible research practices to control all variables of research design \textit{except} researcher position may help convey that position and its impact on study results.
 To our knowledge, there is little explicit discussion in the reproducibility literature about how researcher positionality can or should be recorded and conveyed to other researchers. 
 It would also be interesting to know whether certain elements of researcher positions appear stable across researchers and contexts.
-Such work could also move the conversation about reproducibility away from a current focus on exactly recreating numerical results, and back to the practice's deeper function---independently assessing the claims of prior research.
+Such work could also move the conversation about reproducibility away from a current focus on the exact recreation of numerical results, and back to the practice's deeper function---independently assessing the claims of prior research.
 
@@
 To our knowledge, our work is the first systematic attempt to survey geographic researchers about reproducibility. 
-To draw a reliable and generalizable understanding of this issue, we developed a sampling frame using recent publications in indexed journals to gather information from our target population of individuals actively publishing geographic research.
-Ideally, we would stratify this set of potential respondents into subgroups based on common characteristics meaningful to their knowledge of reproducibility and use of reproducibile research practices, and then randomly draw participants from these subgroups to create a balanced and representative sample.
-If our resulting sample was imbalanced across subgroups, we would then use a post-stratification procedure to adjust the non-representative sample using the predictors known to characterize the strata and response.
+To draw a reliable and generalizable understanding of this issue, we systematically developed robust sampling frame representative of all geographic researchers. 
+Ideally, we would stratify this set of potential respondents into meaningful subgroups based their knowledge of reproducibility, and then randomly draw participants from these subgroups. 
+If our resulting sample was imbalanced, we would then use a post-stratification procedure balance the response.
 
-We could not follow this approach for three reasons. 
+We could not follow this approach for two reasons. 
 First, meaningful stratification and post-stratification require knowledge of what predicts differences in response.
@@
 subfield, methodological approach, or career position.
-We do not have the foundational knowledge needed to identify reliable predictors.
-Inverting the issue our survey as the first discilpine-wide measurement of these issues contributes to the development of this foundational knowledge to support future studies.
-Second, even if predictors could be selected to be used in stratification or post-stratification, they must be measured for the population of geographic researchers.
-We are not aware of any census of geographic researchers that could be used to identify and classify all those working in the field.
-Third, given population-wide measures of key predictors, it would be necessary to have measures of those predictors for potential respondents, which can be difficult within geography.
-For example, divisions between subfields and approaches in geography are often unclear and researchers often identify with multiple subfields and approaches.
-
+We do not have the knowledge needed to identify reliable predictors.
+However, our survey lays an initial foundation for examining reproducibility in subsequent studies by providing the first discipline-wide measurement of predicitive researcher characteristics. 
+Second, meaningful stratification and post-stratification require a population wide census of key predictors of reproducibility.
+We are not aware of any census of geographic researchers that contain this data, and believe that conducting such a census would be difficult given the diversity of the field and the fuzzy boundaries between the discipline's subfields.
 Given the limitations to stratifying or balancing a survey on reproducibility in geography, our study should be viewed as an exploratory analysis with random sampling and a transparent, reproducible methodology for sample frame construction.
 
-Absent stratification, we have taken steps to reduce exclusion bias by including in our sampling frame all researchers publishing as corresponding authors in any one of X geography journals over a five year period.
-While we cannot eliminate the possibility of self-selection bias from our survey, we attempted to quantify potential self-selection by examining the characteristics of researchers who started our survey but did not complete the full survey.
-For 29 researchers who reported their subfield but did not complete the full survey, completion rates for all subfields were between 84 and 87 percent, except slightly higher rates for methods / GIScience (96.8\%).
-Considering 31 researchers who reported their method but did not complete the full survey, completion rates were 84.2 percent for mixed methods, 87.0 percent for qualitative methods, and 91.1 percent for quantitative methods.
+Absent stratification, we have taken steps to reduce several forms of potential bias in our survey. 
+We have worked to eliminate exclusion bias by including in our sampling frame all researchers publishing as corresponding authors in any wide range of geography journals over a five year period.
+While we cannot eliminate the possibility of self-selection bias from our survey, we attempted to quantify potential self-selection by calculating and comparing the completion rates across subfields and approaches.
+Completion rates for all subfields were between 84 and 87 percent, except slightly higher rates for geographic methods and GIS researchers (96.8\%).
+Completion rates were 84.2 percent for mixed methods, 87.0 percent for qualitative methods, and 91.1 percent for quantitative methods. 
 These values suggest that self-selection was not a significant issue.
 Finally, we attempted to mitigate the potential for questionnaire bias, which could be caused by partially basing our survey instrument on prior studies that over-represent perspectives from the computational and experimental sciences.
-To address this concern, we incorporated into our survey questions from a parallel review  of the reproducibility literature available within geography and a review of critiques of positivist science made by social scientists and human geographers, and included space for qualitative responses in each survey theme, and pilot tested out instrument with a diverse set of geographers.
+To address this concern, we incorporated into our survey questions from a parallel review of the reproducibility literature available within geography and a review of critiques of positivist science made by social scientists and human geographers.
+We also included space for text-based qualitative responses in each survey theme, and pilot tested out instrument with a diverse set of geographers.
 
@@
 \section*{Conclusion}
-Reproducibility remains an emerging topic in the geographic literature. 
-In this study, we provide the first systematic survey of the use of reproducible research practices across geography's diverse research traditions. 
+In this study, we have provided the first systematic survey of the use of reproducible research practices across geography's diverse research traditions. 
 Our results make clear that geographic researchers are aware of reproducible research practices, but lack direct experience using those practices.
@@
 
-Arising from survey results, we see two major opportunities for geographers to contribute to the interdisciplinary challenges and debates surrounding reproducibility.
-Geographers may use the methodological and epistemological diversity in our discipline to pragmatically de-emphasize target fixation on computational reproducibility and refocus debates about reproducibility on practical ways in which attempting to reproduce the findings of prior studies may enhance the accumulation of knowledge and learning across different epistemologies.
-By extension, such a pragmatic debate would naturally extend back to approaches to designing and communicating geographic research to facilitate meaningful reproducibility across methodologies and disciplines and beyond the limited scope of computational reproducibility.
-Across subfields and methods, geographers are aware of the challenges that spatial heterogeneity and uniqueness of place may pose for reproducibility, and thus we are well-positioned to infuse the theory and practice of reproducibility with geographic context.
-Both of these contributions are particularly salient in the context of convergence research addressing the most urgent challenges facing humanity, including global health, climate change, poverty, conflict, and resilience and transformation in rapidly changing environments.
+Arising from the survey results, we see an opportunity for geographers to contribute to the interdisciplinary challenges and debates surrounding reproducibility.
+There has been a tendency to reduce reproducibility to a matter of sharing computational artifacts (such as data and code), and to codify artifact sharing as the narrowed goal of reproducibility through requirements for publishing, funding, or badging.
+While these practices may allow independent researchers to more easily reproduce and evaluate some aspects of prior studies, they lose sight of the underlying epistemological functions of reproduction studies.
+Our results demonstrate that geographic researchers have a more varied understanding of reproducibility. 
+While the discipline does not agree on the importance of sharing of artifacts for computational reproducibility, there is alignment on the clear, precise, and open communication of research and the use of reproduction studies to evaluate or extend the claims of prior work.
+This shared understanding provides common ground for a discipline-wide debate about the role reproductions can or may play within different epistemologies and subfields, or in the presence of spatial heterogeneity and unique place-based characteristics.
 
-Our work also creates a foundation for the further empirical investigation of reproducibility within geography and across the discipline's many traditions. 
+Our work also creates a foundation for the further empirical investigation of reproducibility within geography and its many disciplinary traditions, and more broadly across the sciences. 
 We have made all the materials used in the development and execution of this research openly available so others can critique and extend our work.
-We urge other researchers to replicate our research, improve our sampling frame and survey instrument, and progressively create a deeper understanding of questions we only begin to address in this work.
+We urge other researchers to reanalyze our data, replicate our study, improve our sampling frame and survey instrument, and progressively create a deeper understanding of questions we only begin to address in this work.
+One immediate path would be use our materials to survey geographic researchers about replicability, as our results show that some researchers appear to see a clearer role for replications over exact reproductions in their subfields, while other conflate reproducibility and replicability.
+Disentangling these concepts and connecting them with the epistemological debates above is particularly salient in the context of convergence research addressing the most urgent challenges facing humanity, including climate change, global inequality and poverty, global health, and political conflict.
 
@@
          \textit{Sharing of Code/Scripts}     & & & & & & & & & & & \\
-         Familiarity with                   & 64.6\% & 83.6\% & 45.4\% & 38.8\% & & 71.5\% & 57.7\% & 12.5\% & & 59.2\% & 0 \\
+         Familiarity with                   & 64.6\% & 83.6\% & 45.4\% & 38.8\% & & 81.5\% & 57.7\% & 12.5\% & & 59.2\% & 0 \\
          Use of                             & 20.0\% & 32.8\% & 4.5\% & 10.5\% & & 22.8\% & 21.1\% & 5.0\% & & 18.8\% & 1 \\
@@
 Email: Peter.Kedron@asu.edu.
-His research interests include spatial analysis, geographic information science, economic geography, and the accumulation of knowledge about geographic phenomena.
+His research program develops and uses spatial analytical methods to understanding persistently uneven patterns of spatial development.
+His recent work focuses on improving the production and accumulation of knowledge used to benefit society through policy.
 \\
 
-\noindent JOSEPH HOLLER is an Assistant Professor of Geography at Middlebury College, Middlebury, VT, 05753, US. Email: \\
+\noindent JOSEPH HOLLER is an Assistant Professor of Geography at Middlebury College.
+He is human geographer and geographic information scientist with research interests in social vulnerability and adaptation in the context of climate change and environmental degradation.
+His research intersects with work in political ecology, development geography, human dimensions of global change, and geographic information science.
+\\
 
-\noindent SARAH BARDIN is a PhD candidate ...
+\noindent SARAH BARDIN is a doctoral student in Geography at the School of Geographical Sciences and Urban Planning at Arizona State University.
+Her research focuses on leveraging spatial modeling and GIS to generate policy-relevant, actionable insights from data.
 

### 2023-06-01 docs/manuscript/manuscript.tex
Fixed bib issues, need doi

@@
 
-\usepackage{doi}
-\usepackage{natbib}
+% \usepackage{doi}
+% \usepackage{natbib}
 %\bibliographystyle{natbib}
-\bibliographystyle{chicago}
-\setcitestyle{authoryear,open={(},close={)}}
-\renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty
+% \bibliographystyle{chicago}
+% \setcitestyle{authoryear,open={(},close={)}}
+% \renewcommand\bibfont{\fontsize{10}{12}\selectfont}% Bibliography support using natbib.sty
 
@@
 }
+
+\usepackage[
+    backend=biber,
+    style=apa,
+    sorting=nyt,
+    autocite=inline,
+    natbib=false,
+    url=false, 
+    doi=true,
+    eprint=false
+    hyperref=auto
+    ]{biblatex}
+
+\addbibresource{references.bib}
+\newcommand{\citep}{\parencite}
 
@@
 The small number of published attempts to reproduce geographic research have similarly focused on the computational reproducibility of conference papers \citep{Nust-AGILE_2018, Nust_AGILE_2020, Nust_AGILE_2021, Nust_AGILE_2022, ostermann2021} or on specific topics such as COVID-19 \citep{Holler2023disability, Kedron2022dimaggio, Kedron2023Beyond, paez2022reproducibility}.
-More recent reproduction attempts by \citet{Kedron2023Beyond} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.
+More recent reproduction attempts by \textcite{Kedron2023Beyond} show that the factors hindering the recreation of results and the evaluation of claims likely extend beyond computation into the conceptualization and design of geographic research.
 
@@
 \section*{Data and Methods}
-Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research project (\citet{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
+Complete documentation of the procedures, survey instrument, and other materials used in this study are available through the Survey of Reproducibility in Geographic Research project (\textcite{Kedron_Holler_Bardin_Hilgendorf_2022} - \url{https://osf.io/5yeq8/}) hosted by the Open Science Framework (OSF).
 The OSF project connects to a GitHub repository which hosts the anonymized dataset and code used to create all results and supplemental materials along with a complete history of their development. 
@@
 We encourage interested readers to critically evaluate and build on these materials.
-Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\citet{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
+Before the start of data collection, we registered a preanalysis plan for the survey with OSF Registries (\textcite{Kedron_Survey_PAP} - \url{https://osf.io/6zjcp}). 
 The survey was conducted under the approval and supervision of the Arizona State Institutional Review Board - \textit{STUDY00014232}.
@@
 
-First, beginning at the publication level, we identified journals indexed as either geography or physical geography by the Web of Science's Journal Citation Reports that also had a 5-year impact factor greater than 1.5.
+First, beginning at the publication level, we identified journals indexed as either geography or physical geography by the Web of Science's Journal Citation Reports \citep{WOS} that also had a 5-year impact factor greater than 1.5.
 From those journals, we created a database of all articles published between 2017 and 2021.
 
-Second, we used Arizona State University's institutional subscription to the \citet{Scopus} to extract journal information (e.g., subject area), article information (e.g., citation counts), and author information (e.g., corresponding status) for each publication.
+Second, we used Arizona State University's institutional subscription to the \textcite{Scopus} to extract journal information (e.g., subject area), article information (e.g., citation counts), and author information (e.g., corresponding status) for each publication.
 Because our intention was to capture individuals actively publishing new geographic research, we retained publications indexed by Scopus as \textit{document type = ``Article''} and removed all other publication types (e.g., editorials) from our article database.
@@
 We asked each participant to assess their familiarity with the term ``reproducibility'' and to provide their own definition. 
-We then provided a definition based on the \citet{NASEM2019} to establish a common understanding of reproducibility for the remainder of the survey.
+We then provided a definition based on the \textcite{NASEM2019} to establish a common understanding of reproducibility for the remainder of the survey.
 Remaining questions assessed familiarity and use of reproducible research practices (22 questions), perceptions of the reproducibility of geographic research (2 questions), and beliefs about reproducibility with regards to its significance (17 questions) and barriers (13 questions).
@@
 
-The online survey was administered through \href{https://www.qualtrics.com/}{Qualtrics}. 
+The online survey was administered through Qualtrics. 
 Participation in the survey was entirely voluntary. 
@@
 We coded participants' qualitative definitions of ``reproducibility'' following two procedures.
-First, we measured the similarity of each provided definition to the definition adopted by the \citet{NASEM2019}. 
+First, we measured the similarity of each provided definition to the definition adopted by the \textcite{NASEM2019}. 
 The NASEM defines reproducible research as having four characteristics --- same data, same procedure, same results, and same conditions.
@@
 The contact rate for the survey was 13.9 percent and the cooperation rate was 78.7 percent, yielding an overall response rate of 10.9 percent. 
-The refusal rate was 2.9 percent\endnote{All outcome rates are reported using \citet{aaporstandards} standards. 
+The refusal rate was 2.9 percent\endnote{All outcome rates are reported using \textcite{aaporstandards} standards. 
 The outcome rates used were - response rate 2, cooperation rate 2, refusal rate 1, and contact rate 1.}.
@@
 While researchers share beliefs about the epistemological functions of independent reproductions, they provide definitions that contain different requirements for similarity across studies in terms of data, procedures, results, and context.
-Moreover, a subset of researchers define reproducibility as what the \citet{NASEM2019} defines as replicability---the ability to obtain consistent results across studies designed to answer the same question, each of which has obtained its own data.
+Moreover, a subset of researchers define reproducibility as what the \textcite{NASEM2019} defines as replicability---the ability to obtain consistent results across studies designed to answer the same question, each of which has obtained its own data.
 The interchangeable use of reproducibility and replicability, or the outright reversal of definitions we observed in our sample, has also been documented across the sciences \citep{barba2018terminologies, plesser2018reproducibility}.
@@
 \newpage
-\bibliography{references}
+%\bibliography{references}
+\printbibliography
 

### 2023-06-02 docs/manuscript/manuscript.tex
proofing edits

@@
 Attempts to catalog reproducible research practices have drawn samples of research papers from archives such as conference paper series, specific journals, or disciplinary repositories \citep{byrne_2017, gundersen2018state, stodden2016enhancing, stodden2018enabling}.
-Surveys of researchers have drawn samples from authors in specific journals, members of professional associations, or conference attendees \citep{baker20161}.
-All of these sampling frames are convenient, but are not guaranteed to be representative of researchers and research activity in a particular field. 
+Surveys of researchers have similarly drawn samples from authors in specific journals, members of professional associations, or conference attendees \citep{baker20161}.
+All of these sampling frames are convenient, but are also unlikely to be representative of researchers and research activity in a particular field. 
 Surveys have also commonly failed to systematically report the methodological details (e.g., response rate) needed to assess and address potential bias in survey response, which further complicates their evaluation and use.
@@
 Geographers continue to debate the role of reproduction studies in the discipline \citep{brunsdon2016, goodchild2021Annals, kedron2022replication, kedron2021IJGIS, singleton2016, sui2021, Wainwright2021}, examine the reproducibility of individual studies \citep{Nust_AGILE_2022, ostermann2021}, and build the infrastructure needed to support reproducible research \citep{nust2019, wilson2021, yin2019cybergis, Kedron_Holler_Bardin_Hilgendorf_2022}.
-And yet, we still have not systematically assessed the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have hindered geographers from adopting reproducible research practices and conducting reproduction studies.
+However, we have yet to systematically assessed the use of reproducible research practices across the discipline's diverse research traditions, or identified the factors that have hindered geographers from adopting reproducible research practices and conducting reproduction studies.
 Without answers to these questions it is unclear what actions geographers should take if they wish to improve the reproducibility of work in the discipline.
@@
 To address this gap in our collective knowledge, we surveyed geographic researchers about their understanding of reproducibility, perception of reproducibility in their subfields, familiarity and use of reproducible research practices, and barriers to reproducibility.
-To support generalization, we design a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.
+To support generalization, we designed a sampling frame to capture researchers from across disciplinary subfields and methodological approaches, and draw survey participants from that frame using a probability sampling scheme.
 In the remainder of this paper, we first present the design of our survey, sampling strategy, and analytical approach. 
 We then present the results of our survey, first focusing on researcher perceptions and use of reproducible research practices, and then analyzing researcher experiences attempting to reproduce prior work.
-Finally, we discuss the implications of our survey results and limitation of our work, and conclude by proposing where the geography may go from here and how the discipline may contribute to reproducibility across the sciences.
+Finally, we discuss the implications of our survey results and limitation of our work, and conclude by proposing where geography may go from here and how the discipline may contribute to reproducibility across the sciences.
 
@@
 
-Fourth, we constructed a sampling frame of unique researchers and their most recent email contact information. 
-We determined uniqueness by grouping researchers by their \textit{author-id}, and we determined the most recent contact information by selecting records associated with the most recent year of publication.
+Fourth, we determined uniqueness by grouping researchers by their \textit{author-id}, and we determined the most recent contact information by selecting records associated with the most recent year of publication.
 For 383 researchers who had two or more distinct emails in the latest year of publication, we removed non-institutional personal email addresses and then selected one of the remaining institutional email address.
@@
 We then provided a definition based on the \textcite{NASEM2019} to establish a common understanding of reproducibility for the remainder of the survey.
+Specifically, we defined reproducibility as, ``whether research results can be recreated by an independent researcher using the same materials, procedures, and conditions of analysis that were used in the original study."
 Remaining questions assessed familiarity and use of reproducible research practices (22 questions), perceptions of the reproducibility of geographic research (2 questions), and beliefs about reproducibility with regards to its significance (17 questions) and barriers (13 questions).
@@
 At the end of the data collection period, responses were checked for completeness and coded using the reporting standards of the American Association For Public Opinion Research \citep{aaporstandards}.
-Responses were downloaded from Qualtrics, anonymized, and stored in a public de-identified database in the research compendium.
+Responses were downloaded from Qualtrics, anonymized, and stored in a public, de-identified database in the research compendium.
 
@@
 
-\textit{Barriers:} Finally, we asked asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in their subfield. 
+\textit{Barriers:} Finally, we asked respondents to identify how frequently they believe 12 different factors contributed to a lack of reproducibility in their subfield. 
 From those responses, we created a measure of perceived barriers by counting the number of factors a researcher believes `frequently' or `occasionally' contributed to irreproducibility, resulting in a measure with domain [0, 12].
@@
 The lower inclusion of data and context in definitions may be explained by researchers conceptualizing reproducibility as the formal NASEM definition of replicability, which emphasizes the testing of similar questions and procedures in new contexts with new data.
-For example, one respondent defines reproducibility as, ``the extent to which the research design can be replicated in different geographical contexts."
+For example, one respondent defined reproducibility as, ``the extent to which the research design can be replicated in different geographical contexts."
 We observed this alternative definition of reproducibility in 20.4\% of respondents' definitions.
@@
 These comparisons ranged from rigid bitwise quantitative interpretations, as in the ``ability to re-generate exactly the results published based on the data and code provided by the authors", to more flexible interpretations in which ``other researchers could use the same or similar methodology without great difficulty and, given similar data, arrive at comparable results."
-Responses included definitions with a focus on experimental science, as in ``an ability to produce consistent results when an experiment is repeated!"
+Responses also included definitions with a focus on experimental science, as in ``an ability to produce consistent results when an experiment is repeated!"
 
@@
 
-The data from our sample of researchers has shown broad recognition of reproducibility and its importance in geography with three caveats---confusion between reproducibility and replicability, different perspectives from researchers using qualitative methods, and caution about judging the trustworthiness or validity of published research based on its reproducibility.
+The data from our sample of researchers shown that there is broad recognition of reproducibility and its importance in geography with three caveats---conflation of reproducibility and replicability, different perspectives from researchers using qualitative methods, and caution about judging the trustworthiness or validity of published research based on success of failure of an attempt to reproduce study.
 In this context, are individual researchers aware of the research practices needed to enhance reproducibility, and have these practices already been adopted for use in research?
@@
 Our results also suggest the need to change the culture of research, publication, and promotion within the discipline, to one that recognizes, values, and rewards attempting and publishing reproduction studies and original researcher that is reproducible.
-On the whole, awareness of reproducible research practices and the infrastructure to attempt reproductions and publish reproducible work exist within the discipline, but geographers have yet to make either a regular part of disciplinary practice.
+On the whole, some awareness of reproducible research practices and the infrastructure to attempt reproductions and publish reproducible work exist within the discipline, but geographers have yet to make either a regular part of disciplinary practice.
 
@@
 
-More broadly, the variation in terminology we observed is important for at least two reasons. 
+The variation in terminology we observed is important for at least two reasons. 
 First, variation in geographic researchers' understanding of reproducibility reflects the discipline's diverse traditions and ways of knowing. 
 Acknowledging this diversity as a strength of the discipline, productive discussions about reproducibility should consider how reproducible research practice fits into different traditions and what common understanding exists across traditions.
-Second, if researchers lock into an ontological debate about the definition of reproducibility, the community may hinder a more productive discussion about the epistemological role independent reproductions and open science practices can or should play in the discipline.
+Second, if researchers lock into an debate about terminology, the community may hinder a more productive discussion about the epistemological role independent reproductions and open science practices can or should play in the discipline.
 
@@
 
-Qualitative researchers may also have much to contribute to the reproducibility literature owing to their unique perspective and different approach to research.  
+Qualitative researchers may also have much to contribute to the reproducibility literature owing to their unique perspective and approach to research.  
 For example, qualitative researchers are more concerned that any other group that research positionality is a barrier to reproducibility, but other groups also recognize the impact researcher position and experience can have on research.
@@
 To our knowledge, our work is the first systematic attempt to survey geographic researchers about reproducibility. 
-To draw a reliable and generalizable understanding of this issue, we systematically developed robust sampling frame representative of all geographic researchers. 
+To draw a reliable and generalizable understanding of this issue, we systematically developed a robust sampling frame representative of the diversity of active geographic researchers. 
 Ideally, we would stratify this set of potential respondents into meaningful subgroups based their knowledge of reproducibility, and then randomly draw participants from these subgroups. 
@@
 First, meaningful stratification and post-stratification require knowledge of what predicts differences in response.
-Given the currently limited understanding of reproducibility within geography, we can only speculate about the researcher characteristics predictive of different levels of familiarity and experience with reproducible research, e.g.
+Given the currently limited understanding of reproducibility within geography, prior to our study we could only speculate about the researcher characteristics predictive of different levels of familiarity and experience with reproducible research, e.g.
 subfield, methodological approach, or career position.
-We do not have the knowledge needed to identify reliable predictors.
-However, our survey lays an initial foundation for examining reproducibility in subsequent studies by providing the first discipline-wide measurement of predicitive researcher characteristics. 
+We did not have the knowledge needed to identify reliable predictors.
+In this respect, our survey lays an initial foundation for examining reproducibility in subsequent studies by providing the first discipline-wide measurement of predicitive researcher characteristics.
 Second, meaningful stratification and post-stratification require a population wide census of key predictors of reproducibility.

### 2023-07-12 docs/presentation/preprocess.Rmd
viz: preprocessing

---
title: "Preprocessing"
output: 
  html_document:
    theme: flatly
    df_print: paged
date: "2023-07-12"
---

Making sense of the survey data.

The file `analysis_hegs_rpr.csv` was saved from `data\derived\public\analysis_hegs_rpr.rds`.

```{r import, message=FALSE, warning=FALSE}
knitr::opts_chunk$set(
  fig.retina = 4,
  fig.showtext = TRUE,
  message = FALSE,
  warning = FALSE
)

# all your themes are belong to us
# library(ggthemes)
library(readr)
library(tidyverse)
library(magrittr)
# library(showtext)
# font_add_google("Fira Sans", "Fira Sans")

analysis <- read_csv("analysis_hegs_rpr.csv", col_select = starts_with("Q"))
```

## Groups

Dropping NAs for brevity

```{r drop na}
analysis %<>%
  drop_na(Q3_recoded, Q4) %>%
  filter(Q3_recoded != "Other")
```

Question 3: primary subfield of research

```{r q3 groups}
analysis %>%
  group_by(Q3_recoded) %>%
  summarise(n = n())
```

Question 4: type of research

```{r q4 groups}
analysis %>%
  group_by(Q4) %>%
  summarise(n = n())
```

```{r q19 groups}
analysis %>%
  group_by(Q19_recoded) %>%
  summarise(n = n())
```

## Word cloud

~~Per group?~~

```{r DRY wordcloud}
column_to_cloud <- function(
    col, threshold,
    my_palette = c(
      "#cdb4db",
      "#6d597a",
      "#b56576",
      "#e56b6f",
      "#eaac8b"
    )) {
  require(tidytext)
  word_counts <- analysis %>%
    drop_na(all_of(col)) %>%
    unnest_tokens("word", col) %>%
    anti_join(stop_words, by = "word") %>%
    count(word) %>%
    filter(n >= threshold)

  require(wordcloud2)
  wordcloud2(
    word_counts,
    color = rep_len(
      my_palette,
      nrow(word_counts)
    )
  ) %>%
    return()
}
```

Question 10: Thinking about the reproduction(s) you attempted in the last 2 years, what made you decide to attempt the reproduction(s)?

Question 6: What is your understanding of the term "reproducibility" in the context of your own research?

Question 12a: If you were not able to submit all of the findings of your reproduction(s) for publication, why not?

Question 15: Please list any other factors that you believe contribute to a lack of reproducibility in research in your subfield.

Question 17a: Please list any benefits or important function of reproducibility in your subfield not mentioned above.

```{r word clouds}
clouds <- list()
clouds$q6 <- column_to_cloud("Q6", 6)
clouds$q10 <- column_to_cloud("Q10", 4)
clouds$q12a <- column_to_cloud("Q12a", 2)
clouds$q15 <- column_to_cloud("Q15", 4)
clouds$q17a <- column_to_cloud("Q17a", 2)
saveRDS(clouds, file = "clouds.rds")
```

### 2023-07-13 docs/presentation/preprocess.Rmd
viz: more word clouds

@@
 # font_add_google("Fira Sans", "Fira Sans")
+```
 
-analysis <- read_csv("analysis_hegs_rpr.csv", col_select = starts_with("Q"))
+```{r data}
+analysis <- read_csv("data/analysis_hegs_rpr.csv", col_select = starts_with("Q"))
 ```
@@
 
+Q19: demographics
+
+Potentially split into professor - not professor
+
 ```{r q19 groups}
@@
 
-~~Per group?~~
+Q6
+Q10
+Q12a
+Q15
+Q17a
+
+Potentially per group, but only for Q6
 
@@
 column_to_cloud <- function(
-    col, threshold,
+    col, nrows = 30,
+    data = analysis,
     my_palette = c(
@@
   require(tidytext)
-  word_counts <- analysis %>%
+  word_counts <- data %>%
     drop_na(all_of(col)) %>%
     unnest_tokens("word", col) %>%
+    # https://bookdown.org/psonkin18/berkshire/tokenize.html#text-normalization---stemming-and-lemmatization
+    # doesn't work - why is `reproduct` different from `reproduc`?
+    # mutate(word = SnowballC::wordStem(word, language = "english")) %>%
     anti_join(stop_words, by = "word") %>%
     count(word) %>%
-    filter(n >= threshold)
+    arrange(desc(n)) %>%
+    slice(1:nrows)
 
@@
 
-Question 10: Thinking about the reproduction(s) you attempted in the last 2 years, what made you decide to attempt the reproduction(s)?
+```{r word clouds}
+cloud_cols <- list("Q6", "Q10", "Q12a", "Q15", "Q17a")
+clouds <- map(cloud_cols, column_to_cloud) %>%
+  set_names(cloud_cols)
+saveRDS(clouds, file = "data/clouds.rds")
+```
 
-Question 6: What is your understanding of the term "reproducibility" in the context of your own research?
+```{r q6 cloud}
+subfields <- list("Human", "Methods", "Nature/society", "Physical")
+types <- list("Quantitative", "Qualitative", "Mixed Methods")
 
-Question 12a: If you were not able to submit all of the findings of your reproduction(s) for publication, why not?
+clouds_q6_q3 <- map(
+  subfields, ~ analysis %>%
+    filter(Q3_recoded == .x) %>%
+    column_to_cloud("Q6", data = .)
+) %>%
+  set_names(subfields)
 
-Question 15: Please list any other factors that you believe contribute to a lack of reproducibility in research in your subfield.
+clouds_q6_q4 <- map(
+  types, ~ analysis %>%
+    filter(Q4 == .x) %>%
+    column_to_cloud("Q6", data = .)
+) %>%
+  set_names(types)
 
-Question 17a: Please list any benefits or important function of reproducibility in your subfield not mentioned above.
+clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
+clouds_q6$Everyone <- clouds$Q6
+saveRDS(clouds_q6, file = "data/clouds_q6.rds")
+```
 
-```{r word clouds}
-clouds <- list()
-clouds$q6 <- column_to_cloud("Q6", 6)
-clouds$q10 <- column_to_cloud("Q10", 4)
-clouds$q12a <- column_to_cloud("Q12a", 2)
-clouds$q15 <- column_to_cloud("Q15", 4)
-clouds$q17a <- column_to_cloud("Q17a", 2)
-saveRDS(clouds, file = "clouds.rds")
-```
+## Likert charts
+Q8
+
+Q9 (maybe)
+
+Q11
+Q12
+
+Q14
+
+Q17
+
+## Density plots
+Include animations?
+
+Q5 (maybe put with Q6's word cloud)
+
+Q7 (many parts)
+
+Q13 (percentages)
+
+## Bar plot
+Or something simple
+Include animations
+
+Q16
+
+## Demographics

### 2023-07-14 docs/presentation/preprocess.Rmd
viz: skip saving rds

@@
   set_names(cloud_cols)
-saveRDS(clouds, file = "data/clouds.rds")
+# saveRDS(clouds, file = "data/clouds.rds")
 ```
@@
 clouds_q6$Everyone <- clouds$Q6
-saveRDS(clouds_q6, file = "data/clouds_q6.rds")
+# saveRDS(clouds_q6, file = "data/clouds_q6.rds")
 ```
+
+## Density plots
+Include animations?
+
+Q5
+
+```{r q5}
+
+```
+
+Q7 (many parts)
+
+Q13 (percentages)
 
@@
 
-## Density plots
-Include animations?
-
-Q5 (maybe put with Q6's word cloud)
-
-Q7 (many parts)
-
-Q13 (percentages)
-
 ## Bar plot

### 2023-07-14 docs/presentation/preprocess.Rmd
viz: density plots

@@
 library(magrittr)
-# library(showtext)
-# font_add_google("Fira Sans", "Fira Sans")
+library(showtext)
+font_add_google("Fira Sans", "Fira Sans")
 ```
@@
 ```{r q5}
+four_levels = list(
+  "To a great extent" = 1,
+  "Somewhat" = 0.66,
+  "Very little" = 0.33,
+  "Not at all" = 0
+)
 
+analysis %>%
+  mutate(Q5_num = as.numeric(four_levels[Q5])) %>%
+  ggplot() +
+  scale_x_continuous(
+    breaks = as.numeric(four_levels),
+    labels = str_wrap(names(four_levels), width = 9)
+  ) +
+  geom_density(aes(x = Q5_num), adjust = 1.6) +
+  theme_minimal() +
+  theme(
+    text = element_text(family = "Fira Sans", size = 16),
+    axis.text.y = element_blank(),
+    axis.ticks = element_blank()
+  ) +
+  labs(
+    title = "How familiar are you with the term \"reproducibility\"?",
+    subtitle = "In the context of conducting research",
+    x = "", y = ""
+  )
 ```

### 2023-07-14 docs/presentation/preprocess.Rmd
viz: refactor constants

--- 2023-07-14 docs/presentation/preprocess.Rmd
@@
 analysis <- read_csv("data/analysis_hegs_rpr.csv", col_select = starts_with("Q"))
+source("data/constants.R")
 ```
@@
 ```{r word clouds}
-cloud_cols <- list("Q6", "Q10", "Q12a", "Q15", "Q17a")
 clouds <- map(cloud_cols, column_to_cloud) %>%
@@
 ```{r q6 cloud}
-subfields <- list("Human", "Methods", "Nature/society", "Physical")
-types <- list("Quantitative", "Qualitative", "Mixed Methods")
-
 clouds_q6_q3 <- map(
@@
 ```{r q5}
-
+analysis %>%
+  mutate(Q5_num = as.numeric(four_levels[Q5])) %>%
+  ggplot() +
+  scale_x_continuous(
+    breaks = as.numeric(four_levels),
+    labels = str_wrap(names(four_levels), width = 9)
+  ) +
+  geom_density(aes(x = Q5_num), adjust = 1.6) +
+  theme_minimal() +
+  theme(
+    text = element_text(family = "Fira Sans", size = 16),
+    axis.text.y = element_blank(),
+    axis.ticks = element_blank()
+  ) +
+  labs(
+    title = "How familiar are you with the term \"reproducibility\"?",
+    subtitle = "In the context of conducting research",
+    x = "", y = ""
+  )
 ```

### 2023-07-14 docs/presentation/data/constants.R

@@ -1,0 +1,51 @@
+# Group definitions ####
+library(shiny)
+subfields <- list("Human", "Methods", "Nature/society", "Physical")
+types <- list("Quantitative", "Qualitative", "Mixed Methods")
+geo_groups <- list(
+  "Everyone",
+  "Subfield" = subfields,
+  "Type" = types
+)
+
+# Questions for the word cloud ####
+cloud_cols <- list("Q6", "Q10", "Q12a", "Q15", "Q17a")
+cloud_questions <- list(
+  p(
+    icon("circle-question"), strong("Question 6"), br(),
+    "What is your understanding of the term \"reproducibility\" in the context of your own research?", br(),
+    # icon("circle-info"), strong("Note: "), "Only this question is segmentable."
+  ),
+  p(
+    icon("circle-question"), strong("Question 10"), br(),
+    "Thinking about the reproduction(s) you attempted in the last 2 years, what made you decide to attempt the reproduction(s)?"
+  ),
+  p(
+    icon("circle-question"), strong("Question 12a"), br(),
+    "If you were not able to submit all of the findings of your reproduction(s) for publication, why not?"
+  ),
+  p(
+    icon("circle-question"), strong("Question 15"), br(),
+    "Please list any other factors that you believe contribute to a lack of reproducibility in research in your subfield."
+  ),
+  p(
+    icon("circle-question"), strong("Question 17a"), br(),
+    "Please list any benefits or important function of reproducibility in your subfield not mentioned above."
+  )
+)
+
+# Level mappings for density plot ####
+four_levels <- list(
+  "To a great extent" = 1,
+  "Somewhat" = 0.66,
+  "Very little" = 0.33,
+  "Not at all" = 0
+)
+
+five_levels <- list(
+  "Always" = 1,
+  "Most of the time" = 0.75,
+  "Some of the time" = 0.5,
+  "Rarely" = 0.25,
+  "Never" = 0
+)

### 2023-07-17 docs/presentation/preprocess.Rmd
viz: remove density plots
for discrete data

@@
 ```{r data}
-analysis <- read_csv("data/analysis_hegs_rpr.csv", col_select = starts_with("Q"))
+analysis <- read_csv("data/analysis_hegs_rpr.csv")
 source("data/constants.R")
@@
 
-## Density plots
-Include animations?
+## ~~Density plots~~
 
-Q5
-
-```{r q5}
+```{r q5, eval=FALSE, include=FALSE}
 analysis %>%
@@
   )
+```
+
+## Bar charts
+Include animations?
+
+```{r}
+analysis %>%
+  count(dat_rec)
 ```

### 2023-07-17 docs/presentation/data/constants.R

@@ -33,19 +33,3 @@ cloud_questions <- list(
     "Please list any benefits or important function of reproducibility in your subfield not mentioned above."
   )
 )
-
-# Level mappings for density plot ####
-four_levels <- list(
-  "To a great extent" = 1,
-  "Somewhat" = 0.66,
-  "Very little" = 0.33,
-  "Not at all" = 0
-)
-
-five_levels <- list(
-  "Always" = 1,
-  "Most of the time" = 0.75,
-  "Some of the time" = 0.5,
-  "Rarely" = 0.25,
-  "Never" = 0
-)

### 2023-07-20 procedure/code/aag_fig.R
Code for AAG 2023 Presentation figures

@@ -1,0 +1,606 @@
+# AAG FIGURES FOR PETER
+library(here)
+library(tidyverse)
+library(table1)
+library(officer)
+library(ggthemes)
+library(ggridges)
+library("ggtext")
+library(extrafont)
+download.file("http://simonsoftware.se/other/xkcd.ttf",
+              dest="xkcd.ttf", mode="wb")
+system("mkdir ~/.fonts")
+system("cp xkcd.ttf  ~/.fonts")
+font_import(paths = "~/.fonts", pattern="[X/x]kcd")
+fonts()
+loadfonts()
+
+#--------------------------------#
+#-                              -#
+#- PERFORM DESCRIPTIVE ANALYSIS -#
+#-                              -#
+#--------------------------------#
+analysis_hegs_rpl <- readRDS("/Users/sarahbardin/Desktop/OR-Replicability-in-Geography-Survey/data/derived/public/analysis_hegs_rpl.rds")
+
+#-------------------------------------------------------------------------------#
+#Slide 5 - Individual density plots for could, should, have
+#          for RP and RPL OVERALL ONLY, USE SAME VERTICAL AND HORIZONTAL SCALE
+#-------------------------------------------------------------------------------#
+fill <- "#DCE1E5"
+line <- "#003660"
+summary(analysis_hegs_rpl$Q12_pcnt_have_rep_1)
+#COULD RPL
+could_rpl <- ggplot(analysis_hegs_rpl, aes(x=Q13_pcnt_could_rep_1)) + 
+  geom_density(fill=fill, colour = line, size = 1, na.rm = T, )  +
+  scale_x_continuous(name = "**Could** be replicated (%)",
+                     breaks = seq(0, 100, 25),
+                     limits=c(0, 100),
+                     expand = c(0, 2)) +
+  scale_y_continuous(name = "Density",
+                     breaks = seq(0, 0.025, .005),
+                     limits=c(0, 0.025),
+                     expand = c(0, 0)) +
+  theme(axis.line.x.bottom = element_line(size=1, colour = "black"),
+        axis.line.y = element_blank(),
+        axis.ticks.x = element_blank(),
+        axis.ticks.y = element_blank(),
+        panel.grid.major = element_blank(),
+        panel.grid.minor = element_blank(),
+        panel.border = element_blank(), 
+        panel.background = element_blank(),
+        text=element_text(family="Tahoma"),
[…]

### 2023-07-20 docs/presentation/aag/aag_fig.Rmd
viz: aag figures

---
title: "AAG FIGURES FOR PETER"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: flatly
    df_print: paged

---

```{r message=FALSE}
#
# library(here)
library(plyr)
library(tidyverse)
library(table1)
library(officer)
library(showtext)
library(ggthemes)
library(ggridges)
library(ggtext)
font_add_google("Roboto", "Roboto")
knitr::opts_chunk$set(
  fig.retina = 4,
  fig.showtext = TRUE,
  message = FALSE,
  warning = FALSE
)
```

```{css, echo = FALSE}
@import url('https://fonts.googleapis.com/css2?family=Fira+Code:wght@400;700&family=Roboto:ital,wght@0,400;0,700;1,400;1,700&display=swap');
body {
  font-family: "Roboto", "Helvetica Neue", Helvetica, Arial, sans-serif;
}
code, kbd, pre, samp {
  font-family: "Fira Code", "Source Code Pro", "Consolas", monospace;
}
```

# Replicability
```{r}
analysis_hegs_rpl <- readRDS("analysis_hegs_rpl.rds")
```

## Slide 5 - Individual density plots
For could, should, have
for RP and RPL OVERALL ONLY, USE SAME VERTICAL AND HORIZONTAL SCALE
```{r}
fill <- "#DCE1E5"
line <- "#003660"
summary(analysis_hegs_rpl$Q12_pcnt_have_rep_1)
```
```{r}
# COULD RPL
ggplot(analysis_hegs_rpl, aes(x = Q13_pcnt_could_rep_1)) +
  geom_density(fill = fill, colour = line, size = 1, na.rm = T, ) +
  scale_x_continuous(
    name = "**Could** be replicated (%)",
    breaks = seq(0, 100, 25),
    limits = c(0, 100),
    expand = c(0, 2)
  ) +
  scale_y_continuous(
    name = "Density",
    breaks = seq(0, 0.025, .005),
    limits = c(0, 0.025),
    expand = c(0, 0)
  ) +
  theme(
    axis.line.x.bottom = element_line(size = 1, colour = "black"),
    axis.line.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    text = element_text(family = "Roboto"),
    axis.text.x = element_text(colour = "black", size = 9),
    axis.text.y = element_text(colour = "black", size = 9),
    axis.title.x = ggtext::element_markdown()
  ) +
  geom_vline(xintercept = 55.02, size = 1, colour = "#FF3721", linetype = "dashed")
```

```{r}
# SHOULD RPL
ggplot(analysis_hegs_rpl, aes(x = Q14_pcnt_should_rep_1)) +
  geom_density(fill = fill, colour = line, size = 1, na.rm = T, ) +
  scale_x_continuous(
    name = "**Should** be replicated (%)",
    breaks = seq(0, 100, 25),
    limits = c(0, 100),
    expand = c(0, 2)
  ) +
  scale_y_continuous(
    name = "Density",
    breaks = seq(0, 0.025, .005),
    limits = c(0, 0.025),
    expand = c(0, 0)
  ) +
  theme(
    axis.line.x.bottom = element_line(size = 1, colour = "black"),
    axis.line.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    text = element_text(family = "Roboto"),
    axis.text.x = element_text(colour = "black", size = 9),
    axis.text.y = element_text(colour = "black", size = 9),
    axis.title.x = ggtext::element_markdown()
  ) +
  geom_vline(xintercept = 55.86, size = 1, colour = "#FF3721", linetype = "dashed")
```

```{r}
# HAVE
ggplot(analysis_hegs_rpl, aes(x = Q12_pcnt_have_rep_1)) +
  geom_density(fill = fill, colour = line, size = 1, na.rm = T, ) +
  scale_x_continuous(
    name = "**Have** been replicated (%)",
    breaks = seq(0, 100, 25),
    limits = c(0, 100),
    expand = c(0, 2)
  ) +
  scale_y_continuous(
    name = "Density",
    breaks = seq(0, 0.025, .005),
    limits = c(0, 0.025),
    expand = c(0, 0)
  ) +
  theme(
    axis.line.x.bottom = element_line(size = 1, colour = "black"),
    axis.line.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    text = element_text(family = "Roboto"),
    axis.text.x = element_text(colour = "black", size = 9),
    axis.text.y = element_text(colour = "black", size = 9),
    axis.title.x = ggtext::element_markdown()
  ) +
  geom_vline(xintercept = 26.54, size = 1, colour = "#FF3721", linetype = "dashed")
```

## Slide 5 - Ridge line density plots
for could, should, have
Do a ridge line version where all three are in one plot at 3 levels 
have at the top, could in the middle, should at the bottom

```{r}
itemsQ12 <- as.data.frame(analysis_hegs_rpl[, substr(names(analysis_hegs_rpl), 1, 3) == "Q12"])
itemsQ13 <- analysis_hegs_rpl[, substr(names(analysis_hegs_rpl), 1, 3) == "Q13"]
itemsQ14 <- analysis_hegs_rpl[, substr(names(analysis_hegs_rpl), 1, 3) == "Q14"]

itemsQ12 <- itemsQ12 %>% transmute(
  response = ifelse(is.na(Q12_pcnt_have_rep_1), "Have", "Have"),
  value = Q12_pcnt_have_rep_1
)
itemsQ13 <- itemsQ13 %>% transmute(
  response = ifelse(is.na(Q13_pcnt_could_rep_1), "Could", "Could"),
  value = Q13_pcnt_could_rep_1
)
itemsQ14 <- itemsQ14 %>% transmute(
  response = ifelse(is.na(Q14_pcnt_should_rep_1), "Should", "Should"),
  value = Q14_pcnt_should_rep_1
)

data_ridge <- rbind(itemsQ12, itemsQ13, itemsQ14)
data_ridge$response <- factor(data_ridge$response, levels = c("Should", "Could", "Have"), ordered = TRUE)

ggplot(data_ridge, aes(x = value, y = response, group = response)) +
  geom_density_ridges(aes(fill = response), scale = 2, alpha = 0.5, color = line) +
  scale_fill_manual(values = c("#DCD6CC", "#9CBEBE", "#04859B")) +
  # stat_density_ridges(quantile_lines = TRUE, quantiles = 0.5, scale = 2., ) +
  scale_x_continuous(
    name = "",
    breaks = seq(0, 100, 25),
    limits = c(0, 100),
    expand = c(0, 2)
  ) +
  scale_y_discrete(
    name = "",
    expand = c(0, 0)
  ) +
  theme(legend.position = "none") +
  theme(
    axis.line.x.bottom = element_line(size = 0.7, colour = "black"),
    axis.line.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    text = element_text(family = "Roboto"),
    axis.text.x = element_text(colour = "black", size = 9),
    axis.text.y = element_text(colour = "black", size = 12, vjust = -2, face = "bold"),
    axis.title.x = ggtext::element_markdown()
  )
```

## RPL-Q8_1 THROUGH Q8_10 & Q10_1 THROUGH Q8_6 (combined)
```{r}
analysis_hegs_rpl <- analysis_hegs_rpl %>%
  mutate_at(c(
    "Q8_study_factors_1", "Q8_study_factors_2", "Q8_study_factors_3", "Q8_study_factors_4",
    "Q8_study_factors_5", "Q8_study_factors_6", "Q8_study_factors_7", "Q8_study_factors_8",
    "Q8_study_factors_9", "Q8_study_factors_10",
    "Q10_phen_factors_1", "Q10_phen_factors_2", "Q10_phen_factors_3", "Q10_phen_factors_4",
    "Q10_phen_factors_5", "Q10_phen_factors_6"
  ), funs(dplyr::recode(.,
    `Very likely to decrease` = -2,
    `Somewhat likely to decrease` = -1,
    `Not likely to affect` = 0,
    `Somewhat likely to increase` = 1,
    `Very likely to increase` = 2,
    .default = NaN
  ))) %>%
  mutate_at(c(
    "Q15_decision_factors_1", "Q15_decision_factors_2", "Q15_decision_factors_3", "Q15_decision_factors_4",
    "Q15_decision_factors_5", "Q15_decision_factors_6", "Q15_decision_factors_7", "Q15_decision_factors_8",
    "Q15_decision_factors_9", "Q15_decision_factors_10", "Q15_decision_factors_11", "Q15_decision_factors_12"
  ), funs(dplyr::recode(.,
    `Never` = 4,
    `Rarely` = 3,
    `Occasionally` = 2,
    `Frequently` = 1,
    `Always` = 0,
    .default = NaN
  )))
```
```{r}
# Convert to factors
q8_10_levels <- paste(c(
  "Very likely to decrease", "Somewhat likely to decrease", "Not likely to affect",
  "Somewhat likely to increase", "Very likely to increase"
))
q15_levels <- paste(c("Always", "Frequently", "Occasionally", "Rarely", "Never"))

analysis_hegs_rpl[20:29] <- lapply(analysis_hegs_rpl[20:29], factor, levels = -2:2, labels = q8_10_levels)
analysis_hegs_rpl[31:36] <- lapply(analysis_hegs_rpl[31:36], factor, levels = -2:2, labels = q8_10_levels)
analysis_hegs_rpl[41:52] <- lapply(analysis_hegs_rpl[41:52], factor, levels = 0:4, labels = q15_levels)

items8_10 <- analysis_hegs_rpl[, substr(names(analysis_hegs_rpl), 1, 2) == "Q8" | substr(names(analysis_hegs_rpl), 1, 3) == "Q10"]
names(items8_10) <- c(
  "Multiple hypotheses were tested",
  "Quantitative methods were used",
  "Qualitative methods were used",
  "Mixed methods were used",
  "Poor documentation of study methods",
  "Restricted access data were used",
  "Data were gathered from multiple sites",
  "A large research team conducted the study",
  "Relied on expertise unique to the researcher",
  "Relied on the unique position of the researcher",
  "Spatially dependent upon itself",
  "Strongly related with local conditions",
  "Exhibits variation across locations",
  "Cannot be directly measured",
  "Cannot be directly manipulated",
  "Has multiple competing theoretical explanations"
)

items8_10 <- items8_10[, c(5, 6, 7, 8, 9, 10, 1, 2, 3, 4, 11, 12, 13, 14, 15, 16)]
items8_10 <- as.data.frame(items8_10)

items15 <- analysis_hegs_rpl[, substr(names(analysis_hegs_rpl), 1, 3) == c("Q15")]
names(items15) <- c(
  "Pressure to publish original research",
  "Low value of replication studies",
  "Low chances of replicating a result",
  "Lack of experience conducting replications",
  "Difficult publishing peer-reviewed replications",
  "Difficulty accessing/creating relevant data",
  "Insufficient information about original methods",
  "Difficulty recreating similar procedures",
  "Lack of funding for replication studies",
  "Fraud",
  "Ethical concerns",
  "Known spatial variation in phenomena being studied"
)

items15 <- items15[, c(1, 9, 2, 5, 10, 6, 7, 8, 12, 4, 3, 11)]
items15 <- as.data.frame(items15)

test <- pivot_longer(items8_10, everything()) %>%
  group_by(name) %>%
  dplyr::count(value) %>%
  mutate(
    percentage = (n / 283),
    sum_n = sum(n),
    percentage_diverging = ifelse(value %in% c("Very likely to decrease", "Somewhat likely to decrease"),
      -1 * percentage,
      percentage
    ),
    name = factor(name, levels = c(
      "Has multiple competing theoretical explanations",
      "Cannot be directly manipulated",
      "Cannot be directly measured",
      "Exhibits variation across locations",
      "Strongly related with local conditions",
      "Spatially dependent upon itself",
      "Mixed methods were used",
      "Qualitative methods were used",
      "Quantitative methods were used",
      "Multiple hypotheses were tested",
      "Relied on the unique position of the researcher",
      "Relied on expertise unique to the researcher",
      "A large research team conducted the study",
      "Data were gathered from multiple sites",
      "Restricted access data were used",
      "Poor documentation of study methods"
    )),
    label = paste0(round(percentage * 100, 0), "%"),
    value_ordered = relevel(value, "Very likely to increase")
  )
```

## Q8_10 PLOT
ADD MISSING AND DON'T KNOW TO PERCENTAGES BUT DON'T SHOW 
```{r}
pivot_longer(items8_10, everything()) %>%
  group_by(name) %>%
  dplyr::count(value) %>%
  mutate(
    percentage = (n / 283),
    percentage_diverging = ifelse(value %in% c("Very likely to decrease", "Somewhat likely to decrease"),
      -1 * percentage,
      percentage
    ),
    name = factor(name, levels = c(
      "Has multiple competing theoretical explanations",
      "Cannot be directly manipulated",
      "Cannot be directly measured",
      "Exhibits variation across locations",
      "Strongly related with local conditions",
      "Spatially dependent upon itself",
      "Mixed methods were used",
      "Qualitative methods were used",
      "Quantitative methods were used",
      "Multiple hypotheses were tested",
      "Relied on the unique position of the researcher",
      "Relied on expertise unique to the researcher",
      "A large research team conducted the study",
      "Data were gathered from multiple sites",
      "Restricted access data were used",
      "Poor documentation of study methods"
    )),
    label = paste0(round(percentage * 100, 0), "%"),
    value_ordered = relevel(value, "Very likely to increase")
  ) %>%
  filter(!is.na(value) & value != "Not likely to affect") %>%
  ggplot(aes(x = name, y = percentage_diverging, fill = value_ordered)) +
  geom_bar(stat = "identity", width = 0.9) +
  geom_text(aes(label = label), position = position_stack(vjust = 0.4), size = 2.1, colour = "white") +
  coord_flip() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_manual(values = c("#CD2311", "#003660", "#04859B", "#EF5645")) +
  ylab("") +
  xlab("") +
  scale_x_discrete(expand = c(0, 0)) +
  theme(
    axis.line.x = element_line(size = 0.5, colour = "black"),
    axis.ticks.x = element_line(size = 0.5, colour = "black"),
    axis.line.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    text = element_text(family = "Roboto"),
    axis.text.x = element_text(colour = "black", size = 9),
    axis.text.y = element_text(colour = "black", size = 10),
    legend.position = "bottom",
    legend.title = element_blank()
  )
```

## Q15 PLOT
ADD MISSING AND DON'T KNOW TO PERCENTAGES BUT DON'T SHOW 
```{r}
pivot_longer(items15, everything()) %>%
  group_by(name) %>%
  dplyr::count(value) %>%
  filter(!is.na(value)) %>%
  mutate(
    percentage = (n / 283),
    name = factor(name, levels = c(
      "Ethical concerns",
      "Low chances of replicating a result",
      "Lack of experience conducting replications",
      "Known spatial variation in phenomena being studied",
      "Difficulty recreating similar procedures",
      "Insufficient information about original methods",
      "Difficulty accessing/creating relevant data",
      "Fraud",
      "Difficult publishing peer-reviewed replications",
      "Low value of replication studies",
      "Lack of funding for replication studies",
      "Pressure to publish original research"
    ))
  ) %>%
  ggplot(aes(x = name, y = percentage, fill = value)) +
  geom_bar(position = position_fill(reverse = TRUE), stat = "identity", width = 0.8) +
  coord_flip() +
  scale_fill_manual(values = c("#CD2311", "#EF5645", "#BFBFBF", "#D9D9D9", "#F2F2F2")) +
  ylab("") +
  xlab("") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent) +
  theme(
    axis.line.x = element_line(size = 0.5, colour = "black"),
    axis.ticks.x = element_line(size = 0.5, colour = "black"),
    axis.line.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    text = element_text(family = "Roboto"),
    axis.text.x = element_text(colour = "black", size = 9),
    axis.text.y = element_text(colour = "black", size = 10),
    legend.position = "bottom",
    legend.title = element_blank()
  )
```

# Reproducibility
```{r}
rp <- readRDS("analysis_hegs_rpr.rds")
```

## RP_Q14
```{r}
rp <- rp %>%
  mutate_at(
    c(
      "Q14_1", "Q14_2", "Q14_3", "Q14_4",
      "Q14_5", "Q14_6", "Q14_7", "Q14_8",
      "Q14_9", "Q14_10", "Q14_11", "Q14_12"
    ),
    funs(dplyr::recode(.,
      `Frequently` = 1,
      `Occasionally` = 2,
      `Rarely` = 3,
      `Never` = 4,
      .default = NaN
    ))
  )

# Convert to factors
q14_levels <- paste(c("Frequently", "Occasionally", "Rarely", "Never"))

rp[57:68] <- lapply(rp[57:68], factor, levels = 1:4, labels = q14_levels)

items14 <- rp[, substr(names(rp), 1, 3) == "Q14"]
names(items14) <- c(
  "Fraud",
  "Pressure to publish",
  "Insufficient oversight or mentoring",
  "Lack of publishing raw data",
  "Lack of publishing protocol or code",
  "Lack of publishing full results",
  "Differences in software environments",
  "Use of proprietary data or software",
  "Complexity and variability of geographic systems",
  "Random effects",
  "Insufficient metadata",
  "Researcher positionality"
)
test <- pivot_longer(items14, everything()) %>%
  group_by(name) %>%
  dplyr::count(value) %>%
  mutate(
    percentage = (n / 218),
    label = paste0(round(percentage * 100, 0), "%"),
    name = factor(name, levels = c(
      "Differences in software environments",
      "Random effects",
      "Researcher positionality",
      "Complexity and variability of geographic systems",
      "Use of proprietary data or software",
      "Lack of publishing full results",
      "Lack of publishing protocol or code",
      "Lack of publishing raw data",
      "Insufficient metadata",
      "Fraud",
      "Insufficient oversight or mentoring",
      "Pressure to publish"
    ))
  )

# write_csv(test,"rp14_freqs_pcnts.csv")

pivot_longer(items14, everything()) %>%
  group_by(name) %>%
  dplyr::count(value) %>%
  mutate(
    percentage = (n / 218),
    label = paste0(round(percentage * 100, 0), "%"),
    name = factor(name, levels = c(
      "Differences in software environments",
      "Random effects",
      "Researcher positionality",
      "Complexity and variability of geographic systems",
      "Use of proprietary data or software",
      "Lack of publishing full results",
      "Lack of publishing protocol or code",
      "Lack of publishing raw data",
      "Insufficient metadata",
      "Fraud",
      "Insufficient oversight or mentoring",
      "Pressure to publish"
    ))
  ) %>%
  filter(!is.na(value)) %>%
  ggplot(aes(x = name, y = percentage, fill = value)) +
  geom_bar(position = position_fill(reverse = TRUE), stat = "identity", width = 0.8) +
  coord_flip() +
  scale_fill_manual(values = c("#CD2311", "#EF5645", "#D9D9D9", "#F2F2F2")) +
  ylab("") +
  xlab("") +
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_continuous(labels = scales::percent) +
  theme(
    axis.line.x = element_line(size = 0.5, colour = "black"),
    axis.ticks.x = element_line(size = 0.5, colour = "black"),
    axis.line.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    text = element_text(family = "Roboto"),
    axis.text.x = element_text(colour = "black", size = 9),
    axis.text.y = element_text(colour = "black", size = 10),
    legend.position = "bottom",
    legend.title = element_blank()
  )
```

## COULD RPR
```{r}
fill <- "#DCE1E5"
line <- "#003660"
ggplot(rp, aes(x = Q13_1)) +
  geom_density(fill = fill, colour = line, size = 1, na.rm = T, ) +
  scale_x_continuous(
    name = "**Could** be reproduced (%)",
    breaks = seq(0, 100, 25),
    limits = c(0, 100),
    expand = c(0, 2)
  ) +
  scale_y_continuous(
    name = "Density",
    breaks = seq(0, 0.025, .005),
    limits = c(0, 0.025),
    expand = c(0, 0)
  ) +
  theme(
    axis.line.x.bottom = element_line(size = 1, colour = "black"),
    axis.line.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    text = element_text(family = "Roboto"),
    axis.text.x = element_text(colour = "black", size = 9),
    axis.text.y = element_text(colour = "black", size = 9),
    axis.title.x = ggtext::element_markdown()
  ) +
  geom_vline(xintercept = 55, size = 1, colour = "#FF3721", linetype = "dashed")
```

## Slide 5 - Ridge line density plots
for could rpl and could rp
Do a ridge line version where all three are in one plot at 3 levels 
have at the top, could in the middle, should at the bottom
```{r}
itemsQ13_rp <- rp[, substr(names(rp), 1, 5) == "Q13_1"]
itemsQ13_rpl <- analysis_hegs_rpl[, substr(names(analysis_hegs_rpl), 1, 3) == "Q13"]

itemsQ13_rp <- itemsQ13_rp %>% transmute(
  response = ifelse(is.na(Q13_1), "Reproduced", "Reproduced"),
  value = Q13_1
)
itemsQ13_rpl <- itemsQ13_rpl %>% transmute(
  response = ifelse(is.na(Q13_pcnt_could_rep_1), "Replicated", "Replicated"),
  value = Q13_pcnt_could_rep_1
)

data_ridge_2 <- rbind(itemsQ13_rp, itemsQ13_rpl)
data_ridge_2$response <- factor(data_ridge_2$response, levels = c("Reproduced", "Replicated"), ordered = TRUE)

ggplot(data_ridge_2, aes(x = value, y = response, group = response)) +
  geom_density_ridges(aes(fill = response), scale = 2, alpha = 0.5, color = line) +
  scale_fill_manual(values = c("#DCD6CC", "#04859B", "#9CBEBE")) +
  # stat_density_ridges(quantile_lines = TRUE, quantiles = 0.5, scale = 2., ) +
  scale_x_continuous(
    name = "",
    breaks = seq(0, 100, 25),
    limits = c(0, 100),
    expand = c(0, 2)
  ) +
  scale_y_discrete(
    name = "",
    expand = c(0, 0)
  ) +
  theme(legend.position = "none") +
  theme(
    axis.line.x.bottom = element_line(size = 0.7, colour = "black"),
    axis.line.y = element_blank(),
    axis.ticks.x = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    panel.border = element_blank(),
    panel.background = element_blank(),
    text = element_text(family = "Roboto"),
    axis.text.x = element_text(colour = "black", size = 9),
    axis.text.y = element_text(colour = "black", size = 12, vjust = -2, face = "bold"),
    axis.title.x = ggtext::element_markdown()
  )
```

## Likert
```{r}
library(likert)
q8_10_figures <- likert(items8_10)
q15_figures <- likert(items15)
#--THIS WILL BE FOR APPENDIX
plot(q8_10_figures,
  group.order = names(items8_10[1:16]), centered = TRUE,
  plot.percent.neutral = TRUE, plot.percents = TRUE,
  plot.percent.low = FALSE, plot.percent.high = FALSE,
  text.size = 2.5,
  panel.background = element_rect(size = 0, color = "grey70", fill = NA),
  legend = "",
  legend.position = "bottom"
)
```

### CENTERED
```{r}
plot(q8_10_figures,
  group.order = names(items8_10[1:16]),
  include.center = FALSE,
  plot.percents = TRUE,
  plot.percent.low = FALSE, plot.percent.high = FALSE,
  text.size = 2.5,
  panel.background = element_rect(size = 0, color = "grey70", fill = NA),
  legend = "",
  legend.position = "bottom"
)
```

### NOT CENTERED
(UNSURE HOW TO GET PERCENTAGES CORRECT)
```{r}
plot(q8_10_figures,
  group.order = names(items8_10[1:16]),
  include.center = FALSE,
  plot.percents = FALSE,
  plot.percent.low = FALSE, plot.percent.high = FALSE, plot.percent.neutral = TRUE,
  text.size = 2.5,
  panel.background = element_rect(size = 0, color = "grey70", fill = NA),
  centered = FALSE,
  legend = "",
  legend.position = "bottom"
)
```

```{r}
plot(q8_10_figures,
  ordered = TRUE,
  plot.percents = FALSE,
  plot.percent.low = FALSE, plot.percent.high = FALSE, plot.percent.neutral = TRUE,
  text.size = 2.5,
  panel.background = element_rect(size = 0, color = "grey70", fill = NA),
  centered = FALSE,
  legend = "",
  legend.position = "bottom"
)
```

```{r}
plot(q15_figures,
  group.order = names(items15[1:12]),
  include.center = FALSE,
  plot.percents = FALSE,
  plot.percent.low = FALSE, plot.percent.high = FALSE, plot.percent.neutral = FALSE,
  text.size = 2.5,
  panel.background = element_rect(size = 0, color = "grey70", fill = NA),
  centered = FALSE,
  legend = "",
  legend.position = "bottom",
  colors = c("#CD2311", "#EF5645", "#BFBFBF", "#D9D9D9", "#F2F2F2")
)
```

### 2023-07-24 docs/presentation/data/constants.R
viz: function for subplot

@@ -8,6 +8,13 @@ geo_groups <- list(
   "Type" = types
 )
 
+# Columns to cast as factors
+four_levels <- c("Not at all", "Very little", "Somewhat", "To a great extent")
+four_level_cols <- c("Q5", "Q7a", "Q7b", "Q7c", "Q7d", "Q7e")
+
+five_levels <- c("Never", "Rarely", "Some of the time", "Most of the time", "Always")
+five_level_cols <- c("Q7a_1", "Q7a_3", "Q7b_1", "Q7c_1", "Q7c_2", "Q7c_3", "Q7d_1", "Q7d_2", "Q7e_1")
+
 # Questions for the word cloud ####
 cloud_cols <- list("Q6", "Q10", "Q12a", "Q15", "Q17a")
 cloud_questions <- list(
@@ -33,3 +40,21 @@ cloud_questions <- list(
     "Please list any benefits or important function of reproducibility in your subfield not mentioned above."
   )
 )
+
+# Function for subplot
+# Modified from original by Dan Powers <danielp@takomaparkmd.gov> under MIT License
+# https://github.com/dpowerstp/plotlywrappers/blob/76d6bb1d5890c81b4fef00472bc1064926f6aa53/R/subplot_title.R
+subplot_title <- function(plot, title, .x = 0.05, .y = 1.1) {
+  plot %>%
+    plotly::add_annotations(
+      text = title,
+      x = .x,
+      y = .y,
+      yref = "paper",
+      xref = "paper",
+      xanchor = "left",
+      yanchor = "top",
+      showarrow = FALSE,
+      font = list(family = "Fira Sans", size = 24)
+    )
+}

### 2023-07-24 docs/presentation/global.R
viz: shiny app for Q5, Q6

@@ -1,0 +1,16 @@
+# Packages ####
+library(shiny)
+library(plotly)
+library(tidyverse)
+library(wordcloud2)
+
+# theme to match HTML
+thematic::thematic_shiny(font = "auto")
+
+source("data/constants.R")
+
+# load data ####
+analysis <- readRDS("data/analysis.rds")
+
+clouds <- readRDS("data/clouds.rds")
+clouds_q6 <- readRDS("data/clouds_q6.rds")

### 2023-07-24 docs/presentation/server.R

@@ -1,0 +1,110 @@
+# server function ####
+function(input, output, session) {
+  # Data ####
+  d <- reactive({
+    analysis %>%
+      # No idea why ifelse and if_else don't work
+      dplyr::filter(
+        if (input$group %in% subfields) {
+          .data$Q3_recoded == input$group
+        } else if (input$group %in% types) {
+          .data$Q4 == input$group
+        } else {
+          TRUE
+        }
+      )
+  }) %>%
+    bindCache(input$group) %>%
+    bindEvent(input$group)
+
+  # table for debugging ####
+  output$table <- d() %>%
+    # Had to use |> because %>% isn't working here, idk why
+    # Sounds like https://github.com/tidyverse/magrittr/issues/159
+    DT::datatable(extensions = "Responsive") |>
+    DT::renderDT()
+
+  # More debugging ####
+  output$ver <- renderPrint(input$group)
+
+  # Q5 plots ####
+  output$q5 <- renderPlotly({
+    fig1 <- d() %>%
+      count(Q5) %>%
+      plot_ly(
+        x = ~Q5,
+        y = ~n,
+        type = "bar",
+        # https://community.plotly.com/t/33731
+        hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
+      ) %>%
+      subplot_title("Familiarity with \"reproducibility\"")
+
+    fig2 <- d() %>%
+      summarize(across(c(dat_rec, pro_rec, res_rec, con_rec), sum)) %>%
+      plot_ly(
+        x = c("Same data", "Same procedure", "Same result", "Same condition"),
+        y = as.numeric(.),
+        type = "bar",
+        hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
+      ) %>%
+      subplot_title("Reproducibility in terms of...")
+
+    fig3 <- d() %>%
+      count(label) %>%
+      plot_ly(
+        x = ~label,
+        y = ~n,
+        type = "bar",
+        hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
+      ) %>%
+      plotly::layout(
+        xaxis = list(
+          ticktext = c(
+            "Data Collection", "Experiment", "Omit",
+            "Standard", "Transparency\n& Extension"
+          ),
+          tickvals = c(
+            "Data Collection", "Experiment", "Omit",
+            "Standard", "Transparency/Extension"
+          )
+        )
+      ) %>%
[…]

### 2023-07-24 docs/presentation/ui.R

@@ -1,0 +1,95 @@
+# UI function ####
+function(request) {
+  navbarPage(
+    title = "RPr in Geo",
+
+    # customization
+    id = "activeTab",
+    theme = bslib::bs_theme(
+      fg = "#212529", primary = "#1D5B79", secondary = "#C5DFF8",
+      success = "#8EAC50", info = "#468B97", warning = "#F1C93B",
+      base_font = bslib::font_google("Fira Sans"),
+      code_font = bslib::font_google("Fira Code"),
+      bootswatch = "flatly", bg = "#FFFFFF"
+    ),
+    windowTitle = "Reproducibility in Geographic Research",
+    # Access with `Shiny.shinyapp.$inputValues`
+    header = # conditionalPanel(
+    # condition = "input.activeTab !== 'Word Cloud'",
+      selectInput(
+        "group", h5("Choose a group:", style = "margin-top: 20px;"),
+        geo_groups,
+      ),
+    # ),
+
+    # About ####
+    tabPanel(
+      "About",
+      icon = icon("file-alt"),
+      fluidRow(
+        column(
+          12,
+          h1("Debugging"),
+          verbatimTextOutput("ver"),
+          DT::DTOutput("table"),
+        ),
+      ),
+    ),
+
+    # Awareness ####
+    tabPanel(
+      "Awareness",
+      icon = icon("lightbulb"),
+      plotlyOutput("q5", height = "80vh"),
+    ),
+
+    # Word Cloud ####
+    tabPanel(
+      "Word Cloud",
+      icon = icon("cloud"),
+      tabsetPanel(
+        id = "clouds",
+        tabPanel(
+          "Overall",
+          fluidRow(
+            column(
+              3,
+              radioButtons(
+                "cloud",
+                label = h4("Choose a question:"),
+                choiceNames = cloud_questions,
+                choiceValues = cloud_cols
+              ),
+            ),
+            column(
+              9,
+              wordcloud2Output(
+                "cloud",
+                height = "80vh"
+              ),
+            ),
+          ),
+        ),
+        tabPanel(
+          "Q6 (groupwise)",
+          wordcloud2Output(
+            "cloud_q6",
+            height = "80vh"
+          ),
+        )
+      ),
+    ),
+
+    # More Stuff ####
+    tabPanel(
+      "More Stuff",
+      icon = icon("file-alt"),
+      fluidRow(
+        column(
+          6,
+          h1("More Stuff"),
+        ),
+      ),
+    ),
+  )
+}

### 2023-07-25 docs/presentation/preprocess.Rmd
viz: reorder factors
viz: use data folder

@@
 
-The file `analysis_hegs_rpr.csv` was saved from `data\derived\public\analysis_hegs_rpr.rds`.
+The file `analysis_hegs_rpr.csv` is from `data\derived\public\analysis_hegs_rpr.rds`.
 
@@
 # library(ggthemes)
-library(readr)
 library(tidyverse)
@@
 ```{r data}
-analysis <- read_csv("data/analysis_hegs_rpr.csv")
+analysis <- readRDS("../../data/derived/public/analysis_hegs_rpr.rds")
 source("data/constants.R")
@@
 ## Bar charts
-Include animations?
-
+Order Q5 and Q7 responses
 ```{r}
-analysis %>%
-  count(dat_rec)
+analysis %<>%
+  mutate(across(all_of(four_level_cols), ~ factor(., levels = four_levels))) %>%
+  mutate(across(all_of(five_level_cols), ~ factor(., levels = five_levels)))
 ```
@@
 ## Demographics
+
+## Save
+```{r}
+analysis %>%
+  saveRDS("data/analysis.rds", compress = FALSE)
+```

### 2023-07-25 docs/presentation/ui.R
viz: concepts panel

@@ -43,6 +43,30 @@ function(request) {
       plotlyOutput("q5", height = "80vh"),
     ),
 
+    # Concepts ####
+    tabPanel(
+      "Concepts",
+      icon = icon("comments"),
+      tabsetPanel(
+        id = "q7_panel",
+        tabPanel(
+          "Open source",
+        ),
+        tabPanel(
+          "Notebooks",
+        ),
+        tabPanel(
+          "Data archive",
+        ),
+        tabPanel(
+          "Sharing code",
+        ),
+        tabPanel(
+          "Pre-register",
+        ),
+      ),
+    ),
+
     # Word Cloud ####
     tabPanel(
       "Word Cloud",

### 2023-08-01 docs/presentation/preprocess.Rmd
viz: refactor 5 levels to 4

@@
 ## Bar charts
+Cast 5 levels to 4
+```{r eval=FALSE, include=FALSE}
+analysis %<>%
+  mutate(
+    across(
+      all_of(five_level_cols),
+      ~ case_when(
+        . == "Never" ~ "Not at all",
+        . == "Rarely" ~ "Very little",
+        . == "Some of the time" ~ "Somewhat",
+        . %in% c("Most of the time", "Always") ~ "To a great extent"
+      )
+    )
+  )
+```
+
 Order Q5 and Q7 responses
@@
   mutate(across(all_of(four_level_cols), ~ factor(., levels = four_levels))) %>%
-  mutate(across(all_of(five_level_cols), ~ factor(., levels = five_levels)))
+  mutate(across(all_of(five_level_cols), ~ factor(., levels = four_levels)))
 ```

### 2023-08-02 docs/presentation/data/constants.R
viz: cast 5 levels to 4

@@ -1,5 +1,7 @@
-# Group definitions ####
 library(shiny)
+library(plotly)
+
+# Group definitions ####
 subfields <- list("Human", "Methods", "Nature/society", "Physical")
 types <- list("Quantitative", "Qualitative", "Mixed Methods")
 geo_groups <- list(
@@ -8,7 +10,7 @@ geo_groups <- list(
   "Type" = types
 )
 
-# Columns to cast as factors
+# Columns to cast as factors ####
 four_levels <- c("Not at all", "Very little", "Somewhat", "To a great extent")
 four_level_cols <- c("Q5", "Q7a", "Q7b", "Q7c", "Q7d", "Q7e")
 
@@ -41,7 +43,7 @@ cloud_questions <- list(
   )
 )
 
-# Function for subplot
+# Function for subplot ####
 # Modified from original by Dan Powers <danielp@takomaparkmd.gov> under MIT License
 # https://github.com/dpowerstp/plotlywrappers/blob/76d6bb1d5890c81b4fef00472bc1064926f6aa53/R/subplot_title.R
 subplot_title <- function(plot, title, .x = 0.05, .y = 1.1) {

### 2023-08-02 docs/presentation/data/constants.R
viz: refactoring

@@ -60,3 +60,35 @@ subplot_title <- function(plot, title, .x = 0.05, .y = 1.1) {
       font = list(family = "Fira Sans", size = 24)
     )
 }
+
+# Plotly styling ####
+plt_layout <- function(plt, ...) {
+  plotly::layout(
+    plt,
+    xaxis = list(title = FALSE),
+    yaxis = list(title = FALSE),
+    font = list(family = "Fira Sans", size = 16),
+    hoverlabel = list(
+      font = list(family = "Fira Sans", size = 16)
+    ),
+    ...
+  )
+}
+
+# Plotly config ####
+# # https://github.com/plotly/plotly.js/blob/master/src/plot_api/plot_config.js
+plt_config <- function(plt, filename = "", ...) {
+  plotly::config(
+    plt,
+    displaylogo = FALSE,
+    showTips = FALSE,
+    toImageButtonOptions = list(
+      format = "png",
+      filename = filename,
+      # height = 500,
+      # width = 700,
+      scale = 4
+    ),
+    ...
+  )
+}

### 2023-08-02 docs/presentation/global.R

@@ -3,9 +3,13 @@ library(shiny)
 library(plotly)
 library(tidyverse)
 library(wordcloud2)
+library(stringr)
 
 # theme to match HTML
 thematic::thematic_shiny(font = "auto")
+
+# plot height as CSS
+plot_height = "80vh"
 
 source("data/constants.R")
 

### 2023-08-02 docs/presentation/server.R

@@ -52,53 +52,31 @@ function(input, output, session) {
 
     fig3 <- d() %>%
       count(label) %>%
+      mutate(
+        label = label %>%
+          str_replace("/", " & ") %>%
+          str_wrap(width = 20)
+      ) %>%
       plot_ly(
         x = ~label,
         y = ~n,
         type = "bar",
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
       ) %>%
-      plotly::layout(
-        xaxis = list(
-          ticktext = c(
-            "Data Collection", "Experiment", "Omit",
-            "Standard", "Transparency\n& Extension"
-          ),
-          tickvals = c(
-            "Data Collection", "Experiment", "Omit",
-            "Standard", "Transparency/Extension"
-          )
-        )
-      ) %>%
       subplot_title("What is important in reproducibility?")
 
     plotly::subplot(fig1, fig2, fig3, nrows = 1, shareY = TRUE) %>%
-      plotly::layout(
+      plt_layout(
         showlegend = FALSE,
-        xaxis = list(title = FALSE),
-        yaxis = list(title = FALSE),
-        font = list(family = "Fira Sans", size = 16),
-        hoverlabel = list(
-          font = list(family = "Fira Sans", size = 16)
-        ),
         # top margins
         margin = list(t = 100)
       ) %>%
-      # https://github.com/plotly/plotly.js/blob/master/src/plot_api/plot_config.js
-      plotly::config(
-        displaylogo = FALSE,
-        showTips = FALSE,
-        toImageButtonOptions = list(
-          format = "png",
-          filename = paste0(
-            "repro_awareness_",
-            input$group %>%
-              tolower() %>%
-              gsub("[^a-z0-9]", "_", .)
-          ),
-          # height = 500,
-          # width = 700,
-          scale = 4
+      plt_config(
+        filename = paste0(
+          "repro_awareness_",
+          input$group %>%
+            tolower() %>%
+            gsub("[^a-z0-9]", "_", .)
         )
       )
   })

### 2023-08-02 docs/presentation/ui.R

@@ -40,7 +40,7 @@ function(request) {
     tabPanel(
       "Awareness",
       icon = icon("lightbulb"),
-      plotlyOutput("q5", height = "80vh"),
+      plotlyOutput("q5", height = plot_height),
     ),
 
     # Concepts ####
@@ -89,7 +89,7 @@ function(request) {
               9,
               wordcloud2Output(
                 "cloud",
-                height = "80vh"
+                height = plot_height
               ),
             ),
           ),
@@ -98,7 +98,7 @@ function(request) {
           "Q6 (groupwise)",
           wordcloud2Output(
             "cloud_q6",
-            height = "80vh"
+            height = plot_height
           ),
         )
       ),

### 2023-08-02 docs/presentation/global.R
viz: colors & style

@@ -1,15 +1,30 @@
 # Packages ####
 library(shiny)
 library(plotly)
+library(stringr)
 library(tidyverse)
 library(wordcloud2)
-library(stringr)
 
 # theme to match HTML
 thematic::thematic_shiny(font = "auto")
 
+# colors for 4 levels
+# continuous
+mako4 <- viridisLite::plasma(4, begin = 0.3, end = 0.7)
+# discrete
+pal4 <- viridisLite::viridis(4, begin = 0.1, end = 0.9)
+pal5 <- viridisLite::viridis(5, begin = 0.1, end = 0.9)
+# discrete: alternate choices
+# https://stackoverflow.com/a/40181166
+# pal4 <- scales::hue_pal()(4)
+# pal5 <- scales::hue_pal()(5)
+# https://rdrr.io/cran/ggthemes/man/palette_pander.html
+#pal4 <- ggthemes::palette_pander(8)
+#pal5 <- pal4
+
 # plot height as CSS
-plot_height = "80vh"
+plot_full_height <- "80vh"
+plot_height <- "60vh"
 
 source("data/constants.R")
 

### 2023-08-02 docs/presentation/server.R

@@ -35,6 +35,8 @@ function(input, output, session) {
         x = ~Q5,
         y = ~n,
         type = "bar",
+        color = ~Q5,
+        colors = mako4,
         # https://community.plotly.com/t/33731
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
       ) %>%
@@ -42,9 +44,15 @@ function(input, output, session) {
 
     fig2 <- d() %>%
       summarize(across(c(dat_rec, pro_rec, res_rec, con_rec), sum)) %>%
+      pivot_longer(cols = everything()) %>%
+      add_column(label = c(
+        "Same data", "Same procedure", "Same result", "Same condition"
+        )) %>%
       plot_ly(
-        x = c("Same data", "Same procedure", "Same result", "Same condition"),
-        y = as.numeric(.),
+        x = ~label,
+        y = ~value,
+        color = ~label,
+        colors = pal5,
         type = "bar",
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
       ) %>%
@@ -61,6 +69,8 @@ function(input, output, session) {
         x = ~label,
         y = ~n,
         type = "bar",
+        color = ~label,
+        colors = pal5,
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
       ) %>%
       subplot_title("What is important in reproducibility?")

### 2023-08-02 docs/presentation/ui.R

@@ -1,5 +1,10 @@
-# UI function ####
-function(request) {
+# UI tags ####
+tagList(
+  # head
+  tags$head(
+    tags$link(rel = "stylesheet", type = "text/css", href = "style.css"),
+    tags$link(rel = "shortcut icon", href = "favicon.png"),
+  ),
   navbarPage(
     title = "RPr in Geo",
 
@@ -17,7 +22,7 @@ function(request) {
     header = # conditionalPanel(
     # condition = "input.activeTab !== 'Word Cloud'",
       selectInput(
-        "group", h5("Choose a group:", style = "margin-top: 20px;"),
+        "group", h5("Choose a group:"),
         geo_groups,
       ),
     # ),
@@ -40,7 +45,7 @@ function(request) {
     tabPanel(
       "Awareness",
       icon = icon("lightbulb"),
-      plotlyOutput("q5", height = plot_height),
+      plotlyOutput("q5", height = plot_full_height),
     ),
 
     # Concepts ####
@@ -89,7 +94,7 @@ function(request) {
               9,
               wordcloud2Output(
                 "cloud",
-                height = plot_height
+                height = plot_full_height
               ),
             ),
           ),
@@ -98,7 +103,7 @@ function(request) {
           "Q6 (groupwise)",
           wordcloud2Output(
             "cloud_q6",
-            height = plot_height
+            height = plot_full_height
           ),
         )
       ),
@@ -116,4 +121,4 @@ function(request) {
       ),
     ),
   )
-}
+)

### 2023-08-02 docs/presentation/server.R
viz: Q7: OSS

@@ -91,6 +91,73 @@ function(input, output, session) {
       )
   })
 
+  # Q7 open source ####
+  output$q7oss <- renderPlotly({
+    Q7a_1 <- d() %>%
+      drop_na(Q7a_1) %>%
+      count(Q7a_1)
+
+    d() %>%
+      drop_na(Q7a) %>%
+      count(Q7a) %>%
+      plot_ly(
+        x = ~Q7a,
+        y = ~n,
+        type = "bar",
+        name = "Familiar",
+        # marker = list(color = "#1b9e77"),
+        hovertemplate = "<b>%{x}</b>\n%{y} people"
+      ) %>%
+      add_bars(
+        x = ~Q7a_1,
+        y = ~n,
+        data = Q7a_1,
+        name = "Use",
+        # marker = list(color = "#d95f02"),
+        hovertemplate = "<b>%{x}</b>\n%{y} people"
+      ) %>%
+      plt_layout(barmode = "group") %>%
+      plt_config(filename = "repro_oss")
+  })
+
+  output$q7oss_parts <- renderPlotly({
+    d() %>%
+      select(starts_with("Q7a_2")) %>%
+      pivot_longer(cols = everything()) %>%
+      filter(value != 0) %>%
+      group_by(value) %>%
+      summarise(n = n()) %>%
+      mutate(value = str_wrap(value, width = 20)) %>%
+      plot_ly(
+        x = ~value,
+        y = ~n,
+        color = ~value,
+        colors = pal4,
+        type = "bar",
+        name = "Used for",
+        hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
+      ) %>%
+      plt_layout(showlegend = FALSE) %>%
+      plt_config(filename = "repro_oss_usage")
+  })
+  
+  output$q7oss_env <- renderPlotly({
+    d() %>%
+      drop_na(Q7a_3) %>%
+      count(Q7a_3) %>%
+      plot_ly(
+        x = ~Q7a_3,
+        y = ~n,
+        color = ~Q7a_3,
+        type = "bar",
+        # name = "Familiar",
+        colors = mako4,
+        hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
+      ) %>%
+      plt_layout(showlegend = FALSE) %>%
+      plt_config(filename = "repro_oss_env")
+  })
+
 
   # Word cloud ####
   output$cloud <- renderWordcloud2(clouds[[input$cloud]])

### 2023-08-02 docs/presentation/ui.R

@@ -56,6 +56,47 @@ tagList(
         id = "q7_panel",
         tabPanel(
           "Open source",
+          fluidRow(
+            column(
+              4,
+              h5(
+                "How familiar are you with ",
+                strong("open source software", .noWS = "after"), "?",
+                br(),
+                "How often do you use ",
+                strong("open source software", .noWS = "after"), "?"
+              ),
+              plotlyOutput("q7oss", height = plot_height),
+              p(
+                "\"Use\" is recoded for visualization as follows:", br(),
+                "Never -> Not at all", br(),
+                "Rarely -> Very little", br(),
+                "Some of the time -> Somewhat", br(),
+                "Most of the time -> To a great extent", br(),
+                "Always -> To a great extent",
+              ),
+            ),
+            column(
+              4,
+              h5(
+                "You use ",
+                strong("open source software"),
+                "for ...?"
+                ),
+              plotlyOutput("q7oss_parts", height = plot_height),
+            ),
+            column(
+              4,
+              h5(
+                "How often do you ",
+                strong("document or share"),
+                "information related to
+                the computational processing environment
+                used in your own research?"
+              ),
+              plotlyOutput("q7oss_env", height = plot_height),
+            ),
+          ),
         ),
         tabPanel(
           "Notebooks",

### 2023-08-02 docs/presentation/data/constants.R
viz: plot title styling

@@ -77,7 +77,7 @@ plt_layout <- function(plt, ...) {
 
 # Plotly config ####
 # # https://github.com/plotly/plotly.js/blob/master/src/plot_api/plot_config.js
-plt_config <- function(plt, filename = "", ...) {
+plt_config <- function(plt, filename, ...) {
   plotly::config(
     plt,
     displaylogo = FALSE,

### 2023-08-02 docs/presentation/global.R

@@ -12,19 +12,19 @@ thematic::thematic_shiny(font = "auto")
 # continuous
 mako4 <- viridisLite::plasma(4, begin = 0.3, end = 0.7)
 # discrete
-pal4 <- viridisLite::viridis(4, begin = 0.1, end = 0.9)
-pal5 <- viridisLite::viridis(5, begin = 0.1, end = 0.9)
-# discrete: alternate choices
 # https://stackoverflow.com/a/40181166
 # pal4 <- scales::hue_pal()(4)
 # pal5 <- scales::hue_pal()(5)
 # https://rdrr.io/cran/ggthemes/man/palette_pander.html
-#pal4 <- ggthemes::palette_pander(8)
-#pal5 <- pal4
+pal4 <- ggthemes::palette_pander(8)
+pal5 <- pal4
 
 # plot height as CSS
 plot_full_height <- "80vh"
 plot_height <- "60vh"
+
+# text width for axis labels
+width <- 20
 
 source("data/constants.R")
 

### 2023-08-02 docs/presentation/server.R

@@ -39,15 +39,15 @@ function(input, output, session) {
         colors = mako4,
         # https://community.plotly.com/t/33731
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
-      ) %>%
-      subplot_title("Familiarity with \"reproducibility\"")
+      )
 
     fig2 <- d() %>%
       summarize(across(c(dat_rec, pro_rec, res_rec, con_rec), sum)) %>%
       pivot_longer(cols = everything()) %>%
       add_column(label = c(
         "Same data", "Same procedure", "Same result", "Same condition"
-        )) %>%
+      )) %>%
+      mutate(label = str_wrap(label, width = width)) %>%
       plot_ly(
         x = ~label,
         y = ~value,
@@ -55,15 +55,14 @@ function(input, output, session) {
         colors = pal5,
         type = "bar",
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
-      ) %>%
-      subplot_title("Reproducibility in terms of...")
+      )
 
     fig3 <- d() %>%
       count(label) %>%
       mutate(
         label = label %>%
           str_replace("/", " & ") %>%
-          str_wrap(width = 20)
+          str_wrap(width = width)
       ) %>%
       plot_ly(
         x = ~label,
@@ -72,15 +71,10 @@ function(input, output, session) {
         color = ~label,
         colors = pal5,
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
-      ) %>%
-      subplot_title("What is important in reproducibility?")
+      )
 
     plotly::subplot(fig1, fig2, fig3, nrows = 1, shareY = TRUE) %>%
-      plt_layout(
-        showlegend = FALSE,
-        # top margins
-        margin = list(t = 100)
-      ) %>%
+      plt_layout(showlegend = FALSE) %>%
       plt_config(
         filename = paste0(
           "repro_awareness_",
@@ -127,7 +121,7 @@ function(input, output, session) {
       filter(value != 0) %>%
       group_by(value) %>%
       summarise(n = n()) %>%
-      mutate(value = str_wrap(value, width = 20)) %>%
+      mutate(value = str_wrap(value, width = width)) %>%
       plot_ly(
         x = ~value,
         y = ~n,
@@ -140,7 +134,7 @@ function(input, output, session) {
       plt_layout(showlegend = FALSE) %>%
[…]

### 2023-08-02 docs/presentation/ui.R

@@ -45,7 +45,31 @@ tagList(
     tabPanel(
       "Awareness",
       icon = icon("lightbulb"),
-      plotlyOutput("q5", height = plot_full_height),
+      fluidRow(
+        column(
+          4,
+          h4(
+            "How ", strong("familiar"),
+            "are you with the term \"reproducibility\"?"
+          ),
+        ),
+        column(
+          4,
+          h4(
+            "You ", strong("understand"),
+            "\"reproducibility\" in terms of..."
+          ),
+        ),
+        column(
+          4,
+          h4(
+            "What is ", strong("important"),
+            "in the context of \"reproducibility\"?"
+          ),
+        ),
+        class = "plotly-titles",
+      ),
+      plotlyOutput("q5", height = plot_height),
     ),
 
     # Concepts ####
@@ -82,7 +106,7 @@ tagList(
                 "You use ",
                 strong("open source software"),
                 "for ...?"
-                ),
+              ),
               plotlyOutput("q7oss_parts", height = plot_height),
             ),
             column(

### 2023-08-03 docs/presentation/global.R
viz: Q7 notebooks & prereg

@@ -4,6 +4,7 @@ library(plotly)
 library(stringr)
 library(tidyverse)
 library(wordcloud2)
+library(shinycssloaders)
 
 # theme to match HTML
 thematic::thematic_shiny(font = "auto")
@@ -25,6 +26,17 @@ plot_height <- "60vh"
 
 # text width for axis labels
 width <- 20
+
+# spinner
+spin <- function(plt) {
+  shinycssloaders::withSpinner(
+    plt,
+    type = 4,
+    color = "#1D5B79",
+    size = 2,
+    hide.ui = FALSE
+  )
+}
 
 source("data/constants.R")
 

### 2023-08-03 docs/presentation/server.R

@@ -91,7 +91,7 @@ function(input, output, session) {
       drop_na(Q7a_1) %>%
       count(Q7a_1)
 
-    d() %>%
+    plt1 <- d() %>%
       drop_na(Q7a) %>%
       count(Q7a) %>%
       plot_ly(
@@ -110,12 +110,9 @@ function(input, output, session) {
         # marker = list(color = "#d95f02"),
         hovertemplate = "<b>%{x}</b>\n%{y} people"
       ) %>%
-      plt_layout(barmode = "group") %>%
-      plt_config(filename = "repro_oss")
-  })
+      plt_layout(barmode = "group", showlegend = TRUE)
 
-  output$q7oss_parts <- renderPlotly({
-    d() %>%
+    plt2 <- d() %>%
       select(starts_with("Q7a_2")) %>%
       pivot_longer(cols = everything()) %>%
       filter(value != 0) %>%
@@ -130,13 +127,9 @@ function(input, output, session) {
         type = "bar",
         name = "Used for",
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
-      ) %>%
-      plt_layout(showlegend = FALSE) %>%
-      plt_config(filename = "repro_oss_usage")
-  })
+      )
 
-  output$q7oss_env <- renderPlotly({
-    d() %>%
+    plt3 <- d() %>%
       drop_na(Q7a_3) %>%
       count(Q7a_3) %>%
       plot_ly(
@@ -147,9 +140,94 @@ function(input, output, session) {
         # name = "Familiar",
         colors = mako4,
         hovertemplate = "<b>%{x}</b>\n%{y} people<extra></extra>"
-      ) %>%
+      )
+
+    plotly::subplot(plt1, plt2, plt3, nrows = 1, shareY = TRUE) %>%
       plt_layout(showlegend = FALSE) %>%
-      plt_config(filename = "repro_oss_env")
+      plt_config(
+        filename = paste0(
+          "repro_oss_",
+          input$group %>%
+            tolower() %>%
+            gsub("[^a-z0-9]", "_", .)
+        )
+      )
+  })
+
+  # Q7 notebooks ####
+  output$q7nb <- renderPlotly({
+    Q7b_1 <- d() %>%
+      drop_na(Q7b_1) %>%
+      count(Q7b_1)
+
+    d() %>%
+      drop_na(Q7b) %>%
+      count(Q7b) %>%
+      plot_ly(
+        x = ~Q7b,
[…]

### 2023-08-03 docs/presentation/ui.R

@@ -46,6 +46,7 @@ tagList(
       "Awareness",
       icon = icon("lightbulb"),
       fluidRow(
+        class = "plotly-titles",
         column(
           4,
           h4(
@@ -67,9 +68,8 @@ tagList(
             "in the context of \"reproducibility\"?"
           ),
         ),
-        class = "plotly-titles",
       ),
-      plotlyOutput("q5", height = plot_height),
+      plotlyOutput("q5", height = plot_height) %>% spin(),
     ),
 
     # Concepts ####
@@ -81,23 +81,15 @@ tagList(
         tabPanel(
           "Open source",
           fluidRow(
+            class = "plotly-titles",
             column(
               4,
               h5(
-                "How familiar are you with ",
-                strong("open source software", .noWS = "after"), "?",
+                "How ", strong("familiar"),
+                "are you with open source software?",
                 br(),
-                "How often do you use ",
-                strong("open source software", .noWS = "after"), "?"
-              ),
-              plotlyOutput("q7oss", height = plot_height),
-              p(
-                "\"Use\" is recoded for visualization as follows:", br(),
-                "Never -> Not at all", br(),
-                "Rarely -> Very little", br(),
-                "Some of the time -> Somewhat", br(),
-                "Most of the time -> To a great extent", br(),
-                "Always -> To a great extent",
+                "How ", strong("often"),
+                "do you use open source software?",
               ),
             ),
             column(
@@ -107,7 +99,6 @@ tagList(
                 strong("open source software"),
                 "for ...?"
               ),
-              plotlyOutput("q7oss_parts", height = plot_height),
             ),
             column(
               4,
@@ -118,12 +109,33 @@ tagList(
                 the computational processing environment
                 used in your own research?"
               ),
-              plotlyOutput("q7oss_env", height = plot_height),
             ),
+          ),
+          plotlyOutput("q7oss", height = plot_height) %>% spin(),
+          p(
+            "\"Use\" is recoded for visualization as follows:", br(),
+            "Never -> Not at all", br(),
+            "Rarely -> Very little", br(),
+            "Some of the time -> Somewhat", br(),
+            "Most of the time -> To a great extent", br(),
+            "Always -> To a great extent",
           ),
         ),
         tabPanel(
           "Notebooks",
+          fluidRow(
+            column(
+              6,
+              h5(
+                "How ", strong("familiar"),
+                "are you with lab, field, or computational notebooks?",
+                br(),
[…]

### 2023-08-03 docs/presentation/server.R
viz: Q7 bar plots

@@ -106,11 +106,11 @@ function(input, output, session) {
         x = ~Q7a_1,
         y = ~n,
         data = Q7a_1,
-        name = "Use",
+        name = "Use OSS",
         # marker = list(color = "#d95f02"),
         hovertemplate = "<b>%{x}</b>\n%{y} people"
       ) %>%
-      plt_layout(barmode = "group", showlegend = TRUE)
+      plt_layout(barmode = "group")
 
     plt2 <- d() %>%
       select(starts_with("Q7a_2")) %>%
@@ -175,7 +175,7 @@ function(input, output, session) {
         x = ~Q7b_1,
         y = ~n,
         data = Q7b_1,
-        name = "Use",
+        name = "Use notebooks",
         # marker = list(color = "#d95f02"),
         hovertemplate = "<b>%{x}</b>\n%{y} people"
       ) %>%
@@ -191,8 +191,112 @@ function(input, output, session) {
   })
 
   # Q7 archive ####
+  output$q7arch <- renderPlotly({
+    Q7c_1 <- d() %>%
+      drop_na(Q7c_1) %>%
+      count(Q7c_1)
+    
+    Q7c_2 <- d() %>%
+      drop_na(Q7c_2) %>%
+      count(Q7c_2)
+    
+    Q7c_3 <- d() %>%
+      drop_na(Q7c_3) %>%
+      count(Q7c_3)
+    
+    d() %>%
+      drop_na(Q7c) %>%
+      count(Q7c) %>%
+      plot_ly(
+        x = ~Q7c,
+        y = ~n,
+        type = "bar",
+        name = "Familiar",
+        # marker = list(color = "#1b9e77"),
+        hovertemplate = "<b>%{x}</b>\n%{y} people"
+      ) %>%
+      add_bars(
+        x = ~Q7c_1,
+        y = ~n,
+        data = Q7c_1,
+        name = "Archive data",
+        # marker = list(color = "#d95f02"),
+        hovertemplate = "<b>%{x}</b>\n%{y} people"
+      ) %>%
+      add_bars(
+        x = ~Q7c_2,
+        y = ~n,
+        data = Q7c_2,
+        name = "Use DOIs",
+        # marker = list(color = "#d95f02"),
+        hovertemplate = "<b>%{x}</b>\n%{y} people"
+      ) %>%
+      add_bars(
+        x = ~Q7c_3,
+        y = ~n,
+        data = Q7c_3,
+        name = "Use spatial metadata standards",
[…]

### 2023-08-03 docs/presentation/ui.R

@@ -127,6 +127,7 @@ tagList(
             column(
               6,
               h5(
+                class = "plotly-titles",
                 "How ", strong("familiar"),
                 "are you with lab, field, or computational notebooks?",
                 br(),
@@ -139,9 +140,45 @@ tagList(
         ),
         tabPanel(
           "Data archive",
+          column(
+            8,
+            h5(
+              class = "plotly-titles",
+              "How ", strong("familiar"),
+              "are you with sharing or archiving data?",
+              br(),
+              "How ", strong("often"),
+              "do you publicly share or archive data in your own research?",
+              br(),
+              "How ", strong("often"),
+              "do you use digital object identifiers (DOIs) ",
+              "when public sharing or archiving data in your own research?",
+              br(),
+              "How ", strong("often"),
+              "do you use spatial metadata standards ",
+              "when publicly sharing or archiving data in your own research?",
+            ),
+            plotlyOutput("q7arch", height = plot_height) %>% spin(),
+          ),
         ),
         tabPanel(
           "Sharing code",
+          column(
+            8,
+            h5(
+              class = "plotly-titles",
+              "How ", strong("familiar"),
+              "are you with publicly sharing code or scripts?",
+              br(),
+              "How ", strong("often"),
+              "do you publicly share code or scripts in your own research?",
+              br(),
+              "How ", strong("often"),
+              "do you use version control software (e.g., Git) ",
+              "to facilitate sharing code or scripts in your research?",
+            ),
+            plotlyOutput("q7code", height = plot_height) %>% spin(),
+          ),
         ),
         tabPanel(
           "Pre-register",
@@ -149,6 +186,7 @@ tagList(
             column(
               6,
               h5(
+                class = "plotly-titles",
                 "How ", strong("familiar"),
                 "are you with pre-registering research designs or protocols?",
                 br(),

### 2023-08-03 docs/presentation/server.R
viz: aesthetics

@@ -86,7 +86,7 @@ function(input, output, session) {
   })
 
   # Q7 open source ####
-  output$q7oss <- renderPlotly({
+  output$q7a <- renderPlotly({
     Q7a_1 <- d() %>%
       drop_na(Q7a_1) %>%
       count(Q7a_1)
@@ -155,7 +155,7 @@ function(input, output, session) {
   })
 
   # Q7 notebooks ####
-  output$q7nb <- renderPlotly({
+  output$q7b <- renderPlotly({
     Q7b_1 <- d() %>%
       drop_na(Q7b_1) %>%
       count(Q7b_1)
@@ -191,7 +191,7 @@ function(input, output, session) {
   })
 
   # Q7 archive ####
-  output$q7arch <- renderPlotly({
+  output$q7c <- renderPlotly({
     Q7c_1 <- d() %>%
       drop_na(Q7c_1) %>%
       count(Q7c_1)
@@ -251,7 +251,7 @@ function(input, output, session) {
   })
 
   # Q7 codeshare ####
-  output$q7code <- renderPlotly({
+  output$q7d <- renderPlotly({
     Q7d_1 <- d() %>%
       drop_na(Q7d_1) %>%
       count(Q7d_1)
@@ -299,7 +299,7 @@ function(input, output, session) {
   })
 
   # Q7 pre-reg ####
-  output$q7reg <- renderPlotly({
+  output$q7e <- renderPlotly({
     Q7e_1 <- d() %>%
       drop_na(Q7e_1) %>%
       count(Q7e_1)

### 2023-08-03 docs/presentation/ui.R

@@ -30,7 +30,7 @@ tagList(
     # About ####
     tabPanel(
       "About",
-      icon = icon("file-alt"),
+      icon = icon("info-circle"),
       fluidRow(
         column(
           12,
@@ -44,7 +44,7 @@ tagList(
     # Awareness ####
     tabPanel(
       "Awareness",
-      icon = icon("lightbulb"),
+      icon = icon("bullhorn"),
       fluidRow(
         class = "plotly-titles",
         column(
@@ -75,7 +75,7 @@ tagList(
     # Concepts ####
     tabPanel(
       "Concepts",
-      icon = icon("comments"),
+      icon = icon("lightbulb"),
       tabsetPanel(
         id = "q7_panel",
         tabPanel(
@@ -111,7 +111,7 @@ tagList(
               ),
             ),
           ),
-          plotlyOutput("q7oss", height = plot_height) %>% spin(),
+          plotlyOutput("q7a", height = plot_height) %>% spin(),
           p(
             "\"Use\" is recoded for visualization as follows:", br(),
             "Never -> Not at all", br(),
@@ -134,7 +134,7 @@ tagList(
                 "How ", strong("often"),
                 "do you use lab, field, or computational notebooks?",
               ),
-              plotlyOutput("q7nb", height = plot_height) %>% spin(),
+              plotlyOutput("q7b", height = plot_height) %>% spin(),
             ),
           ),
         ),
@@ -158,7 +158,7 @@ tagList(
               "do you use spatial metadata standards ",
               "when publicly sharing or archiving data in your own research?",
             ),
-            plotlyOutput("q7arch", height = plot_height) %>% spin(),
+            plotlyOutput("q7c", height = plot_height) %>% spin(),
           ),
         ),
         tabPanel(
@@ -177,7 +177,7 @@ tagList(
               "do you use version control software (e.g., Git) ",
               "to facilitate sharing code or scripts in your research?",
             ),
-            plotlyOutput("q7code", height = plot_height) %>% spin(),
+            plotlyOutput("q7d", height = plot_height) %>% spin(),
           ),
         ),
         tabPanel(
@@ -193,9 +193,33 @@ tagList(
                 "How ", strong("often"),
                 "do you use pre-registering for research designs or protocols?",
               ),
-              plotlyOutput("q7reg", height = plot_height) %>% spin(),
[…]

### 2023-08-07 docs/presentation/server.R
viz: q13 density plots

@@ -388,6 +388,52 @@ function(input, output, session) {
       )
   })
 
+  # Q13 percentages ####
+
+  output$q13 <- renderPlotly({
+    all_geo <- d()$Q13_1 %>%
+      density(na.rm = TRUE)
+
+    subfield <- d()$Q13_2 %>%
+      density(na.rm = TRUE)
+
+    plot_ly(
+      x = ~ all_geo$x,
+      y = ~ all_geo$y,
+      type = "scatter",
+      mode = "lines",
+      fill = "tozeroy",
+      name = "Geography",
+      hovertemplate = "%{x:.2f}%\n%{y:.2%}"
+    ) %>%
+      add_trace(
+        x = ~ subfield$x,
+        y = ~ subfield$y,
+        type = "scatter",
+        mode = "lines",
+        fill = "tozeroy",
+        name = "Your primary\nsubfield"
+      ) %>%
+      plt_layout(
+        legend = list(font = fira)
+      ) %>%
+      plotly::layout(
+        xaxis = list(range = list(0, 100), ticksuffix = "%"),
+        yaxis = list(tickformat = ".1%"),
+        hovermode = "x"
+      ) %>%
+      plt_config(
+        filename = paste0(
+          "repro_published_",
+          input$group %>%
+            tolower() %>%
+            gsub("[^a-z0-9]", "_", .)
+        )
+      )
+  })
+
+
+
 
   # Word cloud ####
   output$cloud <- renderWordcloud2(clouds[[input$cloud]])

### 2023-08-07 docs/presentation/ui.R

@@ -220,6 +220,20 @@ tagList(
             ),
           ),
         ),
+        tabPanel(
+          "Published results",
+          fluidRow(
+            column(
+              8,
+              h5(
+                class = "plotly-titles",
+                "In your opinion, what percentage of the",
+                "published results are reproducible within...?",
+              ),
+              plotlyOutput("q13", height = plot_height) %>% spin(),
+            ),
+          ),
+        ),
       ),
     ),
 

### 2023-08-08 docs/presentation/server.R
viz: cache plots

@@ -77,7 +77,8 @@ function(input, output, session) {
             gsub("[^a-z0-9]", "_", .)
         )
       )
-  })
+  }) %>%
+    bindCache(input$group)
 
   # Q7 open source ####
   output$q7a <- renderPlotly({
@@ -142,7 +143,8 @@ function(input, output, session) {
             gsub("[^a-z0-9]", "_", .)
         )
       )
-  })
+  }) %>%
+    bindCache(input$group)
 
   # Q7 notebooks ####
   output$q7b <- renderPlotly({
@@ -178,7 +180,8 @@ function(input, output, session) {
             gsub("[^a-z0-9]", "_", .)
         )
       )
-  })
+  }) %>%
+    bindCache(input$group)
 
   # Q7 archive ####
   output$q7c <- renderPlotly({
@@ -238,7 +241,8 @@ function(input, output, session) {
             gsub("[^a-z0-9]", "_", .)
         )
       )
-  })
+  }) %>%
+    bindCache(input$group)
 
   # Q7 codeshare ####
   output$q7d <- renderPlotly({
@@ -286,7 +290,8 @@ function(input, output, session) {
             gsub("[^a-z0-9]", "_", .)
         )
       )
-  })
+  }) %>%
+    bindCache(input$group)
 
   # Q7 pre-reg ####
   output$q7e <- renderPlotly({
@@ -322,7 +327,8 @@ function(input, output, session) {
             gsub("[^a-z0-9]", "_", .)
         )
       )
-  })
+  }) %>%
+    bindCache(input$group)
 
   # Q8 likert ####
   output$q8 <- renderPlotly({
@@ -386,7 +392,8 @@ function(input, output, session) {
             gsub("[^a-z0-9]", "_", .)
         )
       )
-  })
+  }) %>%
+    bindCache(input$group)
 
   # Q13 percentages ####
 
@@ -430,7 +437,8 @@ function(input, output, session) {
             gsub("[^a-z0-9]", "_", .)
         )
       )
-  })
+  }) %>%
+    bindCache(input$group)
 
 
 

### 2023-08-10 docs/presentation/data/constants.R
viz: word cloud changes

@@ -31,7 +31,7 @@ q8_text <- c(
 )
 
 # Questions for the word cloud ####
-cloud_cols <- list("Q6", "Q10", "Q12a", "Q15", "Q17a")
+cloud_cols <- list("Q6", "Q10")
 cloud_questions <- list(
   p(
     icon("circle-question"), strong("Question 6"), br(),

### 2023-08-10 docs/presentation/global.R

@@ -13,7 +13,6 @@ thematic::thematic_shiny(font = "auto")
 pal <- c("#DF4949", "#E27A3F", "#BEBEBE", "#45B29D", "#334D5C")
 
 # plot height as CSS
-plot_full_height <- "80vh"
 plot_height <- "60vh"
 
 # text width for axis labels
@@ -35,5 +34,5 @@ source("data/constants.R")
 # load data ####
 analysis <- readRDS("data/analysis.rds")
 
-clouds <- readRDS("data/clouds.rds")
 clouds_q6 <- readRDS("data/clouds_q6.rds")
+clouds_q10 <- readRDS("data/clouds_q10.rds")

### 2023-08-10 docs/presentation/server.R

@@ -443,7 +443,7 @@ function(input, output, session) {
 
 
 
-  # Word cloud ####
-  output$cloud <- renderWordcloud2(clouds[[input$cloud]])
+  # Q6 & Q10 word clouds ####
   output$cloud_q6 <- renderWordcloud2(clouds_q6[[input$group]])
+  output$cloud_q10 <- renderWordcloud2(clouds_q10[[input$group]])
 }

### 2023-08-10 docs/presentation/ui.R

@@ -45,36 +45,68 @@ tagList(
     tabPanel(
       "Awareness",
       icon = icon("bullhorn"),
-      fluidRow(
-        class = "plotly-titles",
-        column(
-          4,
+      tabsetPanel(
+        id = "awareness-panel",
+        tabPanel(
+          "Question 5",
+          fluidRow(
+            class = "plotly-titles",
+            column(
+              4,
+              h4(
+                "How ", strong("familiar"),
+                "are you with the term \"reproducibility\"?"
+              ),
+            ),
+            column(
+              4,
+              h4(
+                "You ", strong("understand"),
+                "\"reproducibility\" in terms of..."
+              ),
+            ),
+            column(
+              4,
+              h4(
+                "What is the main", strong("motivation"),
+                "of \"reproducibility\"?"
+              ),
+            ),
+          ),
+          plotlyOutput("q5", height = plot_height) %>% spin(),
+        ),
+        tabPanel(
+          "Question 6",
           h4(
-            "How ", strong("familiar"),
-            "are you with the term \"reproducibility\"?"
+            class = "plotly-titles",
+            "What is your ", strong("understanding"),
+            "of the term \"reproducibility\"",
+            "in the context of your own research?",
+          ),
+          wordcloud2Output(
+            "cloud_q6",
+            height = plot_height
           ),
         ),
-        column(
-          4,
+        tabPanel(
+          "Question 10",
           h4(
-            "You ", strong("understand"),
-            "\"reproducibility\" in terms of..."
+            class = "plotly-titles",
+            "Thinking about the reproduction(s) you attempted in the last 2 years,",
+            "What made you decide to ", strong("attempt"),
+            "the reproduction(s)?",
           ),
-        ),
-        column(
-          4,
-          h4(
-            "What is ", strong("important"),
-            "in the context of \"reproducibility\"?"
+          wordcloud2Output(
+            "cloud_q10",
+            height = plot_height
           ),
         ),
       ),
-      plotlyOutput("q5", height = plot_height) %>% spin(),
     ),
 
-    # Concepts ####
+    # Practices ####
     tabPanel(
-      "Concepts",
+      "Practices",
       icon = icon("lightbulb"),
       tabsetPanel(
         id = "q7_panel",
@@ -84,7 +116,7 @@ tagList(
             class = "plotly-titles",
             column(
               4,
-              h5(
+              h4(
                 "How ", strong("familiar"),
                 "are you with open source software?",
                 br(),
@@ -94,7 +126,7 @@ tagList(
[…]

### 2023-08-10 docs/presentation/preprocess.Rmd
viz: cast 5 levels to 4
viz: Q5 changes

@@
 clouds_q6$Everyone <- clouds$Q6
-# saveRDS(clouds_q6, file = "data/clouds_q6.rds")
+saveRDS(clouds_q6, file = "data/clouds_q6.rds")
+```
+
+```{r q10 cloud}
+clouds_q10_q3 <- map(
+  subfields, ~ analysis %>%
+    filter(Q3_recoded == .x) %>%
+    column_to_cloud("Q10", data = .)
+) %>%
+  set_names(subfields)
+
+clouds_q10_q4 <- map(
+  types, ~ analysis %>%
+    filter(Q4 == .x) %>%
+    column_to_cloud("Q10", data = .)
+) %>%
+  set_names(types)
+
+clouds_q10 <- append(clouds_q10_q3, clouds_q10_q4)
+clouds_q10$Everyone <- clouds$Q10
+# saveRDS(clouds_q10, file = "data/clouds_q10.rds")
 ```
@@
 Cast 5 levels to 4
-```{r eval=FALSE, include=FALSE}
+```{r}
 analysis %<>%
@@
 
-Q7 (many parts)
-
-Q13 (percentages)
-
-## Likert charts
-Q8
-
-Q9 (maybe)
-
-Q11
-Q12
-
-Q14
-
-Q17
-
-## Bar plot
-Or something simple
-Include animations
-
-Q16
-
-## Demographics
+Rename Q6 labels
+```{r}
+analysis %<>%
+  mutate(label = case_match(
+    label,
+    "Omit" ~ NA,
+    "Standard" ~ "Assess Prior Work",
+    "Experiment" ~ "Repeatable Experiments",
+    "Data Collection" ~ "Data Collection",
+    "Transparency/Extension" ~ "Transparency/Extension"
+  ))
+```
 

### 2023-08-10 docs/presentation/data/constants.R

@@ -32,29 +32,6 @@ q8_text <- c(
 
 # Questions for the word cloud ####
 cloud_cols <- list("Q6", "Q10")
-cloud_questions <- list(
-  p(
-    icon("circle-question"), strong("Question 6"), br(),
-    "What is your understanding of the term \"reproducibility\" in the context of your own research?", br(),
-    # icon("circle-info"), strong("Note: "), "Only this question is segmentable."
-  ),
-  p(
-    icon("circle-question"), strong("Question 10"), br(),
-    "Thinking about the reproduction(s) you attempted in the last 2 years, what made you decide to attempt the reproduction(s)?"
-  ),
-  p(
-    icon("circle-question"), strong("Question 12a"), br(),
-    "If you were not able to submit all of the findings of your reproduction(s) for publication, why not?"
-  ),
-  p(
-    icon("circle-question"), strong("Question 15"), br(),
-    "Please list any other factors that you believe contribute to a lack of reproducibility in research in your subfield."
-  ),
-  p(
-    icon("circle-question"), strong("Question 17a"), br(),
-    "Please list any benefits or important function of reproducibility in your subfield not mentioned above."
-  )
-)
 
 # Function for subplot ####
 # Modified from original by Dan Powers <danielp@takomaparkmd.gov> under MIT License

### 2023-08-10 docs/presentation/ui.R
viz: add bootstrap breakpoints

@@ -157,7 +157,9 @@ tagList(
           "Notebooks",
           fluidRow(
             column(
-              6,
+              12,
+              # col-sm-12
+              class = "col-lg-10 col-xl-8",
               h4(
                 class = "plotly-titles",
                 "How ", strong("familiar"),
@@ -173,7 +175,9 @@ tagList(
         tabPanel(
           "Data archive",
           column(
-            8,
+            12,
+            # col-sm-12
+            class = "col-lg-10 col-xl-8",
             h4(
               class = "plotly-titles",
               "How ", strong("familiar"),
@@ -196,7 +200,9 @@ tagList(
         tabPanel(
           "Sharing code",
           column(
-            8,
+            12,
+            # col-sm-12
+            class = "col-lg-10 col-xl-8",
             h4(
               class = "plotly-titles",
               "How ", strong("familiar"),
@@ -216,7 +222,9 @@ tagList(
           "Pre-register",
           fluidRow(
             column(
-              6,
+              12,
+              # col-sm-12
+              class = "col-lg-10 col-xl-8",
               h4(
                 class = "plotly-titles",
                 "How ", strong("familiar"),
@@ -242,7 +250,8 @@ tagList(
           "Views",
           fluidRow(
             column(
-              8,
+              class = "col-xxl-8",
+              12,
               h4(
                 class = "plotly-titles",
                 "To what extent do you agree with the following",
@@ -256,7 +265,9 @@ tagList(
           "Published results",
           fluidRow(
             column(
-              8,
+              12,
+              # col-sm-12
+              class = "col-xxl-8",
               h4(
                 class = "plotly-titles",
                 "In your opinion, what percentage of the",

### 2023-08-10 docs/presentation/preprocess.Rmd
viz: q8 pre-calculate

@@
 
+## Q8 Likert
+```{r}
+q8_to_likert <- function(data = analysis) {
+  data %>%
+    # make data for likert
+    pivot_longer(cols = starts_with("Q8")) %>%
+    group_by(name, value) %>%
+    summarise(n = n()) %>%
+    mutate(value = factor(value, levels = agree_levels)) %>%
+    replace_na(list(value = "Don't know")) %>%
+    group_by(name) %>%
+    mutate(perc = n / sum(n)) %>%
+    mutate(
+      yeah = ifelse(any(value == "Agree"), perc[value == "Agree"], 0),
+      idk = ifelse(any(value == "Don't know"), perc[value == "Don't know"] / 2, 0),
+      nah = ifelse(any(value == "Disagree"), perc[value == "Disagree"], 0),
+      start = case_match(
+        value,
+        "Strongly agree" ~ yeah + idk,
+        "Agree" ~ idk,
+        "Don't know" ~ -idk,
+        "Disagree" ~ -idk - perc,
+        "Strongly disagree" ~ -idk - nah - perc,
+      )
+    ) %>%
+    ungroup() %>%
+    dplyr::select(-c(yeah, nah, idk))
+}
+```
+
+```{r Q8}
+q8_q3 <- map(
+  subfields, ~ analysis %>%
+    filter(Q3_recoded == .x) %>%
+    q8_to_likert()
+) %>%
+  set_names(subfields)
+
+q8_q4 <- map(
+  types, ~ analysis %>%
+    filter(Q4 == .x) %>%
+    q8_to_likert()
+) %>%
+  set_names(types)
+
+q8 <- append(q8_q3, q8_q4)
+q8$Everyone <- q8_to_likert()
+saveRDS(q8, file = "data/q8.rds")
+```
+
 ## Save
@@
 analysis %>%
-  saveRDS("data/analysis.rds", compress = FALSE)
+  saveRDS("data/analysis.rds")
 ```

### 2023-08-10 docs/presentation/global.R

@@ -36,3 +36,4 @@ analysis <- readRDS("data/analysis.rds")
 
 clouds_q6 <- readRDS("data/clouds_q6.rds")
 clouds_q10 <- readRDS("data/clouds_q10.rds")
+q8 <- readRDS("data/q8.rds")

### 2023-08-10 docs/presentation/server.R

@@ -332,30 +332,7 @@ function(input, output, session) {
 
   # Q8 likert ####
   output$q8 <- renderPlotly({
-    plt <- d() %>%
-      # make data for likert
-      pivot_longer(cols = starts_with("Q8")) %>%
-      group_by(name, value) %>%
-      summarise(n = n()) %>%
-      mutate(value = factor(value, levels = agree_levels)) %>%
-      replace_na(list(value = "Don't know")) %>%
-      group_by(name) %>%
-      mutate(perc = n / sum(n)) %>%
-      mutate(
-        yeah = ifelse(any(value == "Agree"), perc[value == "Agree"], 0),
-        idk = ifelse(any(value == "Don't know"), perc[value == "Don't know"] / 2, 0),
-        nah = ifelse(any(value == "Disagree"), perc[value == "Disagree"], 0),
-        start = case_match(
-          value,
-          "Strongly agree" ~ yeah + idk,
-          "Agree" ~ idk,
-          "Don't know" ~ -idk,
-          "Disagree" ~ -idk - perc,
-          "Strongly disagree" ~ -idk - nah - perc,
-        )
-      ) %>%
-      ungroup() %>%
-      dplyr::select(-c(yeah, nah, idk)) %>%
+    plt <- q8[[input$group]] %>%
       # ggplot
       ggplot() +
       geom_segment(aes(

### 2023-08-14 docs/presentation/data/constants.R
viz: Q9, Q17, Q14

@@ -30,6 +30,47 @@ q8_text <- c(
   Q8_6 = "Reproducibility is incompatible with the epistemologies within my subfield."
 )
 
+# Q9 questions text ####
+q9_text <- c(
+  Q9_1 = "Thought about the reproducibility of your research",
+  Q9_2 = "Spoke with colleagues about reproducibility",
+  Q9_3 = "Questioned the reproducibility of published research",
+  Q9_4 = "Published original data with your study",
+  Q9_5 = "Published code and/or protocols with your study",
+  Q9_6 = "Considered reproducibility while peer reviewing a grant or publication",
+  Q9_7 = "Attempted to reproduce your own or someone else's research"
+)
+
+# Q14 questions text ####
+q14_text <- c(
+  Q14_1 = "Fraud (e.g., fabricated or falsified results)",
+  Q14_2 = "Pressure to publish for career advancement",
+  Q14_3 = "Insufficient oversight or mentoring",
+  Q14_4 = "Lack of publishing raw data",
+  Q14_5 = "Lack of publishing research protocols or computer code",
+  Q14_6 = "Lack of publishing full results",
+  Q14_7 = "Differences in the software processing environment",
+  Q14_8 = "Use of proprietary data or software",
+  Q14_9 = "Complexity and variability of geographic systems",
+  Q14_10 = "Random effects",
+  Q14_11 = "Insufficient documentation about study data (metadata)",
+  Q14_12 = "Researcher positionality"
+)
+
+# Q17 questions text ####
+q17_text <- c(
+  Q17_1 = "Validating research findings",
+  Q17_2 = "Reducing the risk of errors in the research process",
+  Q17_3 = "Increasing trust in study results",
+  Q17_4 = "Preventing duplication of efforts in future research projects",
+  Q17_5 = "Establishing credibility of research in geography",
+  Q17_6 = "Establishing credibility of research in your primary subfield",
+  Q17_7 = "Communicating research to academics",
+  Q17_8 = "Communicating research to practitioners",
+  Q17_9 = "Training geography students",
+  Q17_10 = "Meta-analyses"
+)
+
 # Questions for the word cloud ####
 cloud_cols <- list("Q6", "Q10")
 

### 2023-08-14 docs/presentation/server.R

@@ -17,16 +17,6 @@ function(input, output, session) {
     bindCache(input$group) %>%
     bindEvent(input$group)
 
-  # table for debugging ####
-  output$table <- d() %>%
-    # Had to use |> because %>% isn't working here, idk why
-    # Sounds like https://github.com/tidyverse/magrittr/issues/159
-    DT::datatable(extensions = "Responsive") |>
-    DT::renderDT()
-
-  # More debugging ####
-  output$ver <- renderPrint(input$group)
-
   # Q5 plots ####
   output$q5 <- renderPlotly({
     fig1 <- d() %>%
@@ -79,6 +69,7 @@ function(input, output, session) {
       )
   }) %>%
     bindCache(input$group)
+
 
   # Q7 open source ####
   output$q7a <- renderPlotly({
@@ -146,6 +137,7 @@ function(input, output, session) {
   }) %>%
     bindCache(input$group)
 
+
   # Q7 notebooks ####
   output$q7b <- renderPlotly({
     Q7b_1 <- d() %>%
@@ -182,6 +174,7 @@ function(input, output, session) {
       )
   }) %>%
     bindCache(input$group)
+
 
   # Q7 archive ####
   output$q7c <- renderPlotly({
@@ -244,6 +237,7 @@ function(input, output, session) {
   }) %>%
     bindCache(input$group)
 
+
   # Q7 codeshare ####
   output$q7d <- renderPlotly({
     Q7d_1 <- d() %>%
@@ -293,6 +287,7 @@ function(input, output, session) {
   }) %>%
     bindCache(input$group)
 
+
   # Q7 pre-reg ####
   output$q7e <- renderPlotly({
     Q7e_1 <- d() %>%
@@ -330,13 +325,15 @@ function(input, output, session) {
   }) %>%
     bindCache(input$group)
 
+
   # Q8 likert ####
   output$q8 <- renderPlotly({
     plt <- q8[[input$group]] %>%
       # ggplot
       ggplot() +
       geom_segment(aes(
-        x = name, y = start,
+        x = fct_rev(name),
+        y = start,
         xend = name, yend = start + perc,
         colour = value,
         text = paste0(
@@ -349,7 +346,9 @@ function(input, output, session) {
       coord_flip() +
       scale_color_manual("Response", values = pal, guide = "legend") +
       labs(title = "", y = "Percent", x = "") +
-      scale_x_discrete(labels = str_wrap(q8_text, width = 40)) +
[…]

### 2023-08-14 docs/presentation/ui.R

@@ -34,9 +34,8 @@ tagList(
       fluidRow(
         column(
           12,
-          h1("Debugging"),
-          verbatimTextOutput("ver"),
-          DT::DTOutput("table"),
+          h1("About"),
+          p("Here is some text"),
         ),
       ),
     ),
@@ -50,7 +49,6 @@ tagList(
         tabPanel(
           "Question 5",
           fluidRow(
-            class = "plotly-titles",
             column(
               4,
               h4(
@@ -78,7 +76,6 @@ tagList(
         tabPanel(
           "Question 6",
           h4(
-            class = "plotly-titles",
             "What is your ", strong("understanding"),
             "of the term \"reproducibility\"",
             "in the context of your own research?",
@@ -91,7 +88,6 @@ tagList(
         tabPanel(
           "Question 10",
           h4(
-            class = "plotly-titles",
             "Thinking about the reproduction(s) you attempted in the last 2 years,",
             "What made you decide to ", strong("attempt"),
             "the reproduction(s)?",
@@ -113,15 +109,16 @@ tagList(
         tabPanel(
           "Open source",
           fluidRow(
-            class = "plotly-titles",
             column(
               4,
               h4(
                 "How ", strong("familiar"),
-                "are you with open source software?",
-                br(),
+                "are you with open source software?"
+              ),
+              h4(
                 "How ", strong("often"),
                 "do you use open source software?",
+                class = "no-mt"
               ),
             ),
             column(
@@ -158,16 +155,20 @@ tagList(
           fluidRow(
             column(
               12,
-              # col-sm-12
-              class = "col-lg-10 col-xl-8",
               h4(
-                class = "plotly-titles",
                 "How ", strong("familiar"),
-                "are you with lab, field, or computational notebooks?",
-                br(),
+                "are you with lab, field, or computational notebooks?"
+              ),
+              h4(
                 "How ", strong("often"),
                 "do you use lab, field, or computational notebooks?",
+                class = "no-mt",
               ),
+            ),
+            column(
+              12,
+              # col-sm-12
+              class = "col-lg-10 col-xl-8",
               plotlyOutput("q7b", height = plot_height) %>% spin(),
             ),
           ),
@@ -176,24 +177,32 @@ tagList(
           "Data archive",
           column(
             12,
-            # col-sm-12
-            class = "col-lg-10 col-xl-8",
             h4(
-              class = "plotly-titles",
               "How ", strong("familiar"),
-              "are you with sharing or archiving data?",
-              br(),
[…]

### 2023-08-14 docs/presentation/global.R
viz: style fixes

@@ -14,6 +14,7 @@ pal <- c("#DF4949", "#E27A3F", "#BEBEBE", "#45B29D", "#334D5C")
 
 # plot height as CSS
 plot_height <- "60vh"
+plot_full_height <- "80vh"
 
 # text width for axis labels
 width <- 20

### 2023-08-14 docs/presentation/server.R

@@ -482,7 +482,7 @@ function(input, output, session) {
       pivot_longer(starts_with("Q14"), values_to = "Response") %>%
       group_by(name) %>%
       mutate(
-        Response = fct_na_value_to_level(Response, "Don't know"),
+        Response = fct_na_value_to_level(Response, "No response"),
       ) %>%
       dplyr::count(Response) %>%
       mutate(perc = n / sum(n)) %>%
@@ -542,7 +542,7 @@ function(input, output, session) {
       pivot_longer(starts_with("Q17_"), values_to = "Response") %>%
       group_by(name) %>%
       mutate(
-        Response = fct_na_value_to_level(Response, "Don't know"),
+        Response = fct_na_value_to_level(Response, "No response"),
       ) %>%
       dplyr::count(Response) %>%
       mutate(perc = n / sum(n)) %>%

### 2023-08-14 docs/presentation/ui.R

@@ -6,7 +6,7 @@ tagList(
     tags$link(rel = "shortcut icon", href = "favicon.png"),
   ),
   navbarPage(
-    title = "RPr in Geo",
+    title = "Reproducibility in Geographic Research",
 
     # customization
     id = "activeTab",
@@ -34,8 +34,85 @@ tagList(
       fluidRow(
         column(
           12,
-          h1("About"),
-          p("Here is some text"),
+          # col-sm-12
+          class = "col-lg-10 col-xl-8 col-xxl-6",
+          style = "margin-left: 3vw;",
+          markdown(
+            "
+            ### Welcome
+            This is an interactive data visualization for
+            *Reproducible Research Practices and Barriers to Reproducible Research in Geography:Insights from a Survey*
+            by Peter Kedron, Joseph Holler, and Sarah Bardin.
+
+            The purpose of the survey was to systematically develop a baseline of information
+            about the state of reproducibility in geography
+            and to identify any important differences between subfields and methodological approaches.
+            
+            This data was collected with an online Qualtrics survey from May 17 to June 10, 2022
+            from a random sample of researchers publishing in geographic academic journals as the corresponding author.
+            
+            The survey inquires researchers about their:
+            
+            1) understanding and awareness of reproducibility;
+            2) awareness and implementation of reproducible research practices;
+            3) opinions and perceptions about the role of reproducibility in geography and their subfield; and
+            4) experience attempting reproductions of prior studies.
+            
+            Within each of these themes, responses can be viewed in aggregate (**Everyone**).
+            
+            Alternatively, subsets of geographers can be selected
+            according to one of four *subfields* they are most closely associated with:
+            
+            - **Human** geography;
+            - Spatial analysis and **methods**;
+            - **Nature/Society**; or
+            - **Physical** geography.
+            
+            Or, one of three *methods* they most frequently use:
+            - **Quantitative**;
+            - **Qualitative**; or
+            - **Mixed Methods**.
+            
+            ### Links
+            Please read our preprint for this study for more details, including discussions of results:
+            
+            Kedron, P., Holler, J., & Bardin, S. (2023, June 3).
+            *Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey*.
+            <https://doi.org/10.31219/osf.io/nyrq9>.
+            
[…]

### 2023-08-14 docs/presentation/preprocess.Rmd
viz: select used cols

@@
 clouds_q6$Everyone <- clouds$Q6
-saveRDS(clouds_q6, file = "data/clouds_q6.rds")
+# saveRDS(clouds_q6, file = "data/clouds_q6.rds")
 ```
@@
 q8$Everyone <- q8_to_likert()
-saveRDS(q8, file = "data/q8.rds")
+# saveRDS(q8, file = "data/q8.rds")
 ```
@@
 analysis %>%
+  select(
+    Q3_recoded, Q4, Q5,
+    dat_rec, pro_rec, res_rec, con_rec, label,
+    starts_with("Q7"),
+    Q13_1, Q13_2,
+    starts_with("Q9"),
+    starts_with("Q14"),
+    starts_with("Q17_")
+  ) %>%
   saveRDS("data/analysis.rds")

### 2023-08-14 docs/presentation/ui.R

@@ -53,10 +53,10 @@ tagList(
             
             The survey inquires researchers about their:
             
-            1) understanding and awareness of reproducibility;
-            2) awareness and implementation of reproducible research practices;
-            3) opinions and perceptions about the role of reproducibility in geography and their subfield; and
-            4) experience attempting reproductions of prior studies.
+            1) understanding and **awareness** of reproducibility;
+            2) awareness and implementation of reproducible research **practices**;
+            3) **opinions** and perceptions about the role of reproducibility in geography and their subfield; and
+            4) **experience** attempting reproductions of prior studies.
             
             Within each of these themes, responses can be viewed in aggregate (**Everyone**).
             

### 2023-08-15 docs/presentation/data/constants.R
viz: refactor bar plots & about page

@@ -125,3 +125,59 @@ plt_config <- function(plt, filename, ...) {
     ...
   )
 }
+
+
+# Function for bar plots
+plt_bar <- function(data, prefix, names, pal, label_width, filename) {
+  plt <- data %>%
+    pivot_longer(starts_with(prefix), values_to = "Response") %>%
+    group_by(name) %>%
+    mutate(
+      Response = fct_na_value_to_level(Response, "No response"),
+    ) %>%
+    dplyr::count(Response) %>%
+    mutate(perc = n / sum(n)) %>%
+    ggplot(aes(
+      x = fct_rev(name),
+      y = n,
+      fill = Response,
+      text = paste0(
+        "<b>", Response, "</b><br>",
+        n, " people<br>",
+        round(perc * 100, 2), " %"
+      )
+    )) +
+    geom_col(
+      position = position_fill(reverse = TRUE),
+      width = 0.8
+    ) +
+    coord_flip() +
+    scale_fill_manual(
+      values = pal
+    ) +
+    scale_x_discrete(
+      expand = c(0, 0),
+      labels = str_wrap(rev(names), width = label_width)
+    ) +
+    scale_y_continuous(labels = scales::percent) +
+    theme(
+      axis.title.x = element_blank(),
+      axis.title.y = element_blank(),
+      axis.line.y = element_blank(),
+      axis.ticks.y = element_blank(),
+      panel.border = element_blank(),
+      panel.background = element_blank(),
+      text = element_text(family = "Fira Sans"),
+      legend.position = "bottom",
+      legend.title = element_blank()
+    )
+  # plotly
+  ggplotly(plt, tooltip = "text") %>%
+    plt_layout(
+      legend = list(font = fira)
+    ) %>%
+    plt_config(
+      filename = filename
+    )
+}
+

### 2023-08-15 docs/presentation/global.R

@@ -9,8 +9,15 @@ library(shinycssloaders)
 # theme to match HTML
 thematic::thematic_shiny(font = "auto")
 
+# About page
+about <- readr::read_file("about-page.md")
+
 # colors for likert
 pal <- c("#DF4949", "#E27A3F", "#BEBEBE", "#45B29D", "#334D5C")
+
+# continuous colors
+pal3 <- c("#EF5645", "#D9D9D9", "#7F7F7F")
+pal5 <- c("#CD2311", "#EF5645", "#D9D9D9", "#F2F2F2", "#7F7F7F")
 
 # plot height as CSS
 plot_height <- "60vh"
@@ -18,6 +25,7 @@ plot_full_height <- "80vh"
 
 # text width for axis labels
 width <- 20
+width_long <- 32
 
 # spinner
 spin <- function(plt) {

### 2023-08-15 docs/presentation/server.R

@@ -395,7 +395,8 @@ function(input, output, session) {
         type = "scatter",
         mode = "lines",
         fill = "tozeroy",
-        name = "Your primary\nsubfield"
+        name = "Your primary\nsubfield",
+        line = list(dash = "dash")
       ) %>%
       plt_layout(
         legend = list(font = fira)
@@ -419,181 +420,49 @@ function(input, output, session) {
 
   # Q9 practices ####
   output$q9 <- renderPlotly({
-    plt <- d() %>%
-      pivot_longer(starts_with("Q9"), values_to = "Response") %>%
-      group_by(name) %>%
-      mutate(
-        Response = fct_na_value_to_level(Response, "Don't know")
-      ) %>%
-      dplyr::count(Response) %>%
-      mutate(perc = n / sum(n)) %>%
-      ggplot(aes(
-        x = fct_rev(name),
-        y = n,
-        fill = Response,
-        text = paste0(
-          "<b>", Response, "</b><br>",
-          n, " people<br>",
-          round(perc * 100, 2), " %"
-        )
-      )) +
-      geom_col(
-        position = position_fill(reverse = TRUE),
-        width = 0.8
-      ) +
-      coord_flip() +
-      scale_fill_manual(
-        values = c("#EF5645", "#D9D9D9", "#7F7F7F")
-      ) +
-      scale_x_discrete(
-        expand = c(0, 0),
-        labels = str_wrap(rev(q9_text), width = 40)
-      ) +
-      scale_y_continuous(labels = scales::percent) +
-      theme(
-        axis.title.x = element_blank(),
-        axis.title.y = element_blank(),
-        axis.line.y = element_blank(),
-        axis.ticks.y = element_blank(),
-        panel.border = element_blank(),
-        panel.background = element_blank(),
-        text = element_text(family = "Fira Sans"),
-        legend.position = "bottom",
-        legend.title = element_blank()
-      )
-    # plotly
-    ggplotly(plt, tooltip = "text") %>%
-      plt_layout(
-        legend = list(font = fira)
-      ) %>%
-      plt_config(
-        filename = paste0(
+    d() %>%
+      plt_bar(
+        "Q9", q9_text, pal3, width_long,
+        paste0(
           "repro_practices_",
           input$group %>%
             tolower() %>%
             gsub("[^a-z0-9]", "_", .)
         )
       )
-  })
+  }) %>%
+    bindCache(input$group)
 
[…]

### 2023-08-15 docs/presentation/ui.R

@@ -37,82 +37,7 @@ tagList(
           # col-sm-12
           class = "col-lg-10 col-xl-8 col-xxl-6",
           style = "margin-left: 3vw;",
-          markdown(
-            "
-            ### Welcome
-            This is an interactive data visualization for
-            *Reproducible Research Practices and Barriers to Reproducible Research in Geography:Insights from a Survey*
-            by Peter Kedron, Joseph Holler, and Sarah Bardin.
-
-            The purpose of the survey was to systematically develop a baseline of information
-            about the state of reproducibility in geography
-            and to identify any important differences between subfields and methodological approaches.
-            
-            This data was collected with an online Qualtrics survey from May 17 to June 10, 2022
-            from a random sample of researchers publishing in geographic academic journals as the corresponding author.
-            
-            The survey inquires researchers about their:
-            
-            1) understanding and **awareness** of reproducibility;
-            2) awareness and implementation of reproducible research **practices**;
-            3) **opinions** and perceptions about the role of reproducibility in geography and their subfield; and
-            4) **experience** attempting reproductions of prior studies.
-            
-            Within each of these themes, responses can be viewed in aggregate (**Everyone**).
-            
-            Alternatively, subsets of geographers can be selected
-            according to one of four *subfields* they are most closely associated with:
-            
-            - **Human** geography;
-            - Spatial analysis and **methods**;
-            - **Nature/Society**; or
-            - **Physical** geography.
-            
-            Or, one of three *methods* they most frequently use:
-            - **Quantitative**;
-            - **Qualitative**; or
-            - **Mixed Methods**.
-            
-            ### Links
-            Please read our preprint for this study for more details, including discussions of results:
-            
-            Kedron, P., Holler, J., & Bardin, S. (2023, June 3).
-            *Reproducible Research Practices and Barriers to Reproducible Research in Geography: Insights from a Survey*.
-            <https://doi.org/10.31219/osf.io/nyrq9>.
-            
-            This data visualization is primarily the work of Yifei Luo
-            with supervision of Joseph Holler, and can be cited as:
-            
-            Holler, J., Luo, Y., Kedron, P., & Bardin, S. (2023, August 9). *Reproducibility Survey Data Visualization*.
-            <https://doi.org/10.17605/osf.io/b47xu>.
-            
-            A sample BibTeX entry is as follows:
-            
-            ```
[…]

### 2023-08-15 docs/presentation/ui.R
viz: rename tabs

@@ -49,7 +49,7 @@ tagList(
       tabsetPanel(
         id = "awareness-panel",
         tabPanel(
-          "Question 5",
+          "Concept",
           fluidRow(
             column(
               4,
@@ -76,7 +76,7 @@ tagList(
           plotlyOutput("q5", height = plot_height) %>% spin(),
         ),
         tabPanel(
-          "Question 6",
+          "Definition",
           h4(
             "What is your ", strong("understanding"),
             "of the term “reproducibility”",
@@ -88,7 +88,7 @@ tagList(
           ),
         ),
         tabPanel(
-          "Question 10",
+          "Motivation",
           h4(
             "Thinking about the reproduction(s)",
             "you attempted in the last 2 years,",

### 2023-08-17 docs/presentation/preprocess.Rmd
viz: merge data

--- 2023-08-10 docs/presentation/preprocess.Rmd
@@
 source("data/constants.R")
+
+gen <- list()
 ```
@@
 
-Q19: demographics
-
-Potentially split into professor - not professor
-
-```{r q19 groups}
-analysis %>%
-  group_by(Q19_recoded) %>%
-  summarise(n = n())
-```
-
 ## Word cloud
 
-Q6
-Q10
-Q12a
-Q15
-Q17a
-
-Potentially per group, but only for Q6
+Potentially per group, but only for Q6 and Q10
 
@@
 
-```{r word clouds}
-clouds <- map(cloud_cols, column_to_cloud) %>%
-  set_names(cloud_cols)
-# saveRDS(clouds, file = "data/clouds.rds")
-```
-
 ```{r q6 cloud}
@@
 
-clouds_q6 <- append(clouds_q6_q3, clouds_q6_q4)
-clouds_q6$Everyone <- clouds$Q6
-saveRDS(clouds_q6, file = "data/clouds_q6.rds")
+gen$q6 <- append(clouds_q6_q3, clouds_q6_q4)
+gen$q6$Everyone <- clouds$Q6
 ```
@@
 
-clouds_q10 <- append(clouds_q10_q3, clouds_q10_q4)
-clouds_q10$Everyone <- clouds$Q10
-# saveRDS(clouds_q10, file = "data/clouds_q10.rds")
+gen$q10 <- append(clouds_q10_q3, clouds_q10_q4)
+gen$q10$Everyone <- clouds$Q10
 ```
@@
 
-q8 <- append(q8_q3, q8_q4)
-q8$Everyone <- q8_to_likert()
-saveRDS(q8, file = "data/q8.rds")
+gen$q8 <- append(q8_q3, q8_q4)
+gen$q8$Everyone <- q8_to_likert()
 ```
@@
 analysis %>%
+  select(
+    Q3_recoded, Q4, Q5,
+    dat_rec, pro_rec, res_rec, con_rec, label,
+    starts_with("Q7"),
+    Q13_1, Q13_2,
+    starts_with("Q9"),
+    starts_with("Q14"),
+    starts_with("Q17_")
+  ) %>%
   saveRDS("data/analysis.rds")
+
+gen %>%
+  saveRDS("data/generated.rds")
 ```

### 2023-08-17 docs/presentation/global.R

@@ -42,7 +42,4 @@ source("data/constants.R")
 
 # load data ####
 analysis <- readRDS("data/analysis.rds")
-
-clouds_q6 <- readRDS("data/clouds_q6.rds")
-clouds_q10 <- readRDS("data/clouds_q10.rds")
-q8 <- readRDS("data/q8.rds")
+gen <- readRDS("data/generated.rds")

### 2023-08-17 docs/presentation/server.R

@@ -328,7 +328,7 @@ function(input, output, session) {
 
   # Q8 likert ####
   output$q8 <- renderPlotly({
-    plt <- q8[[input$group]] %>%
+    plt <- gen$q8[[input$group]] %>%
       # ggplot
       ggplot() +
       geom_segment(aes(
@@ -466,6 +466,6 @@ function(input, output, session) {
 
 
   # Q6 & Q10 word clouds ####
-  output$cloud_q6 <- renderWordcloud2(clouds_q6[[input$group]])
-  output$cloud_q10 <- renderWordcloud2(clouds_q10[[input$group]])
+  output$cloud_q6 <- renderWordcloud2(gen$q6[[input$group]])
+  output$cloud_q10 <- renderWordcloud2(gen$q10[[input$group]])
 }
